### 2018-05-31 chapters/introduction/introduction.tex
import initial files for this repository

\chapter{Introduction}
\label{chap:intro}

\makeatletter
\newenvironment{chapquote}[2][2em]
{\setlength{\@tempdima}{#1} \def\chapquote@author{#2} \parshape 1
  \@tempdima \dimexpr\textwidth-2\@tempdima\relax \itshape}
{\par\normalfont\hfill--\
\chapquote@author\hspace*{\@tempdima}\par\bigskip}
\makeatother

%\begin{chapquote}{Walt Disney}
  %``Of all of our inventions for mass communication, pictures still
  %speak the most universally understood language.''
%\end{chapquote}

%Outline:
\begin{itemize}
  \item sliver bullet and ``summer project'' story
  \item ``summer project'' is still going on
  \item tranditional CV methods and emerge of deep learning (gamer changer)
  \item geometry information are useful for applications, how to learn them
  \item geometry information are useful for image understanding (training), how to use them
  \item overhead image (encoding location) as type of geometry information are useful
  \item growing, densely available in space and time
\end{itemize}

The topic of understanding images has been around for half a century.
A well known [annodose] in computer vision community is set in the
60s. The MIT professor Dr. Marvin Minsky assigned a couple of
undergrads to spend the summer programming a computer to recognize
objects in the scene~\cite{boden2006mind}. Quite like the attempts of
proving the famous ``Four color theorem'', [[story about a prof claim
he can prove it in a class]]. Fortunate for the mathematicans, the
``Four color theorem'' has been proved by using powerful computational
resources, while the computer scientists are still trapped in Dr.
Marvin Minsky's summer program (not fully solved yet).

The ultimate goal of image understanding is to extract high-level
understanding from digital images or videos. The task seems natural
and easy for an adult human, but it is difficult for machines. 1) Silver
bullet does not exist \todo{cite}, no general algorithm, we do things
in a ad-hoc manner.

The emerge of deep neural network brings light to the dream. The
neural network is a biological design, just like our brains. [history
of neural network]. Data and computational power bring us here.

Lots algorithm focus on extract high-level info from the images. More
and more deep learning algorithm start identifying lower-level info
from the image like edge extracting and vanishing point detection.
(geometric info). Identifying geometric information is useful for many
applications.

Geometric information can help training neural network to extract
high-level information.

Specifically, Use of overhead image (or map layout) is useful.
overhead imagery are useful and easy to access, gowing densely
available in space and time.

We use geometric information and DL to solve computer vision problems.

\section{Our Approach}
Our approach conver the following area:

\begin{itemize}[noitemsep]

  \item \textbf{Extract Geometric Info from Image using DL}

  \item \textbf{Overhead Image for Image Understanding}

  \item \textbf{Extract High-Level Feature by Learning When and Where.}

\end{itemize}

\section{Synopsis}

The remainder of this work is organized as follows:

\begin{itemize}[noitemsep]

  \item \textbf{\chapref{dependence} - Are Deep Image Representations
    Geo-Informative?} \newline \newline In this chapter, we
    investigate the usefulness of deep image representations,
    extracted from convolutional neural networks applied to
    traditional vision tasks, for problems in geospatial image
    analysis. In particular, we analyze their discriminative ability
    with regard to location through several problem settings,
    including region identification in ground-level imagery,
    understanding and interpreting overhead images, and cross-view
    image matching.  Our results demonstrate the effectiveness of deep
    image representations extracted from CNNs, on both ground-level
    and overhead imagery, for capturing geographically discriminative
    features relating image appearance to geographic location.  This
    points to a promising direction for future research in building
    deep-learning based models that are directly targeted at problems
    of localization and location-related feature extraction from
    ground-level and overhead imagery.  This work was originally
    reported in~\cite{workman2015geocnn}. \newline

\end{itemize}

### 2018-05-31 dissertation.tex
import initial files for this repository

\documentclass[final]{ukthesis}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{import}
\usepackage{xspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{color}

\usepackage[resetlabels]{multibib}
\newcites{journal,conference,workshop,abstracts}{Refereed
  Journal Publications,Refereed Conference Publications,
  Refereed Workshop Publications,Abstracts}

\usepackage[pdfauthor={Scott Workman},
            pdftitle={Leveraging Overhead Imagery for Localization, Mapping, and Understanding},
            bookmarks=false,
            bookmarksnumbered=true,
            bookmarksopen=true,
            breaklinks=true,
            letterpaper=true,
            linktocpage,
            pagebackref=true]{hyperref}
\usepackage{memhfixc}

\OnehalfSpacing
\setsecnumdepth{subsection}

\DeclareGraphicsExtensions{.pdf,.jpg,.png}
\graphicspath{{images/}}

\newcommand{\inject}[1]{\includefrom{chapters/#1/}{#1}}
\newcommand{\todo}[1]{\textcolor{red}{todo: {\em #1}} }
\newcommand{\chapref}[1]{Chapter~\ref{chap:#1}}
\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\tblref}[1]{Table~\ref{tbl:#1}}
\newcommand{\trans}{\mathsf{T}}
\newcommand{\inv}[1]{\ensuremath{{#1}^{\mathsf{-1}}}}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand{\ditem}[1]{\item {\sc #1}\hspace{.1in}}

\begin{document}
\emergencystretch 3em

\author{Menghua Zhai}
\title{Geometric Information for Image Understanding}

\abstract
{
  \SingleSpacing
    Deep neural networks as one of the machine learning categories have been proposed
    since 1980s and proved successful in recent years. This thesis proposes methods which
    leverage deep neural networks to solve the camera geo-calibration problem, which is
    one of the import computer vision tasks. Furthermore, we also use the geo-calibration
    information (geo-location, orientation, etc.) to boost the training of the deep neural
    networks for image understanding.
    Our work focuses on three primary research areas: 1) estimating vanishing points
    and horizon line using image global context computed with deep neural networks. 2)
    domain adaptation from the ground image semantics to the satellite image semantics,
    and 3) learning transient feature representations for webcam images using the time
    and geo-location information in a semi-supervised manner.
    The primary contribution of this thesis is to explore the relation between the
    camera calibration information and image semantics, and bridge the gap between
    two research domains using deep neural networks, which provides us new ways for
    camera calibration and network training.
}
\keywords{ deep neural networks, computer vision, geo-calibration}

\advisor{Nathan Jacobs}
\dgs{Miroslaw Truszczynski}

\frontmatter
\maketitle

%\begin{acknowledgments}
	%Acknowledge people/things here
%\end{acknowledgments}

%\begin{dedication}
%	Dedicated to things (optional)
%\end{dedication}

\tableofcontents\clearpage
%\listoffigures\clearpage
%\listoftables\clearpage

\mainmatter

\inject{introduction}
%\inject{background}
%\inject{dependence}
%\inject{discussion}

\backmatter

\bibliographystyle{plain}
\bibliography{biblio}

%\inject{vita}

\end{document}

### 2018-06-05 chapters/introduction/introduction.tex
introduce mystyle.sty

@@
 
-Specifically, Use of overhead image (or map layout) is useful.
+\brief{Specifically, Use of overhead image (or map layout) is useful.
 overhead imagery are useful and easy to access, gowing densely
-available in space and time.
+available in space and time.}
+The use of overhead imagery has been proved useful for image
+understanding.
+Several methods have been recently proposed to jointly reason about
+co-located aerial and ground image pairs. Luo
+\etal~\cite{luo2008event} demonstrate that aerial imagery can aid
+in recognizing the visual content of a geo-tagged ground image.
+M{\'a}ttyus \etal~\cite{mattyus2016hd} perform joint inference over
+monocular aerial imagery and stereo ground images for fine-grained
+road segmentation. Wegner \etal~\cite{wegner2016cataloging} build a
+map of street trees. Given the horizon line and the camera intrinsics,
+Ghouaiel and Lef{\`e}vre~\cite{ghouaiel2016coupling} transform
+geo-tagged ground-level panoramas to a top-down view to enable
+comparisons with aerial imagery for the task of change detection.
+Recent work on cross-view image
+geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+ has shown that convolutional neural
+networks are capable of extracting features from aerial imagery
+that can be matched to features extracted from ground imagery.
+Vo \etal~\cite{vo2016localizing} extend this line of work,
+demonstrating improved geolocalization performance by applying an
+auxiliary loss function to regress the ground-level camera orientation
+with respect to the aerial image. To our knowledge, our work is the
+first work to explore predicting the semantic layout of a ground
+image from an aerial image.
 
@@
     of localization and location-related feature extraction from
-    ground-level and overhead imagery.  This work was originally
-    reported in~\cite{workman2015geocnn}. \newline
+    ground-level and overhead imagery. \newline
 

### 2018-06-06 chapters/introduction/introduction.tex
horizon line introduction.

@@
 
-Lots algorithm focus on extract high-level info from the images. More
+\brief{Lots algorithm focus on extract high-level info from the images. More
 and more deep learning algorithm start identifying lower-level info
@@
 (geometric info). Identifying geometric information is useful for many
-applications.
+applications.}
+In computer vision, low-level elements like edges, line segments,
+super-pixels and vanishing points play important roles in many
+applications like image measuration, facade detection, and
+geo-localization.
+Though the CNNs are good at extracting high-level information from
+images, more and more researches start focusing on using CNN to
+extract low-level these elements.
+
+Zhai \etal~\cite{zhai2016horizon} Firstly try to detect horizon
+line and vanishing point using global image context extracted by CNN.
+Workman \etal~\cite{workman2016horizon} take the idea further and
+design an end-to-end network to predict horizon line from images
+in the wild. 
+Hold-Geoffroy \etal~\cite{hold2017perceptual}
+improve~\cite{workman2016horizon}'s results by using deeper networks,
+and introduce a new perceptual measure for horizon line detection.
+Unlike the previous work that mainly focus on horizon line detection,
+Zhang \etal~\cite{zhang2018dominant} propose to detect the dominant
+vanishing point using deep neural networks.
 

### 2018-06-07 chapters/introduction/introduction.tex
add two more references

@@
 
+\brief{
 The topic of understanding images has been around for half a century.
@@
 Marvin Minsky's summer program (not fully solved yet).
+}
 
+\brief{
 The ultimate goal of image understanding is to extract high-level
@@
 in a ad-hoc manner.
+}
 
+\brief{
 The emerge of deep neural network brings light to the dream. The
@@
 of neural network]. Data and computational power bring us here.
+}
 
-\brief{Lots algorithm focus on extract high-level info from the images. More
-and more deep learning algorithm start identifying lower-level info
-from the image like edge extracting and vanishing point detection.
-(geometric info). Identifying geometric information is useful for many
-applications.}
 In computer vision, low-level elements like edges, line segments,
@@
 extract low-level these elements.
-
+%
+Lee \etal~\cite{lee2017semantic} propose to detect semantic line
+segments, which are able to segment the scene semantically, using
+neural network. Maninis \etal~\cite{maninis2016convolutional} and Yang
+\etal~\cite{yang2016object} explore to detect object contours with
+CNNs.
+%
 Zhai \etal~\cite{zhai2016horizon} Firstly try to detect horizon
@@
 
+\brief{
 Geometric information can help training neural network to extract
 high-level information.
+}
 
-\brief{Specifically, Use of overhead image (or map layout) is useful.
-overhead imagery are useful and easy to access, gowing densely
-available in space and time.}
+\todo{re-edit}
 The use of overhead imagery has been proved useful for image
@@
 
+\brief{
 We use geometric information and DL to solve computer vision problems.
+}
 

### 2018-06-07 chapters/introduction/introduction.tex
snapshot

@@
 %
+Aside from edges and contours, another category of low-level
+information that the CNNs can detect is the camera geometry, like
+camera location, vanishing points, and horizon lines.
 Zhai \etal~\cite{zhai2016horizon} Firstly try to detect horizon
@@
 }
+Camera geometry can provide help learn high-level image semantics.
+Hoiem \etal~\cite{hoiem2008putting} demonstrate that taking camera
+perspective (horizon line) into consideration improves the performance
+for object detection.
 

### 2018-06-08 chapters/introduction/introduction.tex
finish approaches

@@
 \section{Our Approach}
-Our approach conver the following area:
+My thesis focuses on the image understanding with camera geometry.
+There are two directions we will address: 1) How can we obtain camera
+geometry from images; 2) How can we use camera geometry to improve the
+current methods for image semantic extracting. For the first direction,
+we explore both the traditional method and deep learning approaches on
+different geometric calibration parameters. For the second direction,
+we will exploit the image geometric location to help extract
+semantically meaningful informations from images.
 
@@
 
-  \item \textbf{Extract Geometric Info from Image using DL}
+  \item \textbf{Complete Camera Geo-Calibration with MCMC Method:} 
+  The complete camera geo-calibration includes the detection of camera
+  location in the world, the pose and the focal length of the camera
+  given the input image. By constructing a objective function that
+  measures the ``matchness'' between the camera calibration and the
+  observation of the image, we are able to optimize the parameters in
+  the calibration space. However, this space multi-dimensional, which
+  makes the naive grid search infeasible. Our insight is to do the
+  optimization using Markov Chain Monte Carlo (MCMC) method. Our
+  algorithm is able to avoid unnecessary sampling in the
+  low-probabilistic region in the parameter space thus reduce the
+  computational time dramatically.
 
-  \item \textbf{Overhead Image for Image Understanding}
+  \item \textbf{Detecting Horizon and VPs using CNN:}
+  Horizon line and vanishing points (VPs) plays important roles in many
+  application such as image mensuration and facade detection. In the
+  previous work, researchers tended to use build bottom-up approaches to
+  solve this problem. Our work is inspired by human's perception of the
+  horizon line and the vanishing point. Our method exploit the image
+  global context to provide a prior distribution of the final solution,
+  thus to reduce the dimensionality of the solution space.
 
-  \item \textbf{Extract High-Level Feature by Learning When and Where.}
+  \item \textbf{Cross-view Domain Adaptation:} 
+  Current machine learning methods address problems that involves mostly
+  the ground imagery. Tons of dataset targeting on ground imagery are
+  annotated while much fewer are done for the overhead imagery.
+  In this work, we try to transfer the semantics from the ground imagery
+  to the overhead imagery by identifying the latent geometry
+  correspondences between these two. Similar to methods that driven by
+  the projection losses \todo{citation}, our network learns 
+  both the geometric projection between the overhead and ground
+  images, and the semantics of the overhead images jointly.
+
+  \item \textbf{Extract High-Level Feature by Learning When and Where:}
+  One of the key to the success of machine learning approaches are the
+  large quantity of annotated data. However, fully annotated imagery
+  only consists of a tiny part of the image resources available online.
+  The idea is to exploit other meta-info that are automatically
+  recorded/captured by devices to train the ML models.  We demonstrate
+  that the camera geometry can be used as weak ground truth for
+  supervision problem. By learning the capture time and the geolocation
+  of the images, our network is able capture the geo-temporal related
+  high-level features.
 

### 2018-06-08 chapters/introduction/introduction.tex
minor changes

@@
 
-  \item \textbf{Complete Camera Geo-Calibration with MCMC Method:} 
-  The complete camera geo-calibration includes the detection of camera
-  location in the world, the pose and the focal length of the camera
-  given the input image. By constructing a objective function that
-  measures the ``matchness'' between the camera calibration and the
-  observation of the image, we are able to optimize the parameters in
-  the calibration space. However, this space multi-dimensional, which
-  makes the naive grid search infeasible. Our insight is to do the
-  optimization using Markov Chain Monte Carlo (MCMC) method. Our
-  algorithm is able to avoid unnecessary sampling in the
-  low-probabilistic region in the parameter space thus reduce the
-  computational time dramatically.
+  \item \textbf{Camera Geometry Detection:} 
+  We investigate different methods to detect camera geometry from the
+  input images. We first explore a sampling approach to find the
+  complete camera calibration parameters that fit the observation of
+  objects (input image) best. In our next work, we use a deep neural
+  network to learn to detect horizon line and vanishing points. These
+  two approaches provides information for the next stage of our
+  research.
 
-  \item \textbf{Detecting Horizon and VPs using CNN:}
-  Horizon line and vanishing points (VPs) plays important roles in many
-  application such as image mensuration and facade detection. In the
-  previous work, researchers tended to use build bottom-up approaches to
-  solve this problem. Our work is inspired by human's perception of the
-  horizon line and the vanishing point. Our method exploit the image
-  global context to provide a prior distribution of the final solution,
-  thus to reduce the dimensionality of the solution space.
-
-  \item \textbf{Cross-view Domain Adaptation:} 
+  \item \textbf{Camera Geometry for Image Understanding:}
+  We explore the potentials of camera geometry for image understanding.
   Current machine learning methods address problems that involves mostly
@@
   annotated while much fewer are done for the overhead imagery.
-  In this work, we try to transfer the semantics from the ground imagery
-  to the overhead imagery by identifying the latent geometry
-  correspondences between these two. Similar to methods that driven by
-  the projection losses \todo{citation}, our network learns 
-  both the geometric projection between the overhead and ground
-  images, and the semantics of the overhead images jointly.
-
-  \item \textbf{Extract High-Level Feature by Learning When and Where:}
-  One of the key to the success of machine learning approaches are the
-  large quantity of annotated data. However, fully annotated imagery
-  only consists of a tiny part of the image resources available online.
-  The idea is to exploit other meta-info that are automatically
-  recorded/captured by devices to train the ML models.  We demonstrate
-  that the camera geometry can be used as weak ground truth for
-  supervision problem. By learning the capture time and the geolocation
-  of the images, our network is able capture the geo-temporal related
-  high-level features.
 
@@
 
+  \item \textbf{\chapref{mcmc} - 
+  Complete Camera Geo-Calibration with MCMC Method:} \newline \newline
+  The complete camera geo-calibration includes the detection of camera
+  location in the world, the pose and the focal length of the camera
+  given the input image. By constructing a objective function that
+  measures the ``matchness'' between the camera calibration and the
+  observation of the image, we are able to optimize the parameters in
+  the calibration space. However, this space multi-dimensional, which
+  makes the naive grid search infeasible. Our insight is to do the
+  optimization using Markov Chain Monte Carlo (MCMC) method. Our
+  algorithm is able to avoid unnecessary sampling in the
+  low-probabilistic region in the parameter space thus reduce the
+  computational time dramatically. \newline
+
+  \item \textbf{\chapref{fasthorizon} -
+  Detecting Horizon and VPs using CNN:} \newline \newline
+  Horizon line and vanishing points (VPs) plays important roles in many
+  application such as image mensuration and facade detection. In the
+  previous work, researchers tended to use build bottom-up approaches to
+  solve this problem. Our work is inspired by human's perception of the
+  horizon line and the vanishing point. Our method exploit the image
+  global context to provide a prior distribution of the final solution,
+  thus to reduce the dimensionality of the solution space. \newline
+
+  \item \textbf{\chapref{crosstransf} -
+  Cross-view Domain Adaptation:} \newline \newline
+  Current machine learning methods address problems that involves mostly
+  the ground imagery. Tons of dataset targeting on ground imagery are
+  annotated while much fewer are done for the overhead imagery.
+  In this work, we try to transfer the semantics from the ground imagery
+  to the overhead imagery by identifying the latent geometry
+  correspondences between these two. Similar to methods that driven by
+  the projection losses \todo{citation}, our network learns 
+  both the geometric projection between the overhead and ground
+  images, and the semantics of the overhead images jointly. \newline
+
+  \item \textbf{\chapref{whenwhere} -
+  Extract High-Level Feature by Learning When and Where:} \newline \newline
+  One of the key to the success of machine learning approaches are the
+  large quantity of annotated data. However, fully annotated imagery
+  only consists of a tiny part of the image resources available online.
+  The idea is to exploit other meta-info that are automatically
+  recorded/captured by devices to train the ML models.  We demonstrate
+  that the camera geometry can be used as weak ground truth for
+  supervision problem. By learning the capture time and the geolocation
+  of the images, our network is able capture the geo-temporal related
+  high-level features. \newline
+
 \end{itemize}

### 2018-06-08 dissertation.tex
introduce mystyle.sty
minor changes

@@
 \usepackage{lipsum}
-\usepackage{color}
+\usepackage{memhfixc}
+\usepackage{miscstyle}
 
-\usepackage[resetlabels]{multibib}
-\newcites{journal,conference,workshop,abstracts}{Refereed
-  Journal Publications,Refereed Conference Publications,
-  Refereed Workshop Publications,Abstracts}
+\newcommand{\disstitle}{Geometric Information for Image Understanding}
 
-\usepackage[pdfauthor={Scott Workman},
-            pdftitle={Leveraging Overhead Imagery for Localization, Mapping, and Understanding},
+\usepackage[pdfauthor={Menghua Zhai},
+            pdftitle={\disstitle},
             bookmarks=false,
@@
             pagebackref=true]{hyperref}
-\usepackage{memhfixc}
-
-\OnehalfSpacing
-\setsecnumdepth{subsection}
-
-\DeclareGraphicsExtensions{.pdf,.jpg,.png}
-\graphicspath{{images/}}
-
-\newcommand{\inject}[1]{\includefrom{chapters/#1/}{#1}}
-\newcommand{\todo}[1]{\textcolor{red}{todo: {\em #1}} }
-\newcommand{\chapref}[1]{Chapter~\ref{chap:#1}}
-\newcommand{\secref}[1]{Section~\ref{sec:#1}}
-\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
-\newcommand{\tblref}[1]{Table~\ref{tbl:#1}}
-\newcommand{\trans}{\mathsf{T}}
-\newcommand{\inv}[1]{\ensuremath{{#1}^{\mathsf{-1}}}}
-\newcommand{\Tr}{\operatorname{Tr}}
-\newcommand*{\eg}{e.g.\@\xspace}
-\newcommand*{\ie}{i.e.\@\xspace}
-\newcommand{\ditem}[1]{\item {\sc #1}\hspace{.1in}}
 
@@
 \author{Menghua Zhai}
-\title{Geometric Information for Image Understanding}
+\title{\disstitle}
 

### 2018-06-11 chapters/introduction/introduction.tex
add mcmc chapters

@@
 
-  \item \textbf{\chapref{dependence} - Are Deep Image Representations
-    Geo-Informative?} \newline \newline In this chapter, we
-    investigate the usefulness of deep image representations,
-    extracted from convolutional neural networks applied to
-    traditional vision tasks, for problems in geospatial image
-    analysis. In particular, we analyze their discriminative ability
-    with regard to location through several problem settings,
-    including region identification in ground-level imagery,
-    understanding and interpreting overhead images, and cross-view
-    image matching.  Our results demonstrate the effectiveness of deep
-    image representations extracted from CNNs, on both ground-level
-    and overhead imagery, for capturing geographically discriminative
-    features relating image appearance to geographic location.  This
-    points to a promising direction for future research in building
-    deep-learning based models that are directly targeted at problems
-    of localization and location-related feature extraction from
-    ground-level and overhead imagery. \newline
-
   \item \textbf{\chapref{mcmc} - 

### 2018-06-11 chapters/mcmc/paper.tex
add mcmc chapters

\section{Introduction}

Automatic image localization continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. Conceptually the task is straightforward; given an
image, identify the location it was captured in the world directly
from image data. Solving this problem is of great value for a wide
variety of fields, with potential applications ranging from the
forensic sciences~\cite{stylianou13jane} to crowd-sourced
environmental monitoring~\cite{zhang2012mining}.

\begin{figure}

  \centering

  \begin{subfigure}{.84\linewidth}
    \includegraphics[width=\linewidth]{mcmc/image_frame}
    %\caption{Labeled query image}
  \end{subfigure}
  \begin{subfigure}{.41\linewidth}
    \includegraphics[width=\linewidth]{mcmc/mcmc_direction}
    %\caption{GIS reference data and best sampled cameras (red arrows)}
  \end{subfigure}
  \begin{subfigure}{.41\linewidth}
    \includegraphics[width=\linewidth]{mcmc/mcmc_score}
    %\caption{Probability distribution over camera location}
  \end{subfigure}

  \caption{We match objects in an image (top) to GIS reference data
  (left) to estimate a probability distribution over locations
(right).  The map (left) also shows the true camera location (green
dot) and the top scoring sampled cameras (red arrows).}

%  \caption{Our approach leverages a geographic reference database (b)
%  to estimate the geo-location (c) of a query image (a). (b) Top scoring
%samples (red arrows) are close to the actual location (green dot).}

  \label{fig:cartoon}

\end{figure}

However, recognizing the geo-location and geo-orientation of an
arbitrary outdoor image is an extremely challenging task.  Many
methods have been proposed; the most common approach is to build a
large database of images with known location and localize a query
image using either local~\cite{li2010location,schindler2008detecting}
or global~\cite{hays2008im2gps,doersch2012what} image features.  This
approach is not applicable when no nearby ground-level imagery exists
in the reference database, such as when the image was not captured
near a popular tourist destination.  Even
when reference imagery is available, the appearance of the objects may
not be visually distinctive, for example a train track or a body of
water.

Instead of matching visually against a reference image set, we exploit
the large quantities of publicly available geospatial data to build a
geographic database containing geometric information for objects of
interest in the world, such as roads, churches, bodies of water, water
towers and golf courses.  Given a query image, we identify visible
objects of interest in the image and apply the Metropolis-Hastings
MCMC algorithm to randomly sample possible cameras.  We assign a score
to each hypothetical camera and use these samples to approximate the
probability distribution over the camera parameters and extract
candidate locations. \figref{cartoon} gives an brief view of our
approach.

Our key contributions are: 1) a flexible approach to the camera
geo-calibration problem that supports priors over camera parameters
and constraints that relate image annotations, camera geometry, and a
geographic database and 2) an extensive comparison of this approach to
uniform and grid-based sampling on real-world data.

\subsection{Related Work}

\begin{figure}[t]

  \centering

  \frame{\includegraphics[width=.3\linewidth]{mcmc/diffmodel_map}}
  \hfill
  \includegraphics[width=.3\linewidth]{mcmc/distance_scoring}
  \hfill
  \includegraphics[width=.3\linewidth]{mcmc/fullmodel_scoring}

  \caption{(left) A map showing two houses (black) and a hypothetical
    ground-truth camera frustum. (middle) The PDF (red is high
    probability) over location for a 2D camera model, in which
    constraints are based on distances between the camera and GIS
  objects. (right) The 4D model we propose enables richer constraints,
  which leads to a more accurate PDF.}

  \label{fig:diffmodel}
\end{figure}

Self-localization has been heavily studied in the robotics community. The task is to
estimate the probability density function (PDF) over the robot's state
space (location and orientation). Early methods attempted to estimate
this density by discretizing the state
space~\cite{burgard1996estimating}. These grid-based approaches
suffered from large computational overhead and memory requirements. To
overcome these limitations, probabilistic particle-based methods like
MCMC were
investigated~\cite{dellaert1999using,fox1999monte,gutmann1998experimental,oh2004map}.
The idea is to approximate the probability density using randomly drawn
samples, while maintaining performance even for high dimensional state
spaces.

Extracting location-dependent features from image data has drawn a
great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch et al. extract location-dependent features that
capture the relative appearance differences of large cities.  Lin et
al.~\cite{lin2013cross} localize a ground-level image by learning the
relationship between pairs of ground and aerial images of the same
location. Other techniques focus on urban environments and infer
location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.

Our work attempts to combine these two research directions. We use
publicly available geospatial data to build a large geographic
database containing geometric information for objects in the world,
identify objects of interest in the query image, and use a
probabilistic approach to estimate camera geo-calibration. To our
knowledge, our approach is the first to apply a probabilistic
particle-based MCMC algorithm for single image camera geo-calibration
using a large geographic database.

\section{Approach}

Given a query image, captured at an unknown location in a known region
of interest (ROI) and annotated with the location of geographic objects
(e.g., buildings and roads), our goal is to estimate the intrinsic and
extrinsic camera parameters.  We base these estimates on a geographic
information system (GIS) database that contains the location and
extent of objects in the ROI.  Assuming a simplified
pinhole camera model
with square pixels and zero skew, the full camera geo-calibration
problem is seven-dimensional: three position parameters, three
orientation parameters, and the field of view. For this work, we
assume that most photos are taken about five feet above the ground
with little tilt or roll and reduce our model to four dimensions:
$\Theta = (Latitude, Longitude, Azimuth, FOV)^\mathsf{T}$. 
%
Adapting to higher or lower dimensional camera models is
straightforward and may be useful depending on the available image
annotations and GIS data.  We find our proposed 4D state space to be
good trade-off between the lack of descriptive power of lower-order
camera models and higher-order camera models that require more
computational time and memory resources. See \figref{diffmodel} for an
% scott review
example that compares our proposed model to a 2D model using only
location.

Since one-to-one matching between image objects and GIS objects is
likely not possible, we instead seek to estimate, $f(\Theta;
\mathbf{C})$, the probability distribution function (PDF) over the
camera parameters, $\Theta$, given a set of constraints, $\mathbf{C}$.
In the following section, we propose a function (an unnormalized
density) that encodes constraints on the geo-calibration.  This score
function, $S(\Theta; \mathbf{C})$, encodes both prior knowledge about
the camera and the geometric relationship between image annotations
and the geographic database.
%
In \secref{mcmc} we show how to estimate $f(\Theta;\mathbf{C})$ by
sampling from this scoring function using an MCMC-based strategy.

\subsection{Scoring Function}
\label{sec:scoring-function}

Proportional to the probability distribution of the camera parameters,
$f(\Theta; \mathbf{C})$, the scoring function, $S(\Theta;
\mathbf{C})$, is defined as a linear combination of multiple constraint
functions:
%
\begin{equation}
  S(\Theta; \mathbf{C}) = \sum_{}{w_i g(c_i, \Theta)} \propto
  f(\Theta; \mathbf{C}),
\end{equation}
%
where $w_i$ is a weight and $g(c_i, \Theta)$ is a constraint function
which is larger if the calibration, $\Theta$, is more consistent with
the image information, $c_i$. While the exact set of constraints
depends on the image and database contents, we define a variety of
% scott review
functions in our implementation, including geometric configuration of
multiple weak correspondences, constraints on geographic location, and
priors over the
%
field of view and camera orientation. We focus on the first
constraint, the latter are simple Gaussian and uniform distributions.

\begin{figure}
\begin{minipage}[b]{1\linewidth}
  \centering
  \centerline{\includegraphics[width=.8\linewidth]{mcmc/scoring_demo}}
\end{minipage}
\caption{Since the exact correspondence between an image pixel and a point
  on a GIS object is unknown, we compute the distance to the closest
  point of the object to compare with the estimated distance.}
\label{fig:scoring-demo}
\end{figure}

% scott review
Given the extent of an object in the image, and an
%
estimated range of distances, $(d_{min},d_{max})$, from the camera to
the object, we propose a constraint function that measures the
geometric consistency between the object in the image and the GIS
database. Given a hypothetical camera, $\Theta$, we compute the
distance, $d$, from the camera, through the object pixel, to the
closest point of the object (see \figref{scoring-demo}), then the
consistency function, $g(c_i, \Theta)$, takes form of a Gaussian
distribution function, with mean $\mu = d - (d_{min} + d_{max})/2$,
and standard deviation $\sigma = d_{max} - d_{min} + o$, where $o$ is
a constant offset ($o=10 m$ for all our experiments) to avoid dividing
by zero. If no object of the correct type intersects the pixel ray,
let $g(c_i, \Theta) = 0$.

\subsection{Monte Carlo Markov Chain}
\label{sec:mcmc}

The MCMC method is an efficient approach for sampling from high
dimensional spaces. Its principal advantage over naive sampling
strategies is that it visits high probability areas more frequently
than the areas of low probability.  We use the Metropolis-Hastings
(MH) algorithm~\cite{chib1995understanding}, a popular member of the
MCMC family.  The algorithm generates a set of possible cameras as
follows: randomly sample a camera and compute its score; randomly
sample (propose) a new nearby camera and compute its score; if the
score of the new camera is higher, replace the old camera with the new
camera, otherwise replace the old probabilistically; repeat this
process many times, recording samples along the way. After a
sufficiently large number of iterations, this process generates a set
of possible cameras that are independent samples from the PDF,
$f(\Theta;\mathbf{C})$, subject to some technical conditions. See
\algref{MH-algorithm} for details of the MH algorithm. We run multiple
chains to mitigate issues with poor initial samples and local maxima.

\begin{algorithm}[t]
  \caption{Metropolis-Hastings Algorithm (MCMC)}
  \begin{algorithmic}[1]
    \REQUIRE $\mathbf{C}$ (constraint set), and $maxIter$
    \STATE Initialize camera parameters, $\Theta_0$
    \STATE $i \gets 0,~~ \mathbb{S} \gets \emptyset,~~s_0 \gets S(\Theta_0;
    \mathbf{C})$
    \WHILE{ $i < maxIter$ }
       \STATE sample new camera parameters: $\Theta_{i+1}$ \label{alg:stp:sampling}
       \STATE scoring: $s_{i+1} \gets S(\Theta_{i+1}; \mathbf{C})$
       \STATE $\mathbb{S} \gets \mathbb{S} \cup \langle\Theta_{i+1}, s_{i+1}\rangle$
       \IF{ $s_{i+1} < s_i$ }
       \STATE $s_{i+1} \gets s_i,~~\Theta_{i+1} \gets \Theta_i$ with 
       %\newline
       prob. $\frac{s_i - s_{i+1}}{s_i}$
       \ENDIF
       \STATE $i \gets i + 1$
    \ENDWHILE
    \STATE \Return $\mathbb{S}$
  \end{algorithmic}
  \label{alg:MH-algorithm}
\end{algorithm}

Aside from the scoring function, $S(\Theta;\mathbf{C})$, the proposal
distribution, $p(\Theta)$, which specifies how new cameras are
sampled from a current camera
(\algref{MH-algorithm}.\textcolor{red}{$4$}), is the most important
choice when using an MCMC approach. We use the joint distribution of
independent Gaussian random variables:
%
\begin{displaymath}
  p(\Theta_{i+1} \given \Theta_i) = \prod_{j =
  1}^{N_{dim}}{\frac{1}{\sigma_j}\phi\left(\frac{\Theta_{i+1,j} -
\Theta_{i,j}}{\sigma_j}\right)},
\end{displaymath}
where $\sigma_j$ denotes the sampling step size on the $j$-th
dimension, and $\phi(x)$ denotes the PDF of the standard normal
distribution. As with all MH-based algorithms, the sampling
performance is sensitive to the choice of step size. If the step size
is too large, the algorithm converges slowly; if too small, the Markov
chain may be trapped in a local maximum.

\section{Evaluation}
\label{sec:evaluation}

We compare our approach with two baseline methods, grid sampling and
uniform random sampling, on real-world GIS data. The quantitative and
qualitative results demonstrate the value of the proposed MH-based
approach.

\begin{figure}
  \centering
  \includegraphics[width=.49\linewidth]{mcmc/total_distance}
  \includegraphics[width=.49\linewidth]{mcmc/total_area}
  \caption{Performance comparison among methods. (left) Total
    distance. (right) Total area. For the grid method the finest
    sampling over spatial dimensions is 30m.}
  \label{fig:comparison}
\end{figure}

\subsection{Methods}

\textbf{Dataset:} 
We build a reference geographic database from
OpenStreetMap\footnote{\url{http://www.openstreetmap.org}} data, which
contains the location and extent of many types of objects around the
world. We only include roads, water, churches, residential buildings,
and commercial buildings. For each query, we focus on a different
$5km\times5 km$ ROI, in Kentucky, USA, each containing approximately
$900$ objects.

\noindent
\textbf{Metrics:}
We propose two evaluation metrics that simulate the process of
manually verifying the camera location. For both, we generate a
candidate list by sorting samples by their scores, then scan from the
top until the ground-truth location is found.
Given a set of samples from the state space and
their corresponding scores, we greedily select the top-$N$ candidates
in terms of score, subject to the constraint that each of them is at
least 200 meters away from the others spatially. Then, if the $k$-th
candidate is the first candidate that is $d$ ($d < 100$) meters away
from the ground truth, we define its {\em total distance} to the ground
truth as follows: $T_d = 200(k-1) + d$.
Intuitively, this metric enforces the diversity of candidate
locations. The first term penalizes the ranking
of the ground-truth candidate. The distance, $d$, distinguishes the
accuracy of predictions in the case that two ground-truth candidate
locations have the same ranking. By definition, a lower total distance
to find the ground-truth candidate is better.
The definition of the {\em total area}, $T_a$, is similar: we center a
$l \times l$ patch around each candidate and compute the union of the
areas from the top candidate patch to the patch that covers the
ground-truth location. We set $l$ to be $50m$ initially, if no patch
covers the ground truth, we double the size of $l$ and redo the
computation until the ground-truth location is covered.

\noindent
\textbf{Implementation Details:}
We use the following fixed set of parameters, which we selected
empirically, for all experiments. The ranges from which azimuth and
FOV are sampled are $[0, 2\pi]$ and $[\pi/3, 2\pi/3]$
respectively. For the grid method, 50 angles are evenly sampled for
azimuth, and 6 for the field of view. Thus at each geographic
location, a total of $300$ scoring samples are generated. For MCMC, 200
chains are independently processed in parallel. The step size is 100m
for location, $\pi/20$ for azimuth, and $\pi/30$ for FOV.

\subsection{Evaluation on Synthetic Data}
\label{sec:quantitative}
We manually constructed twenty-five synthetic queries using our
geographic database. We hand-picked a location for each camera, such
that there exists nearby objects in the database and adjusted the
camera azimuth and field of view such that objects were visible in the
view frustum. We then projected the objects onto the image frame to
obtain labeled pixels, and for each provided a min/max distance from
the camera to them (consistent with the actual distance). To simulate
the estimation error in real life, we set the distance range to be
$1/20$ the length of the actual distance.

For each query, we confined the search area to a $5km\times5km$ 
neighborhood that includes the ground-truth location. We computed the
accuracy in terms of the total distance, $T_d$, and the
total area, $T_a$, and the computation time in terms of
the number of samples. The results of this experiment are shown in
\figref{comparison}. MCMC outperforms the other two baseline methods
in both accuracy and speed. On average, our method only requires
$1/10$ of computational time to converge to the same order of accuracy
than the grid method.

\subsection{Evaluation on Real Data}
\label{sec:qualitative}

We evaluate our method using two real query images obtained from
Google Street View. We hand-picked two locations, downloaded the
corresponding equirectangular panoramas and extracted a perspective
image from each. For each query, we labeled objects and estimated the
min/max distance from the camera to the object in the world.
\figref{real-data} shows the qualitative result of this experiment.
Our method generates high scoring samples that are close to the ground
truth. We also found that simple prior constraints can dramatically
affect localization accuracy. By restricting the range of the azimuth
and FOV to be within $5^\circ$ of the ground truth, the distance from
the top sample to the ground-truth location decreased from $12.5m$ to
$0.6m$ and from $1.73m$ to $0.9m$, respectively, for two test
cases.

%azimuth estimated from the sun position~\cite{lalonde2010sun}

\begin{figure}

  \centering

  \begin{subfigure}{1\linewidth} 
    \centering
    \includegraphics[width=.422\linewidth]{mcmc/streetview1}
    \includegraphics[width=.422\linewidth]{mcmc/streetview2}
    \caption{Query images}
  \end{subfigure}
  \begin{subfigure}{1\linewidth} 
    \centering
    \includegraphics[width=.422\linewidth]{mcmc/streetview1_pdf}
    \includegraphics[width=.422\linewidth]{mcmc/streetview2_pdf}
    \caption{PDF of location}
  \end{subfigure}
  \begin{subfigure}{1\linewidth} 
    \centering
    \fbox{\includegraphics[width=.4\linewidth]{mcmc/streetview1_orient}}
    \fbox{\includegraphics[width=.4\linewidth]{mcmc/streetview2_orient}}
    \caption{Local geographic database and top-15 samples}
  \end{subfigure}

  \caption{Qualitative results for two query images (top). The
  resulting PDFs (middle) and map visualization of the top-15 samples
(bottom) show that the proposed scoring function realistically
captures the  uncertainty.}

 \label{fig:real-data}
\end{figure}

\section{Conclusions}

We proposed an MCMC-based approach framework for single image camera
geo-calibration which leverages a large geographic database. Our
results demonstrate the superiority of our method versus several
baseline methods, without requiring nearby ground-level imagery as is
typical for most vision techniques. For future work, we will explore
methods for integrating approaches which use image-based matching.

### 2018-06-12 chapters/introduction/introduction.tex
camera geometry

@@
   \item sliver bullet and ``summer project'' story
-  \item ``summer project'' is still going on
-  \item tranditional CV methods and emerge of deep learning (gamer changer)
-  \item geometry information are useful for applications, how to learn them
-  \item geometry information are useful for image understanding (training), how to use them
-  \item overhead image (encoding location) as type of geometry information are useful
-  \item growing, densely available in space and time
+  \item Geometry is important.
+  \item traditional method for geometry detection
+  \item deep learning (gamer changer)
+  \item geometry detection with deep learning
+  \item geometry for deep learning training
+  \item overhead images
 \end{itemize}
@@
 
-\brief{
-The ultimate goal of image understanding is to extract high-level
-understanding from digital images or videos. The task seems natural
-and easy for an adult human, but it is difficult for machines. 1) Silver
-bullet does not exist \todo{cite}, no general algorithm, we do things
-in a ad-hoc manner.
-}
+It is not a trivial task for machines to understand images in general.
+To achieve this goal, researchers adopt a divide-and-conquer strategy,
+that is divide image understanding into various sub-problems like
+object recognition, semantic segmentation, and pose estimation \etc.
+During the past decades, a lot of methods are developed to solve there
+sub-problem, many of them adopted a bottom-up (\todo{citations})
+workflow, where basic level cues play important roles
+(\todo{examples}). Among there basic cues, camera geometry are
+particularly useful for some computer vision tasks like facade
+detection, indoor layout estimation~\cite{ren2016coarse}.
+
+In the camera pin-hole model, camera geometry denotes the camera
+both intrinsic and extrinsic parameters. The intrinsic parameters
+encode the information of the camera itself such as focal length,
+principal point \etc; the extrinsic parameters are referred to as the
+external states of the camera, such as the camera poses and
+offset/location under some coordinate system. In this work, our study
+of the camera geometry mainly includes the extrinsic like camera pose
+and the geo-orientation/geo-localization of the camera.
 
@@
   \item \textbf{Camera Geometry for Image Understanding:}
+  \todo{more writing}
   We explore the potentials of camera geometry for image understanding.

### 2018-06-13 chapters/introduction/introduction.tex
many writings.

@@
 
-\brief{
-The emerge of deep neural network brings light to the dream. The
-neural network is a biological design, just like our brains. [history
-of neural network]. Data and computational power bring us here.
-}
+During past dacades, many research has been done to detect the camera
+geometry from input images. \todo{citation and examples}. Most of the
+previous work optimize for a limited set of camera calibration
+parameters only. However, our research found that there exists an
+effective way of optimizing multiple camera calibration parameters at
+simultaneously (refer to \chapref{mcmc}). Our method use the Monte
+Carlo Markov Chain (MCMC) method to sample the possible solutions that
+minimize the objective function, which measure the ``matchness''
+between the observation (input image) and the camera calibration.
 
+Among the most influential approaches for camera geometry estimation,
+most methods are based on traditional statistics diagram. Not until a
+fewer years ago, machine learning based methods gradually caught
+people's attention in this area, thanks for the popularity of deep
+neural network. Neural networks were first proposed in 80th
+(\todo{citation}), The back-forward method develop by Hinton
+\todo{citation} makes the effective training possible. However neural
+networks are generally thought by researchers merely toy that can only
+solve a very limited set of tasks. It is the develop of computational
+resources and the big collection of annotated data that make the
+neural networks deeper and eventually bring it to the stage of
+industrial applications.
+
+In the area of vanishing point detection, we are among the first
+researches that use deep neural networks to solve the problem. The
+deep neural networks prove to be a good tool to extract high-level
+information that offer great help to conquer the problems in camera
+geometry estimation. \todo{many citations}.
+%
+\newline \newline
+%
 In computer vision, low-level elements like edges, line segments,

### 2018-06-13 chapters/introduction/introduction.tex
further improvement

@@
   \item sliver bullet and ``summer project'' story
-  \item Geometry is important.
-  \item traditional method for geometry detection
-  \item deep learning (gamer changer)
-  \item geometry detection with deep learning
+  \item \st{Geometry is important.}
+  \item \st{traditional method for geometry detection}
+  \item \st{deep learning (gamer changer)}
+  \item \st{geometry detection with deep learning}
   \item geometry for deep learning training
@@
 
-In the area of vanishing point detection, we are among the first
-researches that use deep neural networks to solve the problem. The
-deep neural networks prove to be a good tool to extract high-level
-information that offer great help to conquer the problems in camera
-geometry estimation. \todo{many citations}.
-%
-\newline \newline
-%
 In computer vision, low-level elements like edges, line segments,
@@
 camera location, vanishing points, and horizon lines.
-Zhai \etal~\cite{zhai2016horizon} Firstly try to detect horizon
-line and vanishing point using global image context extracted by CNN.
-Workman \etal~\cite{workman2016horizon} take the idea further and
-design an end-to-end network to predict horizon line from images
-in the wild. 
-Hold-Geoffroy \etal~\cite{hold2017perceptual}
-improve~\cite{workman2016horizon}'s results by using deeper networks,
-and introduce a new perceptual measure for horizon line detection.
-Unlike the previous work that mainly focus on horizon line detection,
-Zhang \etal~\cite{zhang2018dominant} propose to detect the dominant
-vanishing point using deep neural networks.
+%
+In the area of vanishing point detection, we are among the first
+researches that use deep neural networks to solve the problem. The
+deep neural networks prove to be a good tool to extract high-level
+information that offer great help to conquer the problems in camera
+geometry estimation. \todo{many citations}.
+%
 

### 2018-06-13 chapters/introduction/junk.tex
further improvement

Hold-Geoffroy \etal~\cite{hold2017perceptual}
improve~\cite{workman2016horizon}'s results by using deeper networks,
and introduce a new perceptual measure for horizon line detection.
Unlike the previous work that mainly focus on horizon line detection,
Zhang \etal~\cite{zhang2018dominant} propose to detect the dominant
vanishing point using deep neural networks.

### 2018-06-14 chapters/introduction/introduction.tex
more texts.

@@
 
-%Outline:
-\begin{itemize}
-  \item sliver bullet and ``summer project'' story
-  \item \st{Geometry is important.}
-  \item \st{traditional method for geometry detection}
-  \item \st{deep learning (gamer changer)}
-  \item \st{geometry detection with deep learning}
-  \item geometry for deep learning training
-  \item overhead images
-\end{itemize}
+%%Outline:
+%\begin{itemize}
+  %\item sliver bullet and ``summer project'' story
+  %\item \st{Geometry is important.}
+  %\item \st{traditional method for geometry detection}
+  %\item \st{deep learning (gamer changer)}
+  %\item \st{geometry detection with deep learning}
+  %\item \st{geometry for deep learning training}
+  %\item \st{overhead images}
+%\end{itemize}
 
@@
 geometry estimation. \todo{many citations}.
-%
 
-\brief{
-Geometric information can help training neural network to extract
-high-level information.
-}
-Camera geometry can provide help learn high-level image semantics.
+In our work, we have shown that deep neural networks are powerful
+tools for camera geometry estimation. In fact, the camera
+geometry can also assist learning high-level image semantics.
 Hoiem \etal~\cite{hoiem2008putting} demonstrate that taking camera
 perspective (horizon line) into consideration improves the performance
-for object detection.
+for object detection. Godard \etal~\cite{godard2017unsupervised}
+learn to predict the scene depth from a single image using left-right
+consistency, which is also an application of camera geometry.
+\todo{more citations about the projective loss}.
 
-\todo{re-edit}
-The use of overhead imagery has been proved useful for image
-understanding.
-Several methods have been recently proposed to jointly reason about
-co-located aerial and ground image pairs. Luo
-\etal~\cite{luo2008event} demonstrate that aerial imagery can aid
-in recognizing the visual content of a geo-tagged ground image.
-M{\'a}ttyus \etal~\cite{mattyus2016hd} perform joint inference over
-monocular aerial imagery and stereo ground images for fine-grained
-road segmentation. Wegner \etal~\cite{wegner2016cataloging} build a
-map of street trees. Given the horizon line and the camera intrinsics,
-Ghouaiel and Lef{\`e}vre~\cite{ghouaiel2016coupling} transform
-geo-tagged ground-level panoramas to a top-down view to enable
-comparisons with aerial imagery for the task of change detection.
-Recent work on cross-view image
-geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
- has shown that convolutional neural
-networks are capable of extracting features from aerial imagery
-that can be matched to features extracted from ground imagery.
-Vo \etal~\cite{vo2016localizing} extend this line of work,
-demonstrating improved geolocalization performance by applying an
-auxiliary loss function to regress the ground-level camera orientation
-with respect to the aerial image. To our knowledge, our work is the
-first work to explore predicting the semantic layout of a ground
-image from an aerial image.
+Another example of camera geometry boosting the learning project is to
+exploit the overhead imagery. Using the geometric locations of the
+ground-view images we can download the corresponding overhead images
+at the same locations through public online resources like bingmap
+\todo{cite}.
+%
+\todo{copy from scott} More recently, efforts have been made to
+automate overhead image analysis. As early as
+1970~\cite{idelsohn1970learning} methods were introduced for
+classifying terrain types from a single overhead image, with the goal
+of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
+et al.~\cite{bajcsy1976computer} described a system for recognizing
+roads, intersections, and other road-like objects in overhead imagery.
+However, as overhead imaging differs drastically from ground-level
+imaging, the majority of techniques that have been developed have
+occurred independently and in task-specific ways~\cite{Rozen}.
+\brief{overhead image grows fast}.
 
-\brief{
-We use geometric information and DL to solve computer vision problems.
-}
+\todo{expand this paragraph}
+Camera geometry can also be used as weak annotations during training
+of the networks for image understanding.
 

### 2018-06-14 chapters/introduction/junk.tex
more texts.

@@
 vanishing point using deep neural networks.
+
+\brief{
+Geometric information can help training neural network to extract
+high-level information.
+}
+
+\todo{re-edit}
+The use of overhead imagery has been proved useful for image
+understanding.
+Several methods have been recently proposed to jointly reason about
+co-located aerial and ground image pairs. Luo
+\etal~\cite{luo2008event} demonstrate that aerial imagery can aid
+in recognizing the visual content of a geo-tagged ground image.
+M{\'a}ttyus \etal~\cite{mattyus2016hd} perform joint inference over
+monocular aerial imagery and stereo ground images for fine-grained
+road segmentation. Wegner \etal~\cite{wegner2016cataloging} build a
+map of street trees. Given the horizon line and the camera intrinsics,
+Ghouaiel and Lef{\`e}vre~\cite{ghouaiel2016coupling} transform
+geo-tagged ground-level panoramas to a top-down view to enable
+comparisons with aerial imagery for the task of change detection.
+Recent work on cross-view image
+geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+ has shown that convolutional neural
+networks are capable of extracting features from aerial imagery
+that can be matched to features extracted from ground imagery.
+Vo \etal~\cite{vo2016localizing} extend this line of work,
+demonstrating improved geolocalization performance by applying an
+auxiliary loss function to regress the ground-level camera orientation
+with respect to the aerial image. To our knowledge, our work is the
+first work to explore predicting the semantic layout of a ground
+image from an aerial image.

### 2018-06-15 dissertation.tex
add mcmc chapters
camera geometry
further improvement
change abstract

@@
 \usepackage{memhfixc}
+\usepackage{algorithm2e, algorithmic}
+\usepackage{soul}
 \usepackage{miscstyle}
 
-\newcommand{\disstitle}{Geometric Information for Image Understanding}
+\newcommand{\disstitle}{Camera Geometry Detection and Use for Image
+Understanding}
 
@@
   \SingleSpacing
-    Deep neural networks as one of the machine learning categories have been proposed
-    since 1980s and proved successful in recent years. This thesis proposes methods which
-    leverage deep neural networks to solve the camera geo-calibration problem, which is
-    one of the import computer vision tasks. Furthermore, we also use the geo-calibration
-    information (geo-location, orientation, etc.) to boost the training of the deep neural
-    networks for image understanding.
-    Our work focuses on three primary research areas: 1) estimating vanishing points
-    and horizon line using image global context computed with deep neural networks. 2)
-    domain adaptation from the ground image semantics to the satellite image semantics,
-    and 3) learning transient feature representations for webcam images using the time
-    and geo-location information in a semi-supervised manner.
-    The primary contribution of this thesis is to explore the relation between the
-    camera calibration information and image semantics, and bridge the gap between
-    two research domains using deep neural networks, which provides us new ways for
-    camera calibration and network training.
+  Camera geometry is one of the fundamental elements in computer vision.
+  It plays an essential role in many applications like depth estimation
+  and image mensuration. 
+  %
+  In recent years, the rise of deep neural networks (DNNs) had changed
+  the game in many computer vision areas, their ability of abstracting
+  high-level semantic knowledges makes a lot of hard challenges
+  solvable. 
+  %
+  This thesis mainly explores the possibility of combining camera
+  geometry and DNNs. That is 1) Detecting camera geometry using DNNs,
+  and 2) Training DNNs with camera geometric information.  Our work
+  includes two research targets: The first part of this thesis focuses
+  on camera geometry detection with DNNs, and the rest of it
+  demonstrates how camera geometry can boost the learning of DNNs.
+  %
+  The primary contribution of this thesis is to explore the relation
+  between camera geometry and image semantics, and bridge the gap
+  between these two research domains, which provides us new ways for
+  both camera calibration and deep neural network training.
 }
-\keywords{ deep neural networks, computer vision, geo-calibration}
+\keywords{ camera geometry, deep neural networks, computer vision}
 
@@
 \inject{introduction}
+%\inject{mcmc}
 %\inject{background}
-%\inject{dependence}
 %\inject{discussion}

### 2018-06-15 junk.tex
change abstract

Deep neural networks as one of the machine learning categories have been proposed
since 1980s and proved successful in recent years. This thesis proposes methods which
leverage deep neural networks to solve the camera geo-calibration problem, which is
one of the import computer vision tasks. Furthermore, we also use the geo-calibration
information (geo-location, orientation, etc.) to boost the training of the deep neural
networks for image understanding.
Our work focuses on three primary research areas: 1) estimating vanishing points
and horizon line using image global context computed with deep neural networks. 2)
domain adaptation from the ground image semantics to the satellite image semantics,
and 3) learning transient feature representations for webcam images using the time
and geo-location information in a semi-supervised manner.
The primary contribution of this thesis is to explore the relation between the
camera calibration information and image semantics, and bridge the gap between
two research domains using deep neural networks, which provides us new ways for
camera calibration and network training.

### 2018-06-16 chapters/introduction/introduction.tex
first paragraph

@@
 
-\brief{
-The topic of understanding images has been around for half a century.
-A well known [annodose] in computer vision community is set in the
-60s. The MIT professor Dr. Marvin Minsky assigned a couple of
-undergrads to spend the summer programming a computer to recognize
-objects in the scene~\cite{boden2006mind}. Quite like the attempts of
-proving the famous ``Four color theorem'', [[story about a prof claim
-he can prove it in a class]]. Fortunate for the mathematicans, the
-``Four color theorem'' has been proved by using powerful computational
-resources, while the computer scientists are still trapped in Dr.
-Marvin Minsky's summer program (not fully solved yet).
-}
+The study of understanding images has been around for half a century.
+A well known anecdote in computer vision community happened in 1960s,
+when the MIT professor Dr. Marvin Minsky assigned a summer programming
+project to his undergraduates, to recognize objects in a
+scene~\cite{boden2006mind}. 
+%
+Similar to the story of the famous ``Four Color Conjecture'', where
+one of the world's renowned mathematicians Dr. Hermann Minkowski
+claimed in his class that he was able to solve it before the class
+ends.  
+However, Not until one hundred years later since it was first
+proposed, the ``Four Color Conjecture'' has been stamped as theorem by
+the continuous efforts of several generations of talented
+mathematicians.  While on the other side, Dr. Marvin Minsky's summer
+program still remains open.
 

### 2018-06-16 chapters/introduction/introduction.tex
updates

@@
 To achieve this goal, researchers adopt a divide-and-conquer strategy,
-that is divide image understanding into various sub-problems like
+that is dividing image understanding into various sub-problems like
 object recognition, semantic segmentation, and pose estimation \etc.
-During the past decades, a lot of methods are developed to solve there
-sub-problem, many of them adopted a bottom-up (\todo{citations})
+During past decades, a lot of methods are developed to solve
+these
+sub-problems. Many of them adopted a bottom-up (\todo{citations})
 workflow, where basic level cues play important roles
-(\todo{examples}). Among there basic cues, camera geometry are
+(\todo{examples}). Among these basic cues, camera geometry is
 particularly useful for some computer vision tasks like facade
@@
 
-During past dacades, many research has been done to detect the camera
+Many research has been done to detect the camera
 geometry from input images. \todo{citation and examples}. Most of the
@@
 Carlo Markov Chain (MCMC) method to sample the possible solutions that
-minimize the objective function, which measure the ``matchness''
+minimize the objective function, which measures the ``matchness''
 between the observation (input image) and the camera calibration.
@@
 neural network. Neural networks were first proposed in 80th
-(\todo{citation}), The back-forward method develop by Hinton
-\todo{citation} makes the effective training possible. However neural
+(\todo{citation}), The back-forward method developed by Hinton
+\todo{citation} makes the effective training possible. However, neural
 networks are generally thought by researchers merely toy that can only
 solve a very limited set of tasks. It is the develop of computational
-resources and the big collection of annotated data that make the
-neural networks deeper and eventually bring it to the stage of
+resources and the big collection of annotated data that enables the
+neural networks to grow deeper and eventually brings it to the stage of
 industrial applications.
@@
 
-In our work, we have shown that deep neural networks are powerful
-tools for camera geometry estimation. In fact, the camera
-geometry can also assist learning high-level image semantics.
+In our previous work, we have shown that deep neural networks are
+powerful tools for camera geometry estimation as well. In fact, the
+camera geometry can also assist learning high-level image semantics.
 Hoiem \etal~\cite{hoiem2008putting} demonstrate that taking camera
 perspective (horizon line) into consideration improves the performance
-for object detection. Godard \etal~\cite{godard2017unsupervised}
-learn to predict the scene depth from a single image using left-right
+for object detection. Godard \etal~\cite{godard2017unsupervised} learn
+to predict the scene depth from a single image using left-right
 consistency, which is also an application of camera geometry.
@@
 at the same locations through public online resources like bingmap
-\todo{cite}.
-%
-\todo{copy from scott} More recently, efforts have been made to
+\todo{cite}. We refer to these image pairs as ``cross-view image
+pairs''.
+
+\todo{copy from scott} Efforts have been made to
 automate overhead image analysis. As early as
@@
 occurred independently and in task-specific ways~\cite{Rozen}.
-\brief{overhead image grows fast}.
+%\brief{overhead image grows fast}.
 
-\todo{expand this paragraph}
+Our work demonstrates that we are able to transfer the learned semantic
+knowledge from the ground image domain to the overhead image domain,
+given the camera geometric information of these two kind of images. In
+our algorithm, the camera geometry helps to collect the ``cross-view
+image pairs'' and aligned the orientation directions of images in a
+pair.
+
 Camera geometry can also be used as weak annotations during training
-of the networks for image understanding.
+of the networks for image understanding.  One of the key to the
+success of machine learning approaches are the large quantity of
+annotated data. However, fully annotated imagery consists of only a
+tiny part of the image resources available online. The idea is to
+exploit other meta-info that are automatically recorded/captured by
+devices to train the ML models. One of the meta-info potentially
+helpful for learning is camera geometry.  We demonstrate that the
+camera geometry can be used as weak ground truth for supervision
+problem. By learning the capture time and the geolocation of the
+images simultaneously, our network is able capture the geo-temporal
+related high-level features.
 
@@
 My thesis focuses on the image understanding with camera geometry.
-There are two directions we will address: 1) How can we obtain camera
+There are two directions we will address: 1) How to estimate camera
 geometry from images; 2) How can we use camera geometry to improve the

### 2018-06-17 chapters/introduction/introduction.tex
introduction draft

@@
 effective way of optimizing multiple camera calibration parameters at
-simultaneously (refer to \chapref{mcmc}). Our method use the Monte
+simultaneously (refer to \chapref{mcmc}). Our algorithm uses the Monte
 Carlo Markov Chain (MCMC) method to sample the possible solutions that
@@
   \item \textbf{Camera Geometry for Image Understanding:}
-  \todo{more writing}
   We explore the potentials of camera geometry for image understanding.
   Current machine learning methods address problems that involves mostly
-  the ground imagery. Tons of dataset targeting on ground imagery are
-  annotated while much fewer are done for the overhead imagery.
+  the ground imagery. 
+  Studies around overhead images are relatively less thus much fewer
+  annotated data exists in public. With the camera geometric
+  information, we can pair the ground imagery with overhead imagery to
+  form cross-view pairs. Our algorithm explore how to transfer the
+  learned knowledge from a network designed for ground level image
+  semantic segmentation to a new network designed for overhead imagery
+  semantic segmentation use these cross-view pairs.
+  Furthermore, we also explore the potential of the camera geometry as
+  weak annotation in supervised learning. Our algorithm shows that by
+  directly learning to predict camera locations, the network networks
+  are able to extract high-level geo-temporal features.
 
@@
   correspondences between these two. Similar to methods that driven by
-  the projection losses \todo{citation}, our network learns 
+  the projective losses \todo{citation}, our network learns 
   both the geometric projection between the overhead and ground

### 2018-06-18 chapters/fasthorizon/paper.tex
add fasthorizon

\section{Introduction}

Automatic vanishing point (VP) and horizon line detection are two of
the most fundamental problems in geometric computer
vision~\cite{barnard1983interpreting,magee1984determining}. Knowledge
of these quantities is the foundation for many higher level
tasks, including image mensuration~\cite{criminisi2000single},
facade detection~\cite{liulocal2014},
geolocalization~\cite{baatz2010handling,workman2014rainbow}, and
camera
calibration~\cite{autorecovery2000,grammatikopoulos2007automatic,
jacobs13cloudcalibration,videocampass2002}. Recent work in this area
\cite{global2013,wildenauer2012,kitware2013} has explored novel
problem formulations that significantly increase robustness to noise.

\begin{figure}
  \centering
  \includegraphics[width=.48\linewidth]{fasthorizon/cover_hybrid_sampling}
  \includegraphics[width=.48\linewidth]{fasthorizon/cover_segment_clusters}

  \caption{An example result of our method. (left) Horizon line
    candidates, colored by their scores (red means high score), and
    the true horizon line (green dash). (right) The horizon line
    (magenta) estimated by our algorithm is very close to the true
    horizon line (green dash).  Line segments are color coded based on
    the most consistent detected vanishing point.}

  \label{fig:cover}
\end{figure}

A vanishing point results from the intersection of projections of a
set of parallel lines in the world. In man-made environments, such
sets of lines are often caused by the edges of buildings, roads, and
signs. VPs can typically be classified as either vertical, there is
one such VP, and horizontal, there are often many such VPs.  Given a
set of horizontal VPs, there are numerous methods to estimate the
horizon line.  Therefore, previous approaches to this problem focus on
first detecting the vanishing points, which is a challenging problem
in many images due to line segment intersections that are not true
VPs.

Our approach is to propose candidate horizon lines, score them, and
keep the best (\figref{cover}). We use a deep convolutional neural network to extract
global image context and guide the generation of a set of horizon line
candidates. For each candidate, we identify vanishing points by
solving a discrete-continuous optimization problem.  The final score for
each candidate line is based on the consistency of the lines in the
image with the selected vanishing points.

This seemingly simple shift in approach leads to the need for novel
algorithms and has excellent performance. We evaluated the proposed
approach on two standard benchmark datasets, the Eurasian Cities
Dataset~\cite{geoparser2010} and the York Urban
Dataset~\cite{edgebased2008}. To our knowledge, our approach has the
current best performance on both datasets. To evaluate our algorithm
further, we also compare with the previous state-of-the-art method
(Lezama et al.~\cite{alignment2014}) on a recently introduced
dataset~\cite{authors2016deephorizon}; the results shows that our
method is more accurate and much faster.

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{fasthorizon/algorithm_pipeline}
  \caption{Algorithm overview: 1) use global image context to estimate
    a prior over horizon lines (\secref{deeplearning}); 2) extract
    line segments; 3) identify the zenith VP
    (\secref{zenithdetection}); 4) sample horizon line candidates
    consistent with the zenith VP (\secref{horizondetection}); 5) find
    VPs on horizon line candidates (\secref{horizondetection}); and 6)
    select the best horizon line based on the VPs it contains
    (\secref{horizonscoring}).}
  \label{fig:pipeline}
\end{figure*}

%This is especially
%impressive considering that we use a single set of parameters for both
%dataset, whereas other methods typically use different sets of
%parameters, fine-tuned for the individual dataset.

The main contributions of this work
are: 1) a novel method for horizon line/vanishing point detection,
which uses global image context to guide precise geometric analysis;
2) a strategy for quickly extracting this context, in the form of
constraints on possible horizon lines, using a deep convolutional
neural network; 3) a discrete-continuous method for scoring horizon
line candidates; and 4) an evaluation of the proposed approach on
three benchmark datasets, which highlights that our method is both
fast and accurate.

\subsection{Related Work}
\label{sec:relatedwork}

Vanishing points and the horizon line provide a strong
characterization of geometric scene structure and as such have been
intensely studied for
decades~\cite{barnard1983interpreting,magee1984determining}.  For
example, Hoiem et al.~\cite{hoiem2008putting} show how the horizon
line improves the accuracy of object detection.  A wide variety of
methods have been introduced to estimate these quantities.  We provide
a brief overview of the main approaches, refer
to~\cite{szeliski2010computer} for a comprehensive review.

Two distinct categories of methods exist, distinguished by the
features they use. The first group of methods~\cite{geoparser2010,
manhattanbayesian1999, edgebased2008,atlanta2004} operate directly
on lower-level features, such as edge pixels or image gradients.  The
second group of methods~\cite{nopriori2003, edgebased2008,
alignment2014, houghvp1994, selfsketch2012, wildenauer2012,
kitware2013} build on top of the closely related problem of line
segment detection.  Our work is most closely related to the latter
category, so we focus our discussion towards them.

The dominant approach to vanishing point detection from line segments
is to cluster the line segments that pass through the same location.
Various methods of clustering have been explored, including
RANSAC~\cite{ransac1981}, J-linkage~\cite{tardif2009}, and the Hough
transform~\cite{hough1959}. Once the line segments have been
clustered, vanishing points can be estimated using one of many
refinement procedures~\cite{alignment2014,atlanta2004,tardif2009,
wildenauer2012,kitware2013}.

These procedures typically minimize a
nonlinear objective function. An important distinction between such
methods is the choice of point and line representation and error
metric. Collins and Weiss~\cite{unitsphere1990} formulate vanishing
point detection as a statistical estimation problem on the Gaussian
Sphere, which is similar to the geometry we use.  More recent work
has explored the use of dual space~\cite{alignment2014,dualspace2013}
representations. Among the clustering-based approaches, Xu et
al.~\cite{kitware2013} improve this pipeline by introducing a new
point-line consistency function that models errors in the line segment
extraction step.

Alternatives to clustering-based approaches have been explored.
For example, vanishing point detection from line segments has been
modeled as an Uncapacitated Facility Location (UFL)
problem~\cite{global2013, selfsketch2012}. To avoid error accumulation
issues encountered by a step-by-step pipeline method, Barinova et
al.~\cite{geoparser2010} solve the problem in a unified framework,
where edges, lines, and vanishing points fit into a single graphical
model.

Our approach is motivated by the fact that properties of the scene,
including objects, can provide additional cues for vanishing point and
horizon line placement than line segments alone. Unlike existing
methods that use J-linkage~\cite{tardif2009, kitware2013} or similar
techniques to find an initial set of VPs by clustering detected lines
followed by a refinement step, our approach first proposes candidate
horizon lines using global image context.

%The advantage of our approach is that it reduces the search space to
%one dimension by finding VPs on the candidate horizon lines. We carry
%out this searching process by solving a maximum independent set
%problem.  Vanishing points on the horizon line candidate are refined
%using a EM-like method that maximizes the total consistency for each
%VP while constraining it to lie on the horizon line candidate.

%
% Geometry
%
\subsection{Approach Overview}

Our approach is motivated by two observations: 1) traditional purely
geometric approaches to vanishing point detection often fail in
seemingly nonsensical ways and 2) identifying the true vanishing
points for many scenes is challenging and computationally expensive
due to the large number of outlier line segments. Driven by these
observations, we propose a two part strategy.  First, we use global
image context to estimate priors over the horizon line and the zenith
vanishing point (\secref{deeplearning}). Using these priors, we
introduce a novel VP detection method (\secref{precise}) that samples
horizon lines from the prior and performs a fast one-dimensional
search for high-quality vanishing points in each. Both steps are
essential for accurate results: the prior helps ensure a good
initialization such that our horizon-first detection method may obtain
very precise estimates that are necessary for many scene understanding
tasks. See \figref{pipeline} for an overview of our algorithm.

\section{Problem Formulation}
\label{sec:problem}

% Each horizontal
% vanishing point corresponds to a world-space direction that is
% perpendicular to the zenith direction. Note that our definition of
% horizon line is based on the gravity vector and not the orientation of
% the local ground plane or the intersection of the sky and the ground.
% The zenith VP refers to the unique vanishing point that results from
% the parallel edges of upright man-made objects.
%
% Horizontal VPs lie on the horizon line and usually correspond to
% sets of line segments that are parallel to the ground plain.

The goal of this work is to detect the horizon line, the zenith
vanishing point, and any horizontal vanishing points from a single
image. The remainder of this section defines the notation and basic
geometric facts that we will use throughout.  For clarity we use
unbolded letters for points in world coordinates or the image plane
and bolded letters for points or lines in homogeneous coordinates.  We
primarily follow the notation convention of Vedaldi and
Zisserman~\cite{selfsketch2012}.

Given a point $(u,v)$ in the image plane, its homogeneous coordinate
with respect to the calibrated image plane is denoted by:
\begin{displaymath}
  \mathbf{p} = [\rho(u-c_u), \rho(v-c_v), 1]^\mathsf{T} / \Sigma \; ,
\end{displaymath}
where $\rho$ is a scale constant, $(c_u, c_v)$ is the camera principal
point in the image frame, which we assume to be the center of the
image, and $\Sigma$ is the constant that makes $\mathbf{p}$ a unit
vector.
%We use $\rho = 2/\operatorname{max}(W,H)$, where $(W, H)$ is
%the size of the image.

In homogeneous coordinates, both lines and points are represented as
three-dimensional vectors (\figref{homoIntersection}). Computing the
line, $\mathbf{l}$, that passes through two points, $(\mathbf{p}_1, \mathbf{p}_2)$, and
the point, $\mathbf{p}$, at the intersection of two lines, $(\mathbf{l}_1,
\mathbf{l}_2)$, are defined as follows:
\begin{align}
  \mathbf{l} = \frac{\mathbf{p}_1 \times \mathbf{p}_2}{\|\mathbf{p}_1 \times
    \mathbf{p}_2\|} 
  &&
  \mathbf{p} = \frac{\mathbf{l}_1 \times \mathbf{l}_2}{\|\mathbf{l}_1 \times \mathbf{l}_2\|} \; .
\end{align}
We denote the smallest angle between two vectors $\mathbf{x}$ and
$\mathbf{y}$ with $\Theta_{\mathbf{x},\mathbf{y}}
= |cos^{-1}(\mathbf{x}^\mathsf{T} \mathbf{y})|$.
We use this to define the consistency between a line, $\mathbf{l}$, and a
point,
$\mathbf{p}$, as: $f_c(\mathbf{p}, \mathbf{l}) =
\operatorname*{max}(\theta_{con} - \Theta_{\mathbf{p},\mathbf{l}}, 0)$.
The maximum value of consistency between a vanishing point and a line
segment is $\theta_{con}$. This will occur if it is possible to extend
the line segment to contain the vanishing point.

%Though more sophisticated consistency measures, like those presented
%by Xu \& al.~\cite{kitware2013}, are open to use, we find in our
%experiments that the simple model we propose above performs well for
%vanishing point estimation task while is much easier to compute.

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{fasthorizon/homoIntersection}
  \caption{In homogeneous coordinates, lines (red lines) are defined
    by the normal (red arrow) of the plane (red triangle) they form
    with the origin (green dot). Two lines form a great circle (blue
    circle), whose normal (blue arrow) is their common point (blue
    dot) in homogeneous coordinates.}
  % \caption{In homogeneous coordinates normals (red arrow) of
  %   concurrent lines (red line) form a great circle (blue circle),
  %   whose normal (blue arrow) is their common point (blue dot) in
  %   homogeneous coordinates.}
  \label{fig:homoIntersection}
\end{figure}

\section{Horizon Priors from Global Image Context}
\label{sec:deeplearning}

Recent studies show that deep convolutional neural networks (CNNs) are
adaptable for a wide variety of tasks~\cite{yosinski2014transferable},
and are quite fast in practice.  We propose to use a CNN to extract
global image context from a single image.

%They have shown great performance improvements in a wide variety of
%vision tasks, such as face recognition~\cite{taigman2014deepface} and
%scene parsing~\cite{pinheiro2014recurrent}.

We parameterize the horizon line by its slope angle, $\alpha \in
[-\pi, \pi)$, and offset, $o \in [0, \inf)$, which is the shortest
distance between the horizon line and the principal point. In order to
span the entire horizon line parameter space, we ``squash'' $o$ from
pixel coordinates to the interval $[0, \pi/2)$, through a one-to-one
function, $w = tan^{-1}(o / \kappa)$, in which $\kappa$ is a
scaling factor that affects how dense the sampling is near the center
of the image.
%In our experiments, we select $\kappa$ to be $H/5$.

%The motivation for squashing is to make it easier to deal with points
%at infinity.

%In the rest of this section we introduce the network architecture
%used for estimating priors over $\alpha$ and $w$ and a dataset we
%constructed to train the network.

\begin{figure*}
  \hfill
  \includegraphics[width=0.19\linewidth]{fasthorizon/im1}
  \hfill
  \includegraphics[width=0.19\linewidth]{fasthorizon/im2}
  \hfill
  \includegraphics[width=0.19\linewidth]{fasthorizon/im3}
  \hfill
  \includegraphics[width=0.19\linewidth]{fasthorizon/im4}
  \hfill
  \includegraphics[width=0.19\linewidth]{fasthorizon/im5}
  \hfill
  \caption{Example images from our training dataset
    (\secref{dataset}), each overlaid with the ground-truth horizon line.
    %As the panoramas are primarily captured in urban areas, the majority of images contain man-made objects.
  }
  \label{fig:dataset}
\end{figure*}

\subsection{Network Architecture}

For our task, we adapt the popular
AlexNet~\cite{krizhevsky2012imagenet} architecture, which was designed
for object recognition as part of the ImageNet ILSVRC-2012
challenge~\cite{russakovsky2015imagenet}. It consists of five
convolutional layers, each followed by a non-linearity (rectified
linear unit), and occasionally interspersed with pooling and local
response normalization. This is followed by three fully connected
layers (referred to as `fc6', `fc7', and `fc8'). A softmax is applied
to the final output layer to produce a categorical distribution over
1000 object classes.  We use this as a foundation to create a CNN that
simultaneously generates a categorical distribution for each
horizon-line parameter.

We modify the original AlexNet architecture in the following way: The
first five convolutional layers are left unmodified. These layers are
initialized with weights from a network trained for object detection
and scene classification~\cite{zhou2014places}. We remove the original
fully connected layers (`fc6'--`fc8') and add two disjoint sets of
fully connected layers (`fc6$\alpha$'--`fc8$\alpha$' and
`fc6$w$'--`fc8$w$'), one for each target label, $\alpha$ and $w$.  We
convert the slope, $\alpha$, and the squashed offset, $w$, into
independent categorical labels by uniformly dividing their respective
domains into 500 bins.  We randomly initialize the weights for these
new layers.

We train our network using stochastic gradient descent, with a
multinomial logistic loss function. The learning rates for the
convolutional layers are progressively increased such that the latter
layers change more. The new fully connected layers are given full
learning rate.
%The following section describes the data we used for training.

\subsection{Training Database}
\label{sec:dataset}
To support training our model of global image context, we construct a
large dataset of images with known horizon lines. We make use of
equirectangular panoramas downloaded from Google Street View in large
metropolitan cities around the world. We identified a set of cities
based on population and Street View coverage. From each city, we
downloaded panoramas randomly sampled in a $5km \times 5km$ region
around the city center. This resulted in $11\,001$ panoramas from 93
cities. Example cities include New York, Rio de Janeiro, London, and
Melbourne.

We extracted 10 perspective images from each panorama with randomly
sampled horizontal field-of-view (FOV), yaw, pitch, and roll. Here yaw
is relative to the Google Street View capture vehicle. We sampled
horizontal FOV from a normal distribution with $\mu=60^\circ$ and
$\sigma=10^\circ$. Similarly, pitch and roll are sampled from normal
distributions with $\mu=0^\circ$ and $\sigma=10^\circ$ and
$\sigma=5^\circ$, respectively. Yaw is sampled uniformly.  We truncate
these distributions such that horizontal FOV $\in [40^\circ,
80^\circ]$, pitch $\in [-30^\circ, 30^\circ]$, and roll $\in
[-20^\circ, 20^\circ]$. These settings were selected empirically to
match the distribution of images captured by casual photographers in
the wild.

Given the FOV, pitch, and roll of a generated perspective image, it is
straightforward to compute the horizon line position in image space.
In total, our training database contains $110\,010$ images with known
horizon line.  \figref{dataset} shows several example images from
our dataset annotated with the ground-truth horizon line.

\subsection{Making the Output Continuous}

Given an image, $I$, the network outputs a categorical probability
distribution for the slope, $\alpha$, and squashed offset, $w$. We
make these distributions continuous by approximating them with a
Gaussian distribution. For each, we estimate the mean and variance
from $5\,000$ samples generated from the categorical probability
distribution. Since the relationship between $w$ and $o$ is
one-to-one, this also results in a continuous distribution over
$o$. The resulting distributions, $p(\alpha \given I)$ and $p(o \given
I)$, are used in the next step of our approach to aid in detecting the
zenith VP and as a prior for sampling candidate horizon
lines. To visualize this distribution we observe that the horizon line
can be uniquely defined by the point on the line closest to the
principal point. Therefore, we can visualize a horizon line
distribution as a distribution over points in the image.
\figref{horpdf} shows this distribution for two images.

\begin{figure}
 \centering
 \includegraphics[width=.48\linewidth]{fasthorizon/4horpdf}
 \includegraphics[width=.48\linewidth]{fasthorizon/68horpdf}

 \caption{Global image context imposes a strong prior on horizon line
   location. The output of our CNN is visualized as an overlaid
   heatmap, with red indicating more likely locations. For each image,
   the ground-truth horizon line (dash green) and the line that
   maximizes the prior (red) are shown.}

 \label{fig:horpdf}
\end{figure}

\section{Horizon-First Vanishing Point Detection}
\label{sec:precise}

We propose an approach to obtain accurate estimates of the horizon
line, the zenith vanishing point, and one or more horizontal vanishing
points. Given an image, our approach makes use of the distributions
estimated from global image context (\secref{deeplearning}) and
line segments extracted with LSD~\cite{lsd2010}. The algorithm
consists of the following major steps:
\begin{compactenum} %[noitemsep]

  \item detect the zenith vanishing point
    (\secref{zenithdetection})

  \item \label{alg:findhorvp} detect horizontal vanishing points on
    horizon line candidates
    (\secref{horizondetection})

  \item \label{alg:scorehorizon} score horizon line candidates with
    horizontal vanishing points (\secref{horizonscoring})

\end{compactenum}
The remainder of this section provides details for each of these steps.

\subsection{Detecting the Zenith Vanishing Point}
\label{sec:zenithdetection}

% To detect the zenith vanishing point, we first estimate the zenith
% direction, $\mathbf{l}_\mathbf{z}$, from the global image context, then attempt to
% refine it using detected line segments~\cite{lsd2010}.

To detect the zenith vanishing point, we first select an initial set
of line segments using the zenith direction,
$\mathbf{l}_\mathbf{z}$, from the global image context, then use
the RANSAC~\cite{ransac1981} algorithm to refine it.  The zenith direction
is the line connecting the principal point and the zenith vanishing
point, which is uniquely determined by the horizon line slope (see
supplemental material for a proof).

We compute our initial estimate of $\mathbf{l}_{\mathbf{z}}$ using the global
image context by choosing the value that maximizes the posterior:
$\hat{\alpha} = \operatorname*{arg\,max}_\alpha p(\alpha \given I)$.
%
To handle the presence of outlier line segments, we first select a set
of candidate vertical line segments as the RANSAC inputs by
thresholding the angle between each line segment and the estimated
zenith direction, $\Theta_{\mathbf{l},\mathbf{l}_{\mathbf{z}}} < \theta_{ver}$.  For a
randomly sampled pair of line segments with intersection, $\mathbf{p}$, we
compute the set of inlier line segments, $\{\mathbf{l} \mid f_c(\mathbf{p}, \mathbf{l})
> 0\}$.  If the largest set of inliers has a sufficient portion (more
than 2\% of candidate line segments), we obtain the final estimate of
the zenith vanishing point, $\mathbf{z}$, by minimizing the algebraic
distance, $\|\mathbf{l}^\mathsf{T} \mathbf{p}\|$ using singular value decomposition
(SVD), and update the zenith direction, $\mathbf{l}_{\mathbf{z}}$. Otherwise, we
keep the zenith direction estimated from the global image context.

\subsection{Detecting Horizontal Vanishing Points}
\label{sec:horizondetection}

We start with sampling a set of horizon line candidates,
$\{\mathbf{h}_i\}_1^S$, that are perpendicular to $\mathbf{l}_{\mathbf{z}}$ in the image
space, under the distribution of horizon line offsets, $p(o | I)$.
See \figref{horsampling} for examples of horizon line sampling with
and without global context.

For each horizon line candidate, we identify a set of horizontal VPs
by selecting points along the horizon line where many line segments
intersect. We assume that for the true horizon line the identified
horizontal VPs will be close to many intersection points and that
these intersections will be more tightly clustered than for
non-horizon lines. We use this intuition to define a scoring function
for horizon line candidates.

As a preprocessing step, given the zenith direction, $\mathbf{l}_{\mathbf{z}}$,
and a horizon line candidate, $\mathbf{h}$, we filter out nearly vertical
line segments ($\Theta_{\mathbf{l},\mathbf{l}_{\mathbf{z}}} < \theta_{ver}$), which are
likely associated with the zenith vanishing point, and nearly
horizontal line segments ($\Theta_{\mathbf{l},\mathbf{h}} < \theta_{hor}$), which
result in noisy horizon line intersection points.  We remove such
lines from consideration because they lead to spurious, or
uninformative, vanishing points, which decreases accuracy.

Given a horizon line candidate, $\mathbf{h}$, and the filtered line segments
in homogeneous coordinates, $\mathcal{L} = \{\mathbf{l}_i\}$, we select
a set of horizontal VPs, $\mathcal{P} = \{\mathbf{p}_i\}$, by minimizing
the following objective function:
%
\begin{align} 
  g(\mathcal{P} \given \mathbf{h}, \mathcal{L}) & = -\sum_{\mathbf{p}_i
    \in \mathcal{P}} {\sum_{\mathbf{l}_j \in
      \mathcal{L}}f_c(\mathbf{p}_i, \mathbf{l}_j)}
  \label{eq:obj} \\
  \text{subject to:} \nonumber \\
   % & \sum_{\mathbf{l}_j \in \mathcal{L}}f_c(\mathbf{p}_i, \mathbf{l}_j) > \varphi_{min},
   % \text{and} \nonumber \\
   & \Theta_{\mathbf{p}_i,\mathbf{p}_j} > \theta_{dist}
  \; \text{and} \; \left< \mathbf{p}_i,\mathbf{h} \right>=0, 
  \; \forall (i,j) \nonumber \; .
\end{align} 
%
% The first constraint suppresses the false positive VPs. The second
The constraint prevents two vanishing points from being too close
together, which eliminates the possibility of selecting multiple
vanishing points in the same location.

We propose the following combinatorial optimization process for
obtaining an initial set of vanishing points, followed by a
constrained nonlinear optimization to refine the vanishing points.

\begin{figure}
  \centering
  \includegraphics[width=.4075\linewidth]{fasthorizon/horizon_sampling_uniform}
  \includegraphics[width=.4075\linewidth]{fasthorizon/horizon_sampling}
  \includegraphics[width=.1630\linewidth]{fasthorizon/offset_distribution}
  \caption{Our method samples more horizon line candidates (red) near
    the ground truth (green dash) with (middle) global image context
    than without (left).  In the case of sampling with global image
    context, the offset PDF, $p(o|I)$ (blue curve), is fit from the
    CNN categorical probability distribution outputs (hollow
    bins). For clarity, we only show a reduced number of horizon line
    candidates and bins.}
  \label{fig:horsampling}
\end{figure}

\subsubsection{Initialization by Random Sampling and Discrete
Optimization}
\label{sec:initialization}

To choose an initial set of candidate vanishing points,
$\{\mathbf{p}_i\}_1^M$, we randomly select a subset of line segments,
$\{\mathbf{l}_i\}_1^M$, and compute their intersection with the horizon
line.  We then construct a graph with a node for each vanishing point,
$\mathbf{p}_i$, each with weight $\sum_{\mathbf{l}_j \in \mathcal{L}}f_c(\mathbf{p}_i,
\mathbf{l}_j)$, which is larger if there are many line segments in the image
that are consistent with $\mathbf{p}_i$. Pairs of nodes, $(i,j)$, are
connected if the corresponding vanishing points, $\mathbf{p}_i, \mathbf{p}_j$, are
sufficiently close in homogeneous space ($\Theta_{\mathbf{p}_i,\mathbf{p}_j} \le
\theta_{dist}$).

From this randomly sampled set, we select an optimal subset of VPs by
maximizing the sum of weights, while ensuring no VPs in the final set
are too close.  Therefore, the problem of choosing the initial set of
VPs reduces to a maximum weighted independent set problem, which is
NP-hard in general. Due to the nature of the constraints, the
resulting graph has a ring-like structure which means that, in
practice, the problem can be quickly solved. Our solver exploits this
sparse ring-like structure by finding a set of VPs that when removed
convert the ring-like graph into a set of nearly linear sub-graphs
(\figref{subset}). We solve each subproblem using dynamic
programming. The set of VPs with maximum weight, $\{\mathbf{p}_i\}_{opt}$,
is used as initialization for local refinement. Usually, 2--4 such
vanishing points are found near the horizon line ground truth.

\begin{figure}
  \centering
  \includegraphics[width=.92\linewidth]{fasthorizon/independent_subset}

  \caption{A ring-like graph (left) is converted into three nearly
    linear subgraphs (right) by partitioning around a node with
    minimal degree. For the subgraphs, the red node is mandatory, the
    dashed nodes are excluded, and a subset of the solid nodes are
    selected using dynamic programming.}

  \label{fig:subset}
\end{figure}

\subsubsection{Vanishing Points Refinement}
\label{sec:refinement}

Since they were randomly sampled, the set of vanishing points
selected during initialization, $\{\mathbf{p}_i\}_{opt}$, may not be at the
optimal locations.  We optimize their locations to further minimize
the objective function \eqref{obj}. We perform an EM-like algorithm
to refine the vanishing point locations, subject to the constraint
that they lie on the horizon line:
\begin{compactitem}

\item \emph{E-step}: Given a vanishing point, $\mathbf{p}$, assign
  line segments that have positive consistency with $\mathbf{p}$:
  $\{\mathbf{l}|f_c(\mathbf{p},\mathbf{l}) > 0\}$.
\item \emph{M-step}: Given the assigned line segments as a matrix,
  $\mathbf{l} = [\mathbf{l}_1, \mathbf{l}_2,\dots ,\mathbf{l}_n]$, and the horizon line,
  $\mathbf{h}$, both represented in homogeneous coordinates, we 
  solve for a refined vanishing point, $\mathbf{p}^*$, by minimizing the algebraic distance, $\|
  \mathbf{l}^\mathsf{T} \mathbf{p} \|$ such that $\mathbf{h}^\mathsf{T} \mathbf{p} = 0$. We define a
  basis, $\mathbf{B}_\mathbf{h}$, for the null space of $\mathbf{h}$, and reformulate
  the problem as $\mathbf{\lambda}^* = \operatorname*{arg\,min} \|
  \mathbf{l}^\top \mathbf{B}_\mathbf{h} \mathbf{\lambda} \|$, which we solve using SVD.
  Given the optimal coefficients, $\mathbf{\lambda}^*$, we reconstruct
  the optimal vanishing point as: $\mathbf{p}^* =
  \frac{\mathbf{B}_\mathbf{h}\mathbf{\lambda}^*}
  {\|\mathbf{B}_\mathbf{h}\mathbf{\lambda}^*\|}$.

\end{compactitem}

We run this refinement iteration until convergence. In practice, this
converges quickly; we run at most three iterations for all the
experiments. The final set of optimized VPs is then used to assign a
score to the current horizon line candidate.

\subsection{Optimal Horizon Line Selection}
\label{sec:horizonscoring}

For each horizon line candidate, we assign a score based on the total
consistency of lines in the image with the VPs selected in the
previous section.  The score of a horizon line candidate, $\mathbf{h}$, is
defined as:
\begin{equation}
  score(\mathbf{h}) = \sum_{\{\tilde{\mathbf{p}}_i\}} \sum_{\mathbf{l}_j \in
    \mathcal{L}}f_c(\tilde{\mathbf{p}}_i, \mathbf{l}_j) \; .
\end{equation}
To reduce the impact of false positive vanishing points, we select
from $\{\mathbf{p}_i\}_{opt}$ the two highest weighted vanishing points (or
one if $\{\mathbf{p}_i\}_{opt}$ contains only one element),
$\{\tilde{\mathbf{p}}_i\}$, for horizon line scoring.

%
% Evaluation
%
\section{Evaluation}
\label{sec:evaluation}

We perform an extensive evaluation of our methods, both quantitatively
and qualitatively, on three benchmark datasets. The results show that
our method achieves state-of-the-art performance based on horizon-line
detection error, the standard criteria in recent work on VP
detection~\cite{geoparser2010,alignment2014,selfsketch2012,kitware2013}.
Horizon detection error is defined as the maximum distance from the
detected horizon line to the ground-truth horizon line, normalized by
the image height.  Following tradition, we show the cumulative
histogram of these errors and report the area under the curve (AUC).

Our method is implemented using MATLAB, with the exception of
detecting line segments, which uses an existing C++
library~\cite{lsd2010}, and extracting global image context, which we
implemented using Caffe~\cite{jia2014caffe}. We use the parameters
defined in \tblref{parameters} for all experiments. This differs from
other methods which usually use different parameters for different
datasets.

\begin{table}[h]
  \centering
  \caption{
   Algorithm parameters (given an $H\times W$ image).
  }
  \vspace{-.5em}
  \begin{tabular}{|c|l|l|}
    \hline
    Name & Usage(s) & Value\\
    \hline
    $\theta_{con}$ & \secref{problem} & $2^\circ$\\
    $\rho$ & \secref{problem} & $2/\operatorname{max}(H,W)$ \\
    $\kappa$ & \secref{deeplearning} & $ 1/5 \times H$ \\
    $\theta_{ver}$ & \secref{zenithdetection}, \secref{horizondetection} & $ \Theta_{\mathbf{l},\mathbf{l}_{\mathbf{z}}} < 10^\circ$ \\
    $\theta_{hor}$ & \secref{horizondetection} & $\Theta_{\mathbf{l},\mathbf{h}} <
    1.5^\circ$ \\
    $S$ & \secref{horizondetection} & 300 candidates \\
    $M$ & \secref{initialization} & 20 line segments \\
    $\theta_{dist}$ & \secref{horizondetection}, \secref{initialization} & $
    \Theta_{\mathbf{p}_i,\mathbf{p}_j} > 33^\circ$\\
    \hline
  \end{tabular}
  \label{tab:parameters}
\end{table}

\begin{figure*}[]
  \centering
  \begin{subfigure}{.30\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fasthorizon/YUD_methods}
    \subcaption{YUD}
    \label{fig:horError_YUD}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fasthorizon/ECD_methods}
    \subcaption{ECD}
    \label{fig:horError_ECD}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fasthorizon/HLW_methods}
    \subcaption{HLW}
    \label{fig:hlw_err}
  \end{subfigure}
  \caption{For three benchmark datasets, the fraction of images
    (y-axis) with a horizon error less than a threshold (x-axis). The
    AUC for each curve is shown in the legend. For additional details see \secref{evaluation}.}
  \label{fig:horError}
\end{figure*}

\subsection{Quantitative Evaluation}

%\paragraph{York Urban Dataset (YUD)}
%\label{sec:yud}

The York Urban Dataset (YUD)~\cite{edgebased2008} is a commonly used dataset
for evaluating horizon line estimation methods. It contains 102 images
and ground-truth vanishing points. The scenes obey the Manhattan-world
assumption, however we do not take advantage of this assumption.
\figref{horError_YUD} shows the performance of our methods relative to
previous work on YUD. These results demonstrate that our method
achieves state-of-the-art AUC, improving upon the previous best of
Lezama et al.~\cite{alignment2014} by 0.28\%, a relative
improvement\footnote{We define the relative improvement as
$\frac{\text{AUC}_{new} - \text{AUC}_{old}}{1 - \text{AUC}_{old}}$.} of
5\%. This is especially impressive given that our method only requires
an average of 1 second per image, while Lezama et al.\ requires
approximately 30 seconds per image.

%\paragraph{Eurasian Cities Dataset (ECD)}

The Eurasian Cities Dataset (ECD)~\cite{geoparser2010} is another
commonly used benchmark dataset, which is considered challenging due
to the large number of outlier line segments and complex scene
geometries. It contains 103 images captured in urban areas and, unlike
the YUD dataset, not all images satisfy the Manhattan-world
assumption. It provides reliable horizon line ground truth and is
widely considered difficult for horizon line detection. To our
knowledge, the previous state-of-the-art performance in terms of the
AUC metric on this dataset was achieved by Lezama et
al.~\cite{alignment2014}. Our algorithm improves upon their
performance, increasing the state of the art to 90.8\%.  This is a
significant relative improvement of 14.8\%, especially considering
their improvement relative to the state of the art was 0.5\%.  On ECD,
our method takes an average of 3 seconds per image, while Lezama et
al.\ requires approximately 60 seconds per image. We present the
performance comparison with other methods in \figref{horError_ECD}.

%\paragraph{Horizon Lines in the Wild (HLW)}

The Horizon Lines in the Wild (HLW)
dataset~\cite{authors2016deephorizon} is a new, very challenging
benchmark dataset. We use the provided test set, which contains
approximately $2\,000$ images from diverse locations, with many images
not adhering to the Manhattan-world assumption. \figref{hlw_err}
compares our method with the method of Lezama et
al.~\cite{alignment2014} (the only publicly available implementation
from a recent method). Our method is significantly better, achieving
58.24\% versus 52.59\% AUC.

\begin{table}[t] \centering
  \caption{Component error analysis (AUC).}
    %AUC performance comparison of our algorithm when major components,
    %``global context'' $+$ ``vanishing point detection'', are
    %omitted or replaced (see \secref{analysis} for details). 
  \vspace{-.5em}
  \begin{tabular}{|l|c|c|c|}
    \hline
    Method & YUD & ECD & HLW \\
    \hline
    \hline
    Lezama et al.~\cite{alignment2014} & 94.51\% & 89.20\% & 52.59\% \\
    \hline
    NONE+FULL & 93.87\% & 87.94\% & 53.04\% \\
    \hline
    GISTRF+EMPTY & 53.36\% &  32.69\% & 31.08\% \\
    GISTRF+FULL & 94.66\% &  87.60\% & 54.95\% \\
    \hline
    CNN+EMPTY & 73.67\% &  67.64\% & 49.03\% \\
    % CNN (No refinement) & 94.61\% & 89.55\% & XX \\
    CNN+FULL (Ours) & \textbf{94.78\%} & \textbf{90.80\%} & \textbf{58.24\%} \\
    \hline
  \end{tabular}
  \label{tab:contribution}
\end{table}

\subsection{Component Error Analysis}
\label{sec:analysis}

Our method consists of two major components: global context extraction
(\secref{deeplearning}) and horizon-first vanishing point detection
(\secref{precise}). This section provides an analysis of the impact
each component has on accuracy.

To evaluate the impact of global context extraction, we considered
three alternatives: our proposed approach (CNN), replacing the CNN
with a random forest (using the Python ``sklearn'' library with 25 trees) applied to a GIST~\cite{oliva2001modeling}
descriptor (GISTRF), and omitting context entirely
(NONE). When omitting the global context, we assume no camera
roll (horizon lines are horizontal in the image) and sample horizon
lines uniformly between $[-2H,2H]$ ($H$ is the image height).  To
evaluate the impact of vanishing point detection, we considered two
alternatives: our proposed approach (FULL) and omitting the vanishing
point detection step (EMPTY). When omitting vanishing point detection,
we directly estimate the horizon line, $(\alpha, o)$, by maximizing
the posterior estimated by our global-context CNN, $p(\alpha, o | I)$.

Quantitative results presented in \tblref{contribution} show that both
components play important roles in the algorithm and that CNN provides
better global context information than GISTRF.  Though our vanishing
point detection performs well by itself (see column NONE+FULL), global
image context helps improve the accuracy further. \figref{hlw_err}
visualizes these results as a cumulative histogram of horizon error
on HLW.  To illustrate the impact of global image context, we present
two examples in \figref{iscontext} that compare horizon line
estimates obtained using global context (CNN+FULL) and without
(NONE+FULL).  When using global context, the estimated horizon lines
are very close to the ground truth.  Without, the estimates obtained
are implausible, even resulting in an estimate that is off the image.

\begin{figure}
  \centering
  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_ecd_hybrid}
  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_ecd_uniform}
  %
  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_yud_hybrid}
  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_yud_uniform}
  \caption{Two images where horizon line estimates are much better with global context (left) than without (right).}
  \label{fig:iscontext}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd5}
  \includegraphics[width=0.0884\linewidth]{fasthorizon/montage_ecd1}
  \includegraphics[width=0.1572\linewidth]{fasthorizon/montage_yud2}
  \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd4}
  \includegraphics[width=0.1572\linewidth]{fasthorizon/montage_yud3}
  \includegraphics[width=0.0884\linewidth]{fasthorizon/montage_ecd6}
  \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd8}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd5_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd1_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud2_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd4_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud3_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd6_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd8_homo}

  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud1}
  \includegraphics[width=0.0867\linewidth]{fasthorizon/montage_ecd3}
  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud5}
  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud4}
  \includegraphics[width=0.1731\linewidth]{fasthorizon/montage_ecd2}
  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud6}
  \includegraphics[width=0.0867\linewidth]{fasthorizon/montage_ecd7}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud1_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd3_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud5_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud4_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd2_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud6_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd7_homo}
  \caption{Example results produced by our method.  (rows 1 and 3)
    Line segments color coded based on the most consistent VP, the
    ground-truth (green dash), and detected horizon lines (magenta).
    For clarity only the top two horizontal VPs are shown.  (rows 2
    and 4) The line segments (dots) and their VPs (rings) represented
    in homogeneous coordinates. (last column) Two failure cases of our
    method, caused by irregularly shaped objects (bottom) and short
    edges (top).}
  \label{fig:examples}
\end{figure*}

\subsection{Failure Cases}

We highlight two representative failure cases in the last column of
\figref{examples}.  The top image fails due to the propagation of
measurement errors from the short line segments. The bottom image is
challenging because the curved structures lead to indistinct VPs.
Despite this, global context helps our method produce plausible
results, while other methods (\eg, \cite{geoparser2010}) fail
dramatically.

\section{Conclusion}

We presented a novel vanishing point detection algorithm that obtains
state-of-the-art performance on three benchmark datasets. The main
innovation in our method is the use of global image context to sample
possible horizon lines, followed by a novel discrete-continuous
procedure to score each horizon line by choosing the optimal vanishing
points for the line. Our method is both more accurate and more
efficient than the previous state-of-the-art algorithm, requiring no
parameter tuning for a new testing dataset, which is common in other
methods.

### 2018-06-18 chapters/crosstransf/paper.tex
crossview paper

\section{Introduction}

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{crosstransf/cartoon}
  \caption{We learn to predict the ground-image
    segmentation directly from an aerial image of the same location,
  thereby transferring the semantics from the ground to the aerial
image domain.}
	\label{fig:overview}
\end{figure}

Learning-based methods for pixel-level labeling of aerial imagery
have long relied on manually annotated training data. Unfortunately,
such data is expensive to create. Furthermore, its value is limited
because a method trained on one dataset will typically not perform
well when applied to another source of aerial imagery.  The
difficulty in obtaining datasets of sufficient scale for all
modalities has hampered progress in applying deep learning techniques
to aerial imagery.  There have been a few notable
exceptions~\cite{mnih2010learning,paisitkriangkrai2015effective}, but
these have all used fairly coarse grained semantic classes, covered a
small spatial area, and are limited to modalities in which human
annotators are able to manually assign labels.

We propose a novel strategy for obtaining semantic labels for
aerial image segmentation.  See \figref{overview} for a schematic
overview of the approach.  Our idea is to use existing methods for
semantic image segmentation, which are tailored for ground
images, and apply these to a large dataset of geo-tagged ground
images.  We use these semantically labeled images as a form of weak
supervision and attempt to predict these semantic labels from an
aerial image centered around the location of the ground
image.  We do not use a parametric transformation between the
aerial and ground-level viewpoints.  Instead, we use a dense
representation, similar in spirit to the general representation,
dubbed filter flow, described by Seitz and Baker~\cite{filterflow}.

There has been significant interest recently in predicting
ground image features from aerial imagery for the task of
ground image geolocalization~\cite{workman2015wide}. Our work is
unique in that it is the first to attempt to predict a dense
pixel-level segmentation of the ground image. We demonstrate the
value of this approach in several ways.

\paragraph{Main Contributions:} The main contributions of this work
are: (1)  a novel convolutional neural network (CNN) architecture that
relates the appearance of a aerial image appearance to the semantic
layout of a ground image of the same location, (2) demonstrating
the value of our training strategy for pre-training a CNN to
understand aerial imagery, (3) extensions of the proposed technique to
the tasks of ground image localization, orientation estimation,
and synthesis, and (4) an extensive evaluation of each of these
techniques on large, real-wold datasets.  Together these represent an
important step in enabling deep learning techniques to be extended to
the domain of aerial image understanding.

\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{crosstransf/architecture}

  \caption{A visual overview of our network architecture. We extract
    features from an aerial image using the VGG16 architecture and
    form a hypercolumn using the PixelNet approach. These features are
    processed by three networks that consist of 1 $\times$ 1
    convolutions: network $A$ converts the hypercolumn into semantic
    features; network $S$ extracts useful features from the aerial
    image for controlling the transformation; and network $F$ 
    defines the transformation between viewpoints.  The
  transformation is applied, $T$, to the aerial semantic features to
create a ground-level semantic labeling.  }

	\label{fig:architecture}
\end{figure*}

\section{Related Work}

\paragraph{Learning Viewpoint Transformations}
Many methods have been proposed to represent the relationship between
the appearance of two viewpoints. Seitz and Baker~\cite{filterflow}
model image transformations using a space-variant linear filter,
similar to a convolution but varying per-pixel. They highlight that a
linear transformation of a vectorized representation of all the pixels
in an image is very general; it can represent all standard parametric
transformations, such as similarity, affine, perspective, and more.
More recently, Jaderberg \etal~\cite{jaderberg2015spatial} describe an
end-to-end learnable module for neural networks, the spatial
transformer, which allows explicit spatial transformations (\eg
scaling, cropping, rotation, non-rigid deformation) of feature maps
within the network that are conditioned on individual data samples.
Practically, including a spatial transformer allows a network to
select regions of interest from an input and transform them to a
canonical pose. Similarly, Tinghui \etal~\cite{tinghui2016flow}
address the problem of novel view synthesis. They observe that the
visual appearance of different views is highly correlated and propose
a CNN architecture for estimating appearance flows, a representation
of which pixels in the input image can be used for reconstruction.

\paragraph{Relating Aerial and Ground-Level Viewpoints}
Several methods have been recently proposed to jointly reason about
co-located aerial and ground image pairs. Luo
\etal~\cite{luo2008event} demonstrate that aerial imagery can aid
in recognizing the visual content of a geo-tagged ground image.
M{\'a}ttyus \etal~\cite{mattyus2016hd} perform joint inference over
monocular aerial imagery and stereo ground images for fine-grained
road segmentation. Wegner \etal~\cite{wegner2016cataloging} build a
map of street trees. Given the horizon line and the camera intrinsics,
Ghouaiel and Lef{\`e}vre~\cite{ghouaiel2016coupling} transform
geo-tagged ground-level panoramas to a top-down view to enable
comparisons with aerial imagery for the task of change detection.
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
 has shown that convolutional neural
networks are capable of extracting features from aerial imagery
that can be matched to features extracted from ground imagery.
Vo \etal~\cite{vo2016localizing} extend this line of work,
demonstrating improved geolocalization performance by applying an
auxiliary loss function to regress the ground-level camera orientation
with respect to the aerial image. To our knowledge, our work is the
first work to explore predicting the semantic layout of a ground
image from an aerial image.

\paragraph{Semantic Segmentation of Aerial/Satellite Imagery}

There is a long tradition of using computer vision techniques for
aerial and satellite image
understanding~\cite{Huertas1988DetectingBI,Willuhn1996ARS,Cheng2016ASO}.
Historically these two domains were distinct.  Satellite imagery was
typically lower-resolution, from a strictly top-down view, and with a
diversity of spectral bands.  Aerial imagery was typically
higher-resolution, with a greater diversity of viewing angles, but
with only RGB and NIR sensors.  Recently these two domains have
converged; we will use the term aerial imagery as we are primarily
working with high-resolution RGB imagery.  However, our approach could
be applied to many types of aerial and satellite imagery.  Kluckner 
\etal~\cite{Kluckner2009SemanticCI} address the task of semantic
segmentation using a random forest to combine color and height
information.  More recent work has explored the use of CNNs for aerial
image understanding. Mnih and Hinton propose a CNN for detecting roads
in aerial imagery~\cite{mnih2010learning} using GIS data as ground
truth.  They extend their approach to handle omission noise and
misregistration between the imagery and the
labels~\cite{mnih2012learning}. These approaches require either
extensive pixel-level manual annotation or existing GIS data. Our work
is the first to demonstrate the ability to transfer a dense
pixel-level labeling of ground imagery to aerial imagery.

\paragraph{Visual Domain Adaptation}
Domain adaptation addresses the misalignment of source and target
domains~\cite{daume2006domain}. A significant amount of work has
explored domain adaptation for visual
recognition~\cite{patel2015visual}. Jhuo \etal~\cite{jhuo2012robust}
propose a low-rank reconstruction approach where the source features
are transformed to an intermediate representation in which they can be
linearly reconstructed by the target samples. Our work is most similar
to that of Sun \etal ~\cite{sun2016unsupervised}, who propose a method
for transferring scene categorizations and attributes from ground
images to aerial imagery. Similar to our approach, they learn a
transformation matrix which minimizes the distance between a source
feature and the target feature. Our work differs in several ways: 1)
we carry out the linear transformation not only in the semantic
dimensions but also in the spatial dimensions, 2) we constrain the
transformation matrix such that the semantic meaning of the source
feature and the target feature remains the same, 3) our transformation
matrix is input dependent, and 4) we learn the transformation matrix
as well as the source feature at the same time, in an end-by-end
manner, which simplifies training.

\section{Cross-view Supervised Training}
\label{sec:method}

We propose a novel training strategy for learning to extract useful
features from aerial imagery.  The idea is to predict the semantic
scene layout, $L_g$, of a ground image, $I_g$, using only an aligned
aerial image, $I_a$, from the same location.  This strategy leverages
existing methods for ground image understanding at training time, but
does not require any ground imagery at testing time.

We represent semantic scene layout, $L_g$, as a pixel-level
probability distribution over classes, such as {\em road}, {\em
vegetation}, and {\em building}.  We construct a training pair by
collecting a georegistered ground panorama and an aerial image of the
same location, orienting the panorama to the aerial image (panoramas
are originally aligned with the road direction), and then extracting
the semantic scene layout, $L_g$, of the panorama using an
off-the-shelf method~\cite{badrinarayanan2015segnet} with four
semantic classes.  We then use an end-to-end training strategy to
learn to extract pixel-level features from the aerial image and
transform them to the ground-level viewpoint.

\subsection{Network Architecture}
\label{sec:architecture}

Our proposed network architecture is composed of four modules. A
convolutional neural network (CNN), $L_a = A(I_a;\Theta_A)$, is used
to extract semantic labels from the aerial imagery. Another CNN,
$S(I_a;\Theta_S)$, uses features extracted from aerial imagery to help 
estimate the transformation matrix, $M = F(x_r, y_r, i_c, j_c,
S(I_a;\Theta_S); \Theta_F)$, based on aerial image features and the
pixel location in the respective images. Finally, we have a
transformation module, $L_{g'}= T(L_a,M)$, that converts from the
aerial viewpoint to the ground-level using the estimated
transformation matrix, $M$. 
There are many choices for these components, and the 
remainder of this section describes the particular choices we made for this 
study. See~\figref{architecture} for a visual overview of the architecture.

\paragraph{Aerial Image Feature Extraction} For $A(I_a;\Theta_A)$, we
use the VGG16~\cite{simonyan2014very} base architecture and convert it to a 
pixel-level labeling method using the PixelNet approach~\cite{BansalChen16}.  
The core idea is to interpolate intermediate feature maps of the base
network to a uniform size, then concatenate them along the channels dimension 
to form a {\em hypercolumn}.  In our experiments, we form the hypercolumn from 
{\em conv-$\{1_2, 2_2, 3_3, 4_3\}$} of the VGG16
network.  The hypercolumn, which is now 256 $\times$ 256 $\times$ 960,
is followed by three 1 $\times$ 1 convolutional layers, with 512,
512, and 4 output channels respectively. The first two 1 $\times$ 1
convolutions have ReLU activations, the final is linear. We designate
the output of the final convolution as $L_a = A(I_a;\Theta_A)$. The
output of this stage is transformed from a aerial viewpoint to a
ground viewpoint by final stage of the network.
\label{sec:aerialnet}

\paragraph{Cross-view Semantic Transformation} We represent 
the transformation between the aerial and ground-level
viewpoints as a linear operation applied channel-wise to $L_a$.  To
transform from the $h_a \times w_a \times$ 4 aerial label, $L_a$, to
the $h_g \times w_g \times$ 4 ground label, $L_{g'}$, we need to
estimate a $h_gw_g \times h_a w_a$ matrix, $M$. Given $M$, the
transformation process is as follows: reshape the aerial label, $L_a$,
into a $h_aw_a \times $ 4 matrix, $l_a$; multiply it by $M$ to get
$l_{g'}$; then reshape $l_{g'}$ to the size of the ground label,
$L_g$, to form our estimate of the ground label, $L_{g'}$.  We
constrain $M$ such that the sum of each row is unit. To account for
the expected layout of the scene, and to handle the sky class (which
is not visible from the aerial image), we carry out the transformation
on the logits of $l_a$, $f_a$, and add a bias term, $b$ to get the
logits of $l_{g'}$, $f_{g'}$: $f_{g'} = M f_a + b$.

There are many ways of representing the transformation matrix, $M$.
The na\"{\i}ve approach is to treat $M$ as a matrix of learnable
variables. However, this approach has two downsides: (1) the
transformation does not depend on the content of the aerial image and
(2) the number of parameters scales quadratically with the number of
pixels in $L_a$ and $L_g$.

We represent each element, $M_{rc}$, in the transformation matrix,
$M$, as the output of a neural network, $F$, which is conditioned on
the aerial image, $I_a$, and the location in the input and output
feature maps. More precisely, each element $M_{rc} =
F(x_r,y_r,i_c,j_c,S(I_a;\Theta_S))$, where $(i_c, j_c) \in [0,1]$, is
the aerial image pixel of the corresponding element, $(y_r, x_r)
\in [0,1]$ is the ground image pixel of the corresponding
element.

We now define the architecture of the transformation estimation neural
network, $F$. The value of the transformation matrix at
location $(r, c)$ is computed through a neural network, $\tilde{F}$,
followed by a {\em softmax} function to normalize the impact of all
pixels sampled from the aerial image:
\begin{align*}
\begin{split}
  M_{rc} &= F\left(r, c, S(I_a; \Theta_S)\right)
  = \frac{e^{\tilde{F}_{r,c}}}{\sum_{c'}{e^{\tilde{F}_{r,c'}}}}, \\
\textrm{where:} ~~~~~&\\
  &\tilde{F}_{r, c} = \tilde{F}\left(i, j, y, x, S(I_a; \Theta_S)\right), 
  ~~\textrm{and}\\
  & i = \lfloor c / w_a \rfloor / h_a, ~~~j = \mathrm{mod}(c,w_a) / w_a, \\
  & y = \lfloor r / w_g \rfloor / h_g, ~~~x = \mathrm{mod}(r,w_g) / w_g.
\label{equ:matmul}
\end{split}
\end{align*}
The base network, $\tilde{F}$, is a multi-layer perceptron, with ReLU
activation functions, that takes as input a 293-element vector.
The network has three layers, with 128, 64 and 1 output channels
respectively (refer to the lower part of~\figref{architecture}).  The
na\"{\i}ve approach can be considered a special case of this
representation where we ignore the aerial image and use a one-hot
encoding representation of rows and columns.

As described above, there are two main advantages of our approach of
representing the transformation matrix: a reduction in the number of
parameters when $M$ is large and the ability to adapt to different
aerial image layouts.  An additional benefit is that if we change the
resolution of our input and output feature maps it is easy to create a
new transformation matrix, $M$, without needing to resort to
interpolation.

\subsection{Dataset}
\label{sec:dataset}

\begin{figure}
	\newlength{\aheight}
	\setlength{\aheight}{1.75cm}
	\newlength{\gwidth}
	\setlength{\gwidth}{.76\linewidth}
	\newlength{\gspace}
	\setlength{\gspace}{.4cm}
	\centering
	\includegraphics[height=\aheight,width=\aheight]{crosstransf/dataset/aerial1}\hspace{6pt}%
	% %
	\begin{minipage}[b]{\gwidth}
	\includegraphics[height=1.75cm,width=\textwidth]{crosstransf/dataset/ground1}\vfill
	\end{minipage}\vspace{1pt}
	\includegraphics[height=1.75cm,	width=1.75cm]{crosstransf/rf/14_a}\hspace{6pt}%	
	\begin{minipage}[b]{\gwidth}
	\includegraphics[height=1.75cm,width=\textwidth]{crosstransf/rf/14_g}\vfill
	\end{minipage}\vspace{1pt}
	\includegraphics[height=1.75cm,	width=1.75cm]{crosstransf/rf/16_a}\hspace{6pt}%	
	\begin{minipage}[b]{\gwidth}
	\includegraphics[height=1.75cm,width=\textwidth]{crosstransf/rf/16_g}\vfill
	\end{minipage}\vspace{1pt}
	\includegraphics[height=1.75cm,	width=1.75cm]{crosstransf/rf/17_a}\hspace{6pt}%	
	\begin{minipage}[b]{\gwidth}
	\includegraphics[height=1.75cm,width=\textwidth]{crosstransf/rf/17_g}\vfill
	\end{minipage}\vspace{1pt}

  \caption{Examples of aligned aerial/ground image pairs from our
dataset. (row 1) In the aerial images, north is the up direction.  In
the ground images, north is the central column. (row 2-4) Image
dependent receptive fields estimated by our algorithm as follows: 1)
fix ground locations $(y, x)$ (locations in squares); 2) select all
$(i, j)$ (locations in contours) with high $\tilde{F}(i,j,y,x,
S(I_a; \Theta_S))$ values.  Corresponding fields between the aerial image and
the ground image are shown in the same color.}

  \label{fig:dataset}
\end{figure}

We collect our training and testing dataset from the CVUSA
dataset~\cite{workman2015wide}. CVUSA contains approximately 1.5 million
geo-tagged pairs of ground and aerial images from across the
United States. We use the Google Street View panoramas of CVUSA as our
ground images. For each panorama, we also
download an aerial image at zoom level 19 from Microsoft Bing Maps 
in the same location. We filter out panoramas with no available 
corresponding aerial imagery. Using the camera's extrinsic
information, we then warp the panoramas to align with the
aerial images.  We also crop the panoramas vertically 
to reduce the portion of the sky and
ground pixels.  In total, we collected 35,532 image pairs for
training and 8,884 image pairs for testing. Some examples aerial/ground 
image pairs in our dataset are shown \figref{dataset}.

\subsection{Implementation Details}
\label{sec:details}

We implemented the proposed architecture using Google's TensorFlow
framework~\cite{abadi2016tensorflow}. We train our networks for 10
epochs with the Adam optimizer~\cite{kingma2014adam}. We enable batch
normalization~\cite{ioffe2015batch} with decay 0.9 in all convolutional and 
fully-connected layers (except for the output layers) to accelerate
the training process. Our implementation is available at \todo{URL withheld 
pending publication}.

The training procedure is as follows: for a given cross-view image
pair, $(I_a, I_g)$, we first compute for the ground semantic pixel
label: $I_g \rightarrow L_g$, using
SegNet~\cite{badrinarayanan2015segnet}. We then minimize the cross
entropy between $L_g$ and $T(A(I_a;\Theta_A);\Theta_T)$ with respect
to the model parameters, $\Theta_A$ and $\Theta_T$.  The resulting
architecture requires a significant amount of memory to output the
full final feature map, which would normally result in very small
batch sizes for GPU training.  Due to the PixelNet approach of using
interpolation to scale the feature maps, we are able to perform sparse
training. Instead of outputting the full-size feature map, we only
extract a dense grid of points, the resulting feature map is 17
$\times$ 17 $\times$ 4.  Despite this, at testing time,  we can provide
an aerial image and generate a full-resolution, semantically meaningful
feature map.

\section{Evaluation and Applications}
\label{sec:evaluation}
In this section, we will show that our network architecture can be
used in four different tasks: 1) weakly supervised semantic learning, 
2) aerial imagery labeling, 3) orientation regression and geocalibration, 
and 4) cross-view image synthesis. Additional qualitative results and 
the complete network structure used for cross-view image synthesis 
can be found in our supplemental materials.

\subsection{Weakly Supervised Learning}
\label{sec:transfer}

We trained our full network architecture (with randomly initialized
weights) to predict ground-level semantic labeling using the dataset
described in \secref{dataset}.  \figref{weakly} shows example output,
$L_a$, from the aerial image understanding CNN. This demonstrates that
the resulting network has learned to extract semantic features from an
aerial image, all without any manual annotated aerial imagery.

\begin{figure}
	\centering
	\includegraphics[width=.19\linewidth]{crosstransf/weakly/0000063_a} \hfill
	\includegraphics[width=.19\linewidth]{crosstransf/weakly/0000140_a} \hfill
	\includegraphics[width=.19\linewidth]{crosstransf/weakly/0000323_a} \hfill
	\includegraphics[width=.19\linewidth]{crosstransf/weakly/0000362_a} \hfill
	\includegraphics[width=.19\linewidth]{crosstransf/weakly/0001415_a}
  \newline
	\includegraphics[width=.19\linewidth]{crosstransf/weakly/0000063_p} \hfill
	\includegraphics[width=.19\linewidth]{crosstransf/weakly/0000140_p} \hfill
	\includegraphics[width=.19\linewidth]{crosstransf/weakly/0000323_p} \hfill
	\includegraphics[width=.19\linewidth]{crosstransf/weakly/0000362_p} \hfill
	\includegraphics[width=.19\linewidth]{crosstransf/weakly/0001415_p}
  \caption{Example outputs from our weakly supervised learning method
    on test images.  For each aerial image (top), we show the
    pixel-level labeling inferred by our model, which uses only noisy
    ground image segmentation as labels.  We visualize three classes:
    {\em road} (red), {\em vegetation} (green), and {\em man-made} 
    (blue).}
  \label{fig:weakly}
\end{figure}

While these results are compelling, they could be better with a higher
quality ground-image segmentation method.  The method we use,
SegNet~\cite{badrinarayanan2015segnet}, was trained on mostly urban
scenes, but many of our images are from rural and suburban areas.  The
end result is that certain classes are often mislabeled in the ground
imagery, including {\em dirt} and {\em building}.  In addition,
because the panoramas and aerial images were not captured at the same
time, we are unable to accurately model transient objects, such as
vehicles and pedestrians. All these factors make the dataset very
challenging for training. Given these limitations, it is, perhaps,
surprising that the resulting aerial image segmentation method works
so well.  In the following section, we show using this network as a
starting point for strongly supervised aerial image segmentation
outperforms two standard initialization methods.

\subsection{Cross-view for Pre-training}

We evaluate our proposed technique as a pre-training strategy for the
task of semantic-pixel labeling of aerial imagery.  Starting from
the optimal weights from the previous section, we finetune and
evaluate using the ISPRS dataset~\cite{rottensteiner2013isprs}.
This dataset contains 33 true orthophotos captured over
Vaihingen, Germany.  The ground sampling distance is 9 cm/px and there
are over 168 million pixels in total.  Ground truth is provided for 16
photos; each pixel is assigned one of six categories: {\em Impervious
surfaces, Building, Low vegetation, Tree, Car, and Clutter/background}.

\paragraph{Image Processing} Compared to the Bing Maps imagery we used
for pre-training, images in the ISPRS dataset are at a
different spatial scale and the color channels represent different
frequency bands (the R channel is actually a near infrared channel).
To ensure that the pre-trained network weights are appropriate for
the new dataset, we adjusted the scale and color channels as follows.
We first resize the ISPRS images to the equivalent of Bing Maps
zoom level 19.  We then label a pixel as vegetation if
$\frac{R}{R+G+B}$ is greater than 0.4. For each pixel labeled as
vegetation, we halve the R channel intensity and swap the R and G
channels.  The resulting images, shown in~\figref{isprs:dataset}, are
much closer in appearance to the Bing Maps imagery than the raw
imagery.

\begin{figure}
	%\centering
  \newlength{\abc}
  \setlength{\abc}{.325\linewidth}
	\includegraphics[width=\abc]{crosstransf/isprs/red}
	\includegraphics[width=\abc]{crosstransf/isprs/green}
	\includegraphics[width=\abc]{crosstransf/isprs/label}
  \caption{An example from the ISPRS dataset~\cite{rottensteiner2013isprs}. 
  (left) Near infrared image; (middle) The same image after pre-processing; 
  (right) Ground-truth annotation of the image.}
	\label{fig:isprs:dataset}
\end{figure}

\paragraph{Evaluation Protocol} We split the 16 annotated images into
training (images 5, 7, 11, 13, 15, 17, and 21), validation sets
(images 1 and 3) and testing (images 23, 26, 28, 30, 32, 37, and 40).
From each set we extracted a set of 224 $\times$ 224 subwindows
(respectively 82, 12, and 34 from training, validation, and testing
respectively).
%as our training images (crops overlap in the left and bottom edges of
%the patches). The validation and test set are evenly divided into 12
%and 34 non-overlapping crops, respectively.
We then compared performance with different numbers of training
images: 1, 2, 7, 20, 54, and 82. We evaluated the performance in terms
of the average precision for all pixels.  We ignore the
\textit{Cluster/background} pixels because of the low number of
assigned pixels.

\paragraph{Training and Testing} We used the same architecture with
the aerial feature extractor, $A(I_a; \Theta_A)$, defined in
~\secref{aerialnet}, to do the semantic labeling on ISPRS.  During
training, we use the Adam optimizer to minimize the cross entropy
between the network outputs and the labels.  We use a batch size of 8,
randomly sample 1,000 pixels per image for sparse training, and train
the network till convergence.  We run the validation set every 1,000 training
iterations and save the optimal network weights for testing.  During
testing, we sample all pixels on the image to generate the dense
labeling.

We experiment using three different initializations of the VGG16
convolutional layers and finetune the remaining layers of the network: 
1) Ours: initialize with model pre-trained using our framework;
2) Random: initialize using Xavier 
initialization~\cite{xavier2010understanding}; 
3) VGG16: initialize with model pre-trained on ImageNet.

Since the VGG16 model we used in this experiment is trained without
batch normalization, it may be less competitive. To achieve a fair
comparison, we turned off batch normalization in this experiment and
re-trained the network for 15 epochs to get the pre-trained model.

Our results (\figref{isprs:precisions}) show that finetuning from the 
VGG16 model performs poorly on the aerial image labeling task. We
think that the patterns it learned mostly from the ground image may
hinder pattern learning for aerial imagery. Our method outperforms
both of the other initialization strategies.  We also present the prediction
precision per class in~\tblref{isprs:precisions}. We highlight that our method
does better especially on the \textit{Building}, \textit{Low Vegetation}, and
\textit{Tree} classes, which can also be found in pre-training
annotations.

\begin{figure}
	\centering
	\includegraphics[width=.8\linewidth]{crosstransf/isprs/precisions}

  \caption{Performance comparison of different initialization methods
  on the ISPRS segmentation task. The $x$-axis is the number of
training images and the $y$-axis is average precision.}

	\label{fig:isprs:precisions}
\end{figure}

\begin{table}
  \centering
  \caption{Per-Class Precision on the ISPRS Segmentation Task}
  \begin{tabular}{@{}llcccccc@{}}
    \toprule
    \multirow{2}{*}{Class} & \multirow{2}{*}{Init.} & \multicolumn{5}{c}{Number 
    of training samples} \\
    \cline{3-8}
                   &       & 1 & 2 & 7 & 20 & 54 & 82\\
    \hline
    \multirow{3}{*}{\textbf{\specialcell{Imp.}}}
    & Ours & 0.67 & \textbf{0.74} & \textbf{0.63} & \textbf{0.64} & 0.66 & 
    0.64  \\ 
    & Random & \textbf{0.70} & 0.70 & 0.54 & 0.62 & 0.61 & \textbf{0.73}  \\ 
    & VGG16 & 0.60 & 0.55 & 0.55 & 0.61 & \textbf{0.70} & 0.59  \\ 
    \hline
    \multirow{3}{*}{\textbf{Bldg}} 
    & Ours & 0.72 & \textbf{0.76} & \textbf{0.76} & \textbf{0.80} & 0.75 & 
    \textbf{0.78}  \\ 
    & Random & 0.56 & 0.62 & 0.63 & 0.64 & \textbf{0.82} & 0.71  \\ 
    & VGG16 & \textbf{0.78} & 0.72 & 0.71 & 0.69 & 0.70 & 0.75  \\ 
    \hline
    \multirow{3}{*}{\textbf{\specialcell{Low.}}}
    & Ours & \textbf{0.37} & \textbf{0.43} & \textbf{0.51} & \textbf{0.65} & 
    \textbf{0.67} & \textbf{0.67}  \\ 
    & Random & 0.29 & 0.29 & 0.29 & 0.37 & 0.67 & 0.64  \\ 
    & VGG16 & 0.25 & 0.25 & 0.29 & 0.44 & 0.53 & 0.57  \\ 
    \hline
    \multirow{3}{*}{\textbf{Tree}} 
    & Ours & \textbf{0.68} & \textbf{0.54} & \textbf{0.71} & \textbf{0.71} & 
    \textbf{0.74} & 0.74  \\ 
    & Random & 0.42 & 0.46 & 0.49 & 0.56 & 0.71 & 0.69  \\ 
    & VGG16 & 0.36 & 0.44 & 0.50 & 0.55 & 0.65 & \textbf{0.74}  \\ 
    \hline
    \multirow{3}{*}{\textbf{Car}} 
    & Ours & \textbf{0.13} & \textbf{0.46} & \textbf{0.67} & \textbf{0.48} & 
    \textbf{0.48} & 0.49  \\ 
    & Random & 0.05 & 0.08 & 0.10 & 0.25 & 0.45 & \textbf{0.57}  \\ 
    & VGG16 & 0.05 & 0.11 & 0.20 & 0.20 & 0.25 & 0.23  \\ 
    \bottomrule
    \end{tabular}
  \label{tab:isprs:precisions}
\end{table}

\subsection{Cross-view for Geocalibration}

%estimated our algorithm is capable to estimate the orientation and
%even the accurate location of the ground-level camera.

We show how the ground-level feature maps we estimate from aerial
imagery can be used to estimate the orientation and location of a
ground image.  We show quantitative results for the orientation
estimation task and qualitative results for simultaneous orientation
and location estimation. We use the following datasets for all
experiments:

\begin{figure*}
  \setlength{\aheight}{63pt}
  \setlength{\gwidth}{52.44pt}
  \centering

% Cityscapes
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/261_g}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/261_gt}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/261_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/cityscapes/261_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/448_g}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/448_gt}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/448_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/cityscapes/448_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/784_g}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/784_gt}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/784_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/cityscapes/784_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/678_g}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/678_gt}
  \includegraphics[width=\textwidth]{crosstransf/cityscapes/678_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/cityscapes/678_pred}

% BingMap
\vspace{5pt}
  \setlength{\aheight}{63pt}
  \setlength{\gwidth}{53.25pt}
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/38_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/38_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/38_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/38_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/57_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/57_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/57_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/57_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/62_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/62_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/62_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/62_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/orient/41_g}
  \includegraphics[width=\textwidth]{crosstransf/orient/41_gt}
  \includegraphics[width=\textwidth]{crosstransf/orient/41_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/orient/41_pred}

  \caption{Qualitative results of orientation predictions on Cityscapes
dataset (top) and CVUSA (bottom). The $I_g$, $L_g$ and
$L_{g'}$ are stacked vertically on the left side of the aerial image.
We visualize three classes on the labels:
    {\em road} (red), {\em vegetation} (green), and {\em man-made} 
    (blue).
The discrete PDFs of the ground camera orientation are visualized with
red arrows, whose lengths indicate the magnitudes. In the CVUSA
results, the ground truth (green) and the optimal prediction (blue)
are also shown with the orientation PDF. The last prediction result is
a typical failure case of our method, where the scene is symmetric
from the aerial point of view.}
  \label{fig:orient:qualitative}
\end{figure*}

\begin{figure}
	\centering
	\includegraphics[width=.7\linewidth]{crosstransf/orient/orient_err}
  \caption{Histogram of the orientation errors on the CVUSA dataset.}
	\label{fig:orient:err}
\end{figure}

\begin{itemize}

\item{\textbf{CVUSA:}} We use the test set introduced
in~\secref{dataset} to create this dataset, it has two parts for
orientation estimation and geocalibration, respectively.  For the
orientation regression task, we rotate the aerial image to a random
angle. For the fine-grained geocalibration experiment, we center-crop
the aerial image around a random $x,y$ offset, then rotate the image to a
random angle.  In both experiments, the heading direction of the
ground images are the same. We center crop a 224 $\times$ 448
cutout from each ground image as the query image.

\item{\textbf{Cityscapes:}}  The Cityscapes dataset~\cite{Cordts2016Cityscapes} 
is a recently released benchmark dataset designed to support the task
of urban scene understanding through semantic pixel labeling. It
consists of stereo video from 50 different cities and fine pixel-level
annotations for 5,000 frames and coarse pixel-level annotations for
20,000 frames.

\end{itemize}

\paragraph{Orientation Estimation}

For this task, we assume the location and focal length of the ground
image, $I_g$, is known but the orientation is not. The intuition
behind our method is that the semantic labeling of the ground image
will be most similar to the feature map of the aerial image at the
actual orientation.  For a query ground image, $I_g$, the first step
is to download the corresponding aerial image, $I_a$.  We then infer
the semantic labeling of the query image, $I_g \rightarrow L_g$, and
predict the ground image label from the aerial image using our learned
network, $I_a \rightarrow L_{g'}$.  We assign an energy to each
possible orientation by computing the cross entropy between $L_g$ and
$L_{g'}$ in a sliding window fashion across all possible orientations.
We select the orientation with the lowest energy.  We present sample results in 
\figref{orient:qualitative} and a histogram of the orientation errors on the 
CVUSA dataset in \figref{orient:err}.

%nbj: not sure why we need this: 
%We adopt a simple sliding window to estimate the PDF of the ground
%image orientation which we assume follows the form of Gibbs
%distribution.

\paragraph{Fine-grained Geocalibration}

For this task, we assume that we know the focal length of the camera
and have a rough estimate of the camera location (i.e., with 100
meters).  We extract 256 $\times$ 256 aerial images from the area
around our rough estimate and extract the corresponding ground-level
feature maps.  We apply our orientation estimation procedure to each
feature map.  The result is a distribution over orientations for each
location.  \figref{geocali:cali} shows several example results,
including the most likely direction for each location, as well as the
most likely location and orientation pair.

\begin{figure*}
  \setlength{\aheight}{93pt}
  \setlength{\gwidth}{60.65pt}
  \centering
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/geocali/186_im_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/186_lb_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/186_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/geocali/186_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/geocali/271_im_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/271_lb_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/271_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/geocali/271_pred}
  \hfill
  \begin{minipage}[b]{\gwidth}
  \includegraphics[width=\textwidth]{crosstransf/geocali/305_im_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/305_lb_g}
  \includegraphics[width=\textwidth]{crosstransf/geocali/305_a2g}
  \end{minipage}
  \includegraphics[height=\aheight]{crosstransf/geocali/305_pred}
  \hfill

  \caption{Fine-grained geocalibration results on CVUSA. (left) From
top to bottom are the $I_g$, $L_g$, and $L_{g'}$ respectively.  We
visualize three classes on the labels: {\em road} (red), {\em
vegetation} (green), and {\em man-made} (blue).  (right) Orientation
flow map (red), where the arrow direction indicates the optimal
direction at that location and length indicates the magnitude. We also
show the optimal prediction and the ground-truth frustums in blue and
green respectively.}
  \label{fig:geocali:cali}
\end{figure*}

\subsection{Synthesizing Ground Images from Aerial Images}

\begin{figure}
	\newlength{\awidth}
	\setlength{\awidth}{.279\linewidth}
	%\newlength{\gwidth}
	\setlength{\gwidth}{.67725\linewidth}
	%\newlength{\gspace}
	\setlength{\gspace}{4pt}
	\centering
	\includegraphics[width=\awidth]{crosstransf/gan/aerial1}\hspace*{\gspace}
	\begin{minipage}[b]{\gwidth}
	\includegraphics[width=\textwidth]{crosstransf/gan/ground1}\vfill
	\vspace*{\gspace}
	\includegraphics[width=\textwidth]{crosstransf/gan/ground1_pred}
	\end{minipage}\vspace*{\gspace}

	\includegraphics[width=\awidth]{crosstransf/gan/aerial2}\hspace*{\gspace}
	\begin{minipage}[b]{\gwidth}
	\includegraphics[width=\textwidth]{crosstransf/gan/ground2}\vfill
	\vspace*{\gspace}
	\includegraphics[width=\textwidth]{crosstransf/gan/ground2_pred}
	\end{minipage}\vspace*{\gspace}

	\includegraphics[width=\awidth]{crosstransf/gan/aerial3}\hspace*{\gspace}
	\begin{minipage}[b]{\gwidth}
	\includegraphics[width=\textwidth]{crosstransf/gan/ground3}\vfill
	\vspace*{\gspace}
	\includegraphics[width=\textwidth]{crosstransf/gan/ground3_pred}
	\end{minipage}\vspace*{\gspace}

	\includegraphics[width=\awidth]{crosstransf/gan/aerial4}\hspace*{\gspace}
	\begin{minipage}[b]{\gwidth}
	\includegraphics[width=\textwidth]{crosstransf/gan/ground4}\vfill
	\vspace*{\gspace}
	\includegraphics[width=\textwidth]{crosstransf/gan/ground4_pred}
	\end{minipage}

	\caption{Synthesized ground-level views. Each row shows an aerial image 
	(left), its corresponding ground-level panorama (top-right), and predicted 
	ground-level panorama (bottom-right).}
	\label{fig:gan}
\end{figure}

We propose a novel application to infer a ground image by using features 
extracted from our network. We begin by describing our network structure and 
then show qualitative results for different generated ground-level scenes.

Our network architecture is based on the deep, directed generative model 
proposed by Kim \etal~\cite{kim2016deep}. Their model consists of two parts: a 
deep generator, $G$, which generates images that try to minimize a deep energy 
model, $E$. A low energy implies the image is real and high energy implies the 
image is fake. The architecture and training methods are inspired by generative 
adversarial networks~\cite{goodfellow2014generative}, however it provides a 
energy-based formulation of the discriminator to address common 
instabilities of adversarial training.

A complete description of the architecture used to design the deep generator 
and deep energy model is provided in our supplemental materials. We begin by 
extracting an 8 
$\times$ 40 $\times$ 512 cross-view feature map, $f$, that has been learned to 
relate an aerial and ground image pair.  The generator is given $f$ 
along with random noise, $z$, as input. The generator outputs a 64 $\times$ 320 
panorama, $I_{\hat{g}}$, that represents the predicted ground image. The 
cross-view feature, predicted panorama, and the ground truth panorama, $I_g$, 
are then passed into the energy model which returns an energy function,

\setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
\setlength{\abovedisplayskip}{0pt} \setlength{\abovedisplayshortskip}{0pt}
\begin{equation*}
E_\Theta (\mathbf{f}, \mathbf{I_{g^*}})) = \frac{1}{\sigma^2} \mathbf{f}^T 
\mathbf{f} - 
\mathbf{b}^T \mathbf{f} \\ - \sum_{i}^{} \mathrm{log}(1 + e^{W_i^T 
\mathbf{I_{g^*}} + b_i}),
\end{equation*}

\noindent similar to the free energy of a Gaussian Restricted Boltzmann Machine 
(RBM). Batch normalization~\cite{ioffe2015batch} is applied in every layer of 
both models, except for the final layers. ReLU activations are used throughout 
the generator and Leaky ReLU, with leak parameter $\alpha = 0.2$, are used in 
the energy model. The models are updated in an alternating fashion, where the 
generator is updated twice for every update of the energy 
model. Both the generator and energy model are optimized using the Adam 
optimizer, with moment parameters $\beta_1 = 0.5$ and 
$\beta_2 = 0.999$. We train using batch sizes of 32 for 30 epochs.

Example outputs generated by our network are shown in \figref{gan}. Each row 
contains an aerial image (left), its respective ground panorama (top-right), 
and our prediction of the ground scene layout (bottom-right), which would 
ideally be the same as its above image. The network has learned the most common 
features, such as roads and their orientations, as well as trees and grass. 
However, it has difficulty hallucinating buildings and the sky, which is likely 
caused by highly variable appearance factors.

We note that the resolution of the synthesized ground-level panoramas is much 
lower than the original panorama, however adversarial generation of 
high-resolution images is an active area of research. We expect that in the 
near future we will be able to use our learned features in a similar manner to 
generate full-resolution panoramas. Additionally, algorithmic improvements to 
our ground image segmentation method would provide more photo-realistic 
predictions.

\section{Conclusion}

We introduced a novel strategy for using automatically labeled ground
images as a form of weak supervision for learning to understand aerial
images. The key is to simultaneously learn to extract features from
the aerial image and learn to map from the aerial to the ground image.
We demonstrated that by using this process we are able to
automatically extract semantically meaningful features from aerial
imagery, refine these to obtain more accurate pixel-level labeling of
aerial imagery, estimate the location and orientation of a ground
image, and synthesize novel ground-level views.  The proposed
technique is equally applicable to other forms of imagery, including
NIR, multispectral, and hyperspectral. For future work, we plan to
explore richer ground image annotation methods to explore the limits
of what is predictable about a ground-level view from an aerial view.

### 2018-06-18 chapters/whenwhere/paper.tex
add whenandwhere

\section{Introduction}

Outdoor images often contain sufficient visual information to
understand geographic information about the scene, such as where the
image was captured. Developing effective algorithms for this task has
received significant attention for many years~\cite{im2gps,planet}.
The appearance of an outdoor scene can also change rapidly. These
changes are often due to fleeting, or transient, attributes such as
lighting and weather conditions, that dramatically affect the visual
perception of an environment. For instance, consider a scene that
changes from sunny and pleasant to rainy and brooding in mere minutes.
Several methods have been proposed for automatically understanding and
extracting these subtle characteristics from
imagery~\cite{patterson2012sun,lu2014two,laffont2014transient,baltenberger16transient}.
Estimating these types of transient attributes has importance in a
number of fields, including: environmental
monitoring~\cite{wang2013observing,fedorov2014snow}, as a
pre-processing step for
calibration~\cite{jacobs13cloudcalibration,workman2014rainbow}, and
enabling semantic browsing of large photo
collections~\cite{jacobs07amos,laffont2014transient}. Our work fuses these two
research areas by learning to estimate geo-temporal image features,
which are related to when and where an image was captured.

Recently, a significant amount of work has explored how sources of
supervision beyond manual annotation can be used to learn useful
representations of images. In general, collecting manual annotations
for millions, or perhaps billions, of images is prohibitively
expensive. As Doersch summarizes~\cite{doersch2016supervision}, ``The
idea is that, given the right task, the computer can learn on its own
to represent useful semantic properties of the visual world.'' Such
learning tasks are often referred to as {\em pretext tasks}; they
serve as an intermediary target for learning the intended
representation.  For example, Doersch et
al~\cite{doersch2015unsupervised} show how spatial context can be used
as a supervisory signal in order to learn a visual representation for
object discovery. Similarly, Pathak et al.~\cite{pathak2016context}
use context-based pixel prediction for pre-training a representation
for classification, detection, and segmentation tasks. We extend this
line of work by using time and location context to learn useful
features from a large corpus of imagery.

Our work makes the following visual assumptions about the world.
First, that photographs provide a direct source of context regarding
the conditions under which they were captured. For example, the time
of day that an image is captured is directly related to the brightness
of the image (i.e., light to dark), season can indicate the expected
weather conditions or how people are dressed, and location can provide
evidence about anticipated styles such as architecture. Second, these
context signals are hard to extract from an image, are potentially
noisy (e.g., snow in April), and can be indicated by multiple sources
(snow on the ground, people wearing heavy coats). These assumptions
motivate our method which integrates image appearance, time, and
location, the latter of which are typically recorded automatically by
the imaging device.

In our approach, we explicitly model the relationship between the
image, its geographic location, and the time of capture. We propose a
novel convolutional neural network architecture that implicitly learns
how to extract geo-temporal features from the imagery by optimizing for
a set of location and time estimation tasks. Specifically,
we structure our network to jointly learn feature representations for
three related spaces: images, time, and location. To accomplish this,
each representation, or combination of representations, is used to
predict held out information. For example, the image representation
and location representation (or the combination of both) are used to
learn to predict when an image was captured. In total, three representations 
are learned using four classification tasks.  We optimize all representations and tasks simultaneously, in an end-to-end fashion.

The main contributions of this work are: 1) a novel approach for
learning geo-temporal image features from a large corpus of imagery
without requiring image-level manual annotations; 2) an evaluation of
the learned features on the task of transient attribute estimation,
where our features outperform those from a network pre-trained using
the strongly supervised ImageNet dataset~\cite{ILSVRC15}; 3) an
evaluation of the accuracy of our learned estimators, highlighting the
value of additional context; and 4) a novel location estimation method
that uses the task of time estimation to localize a static camera.

\section{Related Work}

Image localization, or estimating where an image was captured, is an
important problem in the vision community. Typically, the problem is
formulated as image retrieval using a reference database of
ground-level images~\cite{im2gps} or overhead
images~\cite{lin2015learning,workman2015geocnn,workman2015localize}
with known location.  Other methods have been proposed which take
advantage of photometric and geometric properties such as sun
position~\cite{lalonde2010sun,workman2014rainbow}, and many other
cues. More recently, Weyand et al.~\cite{planet} proposed to directly
predict the geographic location of a single image using a deep
convolutional neural network by classifying the query image into a set
of spatial bins. This style approach is a special case of our proposed
network.

Other work has explored how to estimate the time that an image was
captured. Salem et al.~\cite{salem2016dating} demonstrate that human
appearance, including clothing and hairstyle, is a useful cue for
dating images. Matzen and Snavely predict timestamps for photos by
matching against a time-varying reconstruction of a scene.  Volokitin
et al.~\cite{eth_biwi_01292} use representations extracted from CNNs
to estimate ambient temperature and time of year for outdoor images.
In our work we explore how location and time estimation can be used
as tasks for learning geo-temporal features.

Attribute-based representations have become popular in outdoor scene
understanding to help describe how the appearance of a scene changes
over time. Laffont et al.~\cite{laffont2014transient} introduced a taxonomy
of 40 transient attributes that describe intra-scene variations along
with methods for identifying the presence of such attributes in an
image. Using this dataset, Baltenberger et
al.~\cite{baltenberger16transient} introduce methods for estimating
the presence of transient attributes using convolutional neural
networks. Jacobs et al.~\cite{jacobs07amos} demonstrate
that principle component analysis, when applied to webcam imagery,
results in a decomposition that is closely related to natural changes
in the scene, including the time of day, local weather conditions, and
human activity. Similarly, a body of work has sought understand local
weather conditions~\cite{islam13webcamweather,lu2014two}. Many studies
have shown that these types of transient attributes can be useful for
image and camera localization
tasks~\cite{jacobs07geolocate,baltenberger16transient}.

Recent work has explored the use of self-supervision (sometimes
referred to as unsupervised learning or pretext tasks) for training
deep neural networks that capture useful visual
representations~\cite{doersch2015unsupervised,pathak2016context}. For
example, Zhang et al.~\cite{zhang2016colorful} show how image
colorization (synthesizing colors for a grayscale image) is a powerful
pretext task for learning visual representations. Pathak et
al.~\cite{pathak2017learning} exploit low-level motion-based grouping
cues for unsupervised feature learning. These methods typically
exploit some known quantity of the data (e.g., pixel color values) to
avoid expensive manual annotation. As a byproduct, a useful visual
representation is learned. In our work, we consider two novel pretext
tasks, time and location estimation. Our work is most similar to Li
and Snavely~\cite{li2018learning}, who propose an approach for
learning intrinsic images by observing image sequences with varying
illumination over time. While their targets are reflectance and
shading images of the scene, we focus on location and time.

\section{Estimating Geo-Temporal Image Features}
\label{sec:when-and-where}

\begin{figure}[t]
  \centering

  \includegraphics[width=.7\linewidth]{whenwhere/architecture.pdf}
  \caption{An overview of the proposed network architecture. Our
  approach learns mid-level feature representations for time (orange),
  location (blue), and image appearance (green) by optimizing for a set
  of conditional time and location estimation tasks.}

  \label{fig:architecture}
\end{figure}

We propose a neural network architecture for learning geo-temporal
features from images by optimizing for a set of
location and time estimation tasks. An overview of the proposed
architecture is shown in \figref{architecture}. Our network takes
three inputs: an image, $I$, the time the image was captured, $t$, and
the location of capture, $l$. Each input is independently processed by
a {\em context network} to extract mid-level features. Then, pairs of
these features are used by {\em estimator networks} to predict
distributions over time or location.

\subsection{Context Networks}

We use three {\em context networks}: a temporal context network,
$C_T(t)$; a location context network, $C_L(l)$; and an image context
network, $C_I(I)$. The output of each context network is a 128
dimensional feature with a sigmoid activation function. 
%
For the temporal context network, we parameterize the input timestamp
using a one-hot encoding of month and hour of day, for a total of $12
\times 24$ dimensions.  This encoding is flattened and passed to
$C_T(t)$, which consists of three fully-connected layers (with 256,
512, and 128 channels respectively), the first two with ReLU
activations. 
%
For the location context network, we parameterize the geographic
location, $l$, using standard 3D ECEF coordinates, which we normalize
by the Earth's radius. Other than a different input, the location
context network is identical to the temporal context network. 
%
For the image context network, we use the {\em InceptionV2}
architecture~\cite{szegedy2016rethinking}, up to the last global
average pooling layer, to extract features. We flatten the output
feature map and append the same structure as the other context
networks.

\subsection{Estimator Networks}

The output of the context networks are used as input to four different
estimator networks:
\begin{compactitem}

  \item {\em Location Estimator}, $P(l|(C_I(I))$, which predicts
    location using only image features;

  \item {\em Time Estimator}, $P(t|C_I(I))$, which predicts time using
    only image features;

  \item {\em Time-conditioned Location Estimator}, $P(l|(C_I(I),C_T(t))$, which predicts
    location using features from the image and the known capture time;

  \item {\em Location-conditioned Time Estimator}, $P(t|C_I(I),C_L(l))$, which
    predicts time features from the image and the known geographic
    location.

\end{compactitem}
%
Aside from different output size and activations, the estimator
networks have the same structure as the context networks. We
discretize the output space for location and time, representing the
probability as a categorical distribution (softmax activation). For
location, we use $37 \times 72$ equal-angle lat./long.\ bins.  For
time, we use $12 \times 24$ ``month $\times$ hour'' bins.

\subsection{Implementation Details}

We randomly initialize the {\em InceptionV2} network using the
standard strategy~\cite{szegedy2016rethinking}.
We initialize all other network weights randomly using Xavier
initializer~\cite{glorot2010understanding} and
simultaneously optimize them during training. For each
estimator network, we have a cross entropy loss.  We minimize the sum
of these using the {\em Adam} optimizer \cite{kingma2014adam}
($\beta_1 = 0.9$ and $\beta_2 = 0.999$). We use a learning rate policy
that starts from 0.001 and decreases by half every $50k$ iterations.
For regularization, we apply weight decay with rate of 0.0001. We
train the proposed network for $2.5M$ iterations with batch size 32.
We apply batch
normalization~\cite{inception15} on every layer except the last (for
both context and estimator networks).  The input images are scaled to
$[-1,1]$ and augmented by a random crop to the size of $224 \times
224$. We use Greenwich Mean Time (GMT) for all timestamps.

\section{Experiments}

We evaluate the context networks and estimator networks on various
datasets, visualize specific features in the image context networks,
and show that the image context features have strong correlations with
transient image attributes.

\subsection{Training and Evaluation Datasets}

We use four main datasets to evaluate our approach.  The {\em AMOS}
dataset refers to a subset of the AMOS
database~\cite{jacobs07amos}, which is a collection of over a billion
images captured from public outdoor webcams around the world.  For our
experiments, we use a subset of images: only from cameras with
high-accuracy geolocation and images captured between 2002 to 2017.
This resulted in images from 12,193 webcams from which we held-out 231
for testing. Each image has a timestamp recorded by the image
collection process.  The {\em YFCC} dataset refers to a subset of
the Yahoo 100 million dataset~\cite{yfcc100m}, only including
geotagged images from smart phones.  We restricted the dataset to
smart phone images since we found that non-phone images often had
inaccurate timestamps.  We filter out indoor images using the {\em
Places} network~\cite{zhou2017places}. This results in a training set
of 892,662 images and a test set of 170,994 images.  The
{\em Hybrid} dataset refers to a combination of the {\em AMOS} and
{\em YFCC} training sets (equally sampling for each mini-batch).  The
{\em TA} dataset refers to the Transient Attributes
Dataset~\cite{laffont2014transient}, which contains 8,571 images, each
manually annotated with $40$ transient attributes, such as sunny and
cloudy.

\subsection{Understanding the Image Context Representation}

We conducted several experiments to relate image appearance to the
representation learned by the image context network.
%
To begin, we examined images that correspond with extremal
activations.  For this experiment, we used 10,000 images randomly
sampled from the {\em YFCC} dataset and 7,732 images covering the year of 2015 from 
one camera (ID: 4308) in {\em AMOS} dataset. For each neuron of 
the image context representation, we selected the $10$ images that result in 
the highest activation from the two different sets of images.  \figref{activation} 
shows a montage of images for three neurons.  The neurons appear to capture
semantically meaningful attributes, such as daylight, rainy, and winter. 
%
Similarly, we selected two neurons and visualized their signal over
time using images from a static webcam. \figref{signal} shows how
scene appearance changes are related to the image context features.
For the example shown, it appears that these neurons are related to
daylight and fogginess. 
%
These experiments provide evidence that the mid-level representation
captured by the image context network are related to static and
transient scene attributes.

\begin{figure*}[t] 
  \centering

  \setlength\tabcolsep{2pt}
  \renewcommand{\arraystretch}{0}
  \begin{tabular}{lccc}
    \vspace {0.1cm}
    \raisebox{.3\height}{\rotatebox{90}{\em YFCC}} &
    \includegraphics[width=.30\linewidth]{whenwhere/activation/yfcc/max_0.png} &
    \includegraphics[width=.30\linewidth]{whenwhere/activation/yfcc/max_70.png}&
    \includegraphics[width=.30\linewidth]{whenwhere/activation/yfcc/max_123.png}\\
    \raisebox{-.05\height}{\rotatebox{90}{{\em AMOS:4308}}} &
    \includegraphics[width=.30\linewidth]{whenwhere/activation/cam_4308/max_0.png} &
    \includegraphics[width=.30\linewidth]{whenwhere/activation/cam_4308/max_70.png} &
    \includegraphics[width=.30\linewidth]{whenwhere/activation/cam_4308/max_123.png}

  \end{tabular}

  \caption {Relating image appearance to the image context
    representation by visualizing the images that have the highest
    activation at three different neurons.}

  \label{fig:activation}
\end{figure*}

\begin{figure}
  \centering

  \includegraphics[width=.98\textwidth]{whenwhere/timeline/timeline}

  \caption{The time series of two neurons for a week of webcam
  imagery, with images showing the scene at various points. It appears
  that the top neuron is related to the diurnal cycle and the bottom
  is related to fogginess.}

  \label{fig:signal}
\end{figure}

\subsection{Analyzing Feature Correlation with Transient Attributes}

To analyze quantitatively how much our model learns about transient
attributes, we compute the cross correlations between a mid-level
representation of the image context network and the corresponding
transient attribute labels of all test images in the {\em TA} dataset.
As a baseline, we compare to features of the same architecture trained
for ImageNet~\cite{inception15} classification and features sampled
uniformly at random.  We select the feature
from the last pooling layer ({\em AvgPool\_1a\_7x7}), which is the
deepest layer that this model and ours share in common.
%
We compute the cross correlation scores between the feature and the
transient attribute scores of each image, resulting in a $1024 \times
40$ cross correlation matrix, $M$, where the element $m_{ij}$ is the
cross correlation score between the $i$-th feature channel and the
$j$-th transient attribute.
%
\figref{correlation} shows, for each
transient attribute, the maximum absolute correlation score
over all feature channels. We observe that our proposed method learns
features that are more correlated to the transient attributes (
$\bar{\rho} = 0.414$) than the ImageNet network ($\bar{\rho} =
0.281$).

\begin{figure}
  \centering

  \includegraphics[width=\columnwidth]{whenwhere/correlation/hybrid}

  \caption{Cross-correlation scores between transient attributes and
  three representations. For each attribute, we show the peak
  correlation score. For a majority of attributes our proposed
  representation is more highly correlated than the ImageNet
  baseline.}

  \label{fig:correlation}
\end{figure}

\subsection{Comparing Mid-Level Features for Transient Attribute Estimation}

\begin{figure}
  \centering

  \includegraphics[width=.47\columnwidth]{whenwhere/pretrain/mse_inter}
  \includegraphics[width=.47\columnwidth]{whenwhere/pretrain/mse_intra}

  \caption{Comparing mid-level features for transient attribute
  estimation. (left) Initializing from the weights of our proposed
  approach versus a network trained for image classification and a
  random baseline. (right) Initializing from our method, trained on
  different datasets.}

  \label{fig:pretrain}
\end{figure}

The previous experiment showed that the image context network is
capturing mid-level features correlated with transient attributes. In
this section, we explore the ability of this representation for
directly estimating transient attributes. Similar to the previous
experiment, we truncate our model at the last pooling layer (in order
to compare versus alternative initialization strategies), and add a
final two-layer MLP with 40 outputs corresponding to the 40 transient
attributes in the {\em TA} dataset. We train this
network, initializing from the weights of models trained for different
tasks, including variants of our method trained on the {\em AMOS}, {\em YFCC}, and
{\em Hybrid} datasets. During training, the MLP portions are randomly
initialized while the earlier layers are frozen. We evaluate the
average mean squared error (MSE) for the test set every 500 iterations
(batch size 32). \figref{pretrain} shows the performance comparison
among different mid-level features, including ImageNet and randomly
initialized {\em InceptionV2}. Our features are superior to
all baselines and perform best when learned using the {\em Hybrid} dataset.

\subsection{Application: Image Localization}

There are two image localization formulations that our network
architecture enables. The straightforward approach is to use the
location estimator (or the time-conditioned variant) to generate a
probability distribution over a discrete set of location bins. An
alternative approach is to optimize for a continuous location estimate
by minimizing the loss of the location-conditioned time estimator
network.

\noindent \textbf{Discrete Localization} Given an input image, $I$, we
evaluate the location estimator $P(l|C_I(I))$ and the time-conditioned
location estimator $P(l|C_I(I),C_T(t))$, which requires a timestamp,
$t$. We trained our model on each dataset and perform quantitative
evaluation using the test images from {\em AMOS} and {\em YFCC},
separately. We use the latitude/longitude center of the maximal bin as
our location estimate.  The results of this experiment are presented
in \figref{image_localization}.  We observe that the time-conditioned
location estimator is superior in both cases. We also conclude that
our model performs better if trained on the same imagery source with
the test set, and training the network with the {\em Hybrid} dataset
is competitive on both test sets.

\begin{figure}
  \centering

  \begin{subfigure}[b]{0.47\linewidth}
    \includegraphics[width=\linewidth]{whenwhere/image_localization/amos}
    \caption{Test set: {\em AMOS}}
  \end{subfigure}
  \begin{subfigure}[b]{0.47\linewidth}
    \includegraphics[width=\linewidth]{whenwhere/image_localization/yfcc}
    \caption{Test set: {\em YFCC}}
  \end{subfigure}

  \caption{Quantitative evaluation of localization performance shown
  as a cumulative distance error plot for the {\em YFCC} dataset.}

  \label{fig:image_localization}
\end{figure}
%

\noindent \textbf{Continuous Localization} In this formulation, we use
the location-conditioned time estimator, $P(t|C_I(I),C_L(l))$, to
optimize for a continuous location estimate.  Given the known image
capture time $t^*$, the idea is that the true location should result
in a low value for the loss associated with the estimator, $\ell_t =
\phi(P(t|C_I(I),C_L(l)), t^*)$, where $\phi(\circ,\circ)$ is the
cross-entropy loss. Therefore, we can produce a location estimate by
optimizing the location, $l$, with respect to $\ell_t$. Unfortunately,
an individual image does not typically yield a unique, or accurate,
location estimate using this method. However, if we sum the loss
across images captured at different times, we find that the minima of
the function becomes more distinct. \figref{webcam_localization} shows
several qualitative examples of this localization strategy on static
webcams, where darker colors correspond to more likely locations. We
can see that as additional images are included in the loss, the
uncertainty of the location prediction diminishes.

\begin{figure}
  \centering

  \setlength\tabcolsep{1pt}
  \renewcommand{\arraystretch}{0}
  \begin{tabular}{lcc}
    \raisebox{.5\height}{\rotatebox{90}{\em 1 images}} &
    \includegraphics[width=.45\linewidth]{whenwhere/webcam_localization/5992-loss_maps_hybrid-1} &
    \includegraphics[width=.45\linewidth]{whenwhere/webcam_localization/8260-loss_maps_hybrid-1} \\
    %\raisebox{.5\height}{\rotatebox{90}{\em 5 images}} &
    %\includegraphics[width=.45\linewidth]{whenwhere/webcam_localization/8260-loss_maps_amos-5} &
    %\includegraphics[width=.45\linewidth]{whenwhere/webcam_localization/8260-loss_maps_hybrid-5} \\
    \vspace{.15cm}
    \raisebox{.5\height}{\rotatebox{90}{\em 20 images}} &
    \includegraphics[width=.45\linewidth]{whenwhere/webcam_localization/5992-loss_maps_hybrid-20} &
    \includegraphics[width=.45\linewidth]{whenwhere/webcam_localization/8260-loss_maps_hybrid-20} \\
    & {\em AMOS}: 5992 & {\em AMOS}: 8260 \\
  \end{tabular}

  \caption{Visualizing the time estimation loss for two cameras and
  varying number of images (darker is lower). The red arrows show the
  gradient and the green dot is the true location.}

  \label{fig:webcam_localization}
\end{figure}

\subsection{Application: Time Estimation}

% NBJ MAYBE this is a little wordy at the start

Using the time estimator and location-conditioned time estimator, our
network is able to estimate the capture time of a query image. These
estimators output a distribution in discrete 2D time space. To
evaluate our estimates, we compare the ground-truth capture time and
the marginal probabilities of our predictions on the {\em YFCC}
test set, and present the cumulative error plot in
\figref{time_diff_err}. We observe that including location is not
useful for  pinpointing the month. We suspect this is because most of
our imagery is in the northern hemisphere, and changing the location
within a hemisphere doesn't change the season. However, this is not
the case when estimating the hour.  To visualize this, we show in
\figref{hour-change} the impact of changing the location on the hour
estimate.  We compute the marginal hour distribution at different
latitudes and longitudes. When performing a sweep over latitude, we
fix the longitude value to be the ground truth (and vice versa). We
found that the longitude of the image corresponds more with the hour
prediction than the latitude, which matches expectations.

\begin{figure}
  \centering

  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{whenwhere/time_estimation/yfcc-month}
    \caption{Month Differences}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{whenwhere/time_estimation/yfcc-hour}
    \caption{Hour Differences}
  \end{subfigure}

  \caption{Quantitative evaluation of time estimation (month and hour)
  performance shown as a cumulative error plot for the {\em YFCC}
dataset. Both methods performance better than the random chance.}

  \label{fig:time_diff_err}
\end{figure}

\begin{figure}
  \centering

  \begin{subfigure}[b]{.215\linewidth}
    \includegraphics[width=\linewidth]{whenwhere/time_estimation/49-im}
    \caption{Input Image}
  \end{subfigure}
  \hspace{.25cm}
  \begin{subfigure}[b]{.33\linewidth}
    \includegraphics[width=\linewidth]{whenwhere/time_estimation/49-lat-hour}
    \caption{Latitude Changes}
  \end{subfigure}
  \begin{subfigure}[b]{.338\linewidth}
    \includegraphics[width=\linewidth]{whenwhere/time_estimation/49-lon-hour}
    \caption{Longitude Changes}
  \end{subfigure}

  \caption{Marginal probability of GMT predictions by varying latitude
  and longitude.}

  \label{fig:hour-change}
\end{figure}

\section{Conclusion}

When learning about the world using images, the location and time an
image was captured are useful pieces of metadata that are often
available, but commonly overlooked. We presented a novel architecture
for learning useful representations from images that takes advantage
of this metadata. We found that for the task of transient attribute
estimation, our method, despite being trained without manually
obtained image-level annotations, learned image representations that
outperform the representations learned using ImageNet, a rarely
achieved feat on a frequently used benchmark for unsupervised
representation learning tasks.

### 2018-06-18 chapters/fasthorizon/paper.tex
fix corrupt references
fasthorizon

@@
   \centering
-  \includegraphics[width=.48\linewidth]{fasthorizon/cover_hybrid_sampling}
-  \includegraphics[width=.48\linewidth]{fasthorizon/cover_segment_clusters}
+  \includegraphics[width=.4\linewidth]{fasthorizon/cover_hybrid_sampling}
+  \hfill
+  \includegraphics[width=.4\linewidth]{fasthorizon/cover_segment_clusters}
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{fasthorizon/homoIntersection}
+  \includegraphics[width=0.6\linewidth]{fasthorizon/homoIntersection}
   \caption{In homogeneous coordinates, lines (red lines) are defined
@@
  \centering
- \includegraphics[width=.48\linewidth]{fasthorizon/4horpdf}
- \includegraphics[width=.48\linewidth]{fasthorizon/68horpdf}
+ \includegraphics[width=.4\linewidth]{fasthorizon/4horpdf}
+ \hfill
+ \includegraphics[width=.4\linewidth]{fasthorizon/68horpdf}
 
@@
   \centering
-  \includegraphics[width=.92\linewidth]{fasthorizon/independent_subset}
+  \includegraphics[width=.82\linewidth]{fasthorizon/independent_subset}
 
@@
 optimal locations.  We optimize their locations to further minimize
-the objective function \eqref{obj}. We perform an EM-like algorithm
+the objective function \eqref{eq:obj}. We perform an EM-like algorithm
 to refine the vanishing point locations, subject to the constraint
@@
   \end{tabular}
-  \label{tab:parameters}
+  \label{tbl:parameters}
 \end{table}
@@
   \end{tabular}
-  \label{tab:contribution}
+  \label{tbl:contribution}
 \end{table}
@@
   \centering
-  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_ecd_hybrid}
-  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_ecd_uniform}
-  %
-  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_yud_hybrid}
-  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_yud_uniform}
+  \includegraphics[width=.4\linewidth]{fasthorizon/cnn_vs_nocnn_ecd_hybrid}
+  \includegraphics[width=.4\linewidth]{fasthorizon/cnn_vs_nocnn_ecd_uniform}
+  \\
+  \includegraphics[width=.4\linewidth]{fasthorizon/cnn_vs_nocnn_yud_hybrid}
+  \includegraphics[width=.4\linewidth]{fasthorizon/cnn_vs_nocnn_yud_uniform}
   \caption{Two images where horizon line estimates are much better with global context (left) than without (right).}
@@
   \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd5}
-  \includegraphics[width=0.0884\linewidth]{fasthorizon/montage_ecd1}
+  %\includegraphics[width=0.0884\linewidth]{fasthorizon/montage_ecd1}
   \includegraphics[width=0.1572\linewidth]{fasthorizon/montage_yud2}
@@
   \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd8}
+  \\
   \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd5_homo}
-  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd1_homo}
+  %\includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd1_homo}
   \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud2_homo}
@@
   \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud1}
-  \includegraphics[width=0.0867\linewidth]{fasthorizon/montage_ecd3}
+  %\includegraphics[width=0.0867\linewidth]{fasthorizon/montage_ecd3}
   \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud5}
@@
   \includegraphics[width=0.0867\linewidth]{fasthorizon/montage_ecd7}
+  \\
   \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud1_homo}
-  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd3_homo}
+  %\includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd3_homo}
   \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud5_homo}

### 2018-06-18 chapters/crosstransf/paper.tex
fix corrupt references
cross domain
fix duplicate label definition

@@
 	\centering
-	\includegraphics[width=\linewidth]{crosstransf/cartoon}
+	\includegraphics[width=.5\linewidth]{crosstransf/cartoon}
   \caption{We learn to predict the ground-image
@@
 
-	\label{fig:architecture}
+	\label{fig:architecture_cross}
 \end{figure*}
@@
 remainder of this section describes the particular choices we made for this 
-study. See~\figref{architecture} for a visual overview of the architecture.
+study. See~\figref{architecture_cross} for a visual overview of the architecture.
 
@@
 The network has three layers, with 128, 64 and 1 output channels
-respectively (refer to the lower part of~\figref{architecture}).  The
+respectively (refer to the lower part of~\figref{architecture_cross}).  The
 na\"{\i}ve approach can be considered a special case of this
@@
 \subsection{Dataset}
-\label{sec:dataset}
+\label{sec:dataset_cross}
 
@@
 
-  \label{fig:dataset}
+  \label{fig:dataset_cross}
 \end{figure}
@@
 training and 8,884 image pairs for testing. Some examples aerial/ground 
-image pairs in our dataset are shown \figref{dataset}.
+image pairs in our dataset are shown \figref{dataset_cross}.
 
@@
 fully-connected layers (except for the output layers) to accelerate
-the training process. Our implementation is available at \todo{URL withheld 
-pending publication}.
+the training process.
 
@@
 \section{Evaluation and Applications}
-\label{sec:evaluation}
 In this section, we will show that our network architecture can be
@@
 weights) to predict ground-level semantic labeling using the dataset
-described in \secref{dataset}.  \figref{weakly} shows example output,
+described in \secref{dataset_cross}.  \figref{weakly} shows example output,
 $L_a$, from the aerial image understanding CNN. This demonstrates that
@@
 	\centering
-	\includegraphics[width=.8\linewidth]{crosstransf/isprs/precisions}
+	\includegraphics[width=.7\linewidth]{crosstransf/isprs/precisions}
 
@@
     \end{tabular}
-  \label{tab:isprs:precisions}
+  \label{tbl:isprs:precisions}
 \end{table}
@@
 \begin{figure*}
-  \setlength{\aheight}{63pt}
-  \setlength{\gwidth}{52.44pt}
+  \setlength{\aheight}{53.55pt}
+  \setlength{\gwidth}{44.574pt}
   \centering
@@
 \vspace{5pt}
-  \setlength{\aheight}{63pt}
-  \setlength{\gwidth}{53.25pt}
+  \setlength{\aheight}{53.55pt}
+  \setlength{\gwidth}{45.2625pt}
   \begin{minipage}[b]{\gwidth}
@@
 	\centering
-	\includegraphics[width=.7\linewidth]{crosstransf/orient/orient_err}
+	\includegraphics[width=.5\linewidth]{crosstransf/orient/orient_err}
   \caption{Histogram of the orientation errors on the CVUSA dataset.}
@@
 \item{\textbf{CVUSA:}} We use the test set introduced
-in~\secref{dataset} to create this dataset, it has two parts for
+in~\secref{dataset_cross} to create this dataset, it has two parts for
 orientation estimation and geocalibration, respectively.  For the
@@
 \begin{figure*}
-  \setlength{\aheight}{93pt}
-  \setlength{\gwidth}{60.65pt}
+  \setlength{\aheight}{80pt}
+  \setlength{\gwidth}{52pt}
   \centering

### 2018-06-19 dissertation.tex
updates
update bibliography
change title

@@
 \usepackage{graphicx}
+\usepackage{paralist}
 \usepackage{amsmath}
@@
 \usepackage{soul}
+\usepackage{multirow}
 \usepackage{miscstyle}
 
-\newcommand{\disstitle}{Camera Geometry Detection and Use for Image
-Understanding}
+\newcommand{\disstitle}{Laveging Camera Geometric Information for
+Image Understanding}
 
@@
   Camera geometry is one of the fundamental elements in computer vision.
-  It plays an essential role in many applications like depth estimation
+  It plays essential roles in many applications like depth estimation
   and image mensuration. 
@@
 
-\inject{introduction}
-%\inject{mcmc}
+%\inject{introduction}
 %\inject{background}
+
+\inject{mcmc}
+\inject{fasthorizon}
+\inject{crosstransf}
+\inject{whenwhere}
+
 %\inject{discussion}

### 2018-06-19 dissertation.tex
Updates from ShareLaTeX
update title and abstract

--- 2018-06-15 dissertation.tex
@@
 \usepackage{soul}
+\usepackage{multirow}
 \usepackage{miscstyle}
 
-\newcommand{\disstitle}{Camera Geometry Detection and Use for Image
-Understanding}
-
 \usepackage[pdfauthor={Menghua Zhai},
-            pdftitle={\disstitle},
+            pdftitle={dissertation},
             bookmarks=false,
@@
 \author{Menghua Zhai}
-\title{\disstitle}
+\title{Lavaging Camera Geometry in Deep Neural Network Learning for Image Understanding}
 
 \abstract
-{
-  \SingleSpacing
-  Camera geometry is one of the fundamental elements in computer vision.
-  It plays an essential role in many applications like depth estimation
-  and image mensuration. 
-  %
-  In recent years, the rise of deep neural networks (DNNs) had changed
-  the game in many computer vision areas, their ability of abstracting
-  high-level semantic knowledges makes a lot of hard challenges
-  solvable. 
-  %
-  This thesis mainly explores the possibility of combining camera
-  geometry and DNNs. That is 1) Detecting camera geometry using DNNs,
-  and 2) Training DNNs with camera geometric information.  Our work
-  includes two research targets: The first part of this thesis focuses
-  on camera geometry detection with DNNs, and the rest of it
-  demonstrates how camera geometry can boost the learning of DNNs.
-  %
-  The primary contribution of this thesis is to explore the relation
-  between camera geometry and image semantics, and bridge the gap
-  between these two research domains, which provides us new ways for
-  both camera calibration and deep neural network training.
+{ \SingleSpacing
+In recent years, Deep Neural Networks (DNNs) have proven to be very
+successful in many computer vision areas. Among the most popular
+training techniques, supervised learning is wildly used for DNN
+training and easy to implement. However, successful supervised
+learning approaches are sensitive to the quality of data
+annotations. In some applications like overhead image segmentation and
+transient attributes estimation, data with noise-free annotation is
+either limited in quantity or technically difficult to acquire.
+In this thesis, we use domain adaptation and weak supervision to
+address this problem. Our methods focus on lavaging the camera
+geometric information to deal with the challenges caused by the lack
+of noise-free annotations during DNN training.
+Since the camera geometry affects the way that images manifest
+objects/scenes, it is possible to exploit the relation between the
+camera geometry and image semantics to understand images better.
+Our approach consists of two parts: 1) we explore new methods
+to estimate the camera geometric information from images, and 2) 
+we propose novel algorithms that lavages the camera geometry to train
+deep neural networks.
+The primary contribution of our thesis is to relate the camera
+geometry and image semantics through deep neural networks. Our
+discoveries can provide researchers new insights for both camera
+calibration and DNN training.
 }
@@
 \inject{introduction}
+%\inject{background}
+
 %\inject{mcmc}
-%\inject{background}
+%\inject{fasthorizon}
+%\inject{crosstransf}
+%\inject{whenwhere}
+
 %\inject{discussion}

### 2018-06-19 junk.tex
update title and abstract

@@
 camera calibration and network training.
+
+abstract
+Camera geometry is one of the fundamental elements in computer vision.
+It plays essential roles in many applications like depth estimation
+and image mensuration.
+%
+In recent years, the rise of deep neural networks (DNNs) had changed
+the game in many computer vision areas, their ability of abstracting
+high-level semantic knowledges makes a lot of hard challenges
+solvable.
+%
+This thesis mainly explores the possibility of combining camera
+geometry and DNNs. That is 1) Detecting camera geometry using DNNs,
+and 2) Training DNNs with camera geometric information.  Our work
+includes two research targets: The first part of this thesis focuses
+on camera geometry detection with DNNs, and the rest of it
+demonstrates how camera geometry can boost the learning of DNNs.
+%
+The primary contribution of this thesis is to explore the relation
+between camera geometry and image semantics, and bridge the gap
+between these two research domains, which provides us new ways for
+both camera calibration and deep neural network training.

### 2018-06-20 chapters/introduction/introduction.tex
first paragraph

@@
 
-%\begin{chapquote}{Walt Disney}
-  %``Of all of our inventions for mass communication, pictures still
-  %speak the most universally understood language.''
-%\end{chapquote}
+\begin{chapquote}{Alan Turing}
+  ``I propose to consider the question: Can machine think?''
+\end{chapquote}
 
-%%Outline:
-%\begin{itemize}
-  %\item sliver bullet and ``summer project'' story
-  %\item \st{Geometry is important.}
-  %\item \st{traditional method for geometry detection}
-  %\item \st{deep learning (gamer changer)}
-  %\item \st{geometry detection with deep learning}
-  %\item \st{geometry for deep learning training}
-  %\item \st{overhead images}
-%\end{itemize}
+Before the father of computer asked this question, creating
+machines that can think as human has been a dream through the human
+history. In the late 18th century, Hungarian inventor, Wolfgan von
+Kempelen, constructed an automatic machine called ``The Turk'' (also
+known as the ``Mechanical Turk'') to play a chess game. Though it
+proved to be an elaborate hoax, people's enthusiasm for machine
+intelligence lasts till today. As one of the core elements of
+intelligence, human vision plays an important role in our daily lives.
+In order to make computer understand images, scholars had put a lot of
+research efforts in the study of computer vision. In 1960s, MIT
+professor Dr. Marvin Minsky asked his undergraduates to develop
+programs that can recognize objects from a scene in their summer
+project~\cite{boden2006mind}. Half a century has passed, the question
+of this ``summer project'' still remains open.
 
-The study of understanding images has been around for half a century.
-A well known anecdote in computer vision community happened in 1960s,
-when the MIT professor Dr. Marvin Minsky assigned a summer programming
-project to his undergraduates, to recognize objects in a
-scene~\cite{boden2006mind}. 
-%
-Similar to the story of the famous ``Four Color Conjecture'', where
-one of the world's renowned mathematicians Dr. Hermann Minkowski
-claimed in his class that he was able to solve it before the class
-ends.  
-However, Not until one hundred years later since it was first
-proposed, the ``Four Color Conjecture'' has been stamped as theorem by
-the continuous efforts of several generations of talented
-mathematicians.  While on the other side, Dr. Marvin Minsky's summer
-program still remains open.
-
-It is not a trivial task for machines to understand images in general.
-To achieve this goal, researchers adopt a divide-and-conquer strategy,
-that is dividing image understanding into various sub-problems like
-object recognition, semantic segmentation, and pose estimation \etc.
-During past decades, a lot of methods are developed to solve
-these
+Understanding images is not trivial for machines.  To achieve this
+goal, researchers adopt a divide-and-conquer strategy, that is
+dividing image understanding into various sub-problems like object
+recognition, semantic segmentation, and pose estimation \etc.  During
+past decades, a lot of methods are developed to solve these
 sub-problems. Many of them adopted a bottom-up (\todo{citations})

### 2018-06-20 chapters/introduction/junk.tex
first paragraph

@@
 image from an aerial image.
+
+The study of understanding images has been around for half a century.
+A well known anecdote in computer vision community happened in 1960s,
+when the MIT professor Dr. Marvin Minsky assigned a summer programming
+project to his undergraduates, to recognize objects in a
+scene~\cite{boden2006mind}. 
+%
+Similar to the story of the famous ``Four Color Conjecture'', where
+one of the world's renowned mathematicians Dr. Hermann Minkowski
+claimed in his class that he was able to solve it before the class
+ends.  
+However, Not until one hundred years later since it was first
+proposed, the ``Four Color Conjecture'' has been stamped as theorem by
+the continuous efforts of several generations of talented
+mathematicians.  While on the other side, Dr. Marvin Minsky's summer
+program still remains open.

### 2018-06-21 chapters/introduction/introduction.tex
updates

@@
 
-Understanding images is not trivial for machines.  To achieve this
-goal, researchers adopt a divide-and-conquer strategy, that is
-dividing image understanding into various sub-problems like object
-recognition, semantic segmentation, and pose estimation \etc.  During
-past decades, a lot of methods are developed to solve these
-sub-problems. Many of them adopted a bottom-up (\todo{citations})
-workflow, where basic level cues play important roles
-(\todo{examples}). Among these basic cues, camera geometry is
-particularly useful for some computer vision tasks like facade
-detection, indoor layout estimation~\cite{ren2016coarse}.
+The ultimate goal of image understanding is to transfer the visual
+images into numerical or symbolic descriptions of the world
+that are helpful for other thought processes for decision making.
+In general, understanding images is not trivial for machines.
+For different application scenarios, researchers divide image
+understanding into different computer vision tasks. For example,
+pedestrian detection is essential to autonomous driving, and image
+retrieval to an image searching engine.
+
+Among algorithms that are developed to address these sub-tasks, deep
+neural networks (DNNs) rise as stars in recent years. Methods that
+uses DNNs achieve state-of-the-art performances in many computer
+vision areas (\todo{citations}). As parametric algorithms, deep neural
+networks require training for their parameters. Methods to train DNNs
+include supervised algorithms, unsupervised algorithms, and
+reinforcement learning. Supervised algorithms are the most popular and
+commonly applied in many computer vision areas, thanks to their good
+performances and the fact that they are easy to implement. However,
+supervised learning approaches are sensitive to the quality of data
+annotations. In some applications like overhead image segmentation and
+transient attributes estimation, data with noise-free annotation is
+either limited in quantity or technically difficult to acquire.
+In this thesis, we use domain adaptation and weak supervision to
+counter this drawback. Our methods focus on lavaging the camera
+geometric information to deal with the challenges caused by the lack
+of noise-free annotations during DNN training.
+The insight behind it is that the camera geometry affects the way that
+images manifest objects/scenes, it is possible to exploit the relation
+between the camera geometry and image semantics to understand images
+better.
+
+\sepline
 

### 2018-06-21 chapters/introduction/junk.tex
updates

@@
 program still remains open.
+
+To achieve this
+goal, researchers adopt a divide-and-conquer strategy, that is
+dividing image understanding into various sub-problems like object
+recognition, semantic segmentation, and pose estimation \etc.  During
+past decades, a lot of methods are developed to solve these
+sub-problems. Many of them adopted a bottom-up (\todo{citations})
+workflow, where basic level cues play important roles
+(\todo{examples}). Among these basic cues, camera geometry is
+particularly useful for some computer vision tasks like facade
+detection, indoor layout estimation~\cite{ren2016coarse}.

### 2018-06-21 chapters/introduction/introduction.tex
needs to re-consider the topic

@@
 either limited in quantity or technically difficult to acquire.
-In this thesis, we use domain adaptation and weak supervision to
-counter this drawback. Our methods focus on lavaging the camera
-geometric information to deal with the challenges caused by the lack
-of noise-free annotations during DNN training.
-The insight behind it is that the camera geometry affects the way that
-images manifest objects/scenes, it is possible to exploit the relation
-between the camera geometry and image semantics to understand images
-better.
+In this thesis, Our methods focus on lavaging the camera geometric
+information to deal with the challenges caused by the lack of
+noise-free annotations during DNN training. The insight behind it is
+that the camera geometry affects the way that images manifest
+objects/scenes, so it is possible to exploit the relation between the
+camera geometry and image semantics to understand images better.
 
-\sepline
+In computer vision, the geometric model of camera projection
 
-In the camera pin-hole model, camera geometry denotes the camera
-both intrinsic and extrinsic parameters. The intrinsic parameters
-encode the information of the camera itself such as focal length,
+In the camera pin-hole model, camera geometric parameters consists of
+the camera intrinsics and the extrinsics. The intrinsic parameters of
+a camera encode information of the camera itself such as focal length,
 principal point \etc; the extrinsic parameters are referred to as the

### 2018-06-22 dissertation.tex
updates
update title and abstract

@@
 \author{Menghua Zhai}
-\title{Lavaging Camera Geometry in Deep Neural Network Learning for Image Understanding}
+\title{Lavaging Geographic Information in Deep Neural Networks for Image Understanding}
 
@@
 training techniques, supervised learning is wildly used for DNN
-training and easy to implement. However, successful supervised
+training and easy to implement. However, supervised
 learning approaches are sensitive to the quality of data
@@
 either limited in quantity or technically difficult to acquire.
-In this thesis, we use domain adaptation and weak supervision to
-address this problem. Our methods focus on lavaging the camera
-geometric information to deal with the challenges caused by the lack
-of noise-free annotations during DNN training.
-Since the camera geometry affects the way that images manifest
-objects/scenes, it is possible to exploit the relation between the
-camera geometry and image semantics to understand images better.
+Our work focuses on lavaging the camera geographic information in
+DNN training to deal with the challenges caused by the lack of
+noise-free annotations.
+In this thesis, the contributions of the geographic information for
+DNN training lies in two folds: 1) The geo-calibrated imagery makes it
+possible to relate pairs of images from different image sources, and
+2) the geographic locations also indicate the appearances of the
+scene.
+By exploiting the relation between the geographic information and the
+scene appearances we are able to develop better approaches to train
+deep neural networks than full supervision when quality annotated
+data is limited.
 Our approach consists of two parts: 1) we explore new methods
@@
 }
-\keywords{ camera geometry, deep neural networks, computer vision}
+\keywords{geographic information, deep neural networks, computer vision}
 

### 2018-06-22 dissertation.tex
minor change

@@
 Our approach consists of two parts: 1) we explore new methods
-to estimate the camera geometric information from images, and 2) 
-we propose novel algorithms that lavages the camera geometry to train
-deep neural networks.
+to estimate the camera geographic information from images, and 2) 
+we propose novel algorithms that lavages the geographic information to
+train deep neural networks.
 The primary contribution of our thesis is to relate the camera
-geometry and image semantics through deep neural networks. Our
-discoveries can provide researchers new insights for both camera
-calibration and DNN training.
+geographic information and image semantics through deep neural
+networks. Our discoveries can provide researchers new insights for
+both camera calibration and DNN training.
 }

### 2018-06-25 chapters/introduction/introduction.tex
snapshot

--- 2018-06-21 chapters/introduction/introduction.tex
@@
 either limited in quantity or technically difficult to acquire.
-In this thesis, we use domain adaptation and weak supervision to
-counter this drawback. Our methods focus on lavaging the camera
-geometric information to deal with the challenges caused by the lack
-of noise-free annotations during DNN training.
-The insight behind it is that the camera geometry affects the way that
-images manifest objects/scenes, it is possible to exploit the relation
-between the camera geometry and image semantics to understand images
-better.
+In this thesis, Our methods focus on lavaging the camera geographic
+information to deal with the challenges caused by the lack of
+noise-free annotations during DNN training. The insight is
+that the camera geographic information encodes the semantic
+information because it is related to the appearances of
+the scenes.
+
+The process of estimating the camera geographic information is
+referred to as geo-calibration. The goal is to estimate the geographic
+location and the geo-orientation of the given camera. 
+Compared to the common camera calibration, geo-calibration focuses on
+calibrating the camera in the geographic coordinates.
+
+Geographic
+information reveals the scene appearances
 
 \sepline
-
-In the camera pin-hole model, camera geometry denotes the camera
-both intrinsic and extrinsic parameters. The intrinsic parameters
-encode the information of the camera itself such as focal length,
-principal point \etc; the extrinsic parameters are referred to as the
-external states of the camera, such as the camera poses and
-offset/location under some coordinate system. In this work, our study
-of the camera geometry mainly includes the extrinsic like camera pose
-and the geo-orientation/geo-localization of the camera.
 

### 2018-06-25 chapters/introduction/junk.tex
snapshot

@@
 detection, indoor layout estimation~\cite{ren2016coarse}.
+
+In the camera pin-hole model, camera geometric parameters consists of
+the camera intrinsics and the extrinsics. The intrinsic parameters of
+a camera encode information of the camera itself such as focal length,
+principal point \etc; the extrinsic parameters are referred to as the
+external states of the camera, such as the camera poses and
+offset/location under some coordinate system. In this work, our study
+of the camera geometry mainly includes the extrinsic like camera pose
+and the geo-orientation/geo-localization of the camera.

### 2018-06-25 dissertation.tex
title and abstract

--- 2018-06-19 dissertation.tex
@@
 \author{Menghua Zhai}
-\title{Lavaging Camera Geometry in Deep Neural Network Learning for Image Understanding}
+\title{Building a Probabilistic Model with Deep Neural Networks for Camera Geo-Calibration}
 
@@
 { \SingleSpacing
-In recent years, Deep Neural Networks (DNNs) have proven to be very
-successful in many computer vision areas. Among the most popular
-training techniques, supervised learning is wildly used for DNN
-training and easy to implement. However, successful supervised
-learning approaches are sensitive to the quality of data
-annotations. In some applications like overhead image segmentation and
-transient attributes estimation, data with noise-free annotation is
-either limited in quantity or technically difficult to acquire.
-In this thesis, we use domain adaptation and weak supervision to
-address this problem. Our methods focus on lavaging the camera
-geometric information to deal with the challenges caused by the lack
-of noise-free annotations during DNN training.
-Since the camera geometry affects the way that images manifest
-objects/scenes, it is possible to exploit the relation between the
-camera geometry and image semantics to understand images better.
-Our approach consists of two parts: 1) we explore new methods
-to estimate the camera geometric information from images, and 2) 
-we propose novel algorithms that lavages the camera geometry to train
-deep neural networks.
-The primary contribution of our thesis is to relate the camera
-geometry and image semantics through deep neural networks. Our
-discoveries can provide researchers new insights for both camera
-calibration and DNN training.
+Camera calibration is one of the primary task in computer vision.
+It plays an important role in applications like SLAM, image
+mensuration and indoor layout estimation. Current models for camera
+calibration are mostly deterministic, namely they output fixed
+solutions. However, applications built with graphic models favor
+probabilistic inputs, of which these deterministic calibration
+models are not capable.
+To address this problem, we propose a probabilistic model with deep
+neural networks (DNNs) for camera
+geo-calibration, providing more flexible inputs for applications that
+are interfaced camera calibration parameters. Compared to 
+traditional camera calibration, camera geo-calibration measures the
+camera extrinsic in geographic coordinates.
+Furthermore, our approaches also demonstrate that the geographic
+information is helpful for extracting/transferring high level
+features in DNN training.
+The primary contributions of our thesis include building a
+probabilistic model fro camera geo-calibration ,and relating the
+camera geographic information and image semantics through deep neural
+networks. Our discoveries can provide researchers new insights for
+both camera calibration and DNN training.
 }
-\keywords{ camera geometry, deep neural networks, computer vision}
+\keywords{geo-calibration, deep neural networks, computer vision}
 

### 2018-06-26 chapters/introduction/introduction.tex
minor change

@@
 In general, understanding images is not trivial for machines.
-For different application scenarios, researchers divide image
+Under different scenarios, researchers divide image
 understanding into different computer vision tasks. For example,
@@
 retrieval to an image searching engine.
+
+As one of the primary vision tasks, camera calibration plays an
+important role in many applications like indoor layout estimation and
+image mensuration. 
+In the camera pin-hole model, camera calibration parameters consist of
+the camera intrinsics and the extrinsic. The intrinsic parameters of
+a camera encode information of the camera itself such as focal length,
+principal point \etc; the extrinsic parameters are referred to as the
+external states of the camera, such as the camera poses and
+offset/location under some coordinate system. Specifically,
+camera geo-calibration consider the camera locations in the geographic
+coordinates.
+In this work, our study mainly focus on the extrinsic like camera pose
+and the geo-orientation/geo-localization of the camera.
+
+In current work of camera calibration, most algorithms are
+deterministic, which means they output fixed solutions. Applications
+that takes probabilistic inputs (especially for those which use
+graphic model) don't like it. To address this, we propose to build a
+probabilistic model for camera geo-calibration.
+
+\sepline
 

### 2018-06-26 dissertation.tex
minor change

@@
 The primary contributions of our thesis include building a
-probabilistic model fro camera geo-calibration ,and relating the
+probabilistic model for camera geo-calibration ,and relating the
 camera geographic information and image semantics through deep neural

### 2018-06-27 chapters/introduction/introduction.tex
more

@@
 that takes probabilistic inputs (especially for those which use
-graphic model) don't like it. To address this, we propose to build a
-probabilistic model for camera geo-calibration.
+graphic model) don't like it. To address this, we propose to build
+probabilistic models for camera geo-calibration using deep neural
+networks.
 
-\sepline
+A complete geo-calibration detect both camera intrinsic (focal length,
+principal points \etc) and extrinsic parameters, which includes camera
+roll, pitch angles, geographic orientation and geographic locations.
+In our work, we first build a probabilistic model to detect multiple
+geo-calibration parameters jointly. Our algorithm construct a set of
+constraint functions to measure the fitness between the
+geo-calibration parameters and the observations. An energy function
+is constructed with these constraint functions. Thus each point in the
+solution space forebear a energy score (proportional to the
+probability at that point). We then use graphic model approach to
+sample these point in the space.
 
-Among algorithms that are developed to address these sub-tasks, deep
-neural networks (DNNs) rise as stars in recent years. Methods that
-uses DNNs achieve state-of-the-art performances in many computer
-vision areas (\todo{citations}). As parametric algorithms, deep neural
-networks require training for their parameters. Methods to train DNNs
-include supervised algorithms, unsupervised algorithms, and
-reinforcement learning. Supervised algorithms are the most popular and
-commonly applied in many computer vision areas, thanks to their good
-performances and the fact that they are easy to implement. However,
-supervised learning approaches are sensitive to the quality of data
-annotations. In some applications like overhead image segmentation and
-transient attributes estimation, data with noise-free annotation is
-either limited in quantity or technically difficult to acquire.
-In this thesis, Our methods focus on lavaging the camera geographic
-information to deal with the challenges caused by the lack of
-noise-free annotations during DNN training. The insight is
-that the camera geographic information encodes the semantic
-information because it is related to the appearances of
-the scenes.
+In recent years, deep neural networks (DNNs) rise as stars in recent
+years. Methods that uses DNNs achieve state-of-the-art performances in
+many computer vision areas (\todo{citations}). We demonstrate that
+DNNs are good tools to solve the calibration problems. 
+As a next step of our study, We further
+divide these constraints on subset of the calibration parameters and
+conquer them with DNNs.
 
-The process of estimating the camera geographic information is
-referred to as geo-calibration. The goal is to estimate the geographic
-location and the geo-orientation of the given camera. 
-Compared to the common camera calibration, geo-calibration focuses on
-calibrating the camera in the geographic coordinates.
+We first focus on camera roll and pitch angles. Given the already
+known intrinsic parameters, camera roll and pitch angles can be
+derived from the horizon line position in the image. Detecting horizon
+line is easier because it is tightly related to the content/appearance
+of the scene. In our work, we create a new method to use DNNs to give
+a prior distribution of the horizon line, then assign a probability to
+each by measuring their consistences with vanishing points detected
+with traditional statistic methods.
 
-Geographic
-information reveals the scene appearances
-
-\sepline
-
-Many research has been done to detect the camera
-geometry from input images. \todo{citation and examples}. Most of the
-previous work optimize for a limited set of camera calibration
-parameters only. However, our research found that there exists an
-effective way of optimizing multiple camera calibration parameters at
-simultaneously (refer to \chapref{mcmc}). Our algorithm uses the Monte
-Carlo Markov Chain (MCMC) method to sample the possible solutions that
-minimize the objective function, which measures the ``matchness''
-between the observation (input image) and the camera calibration.
-
-Among the most influential approaches for camera geometry estimation,
-most methods are based on traditional statistics diagram. Not until a
-fewer years ago, machine learning based methods gradually caught
-people's attention in this area, thanks for the popularity of deep
-neural network. Neural networks were first proposed in 80th
-(\todo{citation}), The back-forward method developed by Hinton
-\todo{citation} makes the effective training possible. However, neural
-networks are generally thought by researchers merely toy that can only
-solve a very limited set of tasks. It is the develop of computational
-resources and the big collection of annotated data that enables the
-neural networks to grow deeper and eventually brings it to the stage of
-industrial applications.
-
-In computer vision, low-level elements like edges, line segments,
-super-pixels and vanishing points play important roles in many
-applications like image measuration, facade detection, and
-geo-localization.
-Though the CNNs are good at extracting high-level information from
-images, more and more researches start focusing on using CNN to
-extract low-level these elements.
-%
-Lee \etal~\cite{lee2017semantic} propose to detect semantic line
-segments, which are able to segment the scene semantically, using
-neural network. Maninis \etal~\cite{maninis2016convolutional} and Yang
-\etal~\cite{yang2016object} explore to detect object contours with
-CNNs.
-%
-Aside from edges and contours, another category of low-level
-information that the CNNs can detect is the camera geometry, like
-camera location, vanishing points, and horizon lines.
-%
-In the area of vanishing point detection, we are among the first
-researches that use deep neural networks to solve the problem. The
-deep neural networks prove to be a good tool to extract high-level
-information that offer great help to conquer the problems in camera
-geometry estimation. \todo{many citations}.
-
-In our previous work, we have shown that deep neural networks are
-powerful tools for camera geometry estimation as well. In fact, the
-camera geometry can also assist learning high-level image semantics.
-Hoiem \etal~\cite{hoiem2008putting} demonstrate that taking camera
-perspective (horizon line) into consideration improves the performance
-for object detection. Godard \etal~\cite{godard2017unsupervised} learn
-to predict the scene depth from a single image using left-right
-consistency, which is also an application of camera geometry.
-\todo{more citations about the projective loss}.
-
-Another example of camera geometry boosting the learning project is to
-exploit the overhead imagery. Using the geometric locations of the
-ground-view images we can download the corresponding overhead images
-at the same locations through public online resources like bingmap
-\todo{cite}. We refer to these image pairs as ``cross-view image
-pairs''.
-
-\todo{copy from scott} Efforts have been made to
-automate overhead image analysis. As early as
-1970~\cite{idelsohn1970learning} methods were introduced for
-classifying terrain types from a single overhead image, with the goal
-of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
-et al.~\cite{bajcsy1976computer} described a system for recognizing
-roads, intersections, and other road-like objects in overhead imagery.
-However, as overhead imaging differs drastically from ground-level
-imaging, the majority of techniques that have been developed have
-occurred independently and in task-specific ways~\cite{Rozen}.
-%\brief{overhead image grows fast}.
-
-Our work demonstrates that we are able to transfer the learned semantic
-knowledge from the ground image domain to the overhead image domain,
-given the camera geometric information of these two kind of images. In
-our algorithm, the camera geometry helps to collect the ``cross-view
-image pairs'' and aligned the orientation directions of images in a
-pair.
-
-Camera geometry can also be used as weak annotations during training
-of the networks for image understanding.  One of the key to the
-success of machine learning approaches are the large quantity of
-annotated data. However, fully annotated imagery consists of only a
-tiny part of the image resources available online. The idea is to
-exploit other meta-info that are automatically recorded/captured by
-devices to train the ML models. One of the meta-info potentially
-helpful for learning is camera geometry.  We demonstrate that the
-camera geometry can be used as weak ground truth for supervision
-problem. By learning the capture time and the geolocation of the
-images simultaneously, our network is able capture the geo-temporal
-related high-level features.
+Study of geo-localization has a long history.
 

### 2018-06-27 chapters/introduction/junk.tex
more

@@
 and the geo-orientation/geo-localization of the camera.
+
+\sepline
+
+Among algorithms that are developed to address these sub-tasks, deep
+neural networks (DNNs) rise as stars in recent years. Methods that
+uses DNNs achieve state-of-the-art performances in many computer
+vision areas (\todo{citations}). As parametric algorithms, deep neural
+networks require training for their parameters. Methods to train DNNs
+include supervised algorithms, unsupervised algorithms, and
+reinforcement learning. Supervised algorithms are the most popular and
+commonly applied in many computer vision areas, thanks to their good
+performances and the fact that they are easy to implement. However,
+supervised learning approaches are sensitive to the quality of data
+annotations. In some applications like overhead image segmentation and
+transient attributes estimation, data with noise-free annotation is
+either limited in quantity or technically difficult to acquire.
+In this thesis, Our methods focus on lavaging the camera geographic
+information to deal with the challenges caused by the lack of
+noise-free annotations during DNN training. The insight is
+that the camera geographic information encodes the semantic
+information because it is related to the appearances of
+the scenes.
+
+The process of estimating the camera geographic information is
+referred to as geo-calibration. The goal is to estimate the geographic
+location and the geo-orientation of the given camera. 
+Compared to the common camera calibration, geo-calibration focuses on
+calibrating the camera in the geographic coordinates.
+
+Geographic
+information reveals the scene appearances
+
+\sepline
+
+Many research has been done to detect the camera
+geometry from input images. \todo{citation and examples}. Most of the
+previous work optimize for a limited set of camera calibration
+parameters only. However, our research found that there exists an
+effective way of optimizing multiple camera calibration parameters at
+simultaneously (refer to \chapref{mcmc}). Our algorithm uses the Monte
+Carlo Markov Chain (MCMC) method to sample the possible solutions that
+minimize the objective function, which measures the ``matchness''
+between the observation (input image) and the camera calibration.
+
+Among the most influential approaches for camera geometry estimation,
+most methods are based on traditional statistics diagram. Not until a
+fewer years ago, machine learning based methods gradually caught
+people's attention in this area, thanks for the popularity of deep
+neural network. Neural networks were first proposed in 80th
+(\todo{citation}), The back-forward method developed by Hinton
+\todo{citation} makes the effective training possible. However, neural
+networks are generally thought by researchers merely toy that can only
+solve a very limited set of tasks. It is the develop of computational
+resources and the big collection of annotated data that enables the
+neural networks to grow deeper and eventually brings it to the stage of
+industrial applications.
+
+In computer vision, low-level elements like edges, line segments,
+super-pixels and vanishing points play important roles in many
+applications like image measuration, facade detection, and
+geo-localization.
+Though the CNNs are good at extracting high-level information from
+images, more and more researches start focusing on using CNN to
+extract low-level these elements.
+%
+Lee \etal~\cite{lee2017semantic} propose to detect semantic line
+segments, which are able to segment the scene semantically, using
+neural network. Maninis \etal~\cite{maninis2016convolutional} and Yang
+\etal~\cite{yang2016object} explore to detect object contours with
+CNNs.
+%
+Aside from edges and contours, another category of low-level
+information that the CNNs can detect is the camera geometry, like
+camera location, vanishing points, and horizon lines.
+%
+In the area of vanishing point detection, we are among the first
+researches that use deep neural networks to solve the problem. The
+deep neural networks prove to be a good tool to extract high-level
+information that offer great help to conquer the problems in camera
+geometry estimation. \todo{many citations}.
+
+In our previous work, we have shown that deep neural networks are
+powerful tools for camera geometry estimation as well. In fact, the
+camera geometry can also assist learning high-level image semantics.
+Hoiem \etal~\cite{hoiem2008putting} demonstrate that taking camera
+perspective (horizon line) into consideration improves the performance
+for object detection. Godard \etal~\cite{godard2017unsupervised} learn
+to predict the scene depth from a single image using left-right
+consistency, which is also an application of camera geometry.
+\todo{more citations about the projective loss}.
+
+Another example of camera geometry boosting the learning project is to
+exploit the overhead imagery. Using the geometric locations of the
+ground-view images we can download the corresponding overhead images
+at the same locations through public online resources like bingmap
+\todo{cite}. We refer to these image pairs as ``cross-view image
+pairs''.
+
+\todo{copy from scott} Efforts have been made to
+automate overhead image analysis. As early as
+1970~\cite{idelsohn1970learning} methods were introduced for
+classifying terrain types from a single overhead image, with the goal
+of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
+et al.~\cite{bajcsy1976computer} described a system for recognizing
+roads, intersections, and other road-like objects in overhead imagery.
+However, as overhead imaging differs drastically from ground-level
+imaging, the majority of techniques that have been developed have
+occurred independently and in task-specific ways~\cite{Rozen}.
+%\brief{overhead image grows fast}.
+
+Our work demonstrates that we are able to transfer the learned semantic
+knowledge from the ground image domain to the overhead image domain,
+given the camera geometric information of these two kind of images. In
+our algorithm, the camera geometry helps to collect the ``cross-view
+image pairs'' and aligned the orientation directions of images in a
+pair.
+
+Camera geometry can also be used as weak annotations during training
+of the networks for image understanding.  One of the key to the
+success of machine learning approaches are the large quantity of
+annotated data. However, fully annotated imagery consists of only a
+tiny part of the image resources available online. The idea is to
+exploit other meta-info that are automatically recorded/captured by
+devices to train the ML models. One of the meta-info potentially
+helpful for learning is camera geometry.  We demonstrate that the
+camera geometry can be used as weak ground truth for supervision
+problem. By learning the capture time and the geolocation of the
+images simultaneously, our network is able capture the geo-temporal
+related high-level features.

### 2018-06-28 chapters/introduction/introduction.tex
complete draft

@@
 
-Study of geo-localization has a long history.
+Study of geo-localization has a long history. \todo{citations}. We
+seek to geo-localize images with temporal information. The system
+estimate the geographic location of the camera in the form of discrete
+probabilities over bins. This application works in rough scale. We
+also design another algorithm that can do finer scale localization
+based on the rough location input. In that work, we train a network to
+transfer the semantic segmentation masks from the top-view perspective
+to the ground view perspective. In order to train the network, we have
+to construct the image pairs called cross-view image pairs.
+
+Overhead imagery plays an import role in the cross-view learning area.
+To construct a cross view image pair, we need to know the geographic
+location (sometimes also with the geographic orientation).
+\todo{copy from scott} Efforts have been made to
+automate overhead image analysis. As early as
+1970~\cite{idelsohn1970learning} methods were introduced for
+classifying terrain types from a single overhead image, with the goal
+of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
+et al.~\cite{bajcsy1976computer} described a system for recognizing
+roads, intersections, and other road-like objects in overhead imagery.
+However, as overhead imaging differs drastically from ground-level
+imaging, the majority of techniques that have been developed have
+occurred independently and in task-specific ways~\cite{Rozen}.
+
+Benefited from the fast growing monitoring satellite market, overhead
+imagery grows fast nowadays. Microsoft BingMap provides public access
+to their overhead image database with various resolution options. With
+the geographic information of the ground image, we are able to
+download the corresponding overhead images to form the geo-orientation
+aligned cross-view image pairs.
+
+Our algorithm takes advantage of cross-view pairs, to train a deep
+neural network that can semantically segment the overhead image and
+then transfer the segmentation mask to the ground view. To finer
+geo-orient and localize the image, we can match the ground
+segmentation mask with the mask generated from overhead image at
+location $l$.
+
+Another contribution of our work is that along the training for
+networks that do geo-calibration, we are able to learn to extract
+high-level features from the networks along side.
 
 \section{Our Approach}
-My thesis focuses on the image understanding with camera geometry.
-There are two directions we will address: 1) How to estimate camera
-geometry from images; 2) How can we use camera geometry to improve the
-current methods for image semantic extracting. For the first direction,
-we explore both the traditional method and deep learning approaches on
-different geometric calibration parameters. For the second direction,
-we will exploit the image geometric location to help extract
-semantically meaningful informations from images.
+Our thesis focus on constructing a probabilistic model for camera
+geo-calibration. To do that, we first develop an general architecture
+for geo-calibration with different constraint functions. We then seek
+to conquer constraints in subset of calibration parameters.
 
 \begin{itemize}[noitemsep]
+  \item \textbf{General Architecture for Geo-Calibration:}
+  We designed a graphic model to estimate the probability over
+  geo-calibration parameter space.
 
-  \item \textbf{Camera Geometry Detection:} 
-  We investigate different methods to detect camera geometry from the
-  input images. We first explore a sampling approach to find the
-  complete camera calibration parameters that fit the observation of
-  objects (input image) best. In our next work, we use a deep neural
-  network to learn to detect horizon line and vanishing points. These
-  two approaches provides information for the next stage of our
-  research.
-
-  \item \textbf{Camera Geometry for Image Understanding:}
-  We explore the potentials of camera geometry for image understanding.
-  Current machine learning methods address problems that involves mostly
-  the ground imagery. 
-  Studies around overhead images are relatively less thus much fewer
-  annotated data exists in public. With the camera geometric
-  information, we can pair the ground imagery with overhead imagery to
-  form cross-view pairs. Our algorithm explore how to transfer the
-  learned knowledge from a network designed for ground level image
-  semantic segmentation to a new network designed for overhead imagery
-  semantic segmentation use these cross-view pairs.
-  Furthermore, we also explore the potential of the camera geometry as
-  weak annotation in supervised learning. Our algorithm shows that by
-  directly learning to predict camera locations, the network networks
-  are able to extract high-level geo-temporal features.
+  \item \textbf{Constraints for Subset Parameters:}
+  Divide and conquer the problems.
 
@@
 
+  \item \textbf{\chapref{whenwhere} -
+  Learn Where with When:} \newline \newline
+  One of the key to the success of machine learning approaches are the
+  large quantity of annotated data. However, fully annotated imagery
+  only consists of a tiny part of the image resources available online.
+  The idea is to exploit other meta-info that are automatically
+  recorded/captured by devices to train the ML models.  We demonstrate
+  that the camera geometry can be used as weak ground truth for
+  supervision problem. By learning the capture time and the geolocation
+  of the images, our network is able capture the geo-temporal related
+  high-level features. \newline
+
   \item \textbf{\chapref{crosstransf} -
-  Cross-view Domain Adaptation:} \newline \newline
+  Finer Localization by Matching the Overhead Images:} \newline \newline
   Current machine learning methods address problems that involves mostly
@@
 
-  \item \textbf{\chapref{whenwhere} -
-  Extract High-Level Feature by Learning When and Where:} \newline \newline
-  One of the key to the success of machine learning approaches are the
-  large quantity of annotated data. However, fully annotated imagery
-  only consists of a tiny part of the image resources available online.
-  The idea is to exploit other meta-info that are automatically
-  recorded/captured by devices to train the ML models.  We demonstrate
-  that the camera geometry can be used as weak ground truth for
-  supervision problem. By learning the capture time and the geolocation
-  of the images, our network is able capture the geo-temporal related
-  high-level features. \newline
-
 \end{itemize}

### 2018-06-28 chapters/introduction/junk.tex
complete draft

@@
 related high-level features.
+
+My thesis focuses on the image understanding with camera geometry.
+There are two directions we will address: 1) How to estimate camera
+geometry from images; 2) How can we use camera geometry to improve the
+current methods for image semantic extracting. For the first direction,
+we explore both the traditional method and deep learning approaches on
+different geometric calibration parameters. For the second direction,
+we will exploit the image geometric location to help extract
+semantically meaningful informations from images.
+
+\begin{itemize}[noitemsep]
+
+  \item \textbf{Camera Geometry Detection:} 
+  We investigate different methods to detect camera geometry from the
+  input images. We first explore a sampling approach to find the
+  complete camera calibration parameters that fit the observation of
+  objects (input image) best. In our next work, we use a deep neural
+  network to learn to detect horizon line and vanishing points. These
+  two approaches provides information for the next stage of our
+  research.
+
+  \item \textbf{Camera Geometry for Image Understanding:}
+  We explore the potentials of camera geometry for image understanding.
+  Current machine learning methods address problems that involves mostly
+  the ground imagery. 
+  Studies around overhead images are relatively less thus much fewer
+  annotated data exists in public. With the camera geometric
+  information, we can pair the ground imagery with overhead imagery to
+  form cross-view pairs. Our algorithm explore how to transfer the
+  learned knowledge from a network designed for ground level image
+  semantic segmentation to a new network designed for overhead imagery
+  semantic segmentation use these cross-view pairs.
+  Furthermore, we also explore the potential of the camera geometry as
+  weak annotation in supervised learning. Our algorithm shows that by
+  directly learning to predict camera locations, the network networks
+  are able to extract high-level geo-temporal features.
+\end{itemize}

### 2018-06-30 chapters/introduction/introduction.tex
minor changes

@@
 As one of the primary vision tasks, camera calibration plays an
-important role in many applications like indoor layout estimation and
-image mensuration. 
-In the camera pin-hole model, camera calibration parameters consist of
-the camera intrinsics and the extrinsic. The intrinsic parameters of
-a camera encode information of the camera itself such as focal length,
-principal point \etc; the extrinsic parameters are referred to as the
-external states of the camera, such as the camera poses and
-offset/location under some coordinate system. Specifically,
-camera geo-calibration consider the camera locations in the geographic
-coordinates.
-In this work, our study mainly focus on the extrinsic like camera pose
-and the geo-orientation/geo-localization of the camera.
+important role in many applications like autonomous driving, indoor
+layout estimation and image mensuration. 
+In the camera pin-hole model, the projection from scene to the image
+frame are determined by camera intrinsic and extrinsic parameters. 
+The intrinsic parameters describe the information of camera
+itself such as focal length, principal point \etc; 
+The extrinsic parameters describe the external states of the
+camera, such as the camera poses and translation under some
+coordinate system.
+Some applications like GIS and geo-localization are more interested in
+calibrating the camera under geographic coordinates, namely knowing
+the camera pose with respect to the ground reference frame (\ie ENU)
+and camera location in geographic coordinates. We refer to such
+calibration as \textbf{geo-calibration}.
+In this work, our study mainly focuses on estimating geo-calibration
+extrinsic parameters like camera pose and the
+geo-orientation/geo-localization of the camera.
 
 In current work of camera calibration, most algorithms are
-deterministic, which means they output fixed solutions. Applications
-that takes probabilistic inputs (especially for those which use
-graphic model) don't like it. To address this, we propose to build
-probabilistic models for camera geo-calibration using deep neural
-networks.
+deterministic, which means they output fixed solutions. Deterministic
+systems may seem straight-forward but they also forebear the following
+drawbacks: 1) Deterministic systems can not handle uncertainties which
+are commonly encountered in the real world problems.  2) Deterministic
+systems are not friendly to applications developed with graphic models
+that are interfaced with their outputs.
+To address these drawbacks, We propose to build probabilistic
+models for camera geo-calibration.
 
-A complete geo-calibration detect both camera intrinsic (focal length,
+A complete geo-calibration detects both camera intrinsic (focal length,
 principal points \etc) and extrinsic parameters, which includes camera

### 2018-07-01 chapters/introduction/introduction.tex
minor change

@@
 calibration as \textbf{geo-calibration}.
+The complete geo-calibration includes intrinsic (focal
+length, principal points \etc) and extrinsic parameters.
 In this work, our study mainly focuses on estimating geo-calibration
@@
 models for camera geo-calibration.
+We first build a probabilistic model to detect multiple
+geo-calibration parameters jointly.  Our algorithm treats each set of
+geo-calibration parameters as a point in the solution space. It
+constructs an energy function for points in the solution space to
+measure the fitness between the geo-calibration parameters and the
+observations (images), so that each point is associated with an energy
+score.  The probability over the calibration parameters is
+anti-proportional to the energy score, which we then compute with
+graphic model approach. The essential part of our algorithm is the
+construction of the energy function. To better measure the fitness
+between the calibration parameters and the observation, we divide the
+energy function into a combination of partial calibration problems,
+each of which is responsible for a subset of calibration parameters.
+We will discuss these constraint functions in several following work.
 
-A complete geo-calibration detects both camera intrinsic (focal length,
-principal points \etc) and extrinsic parameters, which includes camera
-roll, pitch angles, geographic orientation and geographic locations.
-In our work, we first build a probabilistic model to detect multiple
-geo-calibration parameters jointly. Our algorithm construct a set of
-constraint functions to measure the fitness between the
-geo-calibration parameters and the observations. An energy function
-is constructed with these constraint functions. Thus each point in the
-solution space forebear a energy score (proportional to the
-probability at that point). We then use graphic model approach to
-sample these point in the space.
+In recent years, deep neural networks (DNNs) rise as stars. Methods
+using DNNs achieve state-of-the-art performances in
+many computer vision areas (\todo{citations}). We demonstrate that
+DNNs are good tools to solve partial calibration problems. 
+As a next step of our study, We focus on calibrating cameras with deep
+neural networks.
 
-In recent years, deep neural networks (DNNs) rise as stars in recent
-years. Methods that uses DNNs achieve state-of-the-art performances in
-many computer vision areas (\todo{citations}). We demonstrate that
-DNNs are good tools to solve the calibration problems. 
-As a next step of our study, We further
-divide these constraints on subset of the calibration parameters and
-conquer them with DNNs.
-
-We first focus on camera roll and pitch angles. Given the already
-known intrinsic parameters, camera roll and pitch angles can be
+We first estimate camera roll and pitch angles. Assuming the intrinsic
+parameters are known, camera roll and pitch angles can be
 derived from the horizon line position in the image. Detecting horizon
 line is easier because it is tightly related to the content/appearance
-of the scene. In our work, we create a new method to use DNNs to give
-a prior distribution of the horizon line, then assign a probability to
-each by measuring their consistences with vanishing points detected
-with traditional statistic methods.
+of the scene. In our work, we first create a new method using DNNs to
+give a prior distribution of the horizon line, then assign a
+probability to each by measuring their consistences with vanishing
+points detected using traditional statistic methods.
 
-Study of geo-localization has a long history. \todo{citations}. We
-seek to geo-localize images with temporal information. The system
-estimate the geographic location of the camera in the form of discrete
-probabilities over bins. This application works in rough scale. We
-also design another algorithm that can do finer scale localization
-based on the rough location input. In that work, we train a network to
-transfer the semantic segmentation masks from the top-view perspective
-to the ground view perspective. In order to train the network, we have
-to construct the image pairs called cross-view image pairs.
+Study of geo-localization has a long history. \todo{citations}. In
+another work, We seek to geo-localize images with temporal
+information. The system estimates the discrete probability over the
+camera geographic location. This application works in rough scale. In
+our next work, we design an algorithm that can do fine-scale localization
+based on the rough geographic location inputs. In that work, we
+designed a deep neural network to transfer the semantic segmentation
+masks from the top-view perspective to the ground view perspective. In
+order to train the network, we have to construct a data form called
+cross-view image pairs.
 
@@
 location (sometimes also with the geographic orientation).
-\todo{copy from scott} Efforts have been made to
+\todo{rewrite the following} Efforts have been made to
 automate overhead image analysis. As early as
@@
 imagery grows fast nowadays. Microsoft BingMap provides public access
-to their overhead image database with various resolution options. With
-the geographic information of the ground image, we are able to
+to their overhead image database with various resolution options.
+Given the geographic information of the ground image, we are able to
 download the corresponding overhead images to form the geo-orientation
@@
 
-Our algorithm takes advantage of cross-view pairs, to train a deep
-neural network that can semantically segment the overhead image and
-then transfer the segmentation mask to the ground view. To finer
-geo-orient and localize the image, we can match the ground
-segmentation mask with the mask generated from overhead image at
-location $l$.
+%Our algorithm takes advantage of the cross-view pairs, to train a deep
+%neural network that can semantically segment the overhead image and
+%then transfer the segmentation mask to the ground view. To finer
+%geo-orient and localize the image, we can match the ground
+%segmentation mask with the mask generated from overhead image at
+%location $l$.
 
@@
 networks that do geo-calibration, we are able to learn to extract
-high-level features from the networks along side.
+high-level features from the networks. \todo{expand}
 

### 2018-07-01 chapters/introduction/introduction.tex
minor change

@@
 \section{Our Approach}
-Our thesis focus on constructing a probabilistic model for camera
-geo-calibration. To do that, we first develop an general architecture
-for geo-calibration with different constraint functions. We then seek
-to conquer constraints in subset of calibration parameters.
+We first propose primary probabilistic model to jointly estimate 
+the full geo-calibration parameters. The key for the success of this
+model is to construct good constraint functions that describe the
+fitness between the calibration parameters and the images. We then
+dismantle the full geo-calibration into several partial
+geo-calibration tasks, each of which provide a constraint function to
+fit in the primary model.
 
 \begin{itemize}[noitemsep]
-  \item \textbf{General Architecture for Geo-Calibration:}
-  We designed a graphic model to estimate the probability over
-  geo-calibration parameter space.
+  \item \textbf{General Probabilistic Architecture for Geo-Calibration:}
+  We design a graphic model to estimate the probability over
+  full geo-calibration parameters. Our model is a general
+  architecture, which can take different constraints to form
+  the energy function.
 
-  \item \textbf{Constraints for Subset Parameters:}
-  Divide and conquer the problems.
+  \item \textbf{Constraint Function for Camera Poses:}
+  We develop a constraint function for two camera pose angles: pitch
+  and roll.
+
+  \item \textbf{Constraint Function for Camera Geographic Locations
+  and Orientations:}
+  We develop a constraint function for camera geographic locations and
+  orientations.
 
@@
   given the input image. By constructing a objective function that
-  measures the ``matchness'' between the camera calibration and the
+  measures the ``fitness'' between the camera calibration and the
   observation of the image, we are able to optimize the parameters in
@@
   \item \textbf{\chapref{fasthorizon} -
-  Detecting Horizon and VPs using CNN:} \newline \newline
+  Detecting Pitch and Roll using CNN:} \newline \newline
+  Assuming the intrinsic parameters are known, camera roll and pitch
+  angles can be derived from the horizon line position in the image.
   Horizon line and vanishing points (VPs) plays important roles in many
@@
   \item \textbf{\chapref{whenwhere} -
-  Learn Where with When:} \newline \newline
+  Estimating Geographic Location with Temporal Information:} \newline \newline
+  In this work, we demonstrate that we can estimate the camera geographic
+  location with the input image and its temporal information.
   One of the key to the success of machine learning approaches are the
@@
   Finer Localization by Matching the Overhead Images:} \newline \newline
+  With the rough geographic location, we are able to refine the result
+  with overhead images.
   Current machine learning methods address problems that involves mostly

### 2018-07-01 dissertation.tex
minor change

@@
 calibration are mostly deterministic, namely they output fixed
-solutions. However, applications built with graphic models favor
-probabilistic inputs, of which these deterministic calibration
-models are not capable.
-To address this problem, we propose a probabilistic model with deep
-neural networks (DNNs) for camera
-geo-calibration, providing more flexible inputs for applications that
-are interfaced camera calibration parameters. Compared to 
-traditional camera calibration, camera geo-calibration measures the
-camera extrinsic in geographic coordinates.
-Furthermore, our approaches also demonstrate that the geographic
-information is helpful for extracting/transferring high level
-features in DNN training.
-The primary contributions of our thesis include building a
-probabilistic model for camera geo-calibration ,and relating the
-camera geographic information and image semantics through deep neural
-networks. Our discoveries can provide researchers new insights for
-both camera calibration and DNN training.
+solutions. 
+However, deterministic calibration models can not handle uncertainties
+in our real life well. Furthermore, they are not very friendly to
+graphic model algorithms with which they interface.
+To address these problems, we propose a probabilistic model with deep
+neural networks (DNNs) for camera geo-calibration, providing more
+flexible inputs. Compared to traditional camera calibration,
+camera geo-calibration measures the camera extrinsic in geographic
+coordinates.  Furthermore, our approaches also demonstrate that the
+geographic information is helpful for extracting/transferring high
+level features in DNN training.  The primary contributions of our
+thesis include building a probabilistic model for camera
+geo-calibration ,and relating the camera geographic information and
+image semantics through deep neural networks. Our discoveries can
+provide researchers new insights for both camera calibration and DNN
+training.
 }

### 2018-07-12 dissertation.tex
change title
change abstract

@@
 \author{Menghua Zhai}
-\title{Building a Probabilistic Model with Deep Neural Networks for Camera Geo-Calibration}
+%\title{Building a Probabilistic Model with Deep Neural Networks for Camera Geo-Calibration}
+%\title{Statistical Models for Camera Geo-Calibration}
+\title{Deep Probabilistic Models for Camera Geo-Calibration}
 
@@
 { \SingleSpacing
-Camera calibration is one of the primary task in computer vision.
-It plays an important role in applications like SLAM, image
-mensuration and indoor layout estimation. Current models for camera
-calibration are mostly deterministic, namely they output fixed
-solutions. 
-However, deterministic calibration models can not handle uncertainties
-in our real life well. Furthermore, they are not very friendly to
-graphic model algorithms with which they interface.
-To address these problems, we propose a probabilistic model with deep
-neural networks (DNNs) for camera geo-calibration, providing more
-flexible inputs. Compared to traditional camera calibration,
-camera geo-calibration measures the camera extrinsic in geographic
-coordinates.  Furthermore, our approaches also demonstrate that the
+The ultimate goal of image understanding is to transfer the visual
+images into numerical or symbolic descriptions of the world
+that are helpful for other thought processes for decision making.
+In general, understanding images is not trivial for machines.
+Under different scenarios, researchers divide image
+understanding into different computer vision tasks. For example,
+pedestrian detection is essential to autonomous driving, and image
+retrieval to an image searching engine. Knowing when, where, and in
+which direction picture was taken, the task of geo-calibration makes
+it possible to use imagery to understand the world and how it changes
+in time. Current models for geo-calibration are mostly deterministic,
+namely they output fixed solutions. However, deterministic 
+models can not handle uncertainties in our real life well.
+Furthermore, their outputs are not very friendly to graphic model
+algorithms. To address these problems, we propose a probabilistic
+model for camera geo-calibration using deep neural networks (DNNs),
+providing more flexible inputs. We also demonstrate that the
 geographic information is helpful for extracting/transferring high
-level features in DNN training.  The primary contributions of our
-thesis include building a probabilistic model for camera
-geo-calibration ,and relating the camera geographic information and
-image semantics through deep neural networks. Our discoveries can
-provide researchers new insights for both camera calibration and DNN
-training.
+level features. The primary contributions of our thesis include
+building a probabilistic model for camera geo-calibration, and
+relating the camera geographic information and image semantics through
+deep neural networks. Our discoveries can provide researchers new
+insights for both camera geo-calibration and DNN training.
 }

### 2018-07-12 junk.tex
change abstract

@@
 both camera calibration and deep neural network training.
+
+abstract
+Camera calibration is one of the primary task in computer vision.
+It plays an important role in applications like SLAM, image
+mensuration and indoor layout estimation. Current models for camera
+calibration are mostly deterministic, namely they output fixed
+solutions. 
+However, deterministic calibration models can not handle uncertainties
+in our real life well. Furthermore, they are not very friendly to
+graphic model algorithms with which they interface.
+To address these problems, we propose a probabilistic model with deep
+neural networks (DNNs) for camera geo-calibration, providing more
+flexible inputs. Compared to traditional camera calibration,
+camera geo-calibration measures the camera extrinsic in geographic
+coordinates.  Furthermore, our approaches also demonstrate that the
+geographic information is helpful for extracting/transferring high
+level features in DNN training.  The primary contributions of our
+thesis include building a probabilistic model for camera
+geo-calibration ,and relating the camera geographic information and
+image semantics through deep neural networks. Our discoveries can
+provide researchers new insights for both camera calibration and DNN
+training.

### 2018-07-13 chapters/introduction/introduction.tex
first change

@@
 machines that can think as human has been a dream through the human
-history. In the late 18th century, Hungarian inventor, Wolfgan von
-Kempelen, constructed an automatic machine called ``The Turk'' (also
-known as the ``Mechanical Turk'') to play a chess game. Though it
-proved to be an elaborate hoax, people's enthusiasm for machine
-intelligence lasts till today. As one of the core elements of
-intelligence, human vision plays an important role in our daily lives.
-In order to make computer understand images, scholars had put a lot of
-research efforts in the study of computer vision. In 1960s, MIT
-professor Dr. Marvin Minsky asked his undergraduates to develop
-programs that can recognize objects from a scene in their summer
-project~\cite{boden2006mind}. Half a century has passed, the question
-of this ``summer project'' still remains open.
+history. In 1960s, MIT professor Dr. Marvin Minsky asked his
+undergraduates to develop programs that can recognize objects from a
+scene in their summer project~\cite{boden2006mind}. Half a century has
+passed, the question of this ``summer project'' still remains open.
 
 The ultimate goal of image understanding is to transfer the visual
-images into numerical or symbolic descriptions of the world
-that are helpful for other thought processes for decision making.
+signals (images/videos) into abstract symbolic descriptions of the
+world which are helpful for decision making.
 In general, understanding images is not trivial for machines.
@@
 retrieval to an image searching engine.
+
+For many applications, knowing when, where, and in which direction a
+picture was taken is important to understand the world. We refer to
+this such a vision task as {\em geo-calibration}.
+In current work of geo-calibration, most algorithms are
+deterministic, which means they output fixed solutions. Deterministic
+systems may seem straight-forward but they also have some 
+drawbacks: 1) Deterministic systems can not handle uncertainties in
+the real world very well. 2) they are not
+friendly to applications developed with graphic models that are
+interfaced with their outputs. To address these problems, We propose
+to build probabilistic models for camera geo-calibration.
+
+\section{Background}
 
@@
 coordinate system.
+
 Some applications like GIS and geo-localization are more interested in

### 2018-07-13 chapters/introduction/junk.tex
first change

@@
 \end{itemize}
+
+In the late 18th century, Hungarian inventor, Wolfgan von
+Kempelen, constructed an automatic machine called ``The Turk'' (also
+known as the ``Mechanical Turk'') to play a chess game. Though it
+proved to be an elaborate hoax, people's enthusiasm for machine
+intelligence lasts till today. As one of the core elements of
+intelligence, human vision plays an important role in our daily lives.
+In order to make computer understand images, scholars had put a lot of
+research efforts in the study of computer vision.

### 2018-07-17 chapters/introduction/introduction.tex
introduction

@@
 
+Beside that, we also explored the possibility to learn high-level
+features from the networks that do geo-calibration. \todo{expand}
+
 \section{Background}
 
-As one of the primary vision tasks, camera calibration plays an
-important role in many applications like autonomous driving, indoor
-layout estimation and image mensuration. 
+\subsection{Geo-Calibration}
 In the camera pin-hole model, the projection from scene to the image
@@
 coordinate system.
-
 Some applications like GIS and geo-localization are more interested in
@@
 and camera location in geographic coordinates. We refer to such
-calibration as \textbf{geo-calibration}.
+calibration task as \textbf{geo-calibration}.
+
 The complete geo-calibration includes intrinsic (focal
@@
 
-In current work of camera calibration, most algorithms are
-deterministic, which means they output fixed solutions. Deterministic
-systems may seem straight-forward but they also forebear the following
-drawbacks: 1) Deterministic systems can not handle uncertainties which
-are commonly encountered in the real world problems.  2) Deterministic
-systems are not friendly to applications developed with graphic models
-that are interfaced with their outputs.
-To address these drawbacks, We propose to build probabilistic
-models for camera geo-calibration.
-We first build a probabilistic model to detect multiple
-geo-calibration parameters jointly.  Our algorithm treats each set of
-geo-calibration parameters as a point in the solution space. It
-constructs an energy function for points in the solution space to
-measure the fitness between the geo-calibration parameters and the
-observations (images), so that each point is associated with an energy
-score.  The probability over the calibration parameters is
-anti-proportional to the energy score, which we then compute with
-graphic model approach. The essential part of our algorithm is the
-construction of the energy function. To better measure the fitness
-between the calibration parameters and the observation, we divide the
-energy function into a combination of partial calibration problems,
-each of which is responsible for a subset of calibration parameters.
-We will discuss these constraint functions in several following work.
-
+\subsection{Deep Neural Networks}
 In recent years, deep neural networks (DNNs) rise as stars. Methods
@@
 
-We first estimate camera roll and pitch angles. Assuming the intrinsic
-parameters are known, camera roll and pitch angles can be
-derived from the horizon line position in the image. Detecting horizon
-line is easier because it is tightly related to the content/appearance
-of the scene. In our work, we first create a new method using DNNs to
-give a prior distribution of the horizon line, then assign a
-probability to each by measuring their consistences with vanishing
-points detected using traditional statistic methods.
-
-Study of geo-localization has a long history. \todo{citations}. In
-another work, We seek to geo-localize images with temporal
-information. The system estimates the discrete probability over the
-camera geographic location. This application works in rough scale. In
-our next work, we design an algorithm that can do fine-scale localization
-based on the rough geographic location inputs. In that work, we
-designed a deep neural network to transfer the semantic segmentation
-masks from the top-view perspective to the ground view perspective. In
-order to train the network, we have to construct a data form called
-cross-view image pairs.
-
+\subsection{Overhead Imagery}
 Overhead imagery plays an import role in the cross-view learning area.
@@
 
-%Our algorithm takes advantage of the cross-view pairs, to train a deep
-%neural network that can semantically segment the overhead image and
-%then transfer the segmentation mask to the ground view. To finer
-%geo-orient and localize the image, we can match the ground
-%segmentation mask with the mask generated from overhead image at
-%location $l$.
+\section{Our Approach}
+We divide our approach in two steps. First, we propose a general
+probabilistic model to jointly estimate the geo-calibration
+parameters. The key for the success of this model is to construct good
+constraint functions that describe the fitness between the calibration
+parameters and the images. Then we dismantle the full geo-calibration
+into several partial geo-calibration tasks, each of which provide a
+constraint function that could fit into our general model.
 
-Another contribution of our work is that along the training for
-networks that do geo-calibration, we are able to learn to extract
-high-level features from the networks. \todo{expand}
+\subsection{General Probabilistic Model for Geo-Calibration}
+The complete camera geo-calibration includes the detection of camera
+geographic location, the pose and the focal length of the camera.  We
+design a graphic model to estimate the probability over these
+geo-calibration parameters. 
+We construct an scoring function to measure the ``fitness'' between
+the calibration parameters and the observation of the image. The
+scoring function is proportional to the probability distribution of
+the camera parameters. We propose a Markov Chain Monte Carlo (MCMC)
+sampling approach to approximate the underlying probability
+distribution over the full geo-calibration of the camera.
+Our model is a general architecture, which can take different
+constraints to form the energy function. The details about this model
+can be found in \chapref{mcmc}.
 
-\section{Our Approach}
-We first propose primary probabilistic model to jointly estimate 
-the full geo-calibration parameters. The key for the success of this
-model is to construct good constraint functions that describe the
-fitness between the calibration parameters and the images. We then
-dismantle the full geo-calibration into several partial
-geo-calibration tasks, each of which provide a constraint function to
-fit in the primary model.
+\subsection{Developing Constraint Functions}
+In our general model, the scoring function is defined as a linear
+combination of multiple constraint functions. We then develop
+these constraint functions to describe different calibration
+parameters.
 
 \begin{itemize}[noitemsep]
-  \item \textbf{General Probabilistic Architecture for Geo-Calibration:}
-  We design a graphic model to estimate the probability over
-  full geo-calibration parameters. Our model is a general
-  architecture, which can take different constraints to form
-  the energy function.
+  \item \textbf{Constraint for Horizon Line and Vanishing Points:}
+  We first estimate camera roll and pitch angles. Assuming the intrinsic
+  parameters are known, camera roll and pitch angles can be
+  derived from the horizon line position in the image. Detecting horizon
+  line is easier because it is tightly related to the content/appearance
+  of the scene. In our work, we first create a new method using DNNs to
+  give a prior distribution of the horizon line, then assign a
+  probability to each by measuring their consistences with vanishing
+  points detected using traditional statistic methods. \newline
 
-  \item \textbf{Constraint Function for Camera Poses:}
-  We develop a constraint function for two camera pose angles: pitch
-  and roll.
-
-  \item \textbf{Constraint Function for Camera Geographic Locations
-  and Orientations:}
-  We develop a constraint function for camera geographic locations and
-  orientations.
-
-\end{itemize}
-
-\section{Synopsis}
-
-The remainder of this work is organized as follows:
-
-\begin{itemize}[noitemsep]
-
-  \item \textbf{\chapref{mcmc} - 
-  Complete Camera Geo-Calibration with MCMC Method:} \newline \newline
-  The complete camera geo-calibration includes the detection of camera
-  location in the world, the pose and the focal length of the camera
-  given the input image. By constructing a objective function that
-  measures the ``fitness'' between the camera calibration and the
-  observation of the image, we are able to optimize the parameters in
-  the calibration space. However, this space multi-dimensional, which
-  makes the naive grid search infeasible. Our insight is to do the
-  optimization using Markov Chain Monte Carlo (MCMC) method. Our
-  algorithm is able to avoid unnecessary sampling in the
-  low-probabilistic region in the parameter space thus reduce the
-  computational time dramatically. \newline
-
-  \item \textbf{\chapref{fasthorizon} -
-  Detecting Pitch and Roll using CNN:} \newline \newline
-  Assuming the intrinsic parameters are known, camera roll and pitch
-  angles can be derived from the horizon line position in the image.
-  Horizon line and vanishing points (VPs) plays important roles in many
-  application such as image mensuration and facade detection. In the
-  previous work, researchers tended to use build bottom-up approaches to
-  solve this problem. Our work is inspired by human's perception of the
-  horizon line and the vanishing point. Our method exploit the image
-  global context to provide a prior distribution of the final solution,
-  thus to reduce the dimensionality of the solution space. \newline
-
-  \item \textbf{\chapref{whenwhere} -
-  Estimating Geographic Location with Temporal Information:} \newline \newline
+  \item \textbf{Constraint for Coarse Geographic Locations:}
   In this work, we demonstrate that we can estimate the camera geographic
@@
 
-  \item \textbf{\chapref{crosstransf} -
-  Finer Localization by Matching the Overhead Images:} \newline \newline
+  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
   With the rough geographic location, we are able to refine the result

### 2018-07-17 chapters/introduction/junk.tex
introduction

@@
 research efforts in the study of computer vision.
+
+As one of the primary vision tasks, camera calibration plays an
+important role in many applications like autonomous driving, indoor
+layout estimation and image mensuration.
+
+In current work of camera calibration, most algorithms are
+deterministic, which means they output fixed solutions. Deterministic
+systems may seem straight-forward but they also forebear the following
+drawbacks: 1) Deterministic systems can not handle uncertainties which
+are commonly encountered in the real world problems.  2) Deterministic
+systems are not friendly to applications developed with graphic models
+that are interfaced with their outputs.
+To address these drawbacks, We propose to build probabilistic
+models for camera geo-calibration.
+We first build a probabilistic model to detect multiple
+geo-calibration parameters jointly.  Our algorithm treats each set of
+geo-calibration parameters as a point in the solution space. It
+constructs an energy function for points in the solution space to
+measure the fitness between the geo-calibration parameters and the
+observations (images), so that each point is associated with an energy
+score.  The probability over the calibration parameters is
+anti-proportional to the energy score, which we then compute with
+graphic model approach. The essential part of our algorithm is the
+construction of the energy function. To better measure the fitness
+between the calibration parameters and the observation, we divide the
+energy function into a combination of partial calibration problems,
+each of which is responsible for a subset of calibration parameters.
+We will discuss these constraint functions in several following work.
+
+However, this space multi-dimensional, which
+makes the naive grid search infeasible. Our insight is to do the
+optimization using Markov Chain Monte Carlo (MCMC) method. Our
+algorithm is able to avoid unnecessary sampling in the
+low-probabilistic region in the parameter space thus reduce the
+computational time dramatically.
+
+  Study of geo-localization has a long history. \todo{citations}. In
+  another work, We seek to geo-localize images with temporal
+  information. The system estimates the discrete probability over the
+  camera geographic location. This application works in rough scale. In
+  our next work, we design an algorithm that can do fine-scale localization
+  based on the rough geographic location inputs. In that work, we
+  designed a deep neural network to transfer the semantic segmentation
+  masks from the top-view perspective to the ground view perspective. In
+  order to train the network, we have to construct a data form called
+  cross-view image pairs. \newline
+
+\section{Synopsis}
+
+The remainder of this work is organized as follows:
+
+\begin{itemize}[noitemsep]
+
+  \item \textbf{\chapref{mcmc} - 
+  Complete Camera Geo-Calibration with MCMC Method:} \newline \newline
+  The complete camera geo-calibration includes the detection of camera
+  location in the world, the pose and the focal length of the camera
+  given the input image. By constructing a objective function that
+  measures the ``fitness'' between the camera calibration and the
+  observation of the image, we are able to optimize the parameters in
+  the calibration space. However, this space multi-dimensional, which
+  makes the naive grid search infeasible. Our insight is to do the
+  optimization using Markov Chain Monte Carlo (MCMC) method. Our
+  algorithm is able to avoid unnecessary sampling in the
+  low-probabilistic region in the parameter space thus reduce the
+  computational time dramatically. \newline
+
+  \item \textbf{\chapref{fasthorizon} -
+  Detecting Pitch and Roll using CNN:} \newline \newline
+  Assuming the intrinsic parameters are known, camera roll and pitch
+  angles can be derived from the horizon line position in the image.
+  Horizon line and vanishing points (VPs) plays important roles in many
+  application such as image mensuration and facade detection. In the
+  previous work, researchers tended to use build bottom-up approaches to
+  solve this problem. Our work is inspired by human's perception of the
+  horizon line and the vanishing point. Our method exploit the image
+  global context to provide a prior distribution of the final solution,
+  thus to reduce the dimensionality of the solution space. \newline
+
+  \item \textbf{\chapref{whenwhere} -
+  Estimating Geographic Location with Temporal Information:} \newline \newline
+  In this work, we demonstrate that we can estimate the camera geographic
+  location with the input image and its temporal information.
+  One of the key to the success of machine learning approaches are the
+  large quantity of annotated data. However, fully annotated imagery
+  only consists of a tiny part of the image resources available online.
+  The idea is to exploit other meta-info that are automatically
+  recorded/captured by devices to train the ML models. We demonstrate
+  that the camera geometry can be used as weak ground truth for
+  supervision problem. By learning the capture time and the geolocation
+  of the images, our network is able capture the geo-temporal related
+  high-level features. \newline
+
+  \item \textbf{\chapref{crosstransf} -
+  Finer Localization by Matching the Overhead Images:} \newline \newline
+  With the rough geographic location, we are able to refine the result
+  with overhead images.
+  Current machine learning methods address problems that involves mostly
+  the ground imagery. Tons of dataset targeting on ground imagery are
+  annotated while much fewer are done for the overhead imagery.
+  In this work, we try to transfer the semantics from the ground imagery
+  to the overhead imagery by identifying the latent geometry
+  correspondences between these two. Similar to methods that driven by
+  the projective losses \todo{citation}, our network learns 
+  both the geometric projection between the overhead and ground
+  images, and the semantics of the overhead images jointly. \newline
+
+\end{itemize}
+
+%Our algorithm takes advantage of the cross-view pairs, to train a deep
+%neural network that can semantically segment the overhead image and
+%then transfer the segmentation mask to the ground view. To finer
+%geo-orient and localize the image, we can match the ground
+%segmentation mask with the mask generated from overhead image at
+%location $l$.

### 2018-07-19 chapters/introduction/introduction.tex
minor change

@@
 \subsection{Geo-Calibration}
-In the camera pin-hole model, the projection from scene to the image
-frame are determined by camera intrinsic and extrinsic parameters. 
-The intrinsic parameters describe the information of camera
-itself such as focal length, principal point \etc; 
-The extrinsic parameters describe the external states of the
-camera, such as the camera poses and translation under some
-coordinate system.
-Some applications like GIS and geo-localization are more interested in
-calibrating the camera under geographic coordinates, namely knowing
-the camera pose with respect to the ground reference frame (\ie ENU)
-and camera location in geographic coordinates. We refer to such
-calibration task as \textbf{geo-calibration}.
+Automatic image geo-calibration continues to grow in importance as a
+direct result of the increasing amount of imagery available
+via the Internet. Conceptually geo-calibration task is
+straightforward: given an image, identify the location it was captured
+in the world and the direction the camera was facing. Solving this
+problem is of great value for a wide variety of fields, with potential
+applications ranging from the forensic sciences~\cite{stylianou13jane}
+to crowd-sourced environmental monitoring~\cite{zhang2012mining}.
 
-The complete geo-calibration includes intrinsic (focal
-length, principal points \etc) and extrinsic parameters.
-In this work, our study mainly focuses on estimating geo-calibration
-extrinsic parameters like camera pose and the
-geo-orientation/geo-localization of the camera.
+Extracting location-dependent or orientation-dependent features from
+image data has drawn a great detail of attention from the vision
+community~\cite{jacobs07geolocate, jacobs11geolocate,
+jacobs08geoorient}. The common trend amongst these methods is that
+they take advantage of a large dataset of geo-referenced images. Hays
+and Efros~\cite{hays2008im2gps} use a data-driven scene matching
+approach to localize a query image using a large dataset of geo-tagged
+images.  Doersch et al. extract location-dependent features that
+capture the relative appearance differences of large cities.  Lin et
+al.~\cite{lin2013cross} localize a ground-level image by learning the
+relationship between pairs of ground and aerial images of the same
+location. Other techniques focus on urban environments and infer
+location using local image
+descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
+al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
+estimate camera pose. Many other cues exist, such as the
+skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
+appearance~\cite{lalonde2010sun,workman2014rainbow}, and
+shadows~\cite{junejo2008estimating,wu2010geo}.
+
+However, recognizing the geo-location and geo-orientation of an
+arbitrary outdoor image is an extremely challenging task.  Many
+methods have been proposed; the most common approach is to build a
+large database of images with known location and localize a query
+image using either local~\cite{li2010location,schindler2008detecting}
+or global~\cite{hays2008im2gps,doersch2012what} image features.  This
+approach is not applicable when no nearby ground-level imagery exists
+in the reference database, such as when the image was not captured
+near a popular tourist destination.  Even when reference imagery is
+available, the appearance of the objects may not be visually
+distinctive, for example a train track or a body of water.
 

### 2018-07-19 chapters/introduction/junk.tex
minor change

@@
 %location $l$.
+
+In the camera pin-hole model, the projection from scene to the image
+frame are determined by the camera intrinsic and extrinsic parameters. 
+The intrinsic parameters describe the information of camera
+itself such as focal length, principal point \etc; 
+The extrinsic parameters describe the external states of the
+camera, such as the camera poses and translation under some
+coordinate system.
+Some applications like GIS and geo-localization are more interested in
+calibrating the camera under geographic coordinates, namely knowing
+the camera pose with respect to the ground reference frame (\ie ENU)
+and camera location in geographic coordinates. We refer to such
+calibration task as \textbf{geo-calibration}.
+
+The complete geo-calibration includes intrinsic (focal
+length, principal points \etc) and extrinsic parameters.
+In this work, our study mainly focuses on estimating geo-calibration
+extrinsic parameters like camera pose and the
+geo-orientation/geo-localization of the camera.

### 2018-07-19 chapters/introduction/introduction.tex
minor change

@@
 
-\subsection{Deep Neural Networks}
+\subsection{Deep Neural Networks for Geo-Calibration}
 In recent years, deep neural networks (DNNs) rise as stars. Methods
 using DNNs achieve state-of-the-art performances in
-many computer vision areas (\todo{citations}). We demonstrate that
-DNNs are good tools to solve partial calibration problems. 
-As a next step of our study, We focus on calibrating cameras with deep
-neural networks.
+many computer vision areas (\todo{citations}). 
+Recent work on cross-view image
+geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+ has shown that convolutional neural
+networks are capable of extracting features from aerial imagery
+that can be matched to features extracted from ground imagery.
+Vo \etal~\cite{vo2016localizing} extend this line of work,
+demonstrating improved geolocalization performance by applying an
+auxiliary loss function to regress the ground-level camera orientation
+with respect to the aerial image.
 

### 2018-07-20 chapters/introduction/introduction.tex
minor change

@@
 In recent years, deep neural networks (DNNs) rise as stars. Methods
-using DNNs achieve state-of-the-art performances in
-many computer vision areas (\todo{citations}). 
+using DNNs have achieved state-of-the-art performances in many computer
+vision areas (\todo{citations}). 
+The deep neural networks prove to be a good tool to extract high-level
+information, this valuable ability offers great help for researchers
+to conquer the problems like geo-localization and camera calibration.
 Recent work on cross-view image
 geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
- has shown that convolutional neural
-networks are capable of extracting features from aerial imagery
-that can be matched to features extracted from ground imagery.
-Vo \etal~\cite{vo2016localizing} extend this line of work,
-demonstrating improved geolocalization performance by applying an
-auxiliary loss function to regress the ground-level camera orientation
-with respect to the aerial image.
+has shown that convolutional neural networks are capable of extracting
+features from aerial imagery that can be matched to features extracted
+from ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
+line of work, demonstrating improved geolocalization performance by
+applying an auxiliary loss function to regress the ground-level camera
+orientation with respect to the aerial image.  Horizon line is
+important indicator for estimating camera poses.
+Work~\cite{workman2016horizon, hold2017perceptual} has been done to to
+identify the horizon line using an end-to-end CNN. Workman
+\etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
+focal length. Kendall \etal~\cite{kendall2015convolutional} propose a
+neural network that can do 6-DOF camera relocalization, but their
+method only limited to specific scenes.
 
@@
 constraint functions that describe the fitness between the calibration
-parameters and the images. Then we dismantle the full geo-calibration
-into several partial geo-calibration tasks, each of which provide a
-constraint function that could fit into our general model.
+parameters and the images. Under this guidance we dismantle the full
+geo-calibration into several partial geo-calibration tasks, each of
+which provides a constraint function that could fit into our general
+model.
 
@@
 geographic location, the pose and the focal length of the camera.  We
-design a graphic model to estimate the probability over these
-geo-calibration parameters. 
-We construct an scoring function to measure the ``fitness'' between
-the calibration parameters and the observation of the image. The
-scoring function is proportional to the probability distribution of
-the camera parameters. We propose a Markov Chain Monte Carlo (MCMC)
-sampling approach to approximate the underlying probability
-distribution over the full geo-calibration of the camera.
-Our model is a general architecture, which can take different
-constraints to form the energy function. The details about this model
-can be found in \chapref{mcmc}.
+design a general model to estimate the probability over these
+geo-calibration parameters: First, we construct a scoring function to
+measure the ``fitness'' between the calibration parameters and the
+observation of the image. The scoring function is proportional to the
+probability distribution of the camera parameters. Then we propose a
+Markov Chain Monte Carlo (MCMC) sampling approach to approximate the
+underlying probability distribution over the full geo-calibration of
+the camera. 
+Our model is a general architecture, which can take
+different constraints to form the energy function. The details about
+this model can be found in \chapref{mcmc}.
 
@@
 In our general model, the scoring function is defined as a linear
-combination of multiple constraint functions. We then develop
-these constraint functions to describe different calibration
-parameters.
+combination of multiple constraint functions.
+In the rest of the work, We focus on developing good constraint
+functions for different set of calibration parameters.
 
@@
   line is easier because it is tightly related to the content/appearance
-  of the scene. In our work, we first create a new method using DNNs to
-  give a prior distribution of the horizon line, then assign a
-  probability to each by measuring their consistences with vanishing
-  points detected using traditional statistic methods. \newline
+  of the scene. In our work, we create a new method using a CNN to
+  estimate the prior distribution of the horizon line. We then assign
+  a probability to each horizon line by measuring their consistences
+  with vanishing points detected using traditional statistic methods.
+  We present the algorithm details in \chapref{fasthorizon}.
+  \newline
 
   \item \textbf{Constraint for Coarse Geographic Locations:}
-  In this work, we demonstrate that we can estimate the camera geographic
-  location with the input image and its temporal information.
-  One of the key to the success of machine learning approaches are the
-  large quantity of annotated data. However, fully annotated imagery
-  only consists of a tiny part of the image resources available online.
-  The idea is to exploit other meta-info that are automatically
-  recorded/captured by devices to train the ML models. We demonstrate
-  that the camera geometry can be used as weak ground truth for
-  supervision problem. By learning the capture time and the geolocation
-  of the images, our network is able capture the geo-temporal related
-  high-level features. \newline
+  In this work, we demonstrate to estimate the camera geographic
+  location with the input image.
+  We provide two approaches to obtain the probability distribution over the camera
+  geographic location. Most straightforwardly, our network output
+  categorical distribution over world into a $N \times M$ bins. Better
+  results can be obtained with temporal inputs (image timestamps). Other
+  than that, our algorithm can also compute the probability for any
+  geographic location.
+  We present the algorithm details in \chapref{whenwhere}.
+  \newline
 
@@
   both the geometric projection between the overhead and ground
-  images, and the semantics of the overhead images jointly. \newline
+  images, and the semantics of the overhead images jointly. 
+  We present the algorithm details in \chapref{crosstransf}
+  \newline
 

### 2018-07-22 chapters/introduction/introduction.tex
background for cross-view imagery

@@
 
-\subsection{Overhead Imagery}
-Overhead imagery plays an import role in the cross-view learning area.
-To construct a cross view image pair, we need to know the geographic
-location (sometimes also with the geographic orientation).
-\todo{rewrite the following} Efforts have been made to
-automate overhead image analysis. As early as
-1970~\cite{idelsohn1970learning} methods were introduced for
+\subsection{Cross-view Imagery}
+Since the cross-view imagery plays an important role in geolocalization,
+we spare an seperate section to introduce it. The cross-view image
+pair consists of a ground-view image and an overhead imager at the
+same location. In some cases, the ground/overhead images are also
+aligned in orientation.
+Specifically, Study of the overhead imagery has been long started.
+Efforts have been made to automate overhead image analysis. As early
+as 1970~\cite{idelsohn1970learning} methods were introduced for
 classifying terrain types from a single overhead image, with the goal
@@
 occurred independently and in task-specific ways~\cite{Rozen}.
-
 Benefited from the fast growing monitoring satellite market, overhead
@@
 Given the geographic information of the ground image, we are able to
-download the corresponding overhead images to form the geo-orientation
+obtain the corresponding overhead images to form the geo-orientation
 aligned cross-view image pairs.
+Given the fact that overhead imagery has much larger earth coverage
+and better registered in geographic locations, many geo-localization
+approaches extract the features of it as reference
+database~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+
+Furthermore, there are many other properties of the cross-view pairs
+to explore for high-level feature extraction \todo{expand}.
 

### 2018-07-23 chapters/introduction/introduction.tex
update approach

@@
   \item \textbf{Constraint for Fine Geographic Locations and Orientations}
-  With the rough geographic location, we are able to refine the result
-  with overhead images.
+  In our previous method, we present that our algorithm can estimate
+  the camera location distribution in low-res world division. In this
+  work we focus on refining the geo-localization results with the help
+  of overhead imagery and estimating the camera geo-orientation.
   Current machine learning methods address problems that involves mostly
@@
   images, and the semantics of the overhead images jointly. 
+  When refining the camera geographic location, we compare the
+  semantic layout of the ground image with those transferred from
+  overhead images sampled from different locations and orientations. The
+  optimal prediction is found when the semantic layouts from these
+  two sources fit best. For probabilistic outputs, we can also assign
+  an energy score to each location and orientation combination
+  according to how well the semantic layouts match to each other.
   We present the algorithm details in \chapref{crosstransf}

### 2018-07-23 dissertation.tex
minor change
update abstract

@@
 Furthermore, their outputs are not very friendly to graphic model
-algorithms. To address these problems, we propose a probabilistic
+algorithms. To address these limitations, we propose a probabilistic
 model for camera geo-calibration using deep neural networks (DNNs),
 providing more flexible inputs. We also demonstrate that the
-geographic information is helpful for extracting/transferring high
-level features. The primary contributions of our thesis include
-building a probabilistic model for camera geo-calibration, and
-relating the camera geographic information and image semantics through
-deep neural networks. Our discoveries can provide researchers new
-insights for both camera geo-calibration and DNN training.
+geographic information is helpful for high-level feature extraction.
+The primary contributions of our thesis include building a
+probabilistic model for camera geo-calibration, and learning
+high-level image representations with help of geographic information.
+Our discoveries can provide researchers new insights for both camera
+geo-calibration and DNN training.
 }
@@
 \inject{introduction}
-%\inject{background}
 

### 2018-07-26 chapters/introduction/introduction.tex
add an image to the dissertation

@@
 picture was taken is important to understand the world. We refer to 
-this such a vision task as {\em geo-calibration}.
+such a vision task as {\em geo-calibration}.
 In current work of geo-calibration, most algorithms are
@@
 
-Beside that, we also explored the possibility to learn high-level
-features from the networks that do geo-calibration. \todo{expand}
+Beside geo-calibration, this thesis also studies the possibility to
+learn high-level image representations with help of geographic
+information. In one of our work, we demonstrate that we are able to
+learn geo-temporal feature representations of image with geographic
+locations and capture time. In another work, knowing the geographic
+location, we transfer the learned knowledge of a CNN for ground image
+segmentation to another CNN designed for overhead image segmentation.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.8\linewidth]{introduction/architecture}
+  \caption{Architecture of our approach.}
+  \label{fig:intro:architecture}
+\end{figure}
 
@@
 The deep neural networks prove to be a good tool to extract high-level
-information, this valuable ability offers great help for researchers
+image representations, this valuable ability offers great help for researchers
 to conquer the problems like geo-localization and camera calibration.
@@
 has shown that convolutional neural networks are capable of extracting
-features from aerial imagery that can be matched to features extracted
-from ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
+features from geo-tagged aerial imagery that can be matched to features extracted
+from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
 line of work, demonstrating improved geolocalization performance by
 applying an auxiliary loss function to regress the ground-level camera
-orientation with respect to the aerial image.  Horizon line is
+orientation with respect to the aerial image.  Horizon line is an
 important indicator for estimating camera poses.
-Work~\cite{workman2016horizon, hold2017perceptual} has been done to to
-identify the horizon line using an end-to-end CNN. Workman
-\etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
-focal length. Kendall \etal~\cite{kendall2015convolutional} propose a
-neural network that can do 6-DOF camera relocalization, but their
-method only limited to specific scenes.
+Work~\cite{zhai2016horizon, workman2016horizon, hold2017perceptual}
+has been done to to identify the horizon line with CNNs.
+Workman \etal~\cite{workman2015deepfocal} develop a CNN to estimate
+the camera focal length. Kendall \etal~\cite{kendall2015convolutional}
+propose a neural network that can identify 6-DOF camera parameters,
+but their method only limited to specific scenes.
 
@@
 Since the cross-view imagery plays an important role in geolocalization,
-we spare an seperate section to introduce it. The cross-view image
-pair consists of a ground-view image and an overhead imager at the
+we spare an separate section to introduce it. A cross-view image
+pair consists of a ground-view image and an overhead image at the
 same location. In some cases, the ground/overhead images are also
@@
 and better registered in geographic locations, many geo-localization
-approaches extract the features of it as reference
-database~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+approaches~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+extract the overhead features as reference database for
+geo-localization.
 
-Furthermore, there are many other properties of the cross-view pairs
-to explore for high-level feature extraction \todo{expand}.
+%Furthermore, there are many other properties of the cross-view pairs
+%to explore for high-level feature extraction \todo{expand}.
 
@@
 which provides a constraint function that could fit into our general
-model.
+model. The architecture of our approaches refers to
+\figref{intro:architecture}.
 

### 2018-07-27 chapters/introduction/introduction.tex
minor changes

@@
   We provide two approaches to obtain the probability distribution over the camera
-  geographic location. Most straightforwardly, our network output
+  geographic location. Most straightforwardly, our network outputs
   categorical distribution over world into a $N \times M$ bins. Better
-  results can be obtained with temporal inputs (image timestamps). Other
-  than that, our algorithm can also compute the probability for any
-  geographic location.
+  results can be obtained with temporal inputs (image timestamps).
+  Our algorithm can also compute the probability at arbitrary
+  geographic location, with lower accuracy than the straightforward
+  method.
+  We also demonstrate that our algorithm can learn a  geo-temporal
+  feature representation of image with geographic locations and capture
+  time.
   We present the algorithm details in \chapref{whenwhere}.
@@
   work we focus on refining the geo-localization results with the help
-  of overhead imagery and estimating the camera geo-orientation.
+  of overhead imagery and on estimating the camera geo-orientation.
   Current machine learning methods address problems that involves mostly
@@
   to the overhead imagery by identifying the latent geometry
-  correspondences between these two. Similar to methods that driven by
-  the projective losses \todo{citation}, our network learns 
-  both the geometric projection between the overhead and ground
-  images, and the semantics of the overhead images jointly. 
+  correspondences between these two. Similar to the monocular depth
+  estimation methods that driven by
+  the technique called {\em Reprojection
+  Losses}~\cite{garg2016unsupervised,
+  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
+  network learns to geometrically project pixels from the overhead
+  images to the ground images,
+  and learns to segment the overhead images jointly. 
   When refining the camera geographic location, we compare the
@@
   optimal prediction is found when the semantic layouts from these
-  two sources fit best. For probabilistic outputs, we can also assign
+  two sources match best. For probabilistic outputs, we can also assign
   an energy score to each location and orientation combination

### 2018-07-31 chapters/introduction/introduction.tex
minor change

@@
 drawbacks: 1) Deterministic systems can not handle uncertainties in
-the real world very well. 2) they are not
-friendly to applications developed with graphic models that are
-interfaced with their outputs. To address these problems, We propose
-to build probabilistic models for camera geo-calibration.
+the real world very well. 2) They are not
+friendly to graphic model applications.
+To address these problems, We propose to build probabilistic models
+for camera geo-calibration.
 
-Beside geo-calibration, this thesis also studies the possibility to
-learn high-level image representations with help of geographic
+Beside geo-calibration, this thesis also studies the possibilities of
+learning high-level image representations with the help of geographic
 information. In one of our work, we demonstrate that we are able to
 learn geo-temporal feature representations of image with geographic
-locations and capture time. In another work, knowing the geographic
-location, we transfer the learned knowledge of a CNN for ground image
-segmentation to another CNN designed for overhead image segmentation.
+locations and image timestamps. In another work, we exploit image geographic
+locations to transfer the learned knowledge of a CNN for ground image
+semantic segmentation to another CNN designed for overhead image
+semantic segmentation.
 
@@
 Since the cross-view imagery plays an important role in geolocalization,
-we spare an separate section to introduce it. A cross-view image
+we spare an separate section to discuss it. A cross-view image
 pair consists of a ground-view image and an overhead image at the
-same location. In some cases, the ground/overhead images are also
-aligned in orientation.
+same location. In some cases, two images are also aligned in
+orientation.
 Specifically, Study of the overhead imagery has been long started.
@@
 \section{Our Approach}
-We divide our approach in two steps. First, we propose a general
+Our approach consists of two big steps. First, we propose a general
 probabilistic model to jointly estimate the geo-calibration
 parameters. The key for the success of this model is to construct good
-constraint functions that describe the fitness between the calibration
-parameters and the images. Under this guidance we dismantle the full
-geo-calibration into several partial geo-calibration tasks, each of
-which provides a constraint function that could fit into our general
-model. The architecture of our approaches refers to
+constraint functions which describe the fitness between the calibration
+parameters and the images. As the second step of our approach, we
+dismantle the full geo-calibration into several partial
+geo-calibration tasks, each of which could provides a strong constraint
+function that fit in the general model. The architecture of
+our approaches refers to
 \figref{intro:architecture}.

### 2018-08-02 chapters/introduction/introduction.tex
some changes

@@
 \subsection{General Probabilistic Model for Geo-Calibration}
-The complete camera geo-calibration includes the detection of camera
-geographic location, the pose and the focal length of the camera.  We
+The complete camera geo-calibration detects the camera
+geographic location, pose, and focal length of the camera.  We
 design a general model to estimate the probability over these
-geo-calibration parameters: First, we construct a scoring function to
-measure the ``fitness'' between the calibration parameters and the
-observation of the image. The scoring function is proportional to the
-probability distribution of the camera parameters. Then we propose a
-Markov Chain Monte Carlo (MCMC) sampling approach to approximate the
-underlying probability distribution over the full geo-calibration of
-the camera. 
-Our model is a general architecture, which can take
-different constraints to form the energy function. The details about
-this model can be found in \chapref{mcmc}.
+geo-calibration parameters: First, we model the relation between the
+image projection of the scene and the geo-calibration parameters. This
+relation is ruled by both the pin-hole model principle and the
+geographic location of the camera.
+We then construct a scoring function to measure the ``fitness'' between the
+calibration parameters and the observation of the image. 
+The scoring function is proportional to the probability distribution
+of the camera parameters. We propose a Markov Chain Monte
+Carlo (MCMC) sampling approach to approximate the underlying
+probability distribution over the full geo-calibration of the camera.
+Our model is a general architecture, which can take different
+constraints to form the scoring function. The details about this model
+can be found in \chapref{mcmc}.
 
@@
 In the rest of the work, We focus on developing good constraint
-functions for different set of calibration parameters.
+functions for different set of calibration parameters. Besides, we
+also show our methods are able to extract high-level image features
+with the help of geographic information.
 
@@
   parameters are known, camera roll and pitch angles can be
-  derived from the horizon line position in the image. Detecting horizon
-  line is easier because it is tightly related to the content/appearance
-  of the scene. In our work, we create a new method using a CNN to
-  estimate the prior distribution of the horizon line. We then assign
+  derived from the horizon line position in the image. Compared to
+  directly detecting the camera pose, identifying horizon line is easier
+  because it is tightly related to the appearance
+  of the scene. In our work, we create a new method using CNN to
+  estimate the prior distribution of the horizon line. We assign
   a probability to each horizon line by measuring their consistences
@@
   We provide two approaches to obtain the probability distribution over the camera
-  geographic location. Most straightforwardly, our network outputs
+  geographic location. Most straightforwardly, our network estimate the
   categorical distribution over world into a $N \times M$ bins. Better
-  results can be obtained with temporal inputs (image timestamps).
+  results can be procured with temporal inputs (image timestamps).
   Our algorithm can also compute the probability at arbitrary
@@
   method.
-  We also demonstrate that our algorithm can learn a  geo-temporal
-  feature representation of image with geographic locations and capture
+  We demonstrate that our algorithm is able to learn geo-temporal
+  image representations with geographic locations and capture
   time.
@@
   optimal prediction is found when the semantic layouts from these
-  two sources match best. For probabilistic outputs, we can also assign
-  an energy score to each location and orientation combination
-  according to how well the semantic layouts match to each other.
+  two sources match best. For probabilistic outputs, we assign
+  a score to each location and orientation setting,
+  based on how well the semantic layouts match to each other.
   We present the algorithm details in \chapref{crosstransf}

### 2018-08-03 chapters/introduction/introduction.tex
introduction first para

@@
 \end{chapquote}
-
-Before the father of computer asked this question, creating
-machines that can think as human has been a dream through the human
-history. In 1960s, MIT professor Dr. Marvin Minsky asked his
-undergraduates to develop programs that can recognize objects from a
-scene in their summer project~\cite{boden2006mind}. Half a century has
-passed, the question of this ``summer project'' still remains open.
-
 The ultimate goal of image understanding is to transfer the visual
@@
 world which are helpful for decision making.
-In general, understanding images is not trivial for machines.
-Under different scenarios, researchers divide image
-understanding into different computer vision tasks. For example,
-pedestrian detection is essential to autonomous driving, and image
-retrieval to an image searching engine.
+However, understanding images is a not trivial task for machines.
+In order to handle various complicated scenarios, researchers divide
+image understanding into different computer vision tasks: Pedestrian
+detection for autonomous driving, and image retrieval for image
+searching engines \etc.
 
@@
 picture was taken is important to understand the world. We refer to 
-such a vision task as {\em geo-calibration}.
+estimating these properties as the task of  {\em geo-calibration}.
 In current work of geo-calibration, most algorithms are
 deterministic, which means they output fixed solutions. Deterministic
-systems may seem straight-forward but they also have some 
-drawbacks: 1) Deterministic systems can not handle uncertainties in
-the real world very well. 2) They are not
-friendly to graphic model applications.
-To address these problems, We propose to build probabilistic models
-for camera geo-calibration.
+systems may seem straight-forward but they also have some obvious
+drawbacks: 1) Deterministic systems can not model the inherent
+uncertainties from images of ambiguous scenes. 2) They are not
+friendly to applications that take probabilistic inputs. To address
+these problems, We propose to build probabilistic models for camera
+geo-calibration.
 
-Beside geo-calibration, this thesis also studies the possibilities of
-learning high-level image representations with the help of geographic
-information. In one of our work, we demonstrate that we are able to
-learn geo-temporal feature representations of image with geographic
-locations and image timestamps. In another work, we exploit image geographic
-locations to transfer the learned knowledge of a CNN for ground image
-semantic segmentation to another CNN designed for overhead image
-semantic segmentation.
+Feature engineering is essential for image understanding. In recent
+years, learning based approaches for high-level feature construction
+like deep neural nets get popular. However, most of these feature
+learning methods heavily relies on manually labeled data. In our
+thesis, we presented alternative ways to learn high-level image
+representations when the manually labeled data is either insufficient
+or absent. We show that learning to geo-calibrate a camera is helpful
+for high-level feature extracting.
 

### 2018-08-03 chapters/introduction/junk.tex
minor change
introduction first para

@@
 geo-orientation/geo-localization of the camera.
+
+%\subsection{Overhead Imagery}
+%Overhead imagery plays an import role in the cross-view learning area.
+%To construct a cross view image pair, we need to know the geographic
+%location (sometimes also with the geographic orientation).
+%\todo{rewrite the following} Efforts have been made to
+%automate overhead image analysis. As early as
+%1970~\cite{idelsohn1970learning} methods were introduced for
+%classifying terrain types from a single overhead image, with the goal
+%of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
+%et al.~\cite{bajcsy1976computer} described a system for recognizing
+%roads, intersections, and other road-like objects in overhead imagery.
+%However, as overhead imaging differs drastically from ground-level
+%imaging, the majority of techniques that have been developed have
+%occurred independently and in task-specific ways~\cite{Rozen}.
+
+%Benefited from the fast growing monitoring satellite market, overhead
+%imagery grows fast nowadays. Microsoft BingMap provides public access
+%to their overhead image database with various resolution options.
+%Given the geographic information of the ground image, we are able to
+%download the corresponding overhead images to form the geo-orientation
+%aligned cross-view image pairs.
+
+Before the father of computer asked this question, creating
+machines that can think as human has been a dream through the human
+history. In 1960s, MIT professor Dr. Marvin Minsky asked his
+undergraduates to develop programs that can recognize objects from a
+scene in their summer project~\cite{boden2006mind}. Half a century has
+passed, the question of this ``summer project'' still remains open.
+
+%Beside geo-calibration, this thesis also studies the possibilities of
+%learning high-level image representations with the help of geographic
+%information. In one of our work, we demonstrate that we are able to
+%learn geo-temporal feature representations of image with geographic
+%locations and image timestamps. In another work, we exploit image geographic
+%locations to transfer the learned knowledge of a CNN for ground image
+%semantic segmentation to another CNN designed for overhead image
+%semantic segmentation.

### 2018-08-03 dissertation.tex
introduction first para

@@
 images into numerical or symbolic descriptions of the world
-that are helpful for other thought processes for decision making.
-In general, understanding images is not trivial for machines.
-Under different scenarios, researchers divide image
-understanding into different computer vision tasks. For example,
-pedestrian detection is essential to autonomous driving, and image
-retrieval to an image searching engine. Knowing when, where, and in
-which direction picture was taken, the task of geo-calibration makes
-it possible to use imagery to understand the world and how it changes
-in time. Current models for geo-calibration are mostly deterministic,
-namely they output fixed solutions. However, deterministic 
-models can not handle uncertainties in our real life well.
-Furthermore, their outputs are not very friendly to graphic model
-algorithms. To address these limitations, we propose a probabilistic
-model for camera geo-calibration using deep neural networks (DNNs),
-providing more flexible inputs. We also demonstrate that the
-geographic information is helpful for high-level feature extraction.
-The primary contributions of our thesis include building a
-probabilistic model for camera geo-calibration, and learning
-high-level image representations with help of geographic information.
-Our discoveries can provide researchers new insights for both camera
-geo-calibration and DNN training.
+that are helpful for decision making.
+%
+%In general, understanding images is not trivial for machines.
+%Under different scenarios, researchers divide image
+%understanding into different computer vision tasks. For example,
+%pedestrian detection is essential to autonomous driving, and image
+%retrieval to an image searching engine.
+%
+Knowing when, where, and in which direction picture was taken, the
+task of geo-calibration makes it possible to use imagery to understand
+the world and how it changes in time. Current models for
+geo-calibration are mostly deterministic, namely they output fixed
+solutions. However, deterministic models can not model the
+uncertainties that are inherent when the scene of the image is ambiguous.
+Furthermore, their outputs are not very friendly to algorithms that
+take probabilistic inputs. To address these limitations, we
+propose a probabilistic model for camera geo-calibration using deep
+neural networks.
+%
+While our primary contribution is geo-calibration, We also show that
+learning to geo-calibrate a camera is helpful for high-level feature
+extraction.
+%
+%Our discoveries can provide researchers new insights for both camera
+%geo-calibration and DNN training.
 }
-\keywords{geo-calibration, deep neural networks, computer vision}
+\keywords{computer vision, geo-calibration, deep neural networks}
 

### 2018-08-09 chapters/introduction/introduction.tex
changes in background

@@
 \subsection{Geo-Calibration}
+\todo{add deterministic methods, add literature for time estimation}
+
 Automatic image geo-calibration continues to grow in importance as a
@@
 via the Internet. Conceptually geo-calibration task is
-straightforward: given an image, identify the location it was captured
-in the world and the direction the camera was facing. Solving this
-problem is of great value for a wide variety of fields, with potential
-applications ranging from the forensic sciences~\cite{stylianou13jane}
-to crowd-sourced environmental monitoring~\cite{zhang2012mining}.
+straightforward: given an image, identify the time and the location it
+was captured in the world and the direction the camera was facing.
+Solving this problem is of great value for a wide variety of fields,
+with potential applications ranging from the forensic
+sciences~\cite{stylianou13jane} to crowd-sourced environmental
+monitoring~\cite{zhang2012mining}.
 
@@
 \subsection{Deep Neural Networks for Geo-Calibration}
-In recent years, deep neural networks (DNNs) rise as stars. Methods
-using DNNs have achieved state-of-the-art performances in many computer
-vision areas (\todo{citations}). 
+In recent years, deep neural networks (DNNs) were proven to be
+extremely successful in many computer vision areas (\todo{citations}). 
 The deep neural networks prove to be a good tool to extract high-level
@@
 Recent work on cross-view image
-geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
 has shown that convolutional neural networks are capable of extracting
@@
 from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
-line of work, demonstrating improved geolocalization performance by
+line of work, demonstrating improved geo-localization performance by
 applying an auxiliary loss function to regress the ground-level camera
-orientation with respect to the aerial image.  Horizon line is an
-important indicator for estimating camera poses.
+orientation with respect to the aerial image.
+
+Closely related to camera geo-calibration, studies also have been done
+to identify the camera poses and focal length using deep neural
+networks.
+Horizon line is an important indicator for estimating camera poses,
+which is, giving the focal length, one can derive the camera roll and
+pitch angles from the horizon line position in the image.
 Work~\cite{zhai2016horizon, workman2016horizon, hold2017perceptual}
-has been done to to identify the horizon line with CNNs.
-Workman \etal~\cite{workman2015deepfocal} develop a CNN to estimate
-the camera focal length. Kendall \etal~\cite{kendall2015convolutional}
-propose a neural network that can identify 6-DOF camera parameters,
-but their method only limited to specific scenes.
+has been done to to identify the horizon line with CNNs.  Workman
+\etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
+focal length. Kendall \etal~\cite{kendall2015convolutional} propose a
+neural network that can identify 6-DOF camera parameters, but their
+method only limited to specific scenes.
 
-\subsection{Cross-view Imagery}
-Since the cross-view imagery plays an important role in geolocalization,
-we spare an separate section to discuss it. A cross-view image
-pair consists of a ground-view image and an overhead image at the
-same location. In some cases, two images are also aligned in
-orientation.
-Specifically, Study of the overhead imagery has been long started.
-Efforts have been made to automate overhead image analysis. As early
-as 1970~\cite{idelsohn1970learning} methods were introduced for
-classifying terrain types from a single overhead image, with the goal
-of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
-et al.~\cite{bajcsy1976computer} described a system for recognizing
-roads, intersections, and other road-like objects in overhead imagery.
-However, as overhead imaging differs drastically from ground-level
-imaging, the majority of techniques that have been developed have
-occurred independently and in task-specific ways~\cite{Rozen}.
+\subsection{Ground-to-Aerial Geo-Calibration}
+Data-driven scene matching approaches are widely used to localize a
+query image by registering in a large dataset of geo-tagged images. 
 Benefited from the fast growing monitoring satellite market, overhead
-imagery grows fast nowadays. Microsoft BingMap provides public access
-to their overhead image database with various resolution options.
-Given the geographic information of the ground image, we are able to
-obtain the corresponding overhead images to form the geo-orientation
-aligned cross-view image pairs.
-Given the fact that overhead imagery has much larger earth coverage
-and better registered in geographic locations, many geo-localization
-approaches~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
-extract the overhead features as reference database for
-geo-localization.
+imagery grows fast nowadays, which also makes it a perfect source for
+database of geo-tagged. We refer to the geo-calibration process of
+matching the ground-level imagery to the aerial imagery as {\em
+Ground-to-Aerial Geo-Calibration}.
+%
+Cross-view image pair is the basic element for ground-to-aerial
+geo-calibration. It consists of a ground-level image and an overhead
+image at the same location. In some cases, two images are also aligned
+in orientation.
 
-%Furthermore, there are many other properties of the cross-view pairs
-%to explore for high-level feature extraction \todo{expand}.
+\todo{cite ground-to-aerial geo-calibration papers}
 

### 2018-08-09 chapters/introduction/junk.tex
changes in background

@@
 %semantic segmentation.
+
+Study of the overhead imagery has been long started.
+Efforts have been made to automate overhead image analysis. As early
+as 1970~\cite{idelsohn1970learning} methods were introduced for
+classifying terrain types from a single overhead image, with the goal
+of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
+et al.~\cite{bajcsy1976computer} described a system for recognizing
+roads, intersections, and other road-like objects in overhead imagery.
+However, as overhead imaging differs drastically from ground-level
+imaging, the majority of techniques that have been developed have
+occurred independently and in task-specific ways~\cite{Rozen}.
+Benefited from the fast growing monitoring satellite market, overhead
+imagery grows fast nowadays. Microsoft BingMap provides public access
+to their overhead image database with various resolution options.
+Given the geographic information of the ground image, we are able to
+obtain the corresponding overhead images to form the geo-orientation
+aligned cross-view image pairs.
+%
+Given the fact that overhead imagery has much larger earth coverage
+and better registered in geographic locations, many geo-localization
+approaches~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+extract the overhead features as reference database for
+geo-localization.

### 2018-08-09 chapters/introduction/introduction.tex
some more background

@@
 
+\section{\todo{Dataset}}
+Introduce the dataset we use.
+
 \section{Our Approach}
@@
 function that fit in the general model. The architecture of
-our approaches refers to
-\figref{intro:architecture}.
+our approaches refers to \figref{intro:architecture}.
+%
+In the end, we show that learning to geo-calibrate a camera is helpful
+for high-level image feature extracting.
 
@@
 design a general model to estimate the probability over these
-geo-calibration parameters: First, we model the relation between the
+geo-calibration parameters: First, we model the relationship between the
 image projection of the scene and the geo-calibration parameters. This
-relation is ruled by both the pin-hole model principle and the
-geographic location of the camera.
+relationship can be described by the pin-hole model, and
+the geographic location of the camera.
 We then construct a scoring function to measure the ``fitness'' between the
@@
 combination of multiple constraint functions.
-In the rest of the work, We focus on developing good constraint
-functions for different set of calibration parameters. Besides, we
-also show our methods are able to extract high-level image features
-with the help of geographic information.
+In the rest of the work, we focus on developing good constraint
+functions for different set of calibration parameters.
 
@@
 \end{itemize}
+
+\section{Geo-Calibration for Feature Learning}

### 2018-08-09 chapters/introduction/introduction.tex
new section for feature learning

@@
 \section{Geo-Calibration for Feature Learning}
+
+Automatic feature engineering has drawn a lot of attention over the
+past years in the computer vision community due to its efficiency and
+not requiring expert knowledge about the data.  In recent years, deep
+neural networks are acknowledged as good tools to learn high-level
+features for image understanding.  As parametric algorithms, deep
+neural networks require training for their parameters.  Methods to
+train deep neural networks include supervised algorithms, unsupervised
+algorithms, and reinforcement learning. Supervised algorithms are the
+most popular and commonly applied in many computer vision areas,
+thanks to their good performances and the fact that they are easy to
+implement. However, supervised learning approaches are sensitive to
+the quality of data annotations. In some applications like overhead
+image segmentation and transient attributes estimation, data with
+noise-free annotation is either very limited in quantity or
+technically difficult to acquire.  In this thesis, Our methods focus
+on lavaging the camera geographic information to deal with the
+challenges of lacking noise-free annotations during DNN training. The
+insight is that the camera geographic information encodes the semantic
+information because it is related to the appearances of the scenes.

### 2018-08-12 chapters/introduction/introduction.tex
minor change

--- 2018-08-09 chapters/introduction/introduction.tex
@@
 
+\subsection{Geo-Calibration for Feature Learning}
+
+Automatic feature engineering has drawn a lot of attention over the
+past years in the computer vision community due to its efficiency and
+not requiring expert knowledge about the data. Deep neural networks
+are wildly accepted by researchers as good tools to learn high-level
+image representations.
+The most commonly used approach for deep image feature learning is
+full supervision, which usually requires manually annotated data
+\todo{citations}.
+Though full supervision work well in many applications, there are
+exponentially more image resources without manual annotations (cell
+phone imagery, YouTube videos\etc), which show a huge potential for
+visual feature learning.  In recent years, people start studying
+various approaches to exploit those unlabeled data. 
+%
+Recent work has explored the use of self-supervision (sometimes
+referred to as unsupervised learning or pretext tasks) for training
+deep neural networks that capture useful visual
+representations~\cite{doersch2015unsupervised,pathak2016context}. 
+These methods typically
+exploit some known quantity of the data (e.g., pixel color values) to
+avoid expensive manual annotation. As a byproduct, a useful visual
+representation is learned.
+For example, Zhang et al.~\cite{zhang2016colorful} show how image
+colorization (synthesizing colors for a grayscale image) is a powerful
+pretext task for learning visual representations. Pathak et
+al.~\cite{pathak2017learning} exploit low-level motion-based grouping
+cues for unsupervised feature learning.  
+%
+As new learning technique address the lack of massive amounts of
+labeled data, domain adaptation adapt the feature generating model to
+another feature domain so that it improve the performance when dealing
+with new input
+data~\cite{fernando2013unsupervised,fernando2015joint,saenko2010adapting,wang2016actions,tinghui2016flow}.
+Duan \etal~\cite{duan2012learning} proposed to learn a linear
+projection to transfer from the source feature subspace to the target
+subspace. Sohn \etal~\cite{sohn2017unsupervised} improved the
+performance of video face recognition using an adversarial-based
+approach to adapt the network to unlabled video imagery.
+
 \section{\todo{Dataset}}
@@
 
-  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
+  \item \textbf{Constraint for Fine Geographic Locations and Orientations:}
   In our previous method, we present that our algorithm can estimate
@@
   of overhead imagery and on estimating the camera geo-orientation. 
-  Current machine learning methods address problems that involves mostly
-  the ground imagery. Tons of dataset targeting on ground imagery are
-  annotated while much fewer are done for the overhead imagery.
-  In this work, we try to transfer the semantics from the ground imagery
-  to the overhead imagery by identifying the latent geometry
-  correspondences between these two. Similar to the monocular depth
-  estimation methods that driven by
-  the technique called {\em Reprojection
-  Losses}~\cite{garg2016unsupervised,
-  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
-  network learns to geometrically project pixels from the overhead
-  images to the ground images,
-  and learns to segment the overhead images jointly. 
+  We first learn to segment the ground scene from its paired aerial image.
   When refining the camera geographic location, we compare the
@@
   based on how well the semantic layouts match to each other.
-  We present the algorithm details in \chapref{crosstransf}
+  We present the algorithm details in \chapref{crosstransf}.
   \newline
@@
 
-\section{Geo-Calibration for Feature Learning}
+\subsection{Geo-Calibration for Feature Learning}
+Our methods focus on lavaging the camera geographic information to
+deal with the challenges of lacking manually annotated data during DNN
+training. The insight is that the camera geographic information
+encodes semantic information because it is related to the
+appearances of the scenes.
+
+\begin{itemize}[noitemsep]
+  \item \textbf{Ground-to-Aerial Feature Learning}
+  Current machine learning methods address problems that involves mostly
+  the ground-level imagery. Tons of dataset targeting on ground imagery are
+  annotated while much fewer are done for the overhead imagery. In
+  \chapref{crosstransf}, we proposed a method to learn aerial image
+  semantic segmentation with ground-level ground truth. Our method
+  exploits the spatial correspondences between images in cross-view
+  pairs. 
+  In this work, we try to transfer the semantics from the ground
+  imagery to the overhead imagery by identifying the latent geometry
+  correspondences between these two.  Similar to the monocular depth
+  estimation methods that driven by the technique called {\em
+  Reprojection Losses}~\cite{garg2016unsupervised,
+  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
+  network learns to geometrically project pixels from the overhead
+  images to the ground images, and to segment the overhead images
+  jointly.
+
+  \item \textbf{Geo-Temporal Feature Learning}
+  In our work, we consider two novel pretext
+  tasks, time and location estimation. Our work is most similar to Li
+  and Snavely~\cite{li2018learning}, who propose an approach for
+  learning intrinsic images by observing image sequences with varying
+  illumination over time. While their targets are reflectance and
+  shading images of the scene, we focus on location and time.
+\end{itemize}

### 2018-08-13 chapters/introduction/introduction.tex
introduction changes

@@
 
-\section{\todo{Dataset}}
-Introduce the dataset we use.
+%\section{\todo{Dataset}}
+%Introduce the dataset we use.
 
@@
 
-  \item \textbf{Constraint for Coarse Geographic Locations:}
-  In this work, we demonstrate to estimate the camera geographic
-  location with the input image.
-  We provide two approaches to obtain the probability distribution over the camera
-  geographic location. Most straightforwardly, our network estimate the
-  categorical distribution over world into a $N \times M$ bins. Better
-  results can be procured with temporal inputs (image timestamps).
-  Our algorithm can also compute the probability at arbitrary
-  geographic location, with lower accuracy than the straightforward
-  method.
-  We demonstrate that our algorithm is able to learn geo-temporal
-  image representations with geographic locations and capture
-  time.
+  \item \textbf{Constraint for Time and Coarse Geographic Locations:}
+  In this work, we demonstrate to estimate the capture time and the
+  camera geographic location with the input image.
+  Our network has two branches to predict the image capture time and
+  the geographic location jointly.
+  For time estimation, our network is able to predict the
+  distribution over the month of the year and the global hour of the
+  day when the input image has been captured.
+  For camera geo-localization, We provide two approaches to obtain the
+  probability distribution over the camera geographic location. Most
+  straightforwardly, our network estimate the categorical distribution
+  over world into a $N \times M$ bins. Better results can be procured
+  with temporal inputs (image timestamps).  Our algorithm can also
+  compute the probability at arbitrary geographic location, with lower
+  accuracy than the straightforward method.
   We present the algorithm details in \chapref{whenwhere}.
@@
 \begin{itemize}[noitemsep]
-  \item \textbf{Ground-to-Aerial Feature Learning}
+  \item \textbf{Ground-to-Aerial Feature Learning:}
   Current machine learning methods address problems that involves mostly
@@
   jointly.
+  \newline
 
-  \item \textbf{Geo-Temporal Feature Learning}
-  In our work, we consider two novel pretext
-  tasks, time and location estimation. Our work is most similar to Li
-  and Snavely~\cite{li2018learning}, who propose an approach for
-  learning intrinsic images by observing image sequences with varying
-  illumination over time. While their targets are reflectance and
-  shading images of the scene, we focus on location and time.
+  \item \textbf{Geo-Temporal Feature Learning:}
+  In \chapref{whenwhere}, we demonstrate that our algorithm is able to
+  learn geo-temporal image representations with geographic locations and
+  capture time.
+  Our work is most similar to Li and Snavely~\cite{li2018learning},
+  who propose an approach for learning intrinsic images by observing
+  image sequences with varying illumination over time. While their
+  targets are reflectance and shading images of the scene, we consider
+  two novel pretext tasks, time and location estimation.
+  By learning to predict its geographic location and capture time from the
+  query image, our network learns to extract geo-temporal features
+  from the image.
+
 \end{itemize}

### 2018-08-13 chapters/introduction/introduction.tex
add time estimation related work

@@
 estimating these properties as the task of  {\em geo-calibration}.
-In current work of geo-calibration, most algorithms are
+In current work of geo-calibration, a lot of them are
 deterministic, which means they output fixed solutions. Deterministic
@@
 shadows~\cite{junejo2008estimating,wu2010geo}.
+For time estimation, Matzen and Snavely~\cite{matzen2014scene} predict
+timestamps for photos by matching against a time-varying
+reconstruction of a scene.  Hill~\cite{hill1994elephant} estimate the
+time of the day by analyze the light intensity profiles captured by
+cameras.
 
@@
 
-\subsection{Deep Neural Networks for Geo-Calibration}
+\subsection{Deep Learning in Geo-Calibration}
 In recent years, deep neural networks (DNNs) were proven to be

### 2018-08-13 chapters/introduction/introduction.tex
Ground-to-aerial geo-calibration

@@
 \subsection{Geo-Calibration}
-\todo{add deterministic methods, add literature for time estimation}
+\todo{add deterministic methods}
 
@@
 to conquer the problems like geo-localization and camera calibration.
-Recent work on cross-view image
-geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
-has shown that convolutional neural networks are capable of extracting
-features from geo-tagged aerial imagery that can be matched to features extracted
-from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
-line of work, demonstrating improved geo-localization performance by
-applying an auxiliary loss function to regress the ground-level camera
-orientation with respect to the aerial image.
 
@@
 Data-driven scene matching approaches are widely used to localize a
-query image by registering in a large dataset of geo-tagged images. 
-Benefited from the fast growing monitoring satellite market, overhead
-imagery grows fast nowadays, which also makes it a perfect source for
-database of geo-tagged. We refer to the geo-calibration process of
-matching the ground-level imagery to the aerial imagery as {\em
-Ground-to-Aerial Geo-Calibration}.
+query image by registering in a large dataset of geo-tagged
+images~\cite{im2gps, li2010location,zamir2010accurate}.
+Benefited from the fast growing monitoring satellite and drone markets,
+satellite/aerial imagery becomes more and more available than ever
+before, which makes it a rich source for
+reference database of geo-tagged images. We refer to the
+geo-calibration methods which uses the aerial imagery as geographic
+reference as {\em Ground-to-Aerial Geo-Calibration}.
 %
@@
 in orientation. 
-
-\todo{cite ground-to-aerial geo-calibration papers}
+%
+Recent work on cross-view image
+geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+has shown that convolutional neural networks are capable of extracting
+features from geo-tagged aerial imagery that can be matched to features extracted
+from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
+line of work, demonstrating improved geo-localization performance by
+applying an auxiliary loss function to regress the ground-level camera
+orientation with respect to the aerial image. Hu and Feng
+\etal~\cite{mh2018cvm} achieve the state-of-the-art performance in
+geo-localization by extracting cross-domain global features using
+NetVLAD~\cite{arandjelovic2016netvlad} technique.
 

### 2018-08-14 chapters/introduction/introduction.tex
add citations

@@
 The deep neural networks prove to be a good tool to extract high-level
-image representations, this valuable ability offers great help for researchers
-to conquer the problems like geo-localization and camera calibration.
+image representations, this valuable ability offers great a help for
+researchers to conquer the problems like geo-localization and camera
+calibration.
+Weyand and Kostrikov \etal~\cite{planet} propose a convolutional
+network to predict the geographic location given an input
+image.~\cite{walch2017image} applies LSTM on CNN features learned for
+camera localization.
 
@@
 The most commonly used approach for deep image feature learning is
-full supervision, which usually requires manually annotated data
-\todo{citations}.
+full supervision, which usually requires manually annotated
+data~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
 Though full supervision work well in many applications, there are

### 2018-08-14 chapters/introduction/introduction.tex
minor changes

@@
 \subsection{Geo-Calibration}
-\todo{add deterministic methods}
-
+%\todo{add deterministic methods}
+%
 Automatic image geo-calibration continues to grow in importance as a
@@
 image using either local~\cite{li2010location,schindler2008detecting}
-or global~\cite{hays2008im2gps,doersch2012what} image features.  This
-approach is not applicable when no nearby ground-level imagery exists
-in the reference database, such as when the image was not captured
-near a popular tourist destination.  Even when reference imagery is
-available, the appearance of the objects may not be visually
-distinctive, for example a train track or a body of water.
+or global~\cite{hays2008im2gps,doersch2012what} image features. 
+%This approach is not applicable when no nearby ground-level imagery
+%exists in the reference database, such as when the image was not
+%captured near a popular tourist destination.  Even when reference
+%imagery is available, the appearance of the objects may not be
+%visually distinctive, for example a train track or a body of water.
 
@@
 Weyand and Kostrikov \etal~\cite{planet} propose a convolutional
-network to predict the geographic location given an input
+network to predict the geographic location of the input
 image.~\cite{walch2017image} applies LSTM on CNN features learned for
@@
 Benefited from the fast growing monitoring satellite and drone markets,
-satellite/aerial imagery becomes more and more available than ever
-before, which makes it a rich source for
-reference database of geo-tagged images. We refer to the
-geo-calibration methods which uses the aerial imagery as geographic
-reference as {\em Ground-to-Aerial Geo-Calibration}.
-%
+geo-tagged satellite/aerial imagery becomes more and more available
+than ever before, which makes it a rich source for building
+reference database. We refer to the geo-calibration methods which use
+the aerial imagery as geographic reference as {\em Ground-to-Aerial
+Geo-Calibration}.
+
 Cross-view image pair is the basic element for ground-to-aerial
 geo-calibration. It consists of a ground-level image and an overhead
-image at the same location. In some cases, two images are also aligned
+image at the same location. In some cases, two images may also be aligned
 in orientation.
-%
-Recent work on cross-view image
+
+Recent work on ground-to-aerial
 geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
@@
 geo-localization by extracting cross-domain global features using
-NetVLAD~\cite{arandjelovic2016netvlad} technique.
+the NetVLAD~\cite{arandjelovic2016netvlad} technique.
 
@@
 image representations.
-The most commonly used approach for deep image feature learning is
+The most commonly used approach for deep feature learning is
 full supervision, which usually requires manually annotated
@@
 Though full supervision work well in many applications, there are
-exponentially more image resources without manual annotations (cell
+exponentially more image resources without manual annotation (cell
 phone imagery, YouTube videos\etc), which show a huge potential for
-visual feature learning.  In recent years, people start studying
-various approaches to exploit those unlabeled data. 
-%
-Recent work has explored the use of self-supervision (sometimes
-referred to as unsupervised learning or pretext tasks) for training
-deep neural networks that capture useful visual
-representations~\cite{doersch2015unsupervised,pathak2016context}. 
+visual feature learning.
+
+To exploit these unlabeled data, recent work has explored the use of
+self-supervision (sometimes referred to as unsupervised learning or
+pretext tasks) for training deep neural networks that capture useful
+visual representations~\cite{doersch2015unsupervised,pathak2016context}. 
 These methods typically
@@
 geo-calibration tasks, each of which could provides a strong constraint
-function that fit in the general model. The architecture of
+function that fits in the general model. The architecture of
 our approaches refers to \figref{intro:architecture}.
@@
   In this work, we demonstrate to estimate the capture time and the
-  camera geographic location with the input image.
-  Our network has two branches to predict the image capture time and
-  the geographic location jointly.
+  camera geographic location given the input image.
+  Our network has two heads to predict the image
+  capture time and the geographic location jointly.
   For time estimation, our network is able to predict the
-  distribution over the month of the year and the global hour of the
+  joint distribution over the month of the year and the global hour of the
   day when the input image has been captured.
@@
   straightforwardly, our network estimate the categorical distribution
-  over world into a $N \times M$ bins. Better results can be procured
-  with temporal inputs (image timestamps).  Our algorithm can also
-  compute the probability at arbitrary geographic location, with lower
-  accuracy than the straightforward method.
-  We present the algorithm details in \chapref{whenwhere}.
+  over location of the world, which is represented as a $N \times M$
+  meshgrid. Better results can be procured with image capture time as
+  auxiliary input (if it is known). 
+  %Our algorithm can also compute the probability at arbitrary
+  %geographic location, with lower accuracy than the straightforward
+  %method.
+  We will present the algorithm details in \chapref{whenwhere}.
   \newline
@@
   work we focus on refining the geo-localization results with the help
-  of overhead imagery and on estimating the camera geo-orientation. 
+  of overhead imagery and on estimating geo-orientation of the camera. 
   We first learn to segment the ground scene from its paired aerial image.
   When refining the camera geographic location, we compare the
-  semantic layout of the ground image with those transferred from
-  overhead images sampled from different locations and orientations. The
-  optimal prediction is found when the semantic layouts from these
-  two sources match best. For probabilistic outputs, we assign
-  a score to each location and orientation setting,
-  based on how well the semantic layouts match to each other.
-  We present the algorithm details in \chapref{crosstransf}.
+  semantic layout of the ground image with the semantic layout
+  transferred from overhead images, which are sampled in different
+  locations and orientation angles. The optimal prediction is found when the
+  semantic layouts from these two sources match best. For probabilistic
+  outputs, we assign a score to each location and orientation setting,
+  based on how well the semantic layouts match to each other. We will
+  present the algorithm details in \chapref{crosstransf}.
   \newline
@@
 \subsection{Geo-Calibration for Feature Learning}
-Our methods focus on lavaging the camera geographic information to
+Our methods also focus on lavaging the camera geographic information to
 deal with the challenges of lacking manually annotated data during DNN
@@
   the ground-level imagery. Tons of dataset targeting on ground imagery are
-  annotated while much fewer are done for the overhead imagery. In
-  \chapref{crosstransf}, we proposed a method to learn aerial image
-  semantic segmentation with ground-level ground truth. Our method
+  annotated while much fewer are done for the satellite/aerial imagery. In
+  \chapref{crosstransf}, we proposed a method to learn the aerial image
+  semantic segmentation with only ground-level ground truth. Our method
   exploits the spatial correspondences between images in cross-view
@@
   In this work, we try to transfer the semantics from the ground
-  imagery to the overhead imagery by identifying the latent geometry
+  imagery to the aerial imagery by identifying the latent geometry
   correspondences between these two. Similar to the monocular depth
@@
   godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
-  network learns to geometrically project pixels from the overhead
-  images to the ground images, and to segment the overhead images
+  network learns to geometrically project pixels from the aerial
+  images to the ground images, and to segment the aerial images
   jointly.
@@
   two novel pretext tasks, time and location estimation.
-  By learning to predict its geographic location and capture time from the
-  query image, our network learns to extract geo-temporal features
+  By learning to predict the geographic location and capture time of
+  the query image, our network learns to extract geo-temporal features
   from the image.

### 2018-08-14 dissertation.tex
new dissertation

@@
 { \SingleSpacing
-The ultimate goal of image understanding is to transfer the visual
-images into numerical or symbolic descriptions of the world
+The ultimate goal of image understanding is to transfer visual
+images into numerical or symbolic descriptions of the scene
 that are helpful for decision making.
@@
 the world and how it changes in time. Current models for
-geo-calibration are mostly deterministic, namely they output fixed
-solutions. However, deterministic models can not model the
-uncertainties that are inherent when the scene of the image is ambiguous.
-Furthermore, their outputs are not very friendly to algorithms that
-take probabilistic inputs. To address these limitations, we
-propose a probabilistic model for camera geo-calibration using deep
-neural networks.
+geo-calibration are mostly deterministic, which fails to model the
+the inherent uncertainties when the scene of the image is ambiguous.
+Furthermore, the outputs of deterministic system can not be used by
+algorithms that take probabilistic inputs. To address these
+limitations, we propose a probabilistic model for camera
+geo-calibration using deep neural networks.
 %

### 2018-08-15 chapters/introduction/introduction.tex
introduction

@@
 \begin{chapquote}{Alan Turing}
-  ``I propose to consider the question: Can machine think?''
+  ``I propose to consider the question: Can machines think?''
 \end{chapquote}
-The ultimate goal of image understanding is to transfer the visual
+The ultimate goal of image understanding is to transfer visual
 signals (images/videos) into abstract symbolic descriptions of the
@@
 In order to handle various complicated scenarios, researchers divide
-image understanding into different computer vision tasks: Pedestrian
-detection for autonomous driving, and image retrieval for image
-searching engines \etc.
+image understanding into different computer vision tasks: pedestrian
+detection for autonomous driving, face recognition for security
+system, and image retrieval for image searching engines.
 
 For many applications, knowing when, where, and in which direction a
-picture was taken is important to understand the world. We refer to 
-estimating these properties as the task of  {\em geo-calibration}.
-In current work of geo-calibration, a lot of them are
-deterministic, which means they output fixed solutions. Deterministic
-systems may seem straight-forward but they also have some obvious
-drawbacks: 1) Deterministic systems can not model the inherent
-uncertainties from images of ambiguous scenes. 2) They are not
-friendly to applications that take probabilistic inputs. To address
-these problems, We propose to build probabilistic models for camera
+picture was taken is important to understand the world. However, most
+images does not carry such information, thus we need to develop
+algorithms to dig them up.  We refer to the task of estimating these
+properties as {\em geo-calibration}.
+Most recent work of geo-calibration focus on deterministic systems, 
+which have some drawbacks: 1) they can not model the inherent
+uncertainties from images of ambiguous scenes, and 2) they can not be
+used by applications that take probabilistic inputs. To address
+these problems, we propose to build probabilistic models for camera
 geo-calibration.
 
-Feature engineering is essential for image understanding. In recent
-years, learning based approaches for high-level feature construction
-like deep neural nets get popular. However, most of these feature
+We also show that learning to geo-calibrate a camera is helpful for
+high-level feature extracting. Feature engineering is essential for
+image understanding. In recent years, learning based approaches for
+high-level feature extracting like deep neural nets have drawn a lot
+of attention due to the fact that they do not need any expert
+knowledge about the target data. However, most of these feature
 learning methods heavily relies on manually labeled data. In our
@@
 representations when the manually labeled data is either insufficient
-or absent. We show that learning to geo-calibrate a camera is helpful
-for high-level feature extracting.
+or absent.
 

### 2018-08-15 chapters/introduction/introduction.tex
background geo-calibration

@@
 direct result of the increasing amount of imagery available
-via the Internet. Conceptually geo-calibration task is
+via the Internet. Conceptually the geo-calibration task is
 straightforward: given an image, identify the time and the location it
@@
 with potential applications ranging from the forensic
-sciences~\cite{stylianou13jane} to crowd-sourced environmental
+sciences~\cite{stylianou13jane} to environmental
 monitoring~\cite{zhang2012mining}.
 
+\begin{itemize}[noitemsep]
+\item \textbf{Geo-Localization:}
 Extracting location-dependent or orientation-dependent features from
@@
 approach to localize a query image using a large dataset of geo-tagged
-images.  Doersch et al. extract location-dependent features that
-capture the relative appearance differences of large cities.  Lin et
-al.~\cite{lin2013cross} localize a ground-level image by learning the
-relationship between pairs of ground and aerial images of the same
-location. Other techniques focus on urban environments and infer
-location using local image
+images.  Doersch \etal~\cite{doersch2012what} extract
+location-dependent features that capture the relative appearance
+differences of large cities.  Lin et al.~\cite{lin2013cross} localize
+a ground-level image by learning the relationship between pairs of
+ground and aerial images of the same location. Other techniques focus
+on urban environments and infer location using local image
 descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
@@
 shadows~\cite{junejo2008estimating,wu2010geo}.
-For time estimation, Matzen and Snavely~\cite{matzen2014scene} predict
+\newline
+
+\item \textbf{Time Estimation:}
+Matzen and Snavely~\cite{matzen2014scene} predict
 timestamps for photos by matching against a time-varying
 reconstruction of a scene.  Hill~\cite{hill1994elephant} estimate the
-time of the day by analyze the light intensity profiles captured by
-cameras.
+time of the day by measuring the light intensity profiles captured by
+cameras.~\cite{salem2016face2year,ginosar2015century} propose to date the
+year book photos by analyzing human appearance. Lee
+\etal~\cite{linking2015iccp} find visual paterns in the buildings,
+relate them to certain time periods.
 
-However, recognizing the geo-location and geo-orientation of an
-arbitrary outdoor image is an extremely challenging task.  Many
-methods have been proposed; the most common approach is to build a
-large database of images with known location and localize a query
-image using either local~\cite{li2010location,schindler2008detecting}
-or global~\cite{hays2008im2gps,doersch2012what} image features. 
-%This approach is not applicable when no nearby ground-level imagery
-%exists in the reference database, such as when the image was not
-%captured near a popular tourist destination.  Even when reference
-%imagery is available, the appearance of the objects may not be
-%visually distinctive, for example a train track or a body of water.
+\end{itemize}
 

### 2018-08-15 chapters/introduction/introduction.tex
background 2

@@
 monitoring~\cite{zhang2012mining}.
+\todo{make it smoother}
 
@@
 time of the day by measuring the light intensity profiles captured by
-cameras.~\cite{salem2016face2year,ginosar2015century} propose to date the
-year book photos by analyzing human appearance. Lee
+cameras. Methods are proposed to date the
+year book photos by analyzing human
+appearance~\cite{salem2016face2year,ginosar2015century}. Lee
 \etal~\cite{linking2015iccp} find visual paterns in the buildings,
 relate them to certain time periods.
+\newline
+
+\item \textbf{Camera Pose Estimation:}
+\todo{}
 
@@
 In recent years, deep neural networks (DNNs) were proven to be
-extremely successful in many computer vision areas (\todo{citations}). 
-The deep neural networks prove to be a good tool to extract high-level
-image representations, this valuable ability offers great a help for
-researchers to conquer the problems like geo-localization and camera
-calibration.
+extremely successful in many computer vision areas. 
+It is widely accepted that DNNs have excellent performance in
+high-level visual feature learning.
+This valuable ability provides researchers powerful tools to
+solve the challenging geo-calibration tasks.
 Weyand and Kostrikov \etal~\cite{planet} propose a convolutional
 network to predict the geographic location of the input
-image.~\cite{walch2017image} applies LSTM on CNN features learned for
-camera localization.
+image. Walch \etal~\cite{walch2017image} aggregate learned CNN
+features with LSTM to generate global image representation for camera
+localization.  In pose estimation aera, Work~\cite{zhai2016horizon,
+workman2016horizon, hold2017perceptual} has been done to to identify
+the horizon line with CNNs (one can derive the camera roll and pitch
+angles from the horizon line position giving the camera focal length).
 
 Closely related to camera geo-calibration, studies also have been done
-to identify the camera poses and focal length using deep neural
-networks.
-Horizon line is an important indicator for estimating camera poses,
-which is, giving the focal length, one can derive the camera roll and
-pitch angles from the horizon line position in the image.
-Work~\cite{zhai2016horizon, workman2016horizon, hold2017perceptual}
-has been done to to identify the horizon line with CNNs.  Workman
-\etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
+to identify the camera intrinsics using deep neural networks.
+Workman \etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
 focal length. Kendall \etal~\cite{kendall2015convolutional} propose a

### 2018-08-16 chapters/introduction/introduction.tex
more changes on background.

@@
 a ground-level image by learning the relationship between pairs of
-ground and aerial images of the same location. Other techniques focus
+ground and aerial images \footnote{In the context of our thesis, we
+do not distinguish between the satellite imagery and the aerial
+imagery} of the same location. Other techniques focus
 on urban environments and infer location using local image
@@
 \subsection{Ground-to-Aerial Geo-Calibration}
-Data-driven scene matching approaches are widely used to localize a
-query image by registering in a large dataset of geo-tagged
-images~\cite{im2gps, li2010location,zamir2010accurate}.
+Data-driven scene matching approaches are widely used to for
+geo-calibration.
+When localizing a camera, data-driven algorithms search for k-nearest
+neighbors of the query image in the database of the geo-tagged imagery.
+To reduce the work of querying, the searching process is usually
+carried out in some feature space with applicable number of  
+dimensions~\cite{im2gps, li2010location,zamir2010accurate}.
+However, as items found in most reference dataset, geo-tagged
+ground-level images collected from the internet are usually noisy and
+sparse in geographic space. To achieve more accurate geo-calibration
+results, we need alternative image resources with more accurate
+geographic tags and denser spatial coverage.
+
 Benefited from the fast growing monitoring satellite and drone markets,
-geo-tagged satellite/aerial imagery becomes more and more available
-than ever before, which makes it a rich source for building
-reference database. We refer to the geo-calibration methods which use
-the aerial imagery as geographic reference as {\em Ground-to-Aerial
-Geo-Calibration}.
-
-Cross-view image pair is the basic element for ground-to-aerial
-geo-calibration. It consists of a ground-level image and an overhead
-image at the same location. In some cases, two images may also be aligned
-in orientation.
+the geo-tagged aerial imagery becomes more publicly accessible
+than ever before. Aerial imagery downloading services like
+Microsoft Bing Map provide aerial images of various
+resolutions, which can cover most areas of the world with accurate
+geographic tags, making aerial imagery a rich source for
+reference database. We refer to the geo-calibration methods
+which use the aerial imagery as geographic reference as
+ground-to-aerial geo-calibration.
 
 Recent work on ground-to-aerial
-geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+geo-calibration~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
 has shown that convolutional neural networks are capable of extracting
-features from geo-tagged aerial imagery that can be matched to features extracted
-from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
-line of work, demonstrating improved geo-localization performance by
-applying an auxiliary loss function to regress the ground-level camera
-orientation with respect to the aerial image. Hu and Feng
-\etal~\cite{mh2018cvm} achieve the state-of-the-art performance in
-geo-localization by extracting cross-domain global features using
-the NetVLAD~\cite{arandjelovic2016netvlad} technique.
+features from geo-tagged aerial imagery that can be matched to
+features extracted from the ground imagery.  Vo
+\etal~\cite{vo2016localizing} extend this line of work, demonstrating
+improved geo-localization performance by applying an auxiliary loss
+function to regress the ground-level camera orientation with respect
+to the aerial image. Hu and Feng \etal~\cite{mh2018cvm} achieve the
+state-of-the-art performance in geo-localization by extracting
+cross-domain global features using the
+NetVLAD~\cite{arandjelovic2016netvlad} technique.
 

### 2018-08-17 chapters/introduction/introduction.tex
geo-calibration feature learning

@@
 Automatic feature engineering has drawn a lot of attention over the
-past years in the computer vision community due to its efficiency and
-not requiring expert knowledge about the data. Deep neural networks
-are wildly accepted by researchers as good tools to learn high-level
-image representations.
+past years due to its ability to learn useful features without strong
+expert knowledge about the data. Among many automatic feature
+engineering approaches, deep neural networks are wildly accepted by
+researchers as good tools to learn high-level image representations.
 The most commonly used approach for deep feature learning is
@@
 data~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
-Though full supervision work well in many applications, there are
-exponentially more image resources without manual annotation (cell
-phone imagery, YouTube videos\etc), which show a huge potential for
-visual feature learning.
+Unfortunately, such data is not always available for certain tasks. 
+In contrast, unlabeled data is offen plentiful (\ie cellphone photos
+in Instagram or Youtube videos).
 
-To exploit these unlabeled data, recent work has explored the use of
-self-supervision (sometimes referred to as unsupervised learning or
+To exploit these unlabeled data, recent work has explored
+self-supervision methods (sometimes referred to as unsupervised learning or
 pretext tasks) for training deep neural networks that capture useful
@@
 approach to adapt the network to unlabled video imagery.
-
-%\section{\todo{Dataset}}
-%Introduce the dataset we use.
 

### 2018-08-17 chapters/introduction/introduction.tex
minor change

@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=.8\linewidth]{introduction/architecture}
-  \caption{Architecture of our approach.}
-  \label{fig:intro:architecture}
-\end{figure}
-
 \section{Background}
@@
 \subsection{Geo-Calibration}
-%\todo{add deterministic methods}
-%
 Automatic image geo-calibration continues to grow in importance as a
 direct result of the increasing amount of imagery available
-via the Internet. Conceptually the geo-calibration task is
-straightforward: given an image, identify the time and the location it
-was captured in the world and the direction the camera was facing.
+via the Internet. 
 Solving this problem is of great value for a wide variety of fields,
@@
 monitoring~\cite{zhang2012mining}.
-\todo{make it smoother}
+Conceptually the geo-calibration task includes:
+identifying the camera pose ({\em pose estimation}), the camera
+geographic location ({\em geo-localization}), and the time the query
+image was captured ({\em time estimation}).
 
 \begin{itemize}[noitemsep]
+
+\item \textbf{Pose Estimation:}
+\newline
+
 \item \textbf{Geo-Localization:}
@@
 \newline
-
-\item \textbf{Camera Pose Estimation:}
-\todo{}
 
@@
 Automatic feature engineering has drawn a lot of attention over the
-past years due to its ability to learn useful features without strong
-expert knowledge about the data. Among many automatic feature
-engineering approaches, deep neural networks are wildly accepted by
-researchers as good tools to learn high-level image representations.
-The most commonly used approach for deep feature learning is
-full supervision, which usually requires manually annotated
+past years. Compared to the manual feature engineering,
+automatic feature engineering approaches are able to to learn useful
+features without strong expert knowledge about the data. Among these
+approaches, deep neural networks are wildly accepted by researchers as
+good tools to learn high-level image representations.  The most
+commonly used approach for deep feature learning is full supervision,
+which usually requires manually annotated
 data~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
@@
 \section{Our Approach}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.8\linewidth]{introduction/architecture}
+  \caption{Architecture of our approach.}
+  \label{fig:intro:architecture}
+\end{figure}
+
 Our approach consists of two big steps. First, we propose a general

### 2018-08-17 chapters/introduction/introduction.tex
calibration related work

@@
 
-\subsection{Geo-Calibration}
-Automatic image geo-calibration continues to grow in importance as a
-direct result of the increasing amount of imagery available
-via the Internet. 
-Solving this problem is of great value for a wide variety of fields,
-with potential applications ranging from the forensic
-sciences~\cite{stylianou13jane} to environmental
-monitoring~\cite{zhang2012mining}.
-Conceptually the geo-calibration task includes:
-identifying the camera pose ({\em pose estimation}), the camera
-geographic location ({\em geo-localization}), and the time the query
-image was captured ({\em time estimation}).
+\subsection{Geo-Calibration of Outdoor Images}
+Automatic image geo-calibration of outdoor images continues to grow in
+importance as a direct result of the increasing amount of imagery
+available via the Internet.  Solving this problem is of great value
+for a wide variety of fields, with potential applications ranging from
+the forensic sciences~\cite{stylianou13jane} to environmental
+monitoring~\cite{zhang2012mining}.  Conceptually the geo-calibration
+task includes: identifying the camera pose ({\em pose estimation}),
+the camera geographic location ({\em geo-localization}), and the time
+the query image was captured ({\em time estimation}).
 
@@
 \item \textbf{Pose Estimation:}
+Li et al.~\cite{li2012worldwide} exploit geo-registered 3D points
+clouds to estimate camera pose.
+Vo \etal~\cite{vo2016localizing} propose a geo-localization network
+that can regress the geo-orientation angle of the camera.
+Agarwal \etal~\cite{agarwal2015metric} keep track of the camera pose
+changes by matching SIFT~\cite{lowe1999object} feature points detected
+between the input image and Google Street View panoramas.
+%
+The estimating of horizon line is an essential step for some pose
+estimation algorithm, because horizon lines are closely related to
+camera pitch and roll angles. If the camera focal length is known, one
+can compute the camera pitch and roll angle from the horizon line.
+Collins and Weiss~\cite{unitsphere1990} formulate horizon line
+detection as a statistical estimation problem on the Gaussian Sphere,
+which is similar to the geometry we use.  More recent work has
+explored the use of dual space~\cite{alignment2014,dualspace2013}
+representations. Among the clustering-based approaches, Xu et
+al.~\cite{kitware2013} improve this pipeline by introducing a new
+point-line consistency function that models errors in the line segment
+extraction step.
 \newline
@@
 \item \textbf{Geo-Localization:}
-Extracting location-dependent or orientation-dependent features from
+Extracting location-dependent features from
 image data has drawn a great detail of attention from the vision
@@
 on urban environments and infer location using local image
-descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
-al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
-estimate camera pose. Many other cues exist, such as the
+descriptors~\cite{schindler2008detecting,snavely2006photo}.
+Many other cues exist, such as the
 skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky

### 2018-08-17 chapters/introduction/introduction.tex
minor changes

@@
 %
-The estimating of horizon line is an essential step for some pose
-estimation algorithm, because horizon lines are closely related to
-camera pitch and roll angles. If the camera focal length is known, one
-can compute the camera pitch and roll angle from the horizon line.
+Horizon line detection is an essential step for some pose
+estimation algorithms, because horizon lines are closely related to
+camera pitch and roll angles.
+%If the camera focal length is known, one can compute the camera pitch
+%and roll angle from the horizon line.
 Collins and Weiss~\cite{unitsphere1990} formulate horizon line

### 2018-08-20 chapters/introduction/introduction.tex
update flow chart, change approach section

@@
 
-\section{Our Approach}
+\section{Main Contributions}
 
@@
   \centering
-  \includegraphics[width=.8\linewidth]{introduction/architecture}
-  \caption{Architecture of our approach.}
+  \includegraphics[width=\linewidth]{introduction/architecture}
+  \caption{A simplified flowchart of our approach. The algorithm
+inputs (images, time and manual annotations) are fed to different
+constraint models which work as constraint functions. 
+The probabilistic distribution over complete geo-calibration
+parameters are then simulated jointly by fusing these constraint
+functions in a general model for geo-calibration.}
   \label{fig:intro:architecture}
@@
 
-Our approach consists of two big steps. First, we propose a general
+We make contributions in three main areas: 1) We proposed a general
 probabilistic model to jointly estimate the geo-calibration
-parameters. The key for the success of this model is to construct good
-constraint functions which describe the fitness between the calibration
-parameters and the images. As the second step of our approach, we
-dismantle the full geo-calibration into several partial
-geo-calibration tasks, each of which could provides a strong constraint
-function that fits in the general model. The architecture of
+parameters, 2) we decompose the full geo-calibration into several
+partial geo-calibration tasks, each of which provides a strong
+constraint function that fits in the general model, and 3) we show
+that learning to geo-calibrate a camera is helpful for high-level
+image feature extraction.
+
+The first two contributions consist of our main approach. Our
+algorithm feeds inputs (images, time and manual annotations) to
+different constraint models, which work as constraint functions. Then
+we fuse these constraint functions to simulate the joint distribution
+over the complete geo-calibration parameters. The flowchart of
 our approaches refers to \figref{intro:architecture}.
-%
-In the end, we show that learning to geo-calibrate a camera is helpful
-for high-level image feature extracting.
+
+Furthermore, we also explore to learning high-level
+visual features and geo-calibrating cameras simultaneously.
+We believe that the geo-calibration parameters are closely related to
+the image representation. 
+Imagine the process of a human doing geo-localization, one could
+roughly guess where a photo was taken when she sees an polar bear on
+an iceberg on it. In this process, learning high-level features
+becomes a necessary step of abstracting visual hints to localize
+the camera.
+Based on this belief, we designed network to learn useful visual
+features by exploiting geographic information, which provides new ways
+for automatic feature learning.
 

### 2018-08-20 chapters/introduction/introduction.tex
a check from the abstract to main contributions

@@
 
-\begin{chapquote}{Alan Turing}
-  ``I propose to consider the question: Can machines think?''
+\begin{chapquote}{Morgan Freeman in {\em Transcendence (2014 film)}
+\\ \todo{don't laugh.}}
+  ``Geo-locating suspects in real time? I've never seen anything like
+it.''
 \end{chapquote}
+
 The ultimate goal of image understanding is to transfer visual
@@
 the camera geographic location ({\em geo-localization}), and the time
-the query image was captured ({\em time estimation}).
+when the query image was captured ({\em time estimation}).
 
@@
 localization.  In pose estimation aera, Work~\cite{zhai2016horizon,
-workman2016horizon, hold2017perceptual} has been done to to identify
+workman2016horizon, hold2017perceptual} has been done to identify
 the horizon line with CNNs (one can derive the camera roll and pitch
@@
 
-Closely related to camera geo-calibration, studies also have been done
-to identify the camera intrinsics using deep neural networks.
+Closely related to camera geo-calibration, problems of identifying
+camera intrinsics using deep neural networks have also been studied.
 Workman \etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
 focal length. Kendall \etal~\cite{kendall2015convolutional} propose a
-neural network that can identify 6-DOF camera parameters, but their
-method only limited to specific scenes.
+neural network that can identify 6-DOF camera parameters for specific
+scenes.
 
 \subsection{Ground-to-Aerial Geo-Calibration}
-Data-driven scene matching approaches are widely used to for
+Data-driven scene matching approaches are commonly used in
 geo-calibration.
 When localizing a camera, data-driven algorithms search for k-nearest
-neighbors of the query image in the database of the geo-tagged imagery.
+neighbors of the query image in a database of the geo-tagged imagery.
 To reduce the work of querying, the searching process is usually
-carried out in some feature space with applicable number of  
+carried out in feature space of applicable number of  
 dimensions~\cite{im2gps, li2010location,zamir2010accurate}.
-However, as items found in most reference dataset, geo-tagged
-ground-level images collected from the internet are usually noisy and
-sparse in geographic space. To achieve more accurate geo-calibration
-results, we need alternative image resources with more accurate
-geographic tags and denser spatial coverage.
+However, due to limited accuracies of GPS signals and the biased
+distribution of human population, geo-tagged ground-level images
+collected from smart devices are usually noisy and sparse in
+geographic space. To achieve better geo-calibration results, we
+need alternative image resources with more accurate geographic tags
+and more complete spatial coverage.
 
@@
 the geo-tagged aerial imagery becomes more publicly accessible
-than ever before. Aerial imagery downloading services like
+than ever. Aerial imagery downloading services like
 Microsoft Bing Map provide aerial images of various
-resolutions, which can cover most areas of the world with accurate
-geographic tags, making aerial imagery a rich source for
-reference database. We refer to the geo-calibration methods
-which use the aerial imagery as geographic reference as
+resolutions, which cover most areas of the world with accurate
+geographic registration, making aerial imagery a rich source for
+reference databases. We refer to geo-calibration
+methods which use the aerial imagery for geographic reference as
 ground-to-aerial geo-calibration.
@@
 geo-calibration~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
-has shown that convolutional neural networks are capable of extracting
+has shown that convolutional neural networks are efficient for extracting
 features from geo-tagged aerial imagery that can be matched to
@@
 past years. Compared to the manual feature engineering,
-automatic feature engineering approaches are able to to learn useful
+automatic feature engineering approaches allow to learn useful
 features without strong expert knowledge about the data. Among these
-approaches, deep neural networks are wildly accepted by researchers as
+approaches, deep neural networks are wildly accepted as
 good tools to learn high-level image representations.  The most
 commonly used approach for deep feature learning is full supervision,
-which usually requires manually annotated
-data~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
+which usually requires manual
+annotations~\cite{yosinski2015transferable,zhou2016learning,wen2016discriminative}.
 Unfortunately, such data is not always available for certain tasks.
-In contrast, unlabeled data is offen plentiful (\ie cellphone photos
+In contrast, unlabeled data is often plentiful (\ie cellphone photos
 in Instagram or Youtube videos).
@@
 %
-As new learning technique address the lack of massive amounts of
-labeled data, domain adaptation adapt the feature generating model to
-another feature domain so that it improve the performance when dealing
-with new input
+As new learning technique that addresses the lack of massive amounts
+of labeled data, domain adaptation forces the feature generating model
+to adapt another feature domain so that it improves the performance
+when dealing with new input
 data~\cite{fernando2013unsupervised,fernando2015joint,saenko2010adapting,wang2016actions,tinghui2016flow}.
-Duan \etal~\cite{duan2012learning} proposed to learn a linear
+Duan \etal~\cite{duan2012learning} propose to learn a linear
 projection to transfer from the source feature subspace to the target
-subspace. Sohn \etal~\cite{sohn2017unsupervised} improved the
+subspace. Sohn \etal~\cite{sohn2017unsupervised} improve the
 performance of video face recognition using an adversarial-based
-approach to adapt the network to unlabled video imagery.
+approach to adapt the network to unlabeled video imagery.
 
@@
 
-We make contributions in three main areas: 1) We proposed a general
+We make contributions in three main areas: 1) we proposed a general
 probabilistic model to jointly estimate the geo-calibration
-parameters, 2) we decompose the full geo-calibration into several
+parameters, 2) we decomposed the full geo-calibration into several
 partial geo-calibration tasks, each of which provides a strong
-constraint function that fits in the general model, and 3) we show
+constraint function that fits into the general model, and 3) we show
 that learning to geo-calibrate a camera is helpful for high-level
@@
 
-The first two contributions consist of our main approach. Our
+The first two contributions form our main approach. Our
 algorithm feeds inputs (images, time and manual annotations) to
@@
 we fuse these constraint functions to simulate the joint distribution
-over the complete geo-calibration parameters. The flowchart of
-our approaches refers to \figref{intro:architecture}.
+over the complete geo-calibration parameters. We present the flowchart of
+our approach in \figref{intro:architecture}.
 
-Furthermore, we also explore to learning high-level
-visual features and geo-calibrating cameras simultaneously.
-We believe that the geo-calibration parameters are closely related to
-the image representation. 
-Imagine the process of a human doing geo-localization, one could
-roughly guess where a photo was taken when she sees an polar bear on
-an iceberg on it. In this process, learning high-level features
-becomes a necessary step of abstracting visual hints to localize
-the camera.
-Based on this belief, we designed network to learn useful visual
-features by exploiting geographic information, which provides new ways
-for automatic feature learning.
+Furthermore, we also explore to learning high-level visual features
+and geo-calibrating cameras simultaneously.  We believe that camera
+poses, geographic locations and image capture times are closely
+related to image representations. 
+Imagine a human geo-localizing a camera from an image it took, one
+could roughly guess where a photo was taken when she sees an polar
+bear on an iceberg. In this scenario, learning high-level
+features becomes a necessary process of abstracting visual hints to
+localize the camera.
+Based on this belief, we designed neural networks to learn useful
+visual features by solving geo-calibration tasks. Our work provide new
+ways for automatic feature learning.
 

### 2018-08-20 dissertation.tex
a check from the abstract to main contributions

@@
 the world and how it changes in time. Current models for
-geo-calibration are mostly deterministic, which fails to model the
-the inherent uncertainties when the scene of the image is ambiguous.
-Furthermore, the outputs of deterministic system can not be used by
-algorithms that take probabilistic inputs. To address these
+geo-calibration are mostly deterministic, which in many cases fails to
+model the inherent uncertainties when the scene of the image is
+ambiguous.  Furthermore, the outputs of deterministic system can not
+be used by algorithms that take probabilistic inputs. To address these
 limitations, we propose a probabilistic model for camera

### 2018-08-21 chapters/introduction/introduction.tex
minor change

@@
 \subsection{General Probabilistic Model for Geo-Calibration}
-The complete camera geo-calibration detects the camera
-geographic location, pose, and focal length of the camera.  We
-design a general model to estimate the probability over these
-geo-calibration parameters: First, we model the relationship between the
-image projection of the scene and the geo-calibration parameters. This
-relationship can be described by the pin-hole model, and
-the geographic location of the camera.
-We then construct a scoring function to measure the ``fitness'' between the
-calibration parameters and the observation of the image. 
+We design a general model to estimate the probability over all
+geo-calibration parameters. First, we model the process of projecting
+from the scene at given location, time, and in given camera pose.
+%This the appearance of the image frame are determined by the pin-hole
+%model and the geographic location of the camera.
+We use a scoring function to measure the ``fitness'' between these
+geo-calibration parameters and the appearance of the image. 
 The scoring function is proportional to the probability distribution
-of the camera parameters. We propose a Markov Chain Monte
-Carlo (MCMC) sampling approach to approximate the underlying
-probability distribution over the full geo-calibration of the camera.
+over the geo-calibration parameters, but the denominator is unknown. We
+then propose a Markov Chain Monte Carlo (MCMC) sampling approach to
+approximate the underlying probability distribution.
 Our model is a general architecture, which can take different
-constraints to form the scoring function. The details about this model
+constraints to form the scoring function. The details of this model
 can be found in \chapref{mcmc}.
@@
 \subsection{Developing Constraint Functions}
-In our general model, the scoring function is defined as a linear
-combination of multiple constraint functions.
+In the general model, we define the scoring function is as a weighted
+summation of a series of constraint functions.
 In the rest of the work, we focus on developing good constraint
-functions for different set of calibration parameters.
+functions for different set of geo-calibration parameters. 
+A constraint function outputs a score or probability for some given
+geo-calibration parameters conditional on the input image.
 
 \begin{itemize}[noitemsep]
-  \item \textbf{Constraint for Horizon Line and Vanishing Points:}
-  We first estimate camera roll and pitch angles. Assuming the intrinsic
-  parameters are known, camera roll and pitch angles can be
-  derived from the horizon line position in the image. Compared to
-  directly detecting the camera pose, identifying horizon line is easier
-  because it is tightly related to the appearance
-  of the scene. In our work, we create a new method using CNN to
-  estimate the prior distribution of the horizon line. We assign
-  a probability to each horizon line by measuring their consistences
-  with vanishing points detected using traditional statistic methods.
-  We present the algorithm details in \chapref{fasthorizon}.
+  \item \textbf{Constraint for Camera Pose:}
+  In this constraint we model the camera roll and pitch angles.
+  Assuming the intrinsic parameters are known, camera roll and pitch
+  angles can be derived from the horizon line position on the image.
+  Compared to directly detecting the camera pose, identifying horizon
+  line is easier because it is tightly related to the scene layout.
+  In our work, we create a new method using CNN to estimate the
+  prior distribution over the horizon line. We assign a probability to
+  each horizon candidate sampled from the prior distribution by
+  measuring their consistences with vanishing points detected using
+  traditional statistic methods. We present the algorithm details in
+  \chapref{fasthorizon}.  \newline
+
+  \item \textbf{Constraint for Time and Coarse Location:}
+  In this work, we demonstrate to estimate probability over the
+  capture time and the camera geographic location given the input image.
+  Our network has two branches which predict the image
+  capture time and the geographic location simultaneously.
+  For time estimation, our network is able to predict the
+  joint distribution over the month of the year and the UTC hour of the
+  day when the input image has been captured.
+  For coarse camera geo-localization, We provide two approaches to
+  obtain the probability distribution over the camera geographic
+  location. Most straightforwardly, our network outputs the discrete
+  distribution over the location in the world, which is uniformly
+  divided as a 2D meshgrid. Better results can be procured with the
+  image capture time as auxiliary input (if it is known). 
+  We present the algorithm details in \chapref{whenwhere}.
   \newline
 
-  \item \textbf{Constraint for Time and Coarse Geographic Locations:}
-  In this work, we demonstrate to estimate the capture time and the
-  camera geographic location given the input image.
-  Our network has two heads to predict the image
-  capture time and the geographic location jointly.
-  For time estimation, our network is able to predict the
-  joint distribution over the month of the year and the global hour of the
-  day when the input image has been captured.
-  For camera geo-localization, We provide two approaches to obtain the
-  probability distribution over the camera geographic location. Most
-  straightforwardly, our network estimate the categorical distribution
-  over location of the world, which is represented as a $N \times M$
-  meshgrid. Better results can be procured with image capture time as
-  auxiliary input (if it is known). 
-  %Our algorithm can also compute the probability at arbitrary
-  %geographic location, with lower accuracy than the straightforward
-  %method.
-  We will present the algorithm details in \chapref{whenwhere}.
-  \newline
-
-  \item \textbf{Constraint for Fine Geographic Locations and Orientations:}
+  \item \textbf{Constraint for Fine Location and Orientation:}
   In our previous method, we present that our algorithm can estimate
@@
   work we focus on refining the geo-localization results with the help
-  of overhead imagery and on estimating geo-orientation of the camera. 
-  We first learn to segment the ground scene from its paired aerial image.
-  When refining the camera geographic location, we compare the
-  semantic layout of the ground image with the semantic layout
-  transferred from overhead images, which are sampled in different
-  locations and orientation angles. The optimal prediction is found when the
-  semantic layouts from these two sources match best. For probabilistic
-  outputs, we assign a score to each location and orientation setting,
-  based on how well the semantic layouts match to each other. We will
-  present the algorithm details in \chapref{crosstransf}.
+  of overhead imagery and on estimating the geo-orientation of the camera. 
+  We trained our network with cross-view pairs.
+  We first learn to deduce the semantic layout of the ground
+  scene from the associated aerial image.
+  Given a geographic location and orientation, we sample the aerial
+  image, then compare its semantic layout of the ground scene
+  with the semantic layout of the query image (ground image).
+  We assign a score to that location and orientation by matching these
+  two semantic layouts.
+  We present the algorithm details in \chapref{crosstransf}.
   \newline

### 2018-08-21 chapters/introduction/introduction.tex
finish up

@@
 methods which use the aerial imagery for geographic reference as
-ground-to-aerial geo-calibration.
+ground-to-aerial geo-calibration. Data used for ground-to-aerial
+geo-calibration is referred to as cross-view pairs.
+A cross-view pair consists of a ground image and an aerial image at
+the same location, and but not necessarily aligned in orientation.
 
@@
 \subsection{Geo-Calibration for Feature Learning}
-Our methods also focus on lavaging the camera geographic information to
-deal with the challenges of lacking manually annotated data during DNN
-training. The insight is that the camera geographic information
-encodes semantic information because it is related to the
-appearances of the scenes.
+Our methods also provide another way to dealing with the challenges of
+lacking manual annotations during DNN training. By learning to
+geo-calibrate a camera, we believe the networks are able to learn
+high-level image representations. This belief comes from the fact that
+the geo-calibration information of a camera encodes semantic
+information because it is closely related to the appearances of the
+scene.
+We explore two types of learning techniques for high-level feature
+extraction: 1) semantic segmentation of the aerial imagery with
+ground-level annotations which is plentiful, and 2) geo-temporal
+features with automatically annotated geographic locations and time.
 
@@
   \item \textbf{Ground-to-Aerial Feature Learning:}
-  Current machine learning methods address problems that involves mostly
-  the ground-level imagery. Tons of dataset targeting on ground imagery are
-  annotated while much fewer are done for the satellite/aerial imagery. In
-  \chapref{crosstransf}, we proposed a method to learn the aerial image
-  semantic segmentation with only ground-level ground truth. Our method
-  exploits the spatial correspondences between images in cross-view
-  pairs. 
-  In this work, we try to transfer the semantics from the ground
-  imagery to the aerial imagery by identifying the latent geometry
-  correspondences between these two. Similar to the monocular depth
-  estimation methods that driven by the technique called {\em
+  Most current machine learning methods study problems involving the
+  ground imagery. There exist many annotated dataset of the ground
+  imagery while much fewer of the aerial imagery. 
+  In \chapref{crosstransf}, we proposed a
+  method to learn to semantically segment aerial images with only
+  ground-level annotations. Our method exploits the spatial
+  correspondences between images in cross-view pairs. 
+  In this work, we try to transfer the semantic knowledge from the
+  ground domain to the aerial domain by identifying their latent
+  geometric correspondences. Similar to {\em
   Reprojection Losses}~\cite{garg2016unsupervised,
-  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
-  network learns to geometrically project pixels from the aerial
-  images to the ground images, and to segment the aerial images
-  jointly.
+  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}
+  which have been successfully applied in monocular depth estimation,
+  our network learns geometric projection from aerial to ground, and
+  to semantically segment the aerial images jointly.
   \newline
@@
   learn geo-temporal image representations with geographic locations and
-  capture time.
+  capture time which are automatically captured by smart devices.
   Our work is most similar to Li and Snavely~\cite{li2018learning},

### 2018-08-23 chapters/introduction/introduction.tex
fix a citation

@@
 which usually requires manual
-annotations~\cite{yosinski2015transferable,zhou2016learning,wen2016discriminative}.
+annotations~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
 Unfortunately, such data is not always available for certain tasks.

### 2018-08-24 chapters/introduction/introduction.tex
background change

@@
 
-\begin{chapquote}{Morgan Freeman in {\em Transcendence (2014 film)}
-\\ \todo{don't laugh.}}
+\begin{chapquote}{Morgan Freeman in {\em Transcendence (2014 film)}}
   ``Geo-locating suspects in real time? I've never seen anything like
@@
 picture was taken is important to understand the world. However, most
-images does not carry such information, thus we need to develop
-algorithms to dig them up.  We refer to the task of estimating these
-properties as {\em geo-calibration}.
-Most recent work of geo-calibration focus on deterministic systems, 
+images does not carry such information. Our thesis focuses on
+developing algorithms to estimate this information.
+We refer to the task of estimating these properties as {\em
+geo-calibration}.
+Most recent work of geo-calibration focus on deterministic systems
+\todo{citations}, 
 which have some drawbacks: 1) they can not model the inherent
-uncertainties from images of ambiguous scenes, and 2) they can not be
-used by applications that take probabilistic inputs. To address
-these problems, we propose to build probabilistic models for camera
-geo-calibration.
+uncertainties from images of ambiguous scenes, and 2) without a proper
+modeling of the uncertainty, subsequent processing can yield overly
+confident predictions. To address these problems, we propose to build
+probabilistic models for camera geo-calibration.
 
-We also show that learning to geo-calibrate a camera is helpful for
-high-level feature extracting. Feature engineering is essential for
-image understanding. In recent years, learning based approaches for
-high-level feature extracting like deep neural nets have drawn a lot
-of attention due to the fact that they do not need any expert
-knowledge about the target data. However, most of these feature
-learning methods heavily relies on manually labeled data. In our
-thesis, we presented alternative ways to learn high-level image
-representations when the manually labeled data is either insufficient
-or absent.
+We also show that learning to geo-calibrate a camera allows us to
+implicitly learn to understand the content of the scene.
+As an essential part of scene understanding, how to extract image
+features is an important problem being studied for decades.  In
+recent years, learning based approaches for image feature extraction
+like convolutional neural networks have drawn a lot of attention due
+to the fact that they do not need expert knowledge about the target
+data. However, most of these feature learning methods require large
+quantity of manually labeled data sets.  In this thesis, we presented
+alternative ways to learn high-level image features when the
+manually labeled data is either insufficient or absent.
 
 \section{Background}
+For a better understanding of our work, before the discussion of the
+main topics, we would like to introduce some related computer vision
+concepts in this section.
 
 \subsection{Geo-Calibration of Outdoor Images}
-Automatic image geo-calibration of outdoor images continues to grow in
+Automatic geo-calibration of outdoor images continues to grow in
 importance as a direct result of the increasing amount of imagery
@@
 \item \textbf{Pose Estimation:}
+Pose estimation includes estimating the camera yaw, pitch, and roll
+angles, $(\theta_{yaw}, \theta_{pitch}, \theta_{roll})$ from a
+image. In the context of geo-calibration, the yaw angle
+$\theta_{yaw}$ is referred to as the geographic orientation angle of
+the camera.
+%
 Li et al.~\cite{li2012worldwide} exploit geo-registered 3D points
@@
 \item \textbf{Geo-Localization:}
-Extracting location-dependent features from
-image data has drawn a great detail of attention from the vision
-community~\cite{jacobs07geolocate, jacobs11geolocate,
-jacobs08geoorient}. The common trend amongst these methods is that
-they take advantage of a large dataset of geo-referenced images. Hays
-and Efros~\cite{hays2008im2gps} use a data-driven scene matching
-approach to localize a query image using a large dataset of geo-tagged
-images.  Doersch \etal~\cite{doersch2012what} extract
-location-dependent features that capture the relative appearance
-differences of large cities.  Lin et al.~\cite{lin2013cross} localize
-a ground-level image by learning the relationship between pairs of
-ground and aerial images \footnote{In the context of our thesis, we
-do not distinguish between the satellite imagery and the aerial
-imagery} of the same location. Other techniques focus
-on urban environments and infer location using local image
-descriptors~\cite{schindler2008detecting,snavely2006photo}.
-Many other cues exist, such as the
+The task of geo-localization estimates the geographic location, $(lat,
+lon)$, of the camera from the input image or video frames.
+%
+As an important step of geo-localization, extracting
+location-dependent features from image data has drawn a great detail
+of attention from the vision community~\cite{jacobs07geolocate,
+jacobs11geolocate, jacobs08geoorient}. The common trend amongst these
+methods is that they take advantage of a large dataset of
+geo-referenced images. Hays and Efros~\cite{hays2008im2gps} use a
+data-driven scene matching approach to localize a query image using a
+large dataset of geo-tagged images.  Doersch
+\etal~\cite{doersch2012what} extract location-dependent features that
+capture the relative appearance differences of large cities.  Lin et
+al.~\cite{lin2013cross} localize a ground-level image by learning the
+relationship between pairs of ground and aerial images \footnote{In
+the context of our thesis, we do not distinguish between satellite
+imagery and aerial imagery} of the same location. Other techniques
+focus on urban environments and infer location using local image
+descriptors~\cite{schindler2008detecting,snavely2006photo}.  Many
+other cues exist, such as the
 skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
@@
 \item \textbf{Time Estimation:}
+The goal of time estimation is to estimate the time when the input
+image was captured. Depending on the application, the scale of a
+time estimator outputs may range from year to hour.
+%
 Matzen and Snavely~\cite{matzen2014scene} predict

### 2018-08-24 dissertation.tex
background change

--- 2018-08-14 dissertation.tex
@@
 that are helpful for decision making.
-%
-%In general, understanding images is not trivial for machines.
-%Under different scenarios, researchers divide image
-%understanding into different computer vision tasks. For example,
-%pedestrian detection is essential to autonomous driving, and image
-%retrieval to an image searching engine.
-%
-Knowing when, where, and in which direction picture was taken, the
-task of geo-calibration makes it possible to use imagery to understand
+Knowing when, where, and in which direction a picture was taken, the
+task of geo-calibration, makes it possible to use imagery to understand
 the world and how it changes in time. Current models for
-geo-calibration are mostly deterministic, which fails to model the
-the inherent uncertainties when the scene of the image is ambiguous.
-Furthermore, the outputs of deterministic system can not be used by
-algorithms that take probabilistic inputs. To address these
-limitations, we propose a probabilistic model for camera
-geo-calibration using deep neural networks.
-%
-While our primary contribution is geo-calibration, We also show that
-learning to geo-calibrate a camera is helpful for high-level feature
-extraction.
-%
-%Our discoveries can provide researchers new insights for both camera
-%geo-calibration and DNN training.
+geo-calibration are mostly deterministic, which in many cases fails to
+model the inherent uncertainties when the image content is
+ambiguous. Furthermore, without a proper modeling of the uncertainty, subsequent
+processing can yield overly confident predictions.
+To address these limitations, we propose a probabilistic model for
+camera geo-calibration using deep neural networks.
+While our primary contribution is geo-calibration, we also show that
+learning to geo-calibrate a camera allows us to implicitly learn to
+understand the content of the scene.
 }

### 2018-08-25 chapters/introduction/introduction.tex
edits before geo-calibration for feature learning section

@@
 \section{Background}
-For a better understanding of our work, before the discussion of the
-main topics, we would like to introduce some related computer vision
-concepts in this section.
+For a better understanding of our work, we would like to introduce
+some related computer vision concepts in this section before the
+discussion of the main topics.
 
@@
 
+In conclusion, most of the geo-calibration algorithms we mention above
+relies on finding visual cues from the input images. The development
+of these algorithms require strong human expertise about the data,
+thus can only be applied in limited scenarios. Therefore, researchers
+need new methodologies in order to make the development of
+geo-calibration algorithms more efficient.
+
 \subsection{Deep Learning in Geo-Calibration}
@@
 Weyand and Kostrikov \etal~\cite{planet} propose a convolutional
-network to predict the geographic location of the input
+neural network (CNN) to predict the geographic location of the input
 image. Walch \etal~\cite{walch2017image} aggregate learned CNN
 features with LSTM to generate global image representation for camera
-localization.  In pose estimation aera, Work~\cite{zhai2016horizon,
-workman2016horizon, hold2017perceptual} has been done to identify
-the horizon line with CNNs (one can derive the camera roll and pitch
-angles from the horizon line position giving the camera focal length).
+localization.  Studies about camera pose
+estimation~\cite{zhai2016horizon, workman2016horizon,
+hold2017perceptual} has been done by identifying the horizon line with
+CNNs (one can derive the camera roll and pitch angles from the horizon
+line position giving the camera focal length).
 
@@
 camera intrinsics using deep neural networks have also been studied.
-Workman \etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
-focal length. Kendall \etal~\cite{kendall2015convolutional} propose a
-neural network that can identify 6-DOF camera parameters for specific
-scenes.
+Workman \etal~\cite{workman2015deepfocal} develop a CNN to estimate
+the camera focal length. Kendall \etal~\cite{kendall2015convolutional}
+propose a neural network that can identify 6-DOF camera parameters for
+specific scenes.
+
+These geo-calibration methods make the predictions directly out of
+DNNs.  There is another big category of geo-calibration methods that
+use aerial imagery as geo-registered database, which we will introduce
+in the following section.
 

### 2018-08-27 chapters/introduction/introduction.tex
minor change

@@
 
+The key for the success of these ground-to-aerial geo-calibration
+methods is to learn descriptive features good for ground-to-aerial
+imagery matching. In the following section, we will show how to use
+geo-calibration information to learn useful features.
+
 \subsection{Geo-Calibration for Feature Learning}
 
-Automatic feature engineering has drawn a lot of attention over the
-past years. Compared to the manual feature engineering,
-automatic feature engineering approaches allow to learn useful
-features without strong expert knowledge about the data. Among these
-approaches, deep neural networks are wildly accepted as
-good tools to learn high-level image representations.  The most
-commonly used approach for deep feature learning is full supervision,
-which usually requires manual
+Manually engineering visual features is a common practice for many
+computer vision tasks. One of the successful example of manually
+engineered feature is the SIFT feature~\cite{lowe1999object}.
+In recent years, automatic feature engineering has drawn a lot
+of attention. Compared to the manual feature
+engineering, automatic feature engineering approaches allow to learn
+useful features without strong expert knowledge about the data. Among
+these approaches, deep neural networks are wildly accepted as good
+tools to learn high-level image representations.  The most commonly
+used approach for deep feature learning is full supervision, which
+usually requires large number of manual
 annotations~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
-Unfortunately, such data is not always available for certain tasks.
+Unfortunately, such data is not always available for certain tasks or
+needs to invest a huge amount of human labors to create.
 In contrast, unlabeled data is often plentiful (\ie cellphone photos
@@
 These methods typically
-exploit some known quantity of the data (e.g., pixel color values) to
-avoid expensive manual annotation. As a byproduct, a useful visual
-representation is learned.
+exploit some known quantity of the data, like pixel color values, to
+avoid expensive manual annotation.
+By learning these quantities associated with the data, one
+can obtain useful features of the image.
 For example, Zhang et al.~\cite{zhang2016colorful} show how image
@@
 approach to adapt the network to unlabeled video imagery.
+
+So far, we have explained four important related computer vision
+concepts. In the following section, we are going to discuss our main
+contributions in this thesis.
 

### 2018-08-28 chapters/introduction/introduction.tex
before fine location and orientation section

@@
 constraint function that fits into the general model, and 3) we show
-that learning to geo-calibrate a camera is helpful for high-level
-image feature extraction.
+that learning to geo-calibrate a camera is a useful pretext for image
+feature learning.
 
-The first two contributions form our main approach. Our
+The first two contributions make our main approach. Our
 algorithm feeds inputs (images, time and manual annotations) to
-different constraint models, which work as constraint functions. Then
+different constraint functions. Then
 we fuse these constraint functions to simulate the joint distribution
@@
 
-Furthermore, we also explore to learning high-level visual features
+Furthermore, we also explore to learning image features
 and geo-calibrating cameras simultaneously.  We believe that camera
@@
 related to image representations. 
-Imagine a human geo-localizing a camera from an image it took, one
-could roughly guess where a photo was taken when she sees an polar
-bear on an iceberg. In this scenario, learning high-level
-features becomes a necessary process of abstracting visual hints to
-localize the camera.
-Based on this belief, we designed neural networks to learn useful
-visual features by solving geo-calibration tasks. Our work provide new
-ways for automatic feature learning.
+Based on the belief that visual features which abstract the image
+contents are the necessary for solving the geo-calibration tasks, we
+designed neural networks to learn useful visual features by
+geo-calibrating cameras. Our work provide new ways for automatic
+feature learning.
 
@@
 approximate the underlying probability distribution.
-Our model is a general architecture, which can take different
-constraints to form the scoring function. The details of this model
+Our model is flexible that it is able to contribute different
+constraint functions to the scoring function. The details of this model
 can be found in \chapref{mcmc}.
@@
 \subsection{Developing Constraint Functions}
-In the general model, we define the scoring function is as a weighted
+In the general model, we define the scoring function as a weighted
 summation of a series of constraint functions.
 In the rest of the work, we focus on developing good constraint
-functions for different set of geo-calibration parameters. 
+functions for different sets of geo-calibration parameters. 
 A constraint function outputs a score or probability for some given
@@
   \item \textbf{Constraint for Camera Pose:}
-  In this constraint we model the camera roll and pitch angles.
+  In this constraint, we model the camera roll and pitch angles.
   Assuming the intrinsic parameters are known, camera roll and pitch
@@
   Compared to directly detecting the camera pose, identifying horizon
-  line is easier because it is tightly related to the scene layout.
+  line is easier because it is reflected by the scene layout.
   In our work, we create a new method using CNN to estimate the
@@
   each horizon candidate sampled from the prior distribution by
-  measuring their consistences with vanishing points detected using
-  traditional statistic methods. We present the algorithm details in
-  \chapref{fasthorizon}.  \newline
+  measuring their consistences with detected vanishing points. We
+  present the algorithm details in \chapref{fasthorizon}.  \newline
 
   \item \textbf{Constraint for Time and Coarse Location:}
-  In this work, we demonstrate to estimate probability over the
+  In this work, we estimate the probability over the
   capture time and the camera geographic location given the input image.
@@
   location. Most straightforwardly, our network outputs the discrete
-  distribution over the location in the world, which is uniformly
-  divided as a 2D meshgrid. Better results can be procured with the
-  image capture time as auxiliary input (if it is known). 
-  We present the algorithm details in \chapref{whenwhere}.
+  distribution over the geographic location of the camera. Better
+  results can be procured with the image capture time as auxiliary input
+  (if it is known).  We present the algorithm details in
+  \chapref{whenwhere}.
   \newline

### 2018-08-28 chapters/introduction/introduction.tex
in location and orientation

@@
 
-  \item \textbf{Constraint for Time and Coarse Location:}
+  \item \textbf{Constraint for Time and Location:}
   In this work, we estimate the probability over the
@@
 
-  \item \textbf{Constraint for Fine Location and Orientation:}
+  \item \textbf{Constraint for Location and Orientation:}
   In our previous method, we present that our algorithm can estimate
-  the camera location distribution in low-res world division. In this
-  work we focus on refining the geo-localization results with the help
-  of overhead imagery and on estimating the geo-orientation of the camera. 
-  We trained our network with cross-view pairs.
+  the discrete camera location. The predictions are only approximate
+  due to the limitation of the algorithm. In this
+  work, we propose a ground-to-aerial geo-calibration method that can
+  further refine the prediction results and estimate the
+  camera geo-orientation with overhead imagery.
+%
   We first learn to deduce the semantic layout of the ground

### 2018-08-29 chapters/introduction/introduction.tex
before geo-calibration for feature learning

@@
 our approach in \figref{intro:architecture}.
-
+%
 Furthermore, we also explore to learning image features
@@
   %
-  We first learn to deduce the semantic layout of the ground
-  scene from the associated aerial image.
-  Given a geographic location and orientation, we sample the aerial
-  image, then compare its semantic layout of the ground scene
-  with the semantic layout of the query image (ground image).
-  We assign a score to that location and orientation by matching these
-  two semantic layouts.
+  We designed a network that can jointly learn the semantic layout of
+  the aerial image and its projection to the ground-level perspective.
+  When computing the value of constraint function, feed the aerial
+  image of a given location and orientation set to the network. 
+  By comparing the aerial-to-ground layout with the real layout of the
+  ground image, we are able to measure the consistency of these two as
+  the value of our constraint function.
   We present the algorithm details in \chapref{crosstransf}.

### 2018-08-29 chapters/introduction/introduction.tex
main contribution first paragraph

@@
   Compared to directly detecting the camera pose, identifying horizon
-  line is easier because it is reflected by the scene layout.
+  line is easier because it can be explicitly estimated from the scene
+  layout.
   In our work, we create a new method using CNN to estimate the
@@
   the aerial image and its projection to the ground-level perspective.
-  When computing the value of constraint function, feed the aerial
+  When computing the value of the constraint function, feed the aerial
   image of a given location and orientation set to the network. 
@@
 
-\subsection{Geo-Calibration for Feature Learning}
-Our methods also provide another way to dealing with the challenges of
-lacking manual annotations during DNN training. By learning to
-geo-calibrate a camera, we believe the networks are able to learn
-high-level image representations. This belief comes from the fact that
-the geo-calibration information of a camera encodes semantic
-information because it is closely related to the appearances of the
-scene.
-We explore two types of learning techniques for high-level feature
-extraction: 1) semantic segmentation of the aerial imagery with
-ground-level annotations which is plentiful, and 2) geo-temporal
-features with automatically annotated geographic locations and time.
+\subsection{Geo-Calibration for Image Feature Learning}
+Full supervision algorithms are powerful tools to learn useful image
+features. However, full supervision algorithms requires large number
+of annotated data, which in many cases are either not available or
+financially infeasible to obtain. On the other hand, images with free
+annotations like time and locations are plentiful on the Internet.
+To use these image resources for image feature learning, 
+we explore two types of learning techniques that uses time and
+locations as annotations: 1) {\em ground-to-aerial segmentation}, and 2)
+{\em geo-temporal feature learning} with time/location tagged images.
 
 \begin{itemize}[noitemsep]
-  \item \textbf{Ground-to-Aerial Feature Learning:}
+  \item \textbf{Ground-to-Aerial Segmentation:}
   Most current machine learning methods study problems involving the

### 2018-08-29 chapters/introduction/junk.tex
background geo-calibration
more changes on background.
geo-calibration feature learning
before fine location and orientation section
main contribution first paragraph

@@
 geo-localization.
+
+%However, recognizing the geo-location and geo-orientation of an
+%arbitrary outdoor image is an extremely challenging task.  Many
+%methods have been proposed; the most common approach is to build a
+%large database of images with known location and localize a query
+%image using either local~\cite{li2010location,schindler2008detecting}
+%or global~\cite{hays2008im2gps,doersch2012what} image features. 
+%This approach is not applicable when no nearby ground-level imagery
+%exists in the reference database, such as when the image was not
+%captured near a popular tourist destination.  Even when reference
+%imagery is available, the appearance of the objects may not be
+%visually distinctive, for example a train track or a body of water.
+
+%Cross-view image pair is the basic element for ground-to-aerial
+%geo-calibration. It consists of a ground-level image and an overhead
+%image at the same location. In some cases, two images may also be aligned
+%in orientation.
+
+Though full supervision work well in many applications, there are
+exponentially more image resources without manual annotation (cell
+phone imagery, YouTube videos\etc), which show a huge potential for
+visual feature learning.
+
+%Imagine a human geo-localizing a camera from an image it took, one
+%could roughly guess where a photo was taken when she sees an polar
+%bear on an iceberg. In this scenario, learning high-level
+%features becomes a necessary process of abstracting visual hints to
+%localize the camera.
+
+Our methods also provide another way to dealing with the challenges of
+lacking manual annotations during DNN training. By learning to
+geo-calibrate a camera, we believe the networks are able to learn
+high-level image representations. This belief comes from the fact that
+the geo-calibration information of a camera encodes semantic
+information because it is closely related to the appearances of the
+scene.

### 2018-08-30 chapters/introduction/introduction.tex
close first run editting

@@
 
-\subsection{Geo-Calibration for Image Feature Learning}
+\subsection{Geo-Calibration for Feature Learning and Image
+Understanding}
 Full supervision algorithms are powerful tools to learn useful image
@@
   \item \textbf{Ground-to-Aerial Segmentation:}
-  Most current machine learning methods study problems involving the
-  ground imagery. There exist many annotated dataset of the ground
-  imagery while much fewer of the aerial imagery. 
-  In \chapref{crosstransf}, we proposed a
-  method to learn to semantically segment aerial images with only
+  Semantic segmentation plays an important role in image understanding.
+  The training for semantic segmentation task requires a large number
+  of annotated data.
+  However, most large scale annotated datasets like ImageNet~\cite{ILSVRC15}
+  and COCO~\cite{lin2014microsoft} are made of ground level images. By
+  comparison, annotated datasets for aerial imagery are rare.
+  %
+  To deal with this problem, we proposed a
+  DNN to learn to semantically segment aerial images with only
   ground-level annotations. Our method exploits the spatial
@@
   which have been successfully applied in monocular depth estimation,
-  our network learns geometric projection from aerial to ground, and
+  our network learns the geometric projection from aerial to ground, and
   to semantically segment the aerial images jointly.
+  We present the learning details in \chapref{crosstransf}
   \newline
 
-  \item \textbf{Geo-Temporal Feature Learning:}
-  In \chapref{whenwhere}, we demonstrate that our algorithm is able to
-  learn geo-temporal image representations with geographic locations and
-  capture time which are automatically captured by smart devices.
-  Our work is most similar to Li and Snavely~\cite{li2018learning},
-  who propose an approach for learning intrinsic images by observing
-  image sequences with varying illumination over time. While their
-  targets are reflectance and shading images of the scene, we consider
-  two novel pretext tasks, time and location estimation.
+  \item \textbf{Location and Time as Pretext Task:}
+  Smart devices like cellphones and webcams becomes popular and most
+  of them are equipped with clocks and GPS modules nowadays. Thanks to
+  the development of social networks, researchers now can find
+  a lot images online that are tagged with time and locations. In
+  \chapref{whenwhere}, we propose an algorithm that treats the location and
+  time as pretext task to learn useful image features.
   By learning to predict the geographic location and capture time of
@@
 \end{itemize}
+
+\todo{describe problems to be solve}
+
+In summary, the main contributions of our work include developing a
+probabilistic framework to solve geo-calibration problems, and
+proposing new methods to learn image features with geo-calibration
+information. We are going to present our approaches in detail in the
+following chapter.

### 2018-08-30 chapters/introduction/junk.tex
close first run editting

@@
 scene.
+
+In \chapref{whenwhere}, we demonstrate that our algorithm is able to
+learn geo-temporal image representations with geographic locations and
+capture time which are automatically captured by smart devices.
+Our work is most similar to Li and Snavely~\cite{li2018learning},
+who propose an approach for learning intrinsic images by observing
+image sequences with varying illumination over time. While their
+targets are reflectance and shading images of the scene, we consider
+two novel pretext tasks, time and location estimation.

### 2018-08-30 chapters/introduction/introduction.tex
minor changes
minor change

@@
 world which are helpful for decision making.
-However, understanding images is a not trivial task for machines.
+However, understanding images is not a trivial task for machines.
 In order to handle various complicated scenarios, researchers divide
@@
 detection for autonomous driving, face recognition for security
-system, and image retrieval for image searching engines.
+system, and image retrieval for searching engines.
 
@@
 images does not carry such information. Our thesis focuses on
-developing algorithms to estimate this information.
-We refer to the task of estimating these properties as {\em
-geo-calibration}.
-Most recent work of geo-calibration focus on deterministic systems
+developing algorithms to estimating these properties. We
+refer to the task as {\em geo-calibration}.
+
+Most recent geo-calibration algorithms are deterministic systems
 \todo{citations}, 
-which have some drawbacks: 1) they can not model the inherent
+which have some obvious drawbacks: 1) they can not model the inherent
 uncertainties from images of ambiguous scenes, and 2) without a proper
-modeling of the uncertainty, subsequent processing can yield overly
+modeling of the uncertainty, the subsequent process can yield overly
 confident predictions. To address these problems, we propose to build
@@
 We also show that learning to geo-calibrate a camera allows us to
-implicitly learn to understand the content of the scene.
+learn to understand the scene.
 As an essential part of scene understanding, how to extract image
@@
 information. We are going to present our approaches in detail in the
-following chapter.
+following chapters.

### 2018-08-31 chapters/introduction/introduction.tex
check a lot of things

@@
 Most recent geo-calibration algorithms are deterministic systems
-\todo{citations}, 
-which have some obvious drawbacks: 1) they can not model the inherent
-uncertainties from images of ambiguous scenes, and 2) without a proper
-modeling of the uncertainty, the subsequent process can yield overly
-confident predictions. To address these problems, we propose to build
-probabilistic models for camera geo-calibration.
+\todo{citations}. 
+Deterministic systems have some obvious drawbacks: 1) they can not
+model the inherent uncertainties from images of ambiguous scenes, and
+2) without a proper modeling of the uncertainty, the subsequent
+process can yield overly confident predictions. To address these
+problems, we propose to build probabilistic systems for camera
+geo-calibration.
 
 We also show that learning to geo-calibrate a camera allows us to
-learn to understand the scene.
+learn about the scene of the image.
 As an essential part of scene understanding, how to extract image
@@
 data. However, most of these feature learning methods require large
-quantity of manually labeled data sets.  In this thesis, we presented
-alternative ways to learn high-level image features when the
+quantity of manually labeled datasets.  In this thesis, we presented
+alternative ways to learn image features when the
 manually labeled data is either insufficient or absent.
@@
 \section{Background}
-For a better understanding of our work, we would like to introduce
-some related computer vision concepts in this section before the
-discussion of the main topics.
+To give a better understanding of our work, we would like to introduce
+some related computer vision concepts before we discuss the main topics.
+We start with the definition of geo-calibration,
+along with its literature. Next, we introduce the history of deep
+learning methods for geo-calibration, and a big category of approaches
+that use aerial imagery. In the end, we cover some related work
+of weakly supervised learning techniques.
 
@@
 monitoring~\cite{zhang2012mining}. Conceptually the geo-calibration
-task includes: identifying the camera pose ({\em pose estimation}),
+task includes identifying: the camera pose ({\em pose estimation}),
 the camera geographic location ({\em geo-localization}), and the time
-when the query image was captured ({\em time estimation}).
+when the image was captured ({\em time estimation}).
 
@@
 \item \textbf{Pose Estimation:}
-Pose estimation includes estimating the camera yaw, pitch, and roll
+Pose estimation is to estimate the camera yaw, pitch, and roll
 angles, $(\theta_{yaw}, \theta_{pitch}, \theta_{roll})$ from a
@@
 camera pitch and roll angles.
-%If the camera focal length is known, one can compute the camera pitch
-%and roll angle from the horizon line.
 Collins and Weiss~\cite{unitsphere1990} formulate horizon line
@@
 The task of geo-localization estimates the geographic location, $(lat,
-lon)$, of the camera from the input image or video frames.
+lon)$, of the camera given image/video inputs.
 %
@@
 \item \textbf{Time Estimation:}
-The goal of time estimation is to estimate the time when the input
-image was captured. Depending on the application, the scale of a
-time estimator outputs may range from year to hour.
+The goal of time estimation is to estimate the time when the 
+image was captured. Depending on the application, the accuracy of
+predictions range from hour to year.
 %
@@
 In conclusion, most of the geo-calibration algorithms we mention above
-relies on finding visual cues from the input images. The development
-of these algorithms require strong human expertise about the data,
-thus can only be applied in limited scenarios. Therefore, researchers
-need new methodologies in order to make the development of
-geo-calibration algorithms more efficient.
+relies on finding visual cues from input images. To extract useful
+visual features majority of these algorithms require strong human
+expertise about the data, thus can only be applied in limited
+scenarios. Therefore, we contribute to developing geo-calibration
+algorithms without need of strong human expertise about the data.
 
@@
 
-These geo-calibration methods make the predictions directly out of
-DNNs.  There is another big category of geo-calibration methods that
-use aerial imagery as geo-registered database, which we will introduce
-in the following section.
+All these geo-calibration methods share the common property that they
+make the predictions directly out of DNNs. Besides these methods,
+there exists another big category of methods that geo-calibrate
+cameras using aerial imagery as geo-registered database. We will
+discuss them in the following section.
 
@@
 
-The key for the success of these ground-to-aerial geo-calibration
-methods is to learn descriptive features good for ground-to-aerial
-imagery matching. In the following section, we will show how to use
-geo-calibration information to learn useful features.
+The key for the success of these methods is to learn good descriptive
+features for ground-to-aerial imagery matching. In the following
+section, we will introduce literature about feature learning techniques.
 
-\subsection{Geo-Calibration for Feature Learning}
+\subsection{Feature Learning with Weak Annotations}
 
-Manually engineering visual features is a common practice for many
-computer vision tasks. One of the successful example of manually
-engineered feature is the SIFT feature~\cite{lowe1999object}.
-In recent years, automatic feature engineering has drawn a lot
-of attention. Compared to the manual feature
+Manually engineering visual features is a common practice for
+computer vision tasks. One of the successful example of manual
+feature is SIFT~\cite{lowe1999object}, which is widely used by many
+computer vision algorithms.
+In recent years, automatic feature engineering has drawn more
+attentions. Compared to the manual feature
 engineering, automatic feature engineering approaches allow to learn
 useful features without strong expert knowledge about the data. Among
-these approaches, deep neural networks are wildly accepted as good
-tools to learn high-level image representations.  The most commonly
-used approach for deep feature learning is full supervision, which
-usually requires large number of manual
+these learning approaches, deep neural networks are intensively studied.
+The most common approach for deep feature learning is full
+supervision, which usually requires large number of manual
 annotations~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
 Unfortunately, such data is not always available for certain tasks or
-needs to invest a huge amount of human labors to create.
-In contrast, unlabeled data is often plentiful (\ie cellphone photos
-in Instagram or Youtube videos).
+needs to invest a huge amount of human labors to create.  In contrast,
+unlabeled data is often plentiful (\ie cellphone photos in Instagram
+or Youtube videos).
 
@@
 concepts. In the following section, we are going to discuss our main
-contributions in this thesis.
+contributions.
 

### 2018-08-31 chapters/introduction/introduction.tex
minor changes

@@
 
-So far, we have explained four important related computer vision
-concepts. In the following section, we are going to discuss our main
-contributions.
+We have explained four related computer vision concepts so far. In the
+following section, we are going to discuss our main contributions.
 
@@
 
-We make contributions in three main areas: 1) we proposed a general
-probabilistic model to jointly estimate the geo-calibration
-parameters, 2) we decomposed the full geo-calibration into several
-partial geo-calibration tasks, each of which provides a strong
-constraint function that fits into the general model, and 3) we show
-that learning to geo-calibrate a camera is a useful pretext for image
-feature learning.
+In this thesis, we make contributions in three main areas: 1) we
+proposed a reflexible probabilistic model to jointly estimate the
+geo-calibration parameters, 2) we decomposed the full geo-calibration
+into several partial geo-calibration tasks, each of which provides a
+strong constraint function that fits into the probabilistic model,
+and 3) we show that learning to geo-calibrate a camera is a useful
+pretext for image feature learning.
 
 The first two contributions make our main approach. Our
-algorithm feeds inputs (images, time and manual annotations) to
-different constraint functions. Then
-we fuse these constraint functions to simulate the joint distribution
-over the complete geo-calibration parameters. We present the flowchart of
-our approach in \figref{intro:architecture}.
+algorithm feeds inputs (images, time, and manual annotations) to
+different constraint functions, which we can fuse together to simulate
+the joint distribution over the complete geo-calibration parameters.
+We present the flowchart of our approach in
+\figref{intro:architecture}.
 %
-Furthermore, we also explore to learning image features
-and geo-calibrating cameras simultaneously.  We believe that camera
-poses, geographic locations and image capture times are closely
-related to image representations. 
-Based on the belief that visual features which abstract the image
-contents are the necessary for solving the geo-calibration tasks, we
-designed neural networks to learn useful visual features by
-geo-calibrating cameras. Our work provide new ways for automatic
-feature learning.
+Furthermore, based on the belief that the content of the image is usually dictated
+by the camera pose, geographic location and image capture time. We
+treat geo-calibration information as pretext task and show that they
+are useful for image feature learning.
 
-\subsection{General Probabilistic Model for Geo-Calibration}
-We design a general model to estimate the probability over all
-geo-calibration parameters. First, we model the process of projecting
-from the scene at given location, time, and in given camera pose.
-%This the appearance of the image frame are determined by the pin-hole
-%model and the geographic location of the camera.
-We use a scoring function to measure the ``fitness'' between these
-geo-calibration parameters and the appearance of the image. 
+\subsection{Flexible Probabilistic Model for Geo-Calibration}
+We design a flexible probabilistic model to estimate the probability
+over all geo-calibration parameters.
+First, we construct a scoring function to model the process of camera
+projecting the scene to image frame at given pose, location, and time.
+%
+The scoring function consists of a series of constraint functions,
+which measures the ``fitness'' between these geo-calibration
+parameters and the appearance of the image. 
+%
 The scoring function is proportional to the probability distribution
-over the geo-calibration parameters, but the denominator is unknown. We
-then propose a Markov Chain Monte Carlo (MCMC) sampling approach to
-approximate the underlying probability distribution.
-Our model is flexible that it is able to contribute different
-constraint functions to the scoring function. The details of this model
-can be found in \chapref{mcmc}.
+over the geo-calibration parameters. Since the integral over all
+possible parameters is intractable, We propose a Markov Chain Monte
+Carlo (MCMC) sampling approach to approximate the underlying
+probability distribution. 
+%
+Our model is flexible that it allows different constraint functions
+contribute to the scoring function. The details of this model can be
+found in \chapref{mcmc}.
 
 \subsection{Developing Constraint Functions}
-In the general model, we define the scoring function as a weighted
-summation of a series of constraint functions.
-In the rest of the work, we focus on developing good constraint
-functions for different sets of geo-calibration parameters. 
-A constraint function outputs a score or probability for some given
-geo-calibration parameters conditional on the input image.
+The scoring function of the probabilistic
+model is defined as a weighted summation of a series of constraint
+functions.
+A constraint function outputs a score (or probability) of the input
+geo-calibration parameters given the input image. In the rest of the
+work, we focus on developing good constraint functions for different
+sets of geo-calibration parameters.
 

### 2018-09-01 chapters/introduction/introduction.tex
minor change

@@
   \item \textbf{Constraint for Camera Pose:}
-  In this constraint, we model the camera roll and pitch angles.
+  We build the constraint function for camera roll and pitch angles.
   Assuming the intrinsic parameters are known, camera roll and pitch
@@
   layout.
-  In our work, we create a new method using CNN to estimate the
-  prior distribution over the horizon line. We assign a probability to
-  each horizon candidate sampled from the prior distribution by
-  measuring their consistences with detected vanishing points. We
-  present the algorithm details in \chapref{fasthorizon}.  \newline
+  In our work, we create a convolutional neural network to estimate the
+  prior distribution over the horizon line.
+  For each horizon line candidate sampled from the prior distribution,
+  we assign a consistency score to it by measuring the consistencies of
+  vanishing points detected on it.
+  The constraint function output is defined as the multiplication of
+  the prior probability of the associated horizon line and its
+  consistency score.
+  We present the algorithm details in \chapref{fasthorizon}.
+  \newline
 
   \item \textbf{Constraint for Time and Location:}
-  In this work, we estimate the probability over the
-  capture time and the camera geographic location given the input image.
-  Our network has two branches which predict the image
+  In this work, we estimate the probability over 
+  the camera geographic location and the capture time of the input
+  image.
+  Our network has two branches that predict the image
   capture time and the geographic location simultaneously.
@@
   joint distribution over the month of the year and the UTC hour of the
-  day when the input image has been captured.
-  For coarse camera geo-localization, We provide two approaches to
-  obtain the probability distribution over the camera geographic
-  location. Most straightforwardly, our network outputs the discrete
+  day when the input image was captured.
+  For camera geo-localization, our network outputs the discrete
   distribution over the geographic location of the camera. Better
   results can be procured with the image capture time as auxiliary input
-  (if it is known).  We present the algorithm details in
-  \chapref{whenwhere}.
+  (if it is known).  
+  We present the algorithm details in \chapref{whenwhere}.
   \newline
@@
   \item \textbf{Constraint for Location and Orientation:}
-  In our previous method, we present that our algorithm can estimate
-  the discrete camera location. The predictions are only approximate
-  due to the limitation of the algorithm. In this
+  The previous algorithm only estimates locations approximately
+  due to the limited capacity of the deep neural network. In this
   work, we propose a ground-to-aerial geo-calibration method that can
   further refine the prediction results and estimate the
-  camera geo-orientation with overhead imagery.
+  camera geo-orientation.
   %
@@
   When computing the value of the constraint function, feed the aerial
-  image of a given location and orientation set to the network. 
+  image of a given location and orientation to the network. 
   By comparing the aerial-to-ground layout with the real layout of the
-  ground image, we are able to measure the consistency of these two as
-  the value of our constraint function.
+  ground image, we are able to measure the consistency between the two
+  and use it as the value of our constraint function.
   We present the algorithm details in \chapref{crosstransf}.

### 2018-09-02 chapters/introduction/introduction.tex
finish another run of editting

@@
 Full supervision algorithms are powerful tools to learn useful image
-features. However, full supervision algorithms requires large number
-of annotated data, which in many cases are either not available or
-financially infeasible to obtain. On the other hand, images with free
-annotations like time and locations are plentiful on the Internet.
-To use these image resources for image feature learning, 
-we explore two types of learning techniques that uses time and
-locations as annotations: 1) {\em ground-to-aerial segmentation}, and 2)
+features. However, full supervision algorithms require large number
+of annotated data, which takes a lot of human labors and is usually
+unavailable.
+On the other hand, images with annotations like tags and GPS locations
+uploaded by individual users or captured automatically by smart
+devices are plentiful on the Internet.
+To use these image resources to understand the world,
+we explore two approaches that use time and
+locations as weak annotations: 1) {\em ground-to-aerial segmentation}, and 2)
 {\em geo-temporal feature learning} with time/location tagged images.
@@
   However, most large scale annotated datasets like ImageNet~\cite{ILSVRC15}
-  and COCO~\cite{lin2014microsoft} are made of ground level images. By
-  comparison, annotated datasets for aerial imagery are rare.
+  and COCO~\cite{lin2014microsoft} are mostly made of ground-level
+  images. By comparison, annotated datasets for aerial imagery are rare.
   %
   To deal with this problem, we proposed a
-  DNN to learn to semantically segment aerial images with only
+  DNN to learn semantic segmentation for aerial images with only
   ground-level annotations. Our method exploits the spatial
-  correspondences between images in cross-view pairs. 
-  In this work, we try to transfer the semantic knowledge from the
+  correspondences between images in the cross-view pair, where the
+  aerial imagery and ground imagery are associated by location and
+  geo-orientation.
+  In this work, we transfer the semantic knowledge from the
   ground domain to the aerial domain by identifying their latent
@@
   Reprojection Losses}~\cite{garg2016unsupervised,
-  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}
-  which have been successfully applied in monocular depth estimation,
+  godard2017unsupervised,zhou2017unsupervised, yan2016perspective},
+  which are proven to be successful in monocular depth estimation,
   our network learns the geometric projection from aerial to ground, and
@@
   \item \textbf{Location and Time as Pretext Task:}
-  Smart devices like cellphones and webcams becomes popular and most
-  of them are equipped with clocks and GPS modules nowadays. Thanks to
+  Smart devices like cellphones and webcams get more sophisticated
+  nowadays. Most of them are equipped with clocks and GPS modules. Thanks to
   the development of social networks, researchers now can find
-  a lot images online that are tagged with time and locations. In
-  \chapref{whenwhere}, we propose an algorithm that treats the location and
-  time as pretext task to learn useful image features.
-  By learning to predict the geographic location and capture time of
-  the query image, our network learns to extract geo-temporal features
-  from the image.
+  large amount of images online that are tagged with time and
+  geographic locations. In \chapref{whenwhere}, we propose an
+  algorithm that treats the location and time as pretext tasks to learn
+  useful image features.  By learning to predict the geographic location
+  and the capture time of the query image, our network learns to extract
+  geo-temporal features from the image.
 

### 2018-09-05 chapters/introduction/introduction.tex
minor change
apply Brent's review opinios

@@
 detection for autonomous driving, face recognition for security
-system, and image retrieval for searching engines.
+systems, and image retrieval for search engines.
 
 For many applications, knowing when, where, and in which direction a
-picture was taken is important to understand the world. However, most
-images does not carry such information. Our thesis focuses on
-developing algorithms to estimating these properties. We
-refer to the task as {\em geo-calibration}.
+picture was taken is important scene understanding. However, most
+images do not carry such information. 
+We refer to the task of estimating this information as {\em
+geo-calibration}. Our thesis focuses on developing geo-calibration
+algorithms.
 
@@
 \todo{citations}. 
-Deterministic systems have some obvious drawbacks: 1) they can not
+Deterministic systems have some obvious drawbacks: 1) they cannot
 model the inherent uncertainties from images of ambiguous scenes, and
@@
 learn about the scene of the image.
-As an essential part of scene understanding, how to extract image
-features is an important problem being studied for decades.  In
+As an essential part of understanding the scene, how to extract image
+features is an important problem has been studied for decades.  In
 recent years, learning based approaches for image feature extraction
@@
 to the fact that they do not need expert knowledge about the target
-data. However, most of these feature learning methods require large
-quantity of manually labeled datasets.  In this thesis, we presented
+data. However, most of these feature learning methods require a large
+quantity of manually labeled datasets. In this thesis, we propose
 alternative ways to learn image features when the
@@
 along with its literature. Next, we introduce the history of deep
-learning methods for geo-calibration, and a big category of approaches
-that use aerial imagery. In the end, we cover some related work
-of weakly supervised learning techniques.
+learning methods for geo-calibration, and data-driven scene matching
+approaches that use aerial imagery. In the end, we cover some related
+work of weakly supervised learning techniques.
 
@@
 the forensic sciences~\cite{stylianou13jane} to environmental
-monitoring~\cite{zhang2012mining}. Conceptually the geo-calibration
-task includes identifying: the camera pose ({\em pose estimation}),
+monitoring~\cite{zhang2012mining}. Conceptually, the geo-calibration
+task includes identifying the camera pose ({\em pose estimation}),
 the camera geographic location ({\em geo-localization}), and the time
@@
 Pose estimation is to estimate the camera yaw, pitch, and roll
-angles, $(\theta_{yaw}, \theta_{pitch}, \theta_{roll})$ from a
+angles, $(\theta_{yaw}, \theta_{pitch}, \theta_{roll})$ from an
 image. In the context of geo-calibration, the yaw angle
@@
 Collins and Weiss~\cite{unitsphere1990} formulate horizon line
-detection as a statistical estimation problem on the Gaussian Sphere,
-which is similar to the geometry we use.  More recent work has
-explored the use of dual space~\cite{alignment2014,dualspace2013}
-representations. Among the clustering-based approaches, Xu et
-al.~\cite{kitware2013} improve this pipeline by introducing a new
-point-line consistency function that models errors in the line segment
-extraction step.
+detection as a statistical estimation problem on the Gaussian Sphere.
+More recent work has explored the use of dual
+space~\cite{alignment2014,dualspace2013} representations. Among the
+clustering-based approaches, Xu et al.~\cite{kitware2013} improve this
+pipeline by introducing a new point-line consistency function that
+models errors in the line segment extraction step.
 \newline
@@
 timestamps for photos by matching against a time-varying
-reconstruction of a scene.  Hill~\cite{hill1994elephant} estimate the
+reconstruction of a scene.  Hill \etal~\cite{hill1994elephant} estimate the
 time of the day by measuring the light intensity profiles captured by
-cameras. Methods are proposed to date the
-year book photos by analyzing human
+cameras. Methods are proposed to date
+yearbook photos by analyzing human
 appearance~\cite{salem2016face2year,ginosar2015century}. Lee
-\etal~\cite{linking2015iccp} find visual paterns in the buildings,
+\etal~\cite{linking2015iccp} find visual patterns in buildings,
 relate them to certain time periods.
@@
 In conclusion, most of the geo-calibration algorithms we mention above
-relies on finding visual cues from input images. To extract useful
-visual features majority of these algorithms require strong human
-expertise about the data, thus can only be applied in limited
+rely on finding visual cues from input images. To extract useful
+visual features, a majority of these algorithms require strong human
+expertise about the data, thus, they can only be applied in limited
 scenarios. Therefore, we contribute to developing geo-calibration
-algorithms without need of strong human expertise about the data.
+algorithms without the need of strong human expertise about the data.
 
@@
 estimation~\cite{zhai2016horizon, workman2016horizon,
-hold2017perceptual} has been done by identifying the horizon line with
+hold2017perceptual} have been done by identifying the horizon line with
 CNNs (one can derive the camera roll and pitch angles from the horizon
@@
 To reduce the work of querying, the searching process is usually
-carried out in feature space of applicable number of  
+carried out in a feature space of an applicable number of  
 dimensions~\cite{im2gps, li2010location,zamir2010accurate}.
@@
 
-Benefited from the fast growing monitoring satellite and drone markets,
-the geo-tagged aerial imagery becomes more publicly accessible
-than ever. Aerial imagery downloading services like
-Microsoft Bing Map provide aerial images of various
+Benefiting from the fast-growing monitoring satellite and drone markets,
+geo-tagged aerial imagery has become more publicly accessible
+than ever. Aerial imagery downloading service like
+Microsoft Bing Map provides aerial images of various
 resolutions, which cover most areas of the world with accurate
@@
 A cross-view pair consists of a ground image and an aerial image at
-the same location, and but not necessarily aligned in orientation.
+the same location (sometimes aligned in orientation).
 
@@
 
-The key for the success of these methods is to learn good descriptive
+The key for the success of these methods is to learn descriptive
 features for ground-to-aerial imagery matching. In the following
@@
 
-\todo{describe problems to be solve}
+\todo{describe problems to solve}
 

### 2018-09-05 dissertation.tex
apply Brent's review opinios

@@
 Knowing when, where, and in which direction a picture was taken, the
-task of geo-calibration, makes it possible to use imagery to understand
+task of geo-calibration makes it possible to use imagery to understand
 the world and how it changes in time. Current models for

### 2018-09-06 chapters/introduction/introduction.tex
Apply Natha (writing center)'s review opinions.

@@
 Manually engineering visual features is a common practice for
-computer vision tasks. One of the successful example of manual
+computer vision tasks. One of successful examples of manual
 feature is SIFT~\cite{lowe1999object}, which is widely used by many
@@
 In recent years, automatic feature engineering has drawn more
-attentions. Compared to the manual feature
-engineering, automatic feature engineering approaches allow to learn
-useful features without strong expert knowledge about the data. Among
-these learning approaches, deep neural networks are intensively studied.
-The most common approach for deep feature learning is full
-supervision, which usually requires large number of manual
+attention. Compared to the manual feature
+engineering, automatic feature engineering allows to learn
+useful features with much less (if not none) knowledge about the data.
+Among these learning approaches, deep neural networks are intensively
+studied.  The most common approach for deep feature learning is full
+supervision, which usually requires a large number of manual
 annotations~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
 Unfortunately, such data is not always available for certain tasks or
-needs to invest a huge amount of human labors to create.  In contrast,
-unlabeled data is often plentiful (\ie cellphone photos in Instagram
+requires a huge amount of human labor. 
+In contrast, unlabeled data is often plentiful (\ie cellphone photos in Instagram
 or Youtube videos).
 
-To exploit these unlabeled data, recent work has explored
+To lavage these unlabeled data, recent work has explored
 self-supervision methods (sometimes referred to as unsupervised learning or
@@
 can obtain useful features of the image.
-For example, Zhang et al.~\cite{zhang2016colorful} show how image
-colorization (synthesizing colors for a grayscale image) is a powerful
+For example, Zhang et al.~\cite{zhang2016colorful} show how
+synthesizing colors for a grayscale image is a powerful
 pretext task for learning visual representations. Pathak et
@@
 %
-As new learning technique that addresses the lack of massive amounts
+As one of new learning techniques that address the lack of massive amounts
 of labeled data, domain adaptation forces the feature generating model
@@
 
-In this thesis, we make contributions in three main areas: 1) we
+We make contributions in three main areas: 1) we
 proposed a reflexible probabilistic model to jointly estimate the
@@
 %
-The scoring function consists of a series of constraint functions,
-which measures the ``fitness'' between these geo-calibration
-parameters and the appearance of the image. 
+The scoring function measures the ``fitness'' between these
+geo-calibration parameters and the appearance of the image. 
+It consists of a series of constraint functions,
 %
@@
 over the geo-calibration parameters. Since the integral over all
-possible parameters is intractable, We propose a Markov Chain Monte
+possible parameters is intractable, we propose a Markov Chain Monte
 Carlo (MCMC) sampling approach to approximate the underlying
@@
 %
-Our model is flexible that it allows different constraint functions
+Our model is flexible because it allows different constraint functions
 contribute to the scoring function. The details of this model can be
@@
   angles can be derived from the horizon line position on the image.
-  Compared to directly detecting the camera pose, identifying horizon
+  Compared to directly detecting the camera pose, identifying the horizon
   line is easier because it can be explicitly estimated from the scene
@@
 features. However, full supervision algorithms require large number
-of annotated data, which takes a lot of human labors and is usually
+of annotated data, which takes a lot of human labor and is usually
 unavailable.
@@
   Semantic segmentation plays an important role in image understanding.
-  The training for semantic segmentation task requires a large number
+  The training for semantic segmentation tasks require a large number
   of annotated data.

### 2018-09-12 chapters/discussion/discussion.tex
add discussion section

\chapter{Discussion}
\label{chap:discussion}

The goal of geo-calibration is to learn the camera pose, location and
the time when the image was captured.
Our thesis focused on developing deep geo-calibration algorithms for
image understanding.
Compared to previous work, our approaches give
probabilistic outputs that are more flexible and are able to handle
the uncertainty of the scene better.

In \chapref{mcmc}, we proposed a flexible model to compute the
probability over all geo-calibration parameters. In the high
dimensional space of geo-calibration parameters, we defined an score
function for every point in that space, to measure how well the
geo-calibration parameters match the content of the input image. The
score function is defined as a weighted summation of a series of
constraint functions, and is proportional to the probability density
function of the distribution. Since xxx is computationally
intractable, in order to xxx, we approximated the probability
density function using MCMC method.
\todo{why grid method doesn't work here}
\todo{evaluation}

In \chapref{fasthorizon}, we focused on constraint function for the
camera pose. Assuming the focal length is known, the camera roll and
pitch angle can be derived from the horizon line position. Our
algorithm identifies the horizon line from an input image that
satisfied the Manhattan world assumption.
Compared to most previous work which applies a bottom-up approach by
fitting the horizon line from the vanishing points, we proposed a
novel horizon-first approach to identify the horizon line.
First we trained a CNN to estimate the distribution of the horizon
line. Then we sample horizon line candidates from the horizon line
distribution. For each horizon candidate, we find the possible
vanishing points on it. Compared to previous work which searches for 
vanishing points on image frame, our method accelerate the searching
process by carrying it out in the 1D space. The probability of the
horizon candidate to be the real horizon line is measured by how many
and good vanishing points found on it.

In \chapref{whenwhere}, we constructed the constraint function for 
the image capture time and the camera location. In order to achieve
this goal, we trained a CNN on a large dataset that consists of
millions webcam frames and smart phone photos. The network takes image
as input and output the discrete probability over location and time.
In this work, we took the advantage that geo-tagged and
temporal-tagged images are common nowadays, to build our training set.
We demonstrate that geo-calibrating the camera helps learn image
representations useful for image understanding.

In \chapref{crosstransf}, we exploit the overhead image to construct
the constraint function for the camera orientation and location.

### 2018-09-16 chapters/discussion/discussion.tex
minor change

@@
 In this work, we took the advantage that geo-tagged and
-temporal-tagged images are common nowadays, to build our training set.
+temporal-tagged images are common nowadays to build the training set.
 We demonstrate that geo-calibrating the camera helps learn image
@@
 
-In \chapref{crosstransf}, we exploit the overhead image to construct
+In \chapref{crosstransf}, we exploit overhead imagery to construct
 the constraint function for the camera orientation and location.
+We trained a CNN that can estimate the semantic layout of the ground
+view image from the overhead image. During training, we learn the
+pixel-to-pixel correspondences from the aerial image to the ground. We
+project the semantic layout the of the overhead image to the ground
+view with the learned correspondence.
+When computing the output of the constraint function, we feed the
+aerial image of the gien location and orientation to the network. By
+comparing the aerial-to-ground with the real layout of the ground
+image, we measure the consistency between the two and use
+it as the value of our constraint function.
+We also demonstrate the efficiency of our method for CNN pre-training
+for aerial image segmentation.
+
+This thesis proposed a probability model for image geo-calibration. 
+Overall, we hope our work can provide xxx.

### 2018-09-17 chapters/discussion/discussion.tex
minor change

@@
 image understanding.
-Compared to previous work, our approaches give
-probabilistic outputs that are more flexible and are able to handle
-the uncertainty of the scene better.
+Compared to previous work, our approaches output probabilistic
+predictions that are able to handle the uncertainty of the scene
+better. Furthermore, we also show that
+learning to geo-calibrate a camera allows us to implicitly learn to
+understand the content of the scene.
 
@@
 density function using MCMC method.
-\todo{why grid method doesn't work here}
-\todo{evaluation}
 
@@
 
-This thesis proposed a probability model for image geo-calibration. 
-Overall, we hope our work can provide xxx.
+This thesis proposed a probabilistic model for image
+geo-calibration.
+The key to the success of this model is to find constraint
+functions that describe the relationship between geo-calibration
+parameters and the image content. We developed constraint
+functions for different set of parameters that can fit to the model.
+Furthermore, we also show that learning to geo-calibrate cameras helps learning
+useful features for image understanding.
+There are several possible future research directions for extending
+this work, including: exploiting map data in cross-view learning,
+replacing the CNN networks in our algorithms with Bayesian neural
+networks (BNNs).
+Overall, we hope our work can provide new ways for geo-calibration and
+pre-task training.

### 2018-09-17 chapters/discussion/discussion.tex
minor change

@@
 probability over all geo-calibration parameters. In the high
-dimensional space of geo-calibration parameters, we defined an score
-function for every point in that space, to measure how well the
-geo-calibration parameters match the content of the input image. The
-score function is defined as a weighted summation of a series of
-constraint functions, and is proportional to the probability density
-function of the distribution. Since xxx is computationally
-intractable, in order to xxx, we approximated the probability
-density function using MCMC method.
+dimensional space of geo-calibration parameters, we defined a score
+function for every point, to measure how well the
+geo-calibration parameters match the content of the input image.
+The score function is a weighted summation of a series of
+constraint functions. It is proportional to the probability density
+function of the distribution. Since the analytic solution to the
+integral of the score function does not exist, we approximated the
+probability density function using MCMC method. Our model is flexible
+to any constraint function for geo-calibration parameters. We also
+demonstrated in our experiment that more accurate predictions can be
+obtained if the score function consists of more constraints.
 
-In \chapref{fasthorizon}, we focused on constraint function for the
-camera pose. Assuming the focal length is known, the camera roll and
-pitch angle can be derived from the horizon line position. Our
-algorithm identifies the horizon line from an input image that
-satisfied the Manhattan world assumption.
-Compared to most previous work which applies a bottom-up approach by
-fitting the horizon line from the vanishing points, we proposed a
-novel horizon-first approach to identify the horizon line.
-First we trained a CNN to estimate the distribution of the horizon
-line. Then we sample horizon line candidates from the horizon line
-distribution. For each horizon candidate, we find the possible
-vanishing points on it. Compared to previous work which searches for 
-vanishing points on image frame, our method accelerate the searching
-process by carrying it out in the 1D space. The probability of the
-horizon candidate to be the real horizon line is measured by how many
-and good vanishing points found on it.
+In \chapref{fasthorizon}, we focused on developing constraint function
+for the camera pose. Assuming the focal length is known, the camera
+roll and pitch angle can be derived from the horizon line position.
+Our algorithm identifies the horizon line from the input image
+satisfying the Manhattan world assumption. Compared to the previous
+work, which applies a bottom-up approach where the horizon line is
+estimated after the vanishing point identification, we proposed a
+novel horizon-first approach where finding horizon line candidates is
+prior to identifying vanishing points.  As the first step, we trained
+a CNN to estimate the probability distribution over the horizon line.
+Then we sample horizon line candidates from the distribution. For each
+horizon candidate, we detect likely vanishing points on it. Compared
+to previous work which searches for vanishing points on the 2D image
+frame, our method is able to accelerate the searching process by
+reducing the searching space to 1D. The probability of the horizon
+line is measured by how convincing are the vanishing points found on
+it.
 

### 2018-09-18 chapters/discussion/discussion.tex
minor change

@@
 
-In \chapref{whenwhere}, we constructed the constraint function for 
-the image capture time and the camera location. In order to achieve
-this goal, we trained a CNN on a large dataset that consists of
-millions webcam frames and smart phone photos. The network takes image
-as input and output the discrete probability over location and time.
-In this work, we took the advantage that geo-tagged and
-temporal-tagged images are common nowadays to build the training set.
-We demonstrate that geo-calibrating the camera helps learn image
-representations useful for image understanding.
+In \chapref{whenwhere}, we developed the constraint function for 
+the image capture time and the camera location. 
+We trained a CNN on a large dataset to learn to predict the discrete
+probabilities over location and time given the input image.
+Unlike full supervision methods which require tedious work for manual
+annotations, our training dataset consists of millions webcam
+frames and smart phone photos with free time/location tags.
+In the experiments, we demonstrated that geo-calibrating the camera
+also helps learn useful image representations for image understanding.
 

### 2018-09-18 chapters/discussion/discussion.tex
minor change

@@
 
-In \chapref{crosstransf}, we exploit overhead imagery to construct
+In \chapref{crosstransf}, we exploited overhead imagery to construct
 the constraint function for the camera orientation and location.
 We trained a CNN that can estimate the semantic layout of the ground
-view image from the overhead image. During training, we learn the
-pixel-to-pixel correspondences from the aerial image to the ground. We
-project the semantic layout the of the overhead image to the ground
-view with the learned correspondence.
+view image from the overhead image. During training, the CNN learns the
+pixel-to-pixel correspondences from the aerial image to the ground
+image. 
+It then projects the semantic layout the of the overhead image to the
+ground view according to the learned correspondence.
 When computing the output of the constraint function, we feed the
-aerial image of the gien location and orientation to the network. By
-comparing the aerial-to-ground with the real layout of the ground
-image, we measure the consistency between the two and use
-it as the value of our constraint function.
-We also demonstrate the efficiency of our method for CNN pre-training
-for aerial image segmentation.
+aerial image of given location and orientation to the network. By
+comparing the aerial-to-ground layout with the layout computed from
+the ground image, we measure the consistency between these two and use
+consistency value as the output of the constraint function. 
+In our experiments, we also demonstrated the efficiency of our method
+for pre-training CNNs for aerial image segmentation.
 
-This thesis proposed a probabilistic model for image
-geo-calibration.
-The key to the success of this model is to find constraint
-functions that describe the relationship between geo-calibration
-parameters and the image content. We developed constraint
-functions for different set of parameters that can fit to the model.
-Furthermore, we also show that learning to geo-calibrate cameras helps learning
-useful features for image understanding.
-There are several possible future research directions for extending
-this work, including: exploiting map data in cross-view learning,
-replacing the CNN networks in our algorithms with Bayesian neural
-networks (BNNs).
-Overall, we hope our work can provide new ways for geo-calibration and
-pre-task training.
+This thesis proposed a probabilistic model for image geo-calibration.
+The key to the success of this model is to find constraint functions
+that describe the relationship between geo-calibration parameters and
+the image content. We developed constraint functions for different set
+of parameters that can fit to the model.  Furthermore, we also show
+that learning to geo-calibrate cameras helps learning useful features
+for image understanding.  There are several possible future research
+directions for extending this work, including: exploiting map data in
+cross-view learning, replacing the CNN networks in our algorithms with
+Bayesian neural networks (BNNs).  Overall, we hope our work can
+provide new ways for geo-calibration and pre-task training.

### 2018-09-18 chapters/discussion/discussion.tex
minor change

@@
 
-This thesis proposed a probabilistic model for image geo-calibration.
-The key to the success of this model is to find constraint functions
-that describe the relationship between geo-calibration parameters and
-the image content. We developed constraint functions for different set
-of parameters that can fit to the model.  Furthermore, we also show
-that learning to geo-calibrate cameras helps learning useful features
-for image understanding.  There are several possible future research
-directions for extending this work, including: exploiting map data in
-cross-view learning, replacing the CNN networks in our algorithms with
-Bayesian neural networks (BNNs).  Overall, we hope our work can
-provide new ways for geo-calibration and pre-task training.
+This thesis proposed a flexible probabilistic framework for image
+geo-calibration. The key to the success of the framework is to find
+constraint functions that can accurately model the relationship between
+geo-calibration parameters and the image content. 
+We developed constraint functions for different set of parameters to
+fit to the framework. 
+Furthermore, we also show that learning to geo-calibrate cameras helps
+learning useful features for image understanding. There are several
+possible future research directions for extending this work,
+including: exploiting map data in cross-view learning, replacing the
+CNN networks in our algorithms with Bayesian neural networks (BNNs).
+Overall, we hope our work can provide new ways for geo-calibration and
+pretext task for learning image representations.

### 2018-09-18 chapters/introduction/introduction.tex
minor change
minor changes

@@
 
-Most recent geo-calibration algorithms are deterministic systems
-\todo{citations}. 
+Most recent geo-calibration algorithms are deterministic
+systems~\cite{baatz2012large,doersch2012what,li2012worldwide}.
 Deterministic systems have some obvious drawbacks: 1) they cannot
@@
   the aerial image and its projection to the ground-level perspective.
-  When computing the value of the constraint function, feed the aerial
+  When computing the value of the constraint function, we feed the aerial
   image of a given location and orientation to the network. 
@@
 
-\todo{describe problems to solve}
-
 In summary, the main contributions of our work include developing a

### 2018-09-18 chapters/discussion/discussion.tex
last editing

@@
 Compared to previous work, our approaches output probabilistic
-predictions that are able to handle the uncertainty of the scene
-better. Furthermore, we also show that
+predictions that handle the uncertainty of the scene
+better. Furthermore, we show that
 learning to geo-calibrate a camera allows us to implicitly learn to
@@
 In \chapref{mcmc}, we proposed a flexible model to compute the
-probability over all geo-calibration parameters. In the high
-dimensional space of geo-calibration parameters, we defined a score
-function for every point, to measure how well the
-geo-calibration parameters match the content of the input image.
-The score function is a weighted summation of a series of
+probability over geo-calibration parameters. We defined a score
+function in the space of geo-calibration parameters, to measure how
+well the geo-calibration parameters are able to describe the content
+of the input image.
+The score function is the summation of a series of weighted
 constraint functions. It is proportional to the probability density
-function of the distribution. Since the analytic solution to the
+function (PDF) of the distribution over the geo-calibration parameter setting.
+Since the analytic solution to the
 integral of the score function does not exist, we approximated the
-probability density function using MCMC method. Our model is flexible
-to any constraint function for geo-calibration parameters. We also
-demonstrated in our experiment that more accurate predictions can be
-obtained if the score function consists of more constraints.
+PDF using MCMC method. Our model is flexible such that one can apply
+any kind and number of constraint functions for geo-calibration
+parameters. We also demonstrated in our experiment that 
+score function with more constraint functions yields more accurate
+predictions.
 
-In \chapref{fasthorizon}, we focused on developing constraint function
-for the camera pose. Assuming the focal length is known, the camera
-roll and pitch angle can be derived from the horizon line position.
-Our algorithm identifies the horizon line from the input image
-satisfying the Manhattan world assumption. Compared to the previous
-work, which applies a bottom-up approach where the horizon line is
-estimated after the vanishing point identification, we proposed a
-novel horizon-first approach where finding horizon line candidates is
-prior to identifying vanishing points.  As the first step, we trained
-a CNN to estimate the probability distribution over the horizon line.
-Then we sample horizon line candidates from the distribution. For each
-horizon candidate, we detect likely vanishing points on it. Compared
-to previous work which searches for vanishing points on the 2D image
-frame, our method is able to accelerate the searching process by
-reducing the searching space to 1D. The probability of the horizon
-line is measured by how convincing are the vanishing points found on
-it.
+In \chapref{fasthorizon}, we developed a constraint function for the
+camera pose. Since the camera roll and pitch angle can be derived from
+the horizon line position, our algorithm focuses on identifying the
+horizon line from the input image.
+Compared to the previous work, which applies bottom-up
+approaches where the horizon line is estimated after finding vanishing
+points, we proposed a novel horizon-first approach where
+identifying possible horizon lines is prior to detecting vanishing
+points. 
+Firstly, we trained a CNN to estimate the probability distribution
+over the horizon line. Then we sample horizon line candidates from
+it. For each horizon candidate, we detect likely
+vanishing points on it. Unlike the previous work which searches for
+vanishing points on the 2D image frame, our method is able to
+accelerate this process by reducing the searching space to
+1D (a line). The probability of the horizon line is measured by how
+convincing are the vanishing points found on it.
 
@@
 the image capture time and the camera location. 
-We trained a CNN on a large dataset to learn to predict the discrete
-probabilities over location and time given the input image.
+We trained a CNN on a large dataset to predict the discrete
+probabilities over the capture time and the camera location given the
+input image.
 Unlike full supervision methods which require tedious work for manual
-annotations, our training dataset consists of millions webcam
+annotations, our training dataset consists of millions of webcam
 frames and smart phone photos with free time/location tags.
-In the experiments, we demonstrated that geo-calibrating the camera
-also helps learn useful image representations for image understanding.
+In the experiments, we demonstrated that learning to geo-calibrate the
+camera helps learn useful image representations for image understanding.
 
@@
 the constraint function for the camera orientation and location.
-We trained a CNN that can estimate the semantic layout of the ground
-view image from the overhead image. During training, the CNN learns the
-pixel-to-pixel correspondences from the aerial image to the ground
-image. 
-It then projects the semantic layout the of the overhead image to the
-ground view according to the learned correspondence.
+We trained a CNN to estimate the semantic layout of the
+ground-view image from the overhead image. During training, the CNN
+learns the pixel-to-pixel correspondences from the aerial image to the
+ground image. Then it projects the semantic layout the of the overhead
+image to the ground view according to the learned correspondences.
 When computing the output of the constraint function, we feed the
@@
 the ground image, we measure the consistency between these two and use
-consistency value as the output of the constraint function. 
+the consistency value as the output of the constraint function. 
 In our experiments, we also demonstrated the efficiency of our method
@@
 This thesis proposed a flexible probabilistic framework for image
-geo-calibration. The key to the success of the framework is to find
+geo-calibration. The key to the success of this framework is to find
 constraint functions that can accurately model the relationship between
-geo-calibration parameters and the image content. 
+geo-calibration parameters and the content of the image. 
 We developed constraint functions for different set of parameters to
 fit to the framework. 
-Furthermore, we also show that learning to geo-calibrate cameras helps
+Furthermore, we also showed that learning to geo-calibrate cameras helps
 learning useful features for image understanding. There are several
@@
 Overall, we hope our work can provide new ways for geo-calibration and
-pretext task for learning image representations.
+image feature learning.

### 2018-09-20 chapters/mcmc/paper.tex
fix image layout
change title

@@
 dot) and the top scoring sampled cameras (red arrows).}
-
-%  \caption{Our approach leverages a geographic reference database (b)
-%  to estimate the geo-location (c) of a query image (a). (b) Top scoring
-%samples (red arrows) are close to the actual location (green dot).}
 
@@
 multiple weak correspondences, constraints on geographic location, and
-priors over the
+priors over the field of view and camera orientation. 
 %
-field of view and camera orientation. We focus on the first
+We focus on the first
 constraint, the latter are simple Gaussian and uniform distributions.

### 2018-09-20 chapters/mcmc/paper.tex
changes in mcmc

@@
 which is larger if the calibration, $\Theta$, is more consistent with
-the image information, $c_i$. While the exact set of constraints
-depends on the image and database contents, we define a variety of
-% scott review
-functions in our implementation, including geometric configuration of
-multiple weak correspondences, constraints on geographic location, and
-priors over the field of view and camera orientation. 
+the image information, $c_i$. 
 %
-We focus on the first
-constraint, the latter are simple Gaussian and uniform distributions.
+While the scoring function can take any type of constraint functions,
+we define a variety of functions in our implementation, including
+geometric configuration of multiple weak correspondences, constraints
+on geographic location, and priors over the field of view and camera
+orientation, to demonstrate the performance of our model. 
+%
+%While the exact set of constraints
+%depends on the image and database contents, we define a variety of
+%functions in our implementation, including geometric configuration of
+%multiple weak correspondences, constraints on geographic location, and
+%priors over the field of view and camera orientation. 
+%
+We focus on the first constraint specifically, the latter are simple
+Gaussian and uniform distributions.
 
@@
 
-We evaluate our method using two real query images obtained from
-Google Street View. We hand-picked two locations, downloaded the
-corresponding equirectangular panoramas and extracted a perspective
-image from each. For each query, we labeled objects and estimated the
-min/max distance from the camera to the object in the world.
-\figref{real-data} shows the qualitative result of this experiment.
-Our method generates high scoring samples that are close to the ground
-truth. We also found that simple prior constraints can dramatically
-affect localization accuracy. By restricting the range of the azimuth
-and FOV to be within $5^\circ$ of the ground truth, the distance from
-the top sample to the ground-truth location decreased from $12.5m$ to
-$0.6m$ and from $1.73m$ to $0.9m$, respectively, for two test
-cases.
-
-%azimuth estimated from the sun position~\cite{lalonde2010sun}
-
 \begin{figure}
@@
 
+We evaluate our method using two real query images obtained from
+Google Street View. We hand-picked two locations, downloaded the
+corresponding equirectangular panoramas and extracted a perspective
+image from each. For each query, we labeled objects and estimated the
+min/max distance from the camera to the object in the world.
+\figref{real-data} shows the qualitative result of this experiment.
+Our method generates high scoring samples that are close to the ground
+truth. We also found that simple prior constraints can dramatically
+affect localization accuracy. By restricting the range of the azimuth
+and FOV to be within $5^\circ$ of the ground truth, the distance from
+the top sample to the ground-truth location decreased from $12.5m$ to
+$0.6m$ and from $1.73m$ to $0.9m$, respectively, for two test
+cases.
+
+%azimuth estimated from the sun position~\cite{lalonde2010sun}
+
 \section{Conclusions}
@@
 baseline methods, without requiring nearby ground-level imagery as is
-typical for most vision techniques. For future work, we will explore
-methods for integrating approaches which use image-based matching.
+typical for most vision techniques.
+While we applied only a small set of primitive constraints in this work,  
+the proposed framework is able to take any kind of constraints.
+In the following chapters, we will explore to develop more sophisticated
+constraint functions.

### 2018-09-20 chapters/whenwhere/paper.tex
add time estimation related work
constraint functions

@@
 
+In this chapter, we focus on developing the constraint function for 
+the capture time and the camera location for outdoor images.
 Outdoor images often contain sufficient visual information to
@@
 appearance, including clothing and hairstyle, is a useful cue for
-dating images. Matzen and Snavely predict timestamps for photos by
+dating images. Matzen and Snavely~\cite{matzen2014scene} predict timestamps for photos by
 matching against a time-varying reconstruction of a scene.  Volokitin

### 2018-09-20 chapters/discussion/discussion.tex
minor change
disscussion

@@
-\chapter{Discussion}
+\chapter{Summary}
 \label{chap:discussion}
@@
 integral of the score function does not exist, we approximated the
-PDF using MCMC method. Our model is flexible such that one can apply
-any kind and number of constraint functions for geo-calibration
-parameters. We also demonstrated in our experiment that 
-score function with more constraint functions yields more accurate
-predictions.
+PDF using the MCMC method. Our model is flexible such that one can apply
+any kind and number of constraint functions.
+We also demonstrated in our experiments that score functions with more
+constraint functions yields more accurate predictions.
 
-In \chapref{fasthorizon}, we developed a constraint function for the
+In \chapref{fasthorizon}, we developed a constraint function for
 camera pose. Since the camera roll and pitch angle can be derived from
@@
 points, we proposed a novel horizon-first approach where
-identifying possible horizon lines is prior to detecting vanishing
+identifying possible horizon lines happens before detecting vanishing
 points. 
 Firstly, we trained a CNN to estimate the probability distribution
-over the horizon line. Then we sample horizon line candidates from
-it. For each horizon candidate, we detect likely
+over the horizon line. Then we sampled horizon line candidates from
+it. For each horizon candidate, we detected likely
 vanishing points on it. Unlike the previous work which searches for
@@
 learns the pixel-to-pixel correspondences from the aerial image to the
-ground image. Then it projects the semantic layout the of the overhead
+ground image. Then it projects the semantic layout of the overhead
 image to the ground view according to the learned correspondences.
 When computing the output of the constraint function, we feed the
-aerial image of given location and orientation to the network. By
+aerial image of the given location and orientation to the network. By
 comparing the aerial-to-ground layout with the layout computed from
@@
 geo-calibration parameters and the content of the image. 
-We developed constraint functions for different set of parameters to
+We developed constraint functions for different sets of parameters to
 fit to the framework. 
 Furthermore, we also showed that learning to geo-calibrate cameras helps
-learning useful features for image understanding. There are several
-possible future research directions for extending this work,
-including: exploiting map data in cross-view learning, replacing the
-CNN networks in our algorithms with Bayesian neural networks (BNNs).
-Overall, we hope our work can provide new ways for geo-calibration and
-image feature learning.
+learning useful features for image understanding. 
+%
+There are several possible future research directions for extending
+this work. For example, like aerial imagery, map data also
+provides rich information about the environment from the top-view
+perspective. In \chapref{crosstransf}, we can incorporate map data in
+cross-view learning.
+%
+Bayesian neural networks (BNNs) have drawn a lot
+of attentions in recent years. The probabilistic nature of BNNs makes
+them excellent tools to model uncertainties. We can also replace CNNs
+with BNNs in our algorithms to achieve better performances.
+%There are several possible future research directions for extending
+%this work, including: exploiting map data in cross-view learning,
+%replacing the CNN networks in our algorithms with Bayesian neural
+%networks (BNNs).
+Overall, we hope our work can provide new ways for
+geo-calibration and image feature learning.

### 2018-10-01 chapters/introduction/introduction.tex
add one more citation to deternimistic system
fix a duplicate reference img2gps

@@
 Most recent geo-calibration algorithms are deterministic
-systems~\cite{baatz2012large,doersch2012what,li2012worldwide}.
+systems~\cite{baatz2012large,doersch2012what,li2012worldwide,kendall2015convolutional}.
 Deterministic systems have some obvious drawbacks: 1) they cannot
@@
 methods is that they take advantage of a large dataset of
-geo-referenced images. Hays and Efros~\cite{hays2008im2gps} use a
+geo-referenced images. Hays and Efros~\cite{im2gps} use a
 data-driven scene matching approach to localize a query image using a

### 2018-10-01 chapters/mcmc/paper.tex
fix a duplicate reference img2gps

@@
 image using either local~\cite{li2010location,schindler2008detecting}
-or global~\cite{hays2008im2gps,doersch2012what} image features.  This
+or global~\cite{im2gps,doersch2012what} image features.  This
 approach is not applicable when no nearby ground-level imagery exists
@@
 they take advantage of a large dataset of geo-referenced images. Hays
-and Efros~\cite{hays2008im2gps} use a data-driven scene matching
+and Efros~\cite{im2gps} use a data-driven scene matching
 approach to localize a query image using a large dataset of geo-tagged

### 2018-10-24 chapters/crosstransf/paper.tex
minor change
geolocalization -> geo-localization geocalibration -> geo-calibration

@@
 
+In this chapter, we will exploit overhead imagery to construct
+the constraint function for the camera orientation and location.
+%
 Learning-based methods for pixel-level labeling of aerial imagery
@@
 ground image features from aerial imagery for the task of
-ground image geolocalization~\cite{workman2015wide}. Our work is
+ground image geo-localization~\cite{workman2015wide}. Our work is
 unique in that it is the first to attempt to predict a dense
@@
 Recent work on cross-view image
-geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
+geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
  has shown that convolutional neural
@@
 Vo \etal~\cite{vo2016localizing} extend this line of work,
-demonstrating improved geolocalization performance by applying an
+demonstrating improved geo-localization performance by applying an
 auxiliary loss function to regress the ground-level camera orientation
@@
 used in four different tasks: 1) weakly supervised semantic learning, 
-2) aerial imagery labeling, 3) orientation regression and geocalibration, 
+2) aerial imagery labeling, 3) orientation regression and geo-calibration, 
 and 4) cross-view image synthesis. Additional qualitative results and 
@@
 
-\subsection{Cross-view for Geocalibration}
+\subsection{Cross-view for Geo-Calibration}
 
@@
 in~\secref{dataset_cross} to create this dataset, it has two parts for
-orientation estimation and geocalibration, respectively.  For the
+orientation estimation and geo-calibration, respectively.  For the
 orientation regression task, we rotate the aerial image to a random
-angle. For the fine-grained geocalibration experiment, we center-crop
+angle. For the fine-grained geo-calibration experiment, we center-crop
 the aerial image around a random $x,y$ offset, then rotate the image to a
@@
 
-\paragraph{Fine-grained Geocalibration}
+\paragraph{Fine-grained Geo-Calibration}
 
@@
 
-  \caption{Fine-grained geocalibration results on CVUSA. (left) From
+  \caption{Fine-grained geo-calibration results on CVUSA. (left) From
 top to bottom are the $I_g$, $L_g$, and $L_{g'}$ respectively.  We

### 2018-10-24 chapters/fasthorizon/paper.tex
fix duplicate label definition
constraint functions
geolocalization -> geo-localization geocalibration -> geo-calibration

@@
 \section{Introduction}
+
+In this chapter, we will develop a constraint function for
+camera pose. Since the camera roll and pitch angle can be derived from
+the horizon line position, our algorithm focuses on detecting the
+horizon line from the input image.
 
@@
 facade detection~\cite{liulocal2014},
-geolocalization~\cite{baatz2010handling,workman2014rainbow}, and
+geo-localization~\cite{baatz2010handling,workman2014rainbow}, and
 camera
@@
 \section{Evaluation}
-\label{sec:evaluation}
+\label{sec:evaluation_fast}
 
@@
     (y-axis) with a horizon error less than a threshold (x-axis). The
-    AUC for each curve is shown in the legend. For additional details see \secref{evaluation}.}
+    AUC for each curve is shown in the legend. For additional details
+see \secref{evaluation_fast}.}
   \label{fig:horError}

### 2018-10-24 chapters/discussion/discussion.tex
change in disscussion section.

@@
 of the input image.
-The score function is the summation of a series of weighted
+The score function is a summation of a series of weighted
 constraint functions. It is proportional to the probability density
@@
 PDF using the MCMC method. Our model is flexible such that one can apply
-any kind and number of constraint functions.
-We also demonstrated in our experiments that score functions with more
+any kind and any number of constraint functions.
+We also demonstrated in our experiments that the score function with more
 constraint functions yields more accurate predictions.
 
-In \chapref{fasthorizon}, we developed a constraint function for
-camera pose. Since the camera roll and pitch angle can be derived from
+In \chapref{fasthorizon}, we developed a constraint function for the
+camera pose. Since the camera roll and pitch angles can be derived from
 the horizon line position, our algorithm focuses on identifying the
@@
 1D (a line). The probability of the horizon line is measured by how
-convincing are the vanishing points found on it.
+convincing the vanishing points are found on it.
 
@@
 probabilities over the capture time and the camera location given the
-input image.
-Unlike full supervision methods which require tedious work for manual
-annotations, our training dataset consists of millions of webcam
+input image, as well as to learn a geo-temporal representation
+of the image.
+Unlike most full supervision methods which require tedious work for 
+annotation collection, our training dataset consists of millions of webcam
 frames and smart phone photos with free time/location tags.
@@
 We developed constraint functions for different sets of parameters to
-fit to the framework. 
+fit in the framework. 
 Furthermore, we also showed that learning to geo-calibrate cameras helps
@@
 provides rich information about the environment from the top-view
-perspective. In \chapref{crosstransf}, we can incorporate map data in
-cross-view learning.
+perspective. In \chapref{crosstransf}, we can incorporate map data
+as top-view imagery during training.
 %
-Bayesian neural networks (BNNs) have drawn a lot
+Another future work direction is to use Bayesian neural networks
+(BNNs). Bayesian neural networks have drawn a lot
 of attentions in recent years. The probabilistic nature of BNNs makes
-them excellent tools to model uncertainties. We can also replace CNNs
+them excellent tools to model uncertainties. We can replace CNNs
 with BNNs in our algorithms to achieve better performances.
-%There are several possible future research directions for extending
-%this work, including: exploiting map data in cross-view learning,
-%replacing the CNN networks in our algorithms with Bayesian neural
-%networks (BNNs).
-Overall, we hope our work can provide new ways for
-geo-calibration and image feature learning.
+Overall, we hope our work can provide new ways for geo-calibration and
+image feature learning.

### 2018-10-24 chapters/fasthorizon/paper.tex
last change

@@
 
-In this chapter, we will develop a constraint function for
-camera pose. Since the camera roll and pitch angle can be derived from
+In this chapter, we develop a constraint function for the
+camera pose. Since the camera roll and pitch angles can be derived from
 the horizon line position, our algorithm focuses on detecting the

### 2018-12-06 dissertation.tex
add discussion section
disscussion
add vita to dissertation
put orcid in the front page
include acknowledgment

@@
 \usepackage{xspace}
-\usepackage{titlesec}
+%\usepackage{titlesec}
 \usepackage{enumitem}
@@
 \author{Menghua Zhai}
-%\title{Building a Probabilistic Model with Deep Neural Networks for Camera Geo-Calibration}
-%\title{Statistical Models for Camera Geo-Calibration}
+\orcid{0000-0001-5874-238X}
 \title{Deep Probabilistic Models for Camera Geo-Calibration}
@@
 
-%\begin{acknowledgments}
-	%Acknowledge people/things here
-%\end{acknowledgments}
+\begin{acknowledgments}
+  I would like to express the deepest appreciation to my advisor,
+Professor Nathan Jacobs, who not only financed my Ph.D. career, but
+also supported my research with his profound insight
+and knowledge. Over the years I have benefited from guidance,
+expertise, and patience. I have also learned a lot from his efficient
+work style and the way he attacks problems. I honestly fell lucky to
+have had the opportunity to work alongside him and I am proud of what
+we have accomplished together.
+
+I would like to take this opportunity to give my thanks to several
+individuals who helped me through the path:  Jinze Liu, who
+first got me enrolled to the graduate school; 
+Qiang Ye, Judy Goldsmith, and Andrew Klapper, for intriguing
+my desires for pursuing advanced knowledge. A huge appreciation to the
+other members of my advisory committee, Ruigang Yang and Ramakanth
+Kavuluru, for their invaluable feedback through my defense.
+
+I have had the privilege of working and collaborating with many
+individuals, including: Zachary Bessinger, Tawfiq Salem, Connor
+Greenwell, Ryan Baltenberger, Neil Moore, Samuel Schulter, and others.
+In the end, I would like to thank my friend and colleague, Scott
+Workman, with whom I worked closest and accomplished a great deal of
+research projects.
+\end{acknowledgments}
 
@@
 \tableofcontents\clearpage
-%\listoffigures\clearpage
-%\listoftables\clearpage
+\listoffigures\clearpage
+\listoftables\clearpage
 
@@
 
-%\inject{mcmc}
-%\inject{fasthorizon}
-%\inject{crosstransf}
-%\inject{whenwhere}
+\inject{mcmc}
+\inject{fasthorizon}
+\inject{whenwhere}
+\inject{crosstransf}
 
-%\inject{discussion}
+\inject{discussion}
 
@@
 
-%\inject{vita}
+\inject{vita}
 

### 2018-12-06 dissertation.tex
small change

@@
 Qiang Ye, Judy Goldsmith, and Andrew Klapper, for intriguing
-my desires for pursuing advanced knowledge. A huge appreciation to the
+my desire for higher-level knowledge. A huge appreciation to the
 other members of my advisory committee, Ruigang Yang and Ramakanth

### 2018-12-06 dissertation.tex
minor change

@@
 Qiang Ye, Judy Goldsmith, and Andrew Klapper, for intriguing
-my desire for higher-level knowledge. A huge appreciation to the
+my desire for higher-level knowledge. A huge appreciation to 
 other members of my advisory committee, Ruigang Yang and Ramakanth
-Kavuluru, for their invaluable feedback through my defense.
+Kavuluru, for their invaluable feedback during my defense.
 

### 2018-12-07 dissertation.tex
add bookmarks (can only view in chrome)

@@
             pdftitle={dissertation},
-            bookmarks=false,
+            bookmarks=true,
             bookmarksnumbered=true,
